### 2023-03-10 TeX/draft.tex
Init overleaf integration

\documentclass[11pt,reqno]{amsart}
% We ain't got no time for eq. nums. on the left

% Enable UTF-8 encodings for input, to enter é instead of \'{e}.
\usepackage[utf8]{inputenc}

\usepackage{amsmath,amsthm,amssymb}

% Presented to you by Technicolor, and the number 3
\usepackage{graphics}
\usepackage{hyperref}
\usepackage[usenames, dvipsnames]{xcolor}

% For full page usage, shockingly
%\usepackage{fullpage}

% Don't worry about starred environments. YOU are the star!
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}

% For ease in writing labels and references
%\usepackage{showkeys}
\usepackage[square,sort,comma,numbers]{natbib}

% For pretty hyperlinks
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
  linkcolor=darkblue,urlcolor=darkblue,
anchorcolor=darkblue,citecolor=darkblue}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}%[section]
\newtheorem*{theorem*}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem*{proposition*}{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem*{corollary*}{Corollary}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{question}[theorem]{Question}
\theoremstyle{definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}

%\numberwithin{equation}{section}

% Nongross real and imaginary parts
\renewcommand{\Im}{\operatorname{Im}}
\renewcommand{\Re}{\operatorname{Re}}

\newcommand{\davidnote}[1]{\marginpar{\footnotesize{\textcolor{Plum}{David: #1}}}}

% Don't have subsections appear in TOC
%\setcounter{tocdepth}{1}

\title{title}
\author{DLD}
\date{\today}
%% Grant Info
% \thanks{This work was supported by the Simons Collaboration in Arithmetic
% Geometry, Number Theory, and Computation via the Simons Foundation grant
% 546235.}

\begin{document}

\maketitle

Content

\vspace{20 mm}
\bibliographystyle{alpha}
\bibliography{bibliofile}

\end{document}

### 2023-03-10 TeX/author_info.tex
Better latex templating

\author[Doe]{Your Name Here}
\address{
  John Doe,
  Monsters University,
  Department of Mathematics,
  123 Main Street,
  Anywhere, CA
  United States of America
}
\email{\url{foobar@example.com}}
\thanks{JD is supported by the Imaginary Friend association}

\author[Keller]{Timo Keller}
\address{Timo Keller, Department of Mathematics, Lehrstuhl Computeralgebra, Universität Bayreuth, Universitäts\-straße 30, 95448 Bayreuth, Germany}
\curraddr{Leibniz Universität Hannover, Institut für Algebra, Zahlentheorie und Diskrete Mathematik, Welfengarten 1, 30167 Hannover, Germany}
\email{keller@math.uni-hannover.de}
\urladdr{\url{https://www.timo-keller.de}}

\author[Lowry-Duda]{David Lowry-Duda}
\address{%
  David Lowry-Duda, ICERM, 121 South Main Street, Box E, 11th Floor,
  Providence, RI, 02903
}
\email{\url{david@lowryduda.com}}
\urladdr{\url{https://davidlowryduda.com}}
\thanks{%
  DLD was supported by the Simons Collaboration in Arithmetic Geometry, Number
  Theory, and Computation via the Simons Foundation grant 546235.
}

### 2023-03-11 TeX/draft.tex
Better latex templating
Updates from Overleaf

@@
 % For full page usage, shockingly
-%\usepackage{fullpage}
+\usepackage{fullpage}
 
@@
 \renewcommand{\Re}{\operatorname{Re}}
+\newcommand{\Q}{\mathbb{Q}}
 
@@
 
-\title{title}
-\author{DLD}
+\title{Towards a Classification of Sporadic $j$-invariants}
+\input{author_info.tex}
 \date{\today}
-%% Grant Info
-% \thanks{This work was supported by the Simons Collaboration in Arithmetic
-% Geometry, Number Theory, and Computation via the Simons Foundation grant
-% 546235.}
 
 \begin{document}
-
+\begin{abstract}
+We develop an algorithm to test whether a non-CM elliptic curve $E/\Q$ gives rise to a sporadic point of any degree on any modular curve of the form $X_1(N)$.
+This builds on prior work of Zywina which gives a method for computing the image of the adelic Galois representation associated to $E$.
+Running this algorithm on all elliptic curves presetly in the LMFDB yields strong evidence for the fact that $E$ gives rise to a sporadic point if and only if $j(E)=-140625/8$ or $-9317$.
+    \end{abstract}
 \maketitle
 
-Content
+The modular curve $X_1(N)$ is an algebraic curve over $\Q$ whose non-cuspidal points parametrize elliptic curves with a distinguished point of order $N$.
+We are interested in studying \textbf{sporadic} points $x \in X_1(N)$, which are points for which there are only finitely many points on $X_1(N)$ of degree at most $\deg(x)$.
+Hence a non-cuspidal sporadic point corresponds to an elliptic curve with a point of order $N$ in ``usually low degree." Elliptic curves with complex multiplication (CM) provide many natural examples of sporadic points, as the extra endomorphisms of a CM elliptic curve give constraints on the size of the image of the associated Galois representation.
+Indeed, there exist sporadic CM points on $X_1(N)$ for all $N\geq 721$; see \cite[Theorem 8.2]{CGPS2022}.
+
+Non-CM sporadic points on $X_1(N)$ remain much more mysterious.
+One recent line of investigation has focused on the class of sporadic points associated to non-CM elliptic curves with $j$-invariant in $\Q$.
+To date, there are only two known examples of such curves, up to isomorphism over $\overline{\Q}$:
+\begin{itemize}
+\item The elliptic curve with $j$-invariant $-140625/8$ corresponds to points of degree 3 on $X_1(21)$.
+As there are only finitely many points of degree at most 3 on this modular curve, these are sporadic.
+This example was first discovered by Najman \cite{najman16}.
+In fact, this is the unique elliptic curve giving a sporadic point of degree at most 3 on \emph{any} modular curve of the form $X_1(N)$, as shown in recent work of Derickx, Etropolski, van Hoeij, Morrow, and Zureick-Brown \cite{DEvHMZB2021}.
+\item The elliptic curve with $j$-invariant $-9317$ gives a degree 6 point on $X_1(37)$, as in work of van Hoeij \cite{vanHoeij}.
+Since this degree is less than half the $\Q$-gonality of $X_1(37)$, as computed in \cite{DerickxVanHoeij2014}, the point is necessarily sporadic by work of Frey \cite{frey}.
+\end{itemize}
+
+We say these are \textbf{sporadic $j$-invariants} since they are the image of a sporadic point on $X_1(N)$.
+We have good reason to believe that the collection of all sporadic $j$-invariants in $\Q$ is finite.
+\begin{theorem}[Bourdon, Ejder, Liu, Odumodu, Viray \cite{BELOV}]
+Suppose there exists a constant $C$ such that the mod $\ell$ Galois representation of any non-CM elliptic curve over $\Q$ is surjective for primes $\ell>C$.
+Then there are only finitely many sporadic $j$-invariants in $\Q$.
+\end{theorem}
+
+\noindent The assumption about Galois representations stated in Theorem 1 was originally asked as a question by Serre \cite{serre72}, and it has now been formally conjectured by both Sutherland \cite{sutherland} and Zywina \cite{ZywinaImages}.
+It is even suspected that $C=37$.
+Theorem 1 is known unconditionally for points of odd degree \cite{OddDeg}: indeed, $j=-140625/8$ is the only non-CM $j$-invariant in $\Q$ giving a sporadic point of odd degree on $X_1(N)$, even as $N$ ranges over all positive integers.
+
+In \cite{BELOV}, they ask whether one can explicitly determine the set of sporadic $j$-invariants in $\Q$, and this is the motivation for the present work.
+In particular, we conjecture that the two non-CM sporadic $j$-invariants identified above are in fact the \emph{only} sporadic $j$-invariants in $\Q$ associated to non-CM elliptic curves.
+
+\begin{conjecture}
+If $x\in X_1(N)$ is a sporadic point with $j(x) \in \Q$, then $j(x)=-140625/8$ or $-9317$ or is one of the 13 CM $j$-invariants in $\Q$. 
+\end{conjecture}
+
+\noindent Since any CM elliptic curve is known to produce sproadic points on infinitely many modular curves of the form $X_1(N)$, it follows conversely that every $j$-invariant in this set is sporadic.
+
+The basis for this conjecture is the following result.
+
+\begin{theorem}
+Let $x=[E,P]\in X_1(N)$ be a non-CM sporadic point with $j(E) \in \Q$. Fix an equation of $E/\Q$, and let $N_E$ denote its conductor. Suppose
+\begin{itemize}
+\item$N_E \leq 500,000$,
+\item $N_E$ is only divisible prime primes $p \leq 7$, or
+\item $N_E=p \leq 200,000,000$ for some prime number $p$.
+\end{itemize}
+Then $j(E) =-140625/8$ or $-9317$.
+\end{theorem}
+
+Since both known examples of sporadic points on $X_1(N)$ associated to non-CM rational $j$-invariants lie above exceptional rational points on $X_0(N)$ -- that is, they correspond to rational points in cases where the set of all such rational points is finite -- is natural to ask whether this construction might yield other examples of sporadic points.
+Our work shows that the answer is no.
+\begin{corollary}
+Let $X_0(N)$ have genus greater than 0, and let $E$ be a non-CM elliptic curve corresponding to a rational point on $X_0(N)$.
+If there exists a sporadic point $x \in X_1(N')$ with $j(x)=j(E)$, then $j(E) =-140625/8$ or $-9317$.
+\end{corollary}
 
@@
 \bibliographystyle{alpha}
-\bibliography{bibliofile}
+\bibliography{bibfile}
 

### 2023-03-13 TeX/author_info.tex
Updates from Overleaf

@@
 
+\author[Bourdon]{Abbey Bourdon}
+\address{
+  Abbey Bourdon,
+  Wake Forest University,
+  Department of Mathematics, 127 Manchester Hall, PO Box 7388, Winston-Salem, NC 27109
+}
+\email{\url{bourdoam@wfu.edu}}
+\thanks{AB is supported by NSF Grant DMS-2145270.}
+
 \author[Keller]{Timo Keller}
-\address{Timo Keller, Department of Mathematics, Lehrstuhl Computeralgebra, Universität Bayreuth, Universitäts\-straße 30, 95448 Bayreuth, Germany}
-\curraddr{Leibniz Universität Hannover, Institut für Algebra, Zahlentheorie und Diskrete Mathematik, Welfengarten 1, 30167 Hannover, Germany}
+\address{Timo Keller, Leibniz Universität Hannover, Institut für Algebra, Zahlentheorie und Diskrete Mathematik, Welfengarten 1, 30167 Hannover, Germany}
 \email{keller@math.uni-hannover.de}

### 2023-03-13 TeX/draft.tex
Updates from Overleaf

@@
 \newtheorem{exercise}[theorem]{Exercise}
+\newtheorem{algorithm}[theorem]{Algorithm}
 
 %\numberwithin{equation}{section}
+
+\renewcommand{\epsilon}{\varepsilon}
+\renewcommand{\phi}{\varphi}
+\renewcommand{\theta}{\vartheta}
+
+\renewcommand\labelenumi{(\theenumi)}
+\renewcommand{\theenumi}{\roman{enumi}}
+
+%%% Basic Macro%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\def\ol#1{\overline{#1}}% 		overline
+\def\wh#1{\widehat{#1}}% 	wide hat
+\def\wt#1{\widetilde{#1}}% 	wide tilde
+\def\ul#1{\underline{#1}}% 	underline
+\def\smcompactification#1{\ol{#1}}% 	wide tilde
+%%% Define \Alphabet&\endpiece------------------------------------------------------------------------
+\def\Alphabet{A,B,C,D,E,F,G,H,I,J,K,L,M,N,O,P,Q,R,S,T,U,V,W,X,Y,Z}%  Capitalized Alphabet
+\def\alphabet{a,b,c,d,e,f,g,h,i,j,k,l,m,n,o,p,q,r,s,t,u,v,w,x,y,z}%	lowercase alphabet
+\def\endpiece{xxx}%									marks end of list
+%%% Define \makeAlphabet------------------------------------------------------------------------
+\def\makeAlphabet[#1]{\expandafter\makeA#1,xxx,}%		Ex. \makeAlphabet[A,B]
+\def\makealphabet[#1]{\expandafter\makea#1,xxx,}%		Ex. \makealphabet[c,d]
+\def\makeA#1,{\def\temp{#1}\ifx\temp\endpiece\else%
+	\mkbb{#1}\mkfrak{#1}\mkbf{#1}\mkcal{#1}\mkscr{#1}\mkbs{#1}\expandafter\makeA\fi}%
+\def\makea#1,{\def\temp{#1}\ifx\temp\endpiece\else\mkfrak{#1}\mkbf{#1}\mkbs{#1}\expandafter\makea\fi}%
+\def\mkbb#1{\expandafter\def\csname bb#1\endcsname{\mathbb{#1}}}%      Define bb
+\def\mkfrak#1{\expandafter\def\csname fr#1\endcsname{\mathfrak{#1}}}%    Define frak
+\def\mkbf#1{\expandafter\def\csname b#1\endcsname{\mathbf{#1}}}%           Define bold letters
+\def\mkcal#1{\expandafter\def\csname c#1\endcsname{\mathcal{#1}}}%       Define calligraphy
+\def\mkscr#1{\expandafter\def\csname s#1\endcsname{\mathscr{#1}}}%       Define script
+\def\mkbs#1{\expandafter\def\csname bs#1\endcsname{{\boldsymbol{#1}}}}%       Define bold symbol
+%%% Define \makeop-------------------------------------------------------------------------------------------------------
+\def\makeop[#1]{\xmakeop#1,xxx,}%					Ex. \makeop[Hom,Spec]
+\def\mkop#1{\expandafter\def\csname #1\endcsname{{\mathrm{#1}}}} %
+\def\xmakeop#1,{\def\temp{#1}\ifx\temp\endpiece\else\mkop{#1}\expandafter\xmakeop\fi}%
+\def\makeup[#1]{\xmakeup#1,xxx,}%					Ex. \makeop[Hom,Spec]
+\def\mkup#1{\expandafter\def\csname #1\endcsname{{\mathrm{#1}\,}}} %
+\def\xmakeup#1,{\def\temp{#1}\ifx\temp\endpiece\else\mkup{#1}\expandafter\xmakeup\fi}%
+%%% Initialize------------------------------------------------------------------------------------------------------------------
+% Define Alphabets.  Alphabets stored in \Alphabet
+\makeAlphabet[\Alphabet]%				Define bb, frak, bf, cal for Capitalized Alphabet
+\makealphabet[\alphabet]%  				Define frak and bf for uncapitalized alphabet
+% Define Operators.  Separate Items by using comma.
+\makeop[Hom,Aut,End,Mor,SL,GL,H,ord,Irr,Ell,Gal,Cl,Pic,NS,Gal,d,Re,Im,res,Symb,Ev,Char,Ram,SU]
+% 		Homs
+\makeup[Spec,Proj,id,dR,new,old,AJ,tr,dim,ker,im,coker]
 
@@
 \renewcommand{\Re}{\operatorname{Re}}
-\newcommand{\Q}{\mathbb{Q}}
+\newcommand{\Q}{\bQ}
+\newcommand{\Z}{\bZ}
 
@@
 
+\section{Proving that a point is not sporadic}
+
+\begin{algorithm}
+\textbf{Input:} A non-CM $j$-invariant $j = j(E) \in \Q$.
+
+\textbf{Output:} \textsc{False} if $j$ is not a sporadic $j$-invariant.
+
+\begin{enumerate}
+    \item Compute the adelic image of $E/\Q$ as a subgroup of $\GL_2(\hat{\Z})$ using Zywina's algorithm. Represent the output as some \emph{level} $M$ together with a subgroup $G$ of $\GL_2(\Z/M\Z)$.
+\end{enumerate}
+\end{algorithm}
+
 \vspace{20 mm}

### 2023-03-15 TeX/draft.tex
Updates from Overleaf

@@
 \newcommand{\Z}{\bZ}
-
+\newcommand{\filip}[1]{{\color{cyan} \textsf{$\sun\sun\sun$ Filip: [#1]}}}
 \newcommand{\davidnote}[1]{\marginpar{\footnotesize{\textcolor{Plum}{David: #1}}}}
@@
 \begin{itemize}
-\item$N_E \leq 500,000$,
+\item$N_E \leq 500{,}000$,
 \item $N_E$ is only divisible prime primes $p \leq 7$, or
-\item $N_E=p \leq 200,000,000$ for some prime number $p$.
+\item $N_E=p \leq 200{,}000{,}000$ for some prime number $p$.
 \end{itemize}
@@
 \begin{enumerate}
-    \item Compute the adelic image of $E/\Q$ as a subgroup of $\GL_2(\hat{\Z})$ using Zywina's algorithm. Represent the output as some \emph{level} $M$ together with a subgroup $G$ of $\GL_2(\Z/M\Z)$.
+    \item Compute the adelic image $G$ of $E/\Q$ as a subgroup of $\GL_2(\hat{\Z})$ using Zywina's algorithm.
+Represent the output as some \emph{level} $M$ together with a subgroup $G$ of $\GL_2(\Z/M\Z)$.
+
+    \item Reduce level.
+
+    \item For all $12 < b \mid M$ compute the minimum degree of the field of definition of a point with respect to $G \mod b$, the image of $G$ in $\GL_2(\Z/b\Z)$.
+(For that, compute the orbits of $\langle G, -G \rangle \mod b$ on $\bP^1(\Z/b\Z)$.
+Sort the orbits by size.
+Return ) \filip{We need to look at the orbits of $\langle G, -G \rangle \mod b$ on $(\Z/b\Z)^2$, not $\bP^1(\Z/b\Z)$.
+If we consider the action on $\bP^1(\Z/b\Z)$, the orbits might be too small and hence the degree we get.
+Furthermore, it is necessary to consider only the elements of $(\Z/b\Z)^2$ of order $b$.}
 \end{enumerate}
 \end{algorithm}
+
+(In the \texttt{Magma} implementation, we have to be careful that \texttt{Magma} uses right actions, but in our mathematics, we use left action.
+We therefore use the transposes of the matrices in $\GL_2(\Z/M\Z)$.)
 

### 2023-03-15 deleteduplicates.py
upload data from lmfdb for isolated points

@@ -1,0 +1,23 @@
+#code to get isolated_refined.txt from isolated.txt
+
+file = open('isolated.txt', 'r')
+data = file.readlines()
+from collections import defaultdict
+dict = defaultdict(list)
+for line in data:
+    jinv, ainv = line.split('","')
+    a,b =jinv[1:].split(',')
+    j = (eval(a[1:]),eval(b[:-1]))
+    ainv = ainv[:-2].replace('{','[')
+    ainv = ainv.replace('}', ']')
+    ainvs = eval(ainv)
+    dict[j].append(ainv)
+file.close()
+
+fileout = open('isolated_refined.txt', 'w')
+for j in dict.keys():
+    fileout.write(str(j))
+    fileout.write(',')
+    fileout.write(str(dict[j][0]))
+    fileout.write('\n')
+fileout.close()

### 2023-03-16 isolated_points/NotIsolated.m
magma file containing code to check not isolated points

@@ -1,0 +1,205 @@
+AttachSpec("~/ModularCurves/equations/equations.spec");//change if you have 
+                                                       //different path to the spec file
+path := OpenImageContext("~/ModularCurves/equations/OpenImage/data-files"); //change if you have 
+                                                                            //different path to 
+                                                                            //data-files.
+
+
+/*
+PrimitiveVectors:=function(m)
+        V:=RSpace(Integers(m),2);
+        W:=[V![d,a]:d in Divisors(m), a in [1..m]|GCD(a,d) eq 1];
+        return W;
+end function;
+*/
+
+//MinDegreeOfPoint:=function(G)
+        //m:=Modulus(BaseRing(G));
+        //H:=sub<GL(2,Integers(m))|G,-G!1>;
+        //W:=PrimitiveVectors(m);
+        //c:=Min({Integers()!(#H/(2*#Stabilizer(H,v))):v in W});
+        //return c;
+//end function;
+
+
+/*
+NotSporadic:=procedure(a);
+	E:=EllipticCurve(a);
+	G,n,S:=FindOpenImage(path, E);
+	G0:=ReducedLevel(G);
+	G0t := sub<GL(2,Integers(#BaseRing(G0))) | [Transpose(g):g in Generators(G0)]>;
+	k:=#BaseRing(G0t);
+	for b in Divisors(k) do
+	if b gt 12 then
+	   bool:=MinDegreeOfPoint(ChangeRing(G0t,Integers(b))) ge (Genus(Gamma1(b))+1); 
+       print bool,b,MinDegreeOfPoint(ChangeRing(G0t,Integers(b))); 
+    end if;
+end for;
+end procedure;
+*/
+
+/*
+function form_p1_data(M);
+    grid := Matrix(M,M,[<1,1,0>]);
+    list:=[];
+    counter:=0;
+    for r in [1..M-1] do
+        for c in [0..M-1] do
+            if (Gcd(Gcd(r,c),M) eq 1) then
+                if grid[r+1,c+1] eq 0 then
+                    counter:=counter + 1;
+                    grid[r+1,c+1]:=counter;
+                    list := list cat [[r,c]];
+                    for a in [1..M] do
+                        if Gcd(a,M) eq 1 then
+                            rr := (r * a) mod M;
+                            cc := (c * a) mod M;
+                            grid[rr+1,cc+1]:=grid[r+1,c+1];
+                        end if;
+                    end for;
+                end if;
+            else
[…]

### 2023-03-16 isolated_points/arrangement.m
file contains the code to arrange the potentially bad curves data in nicer forms for analysis.

@@ -1,0 +1,99 @@
+
+
+
+
+
+load "PotentiallyBadCurves.m";
+pos_bad_levels_single := {};
+for d in pot_false_data do
+    if #d[4] eq 1 then Include(~pos_bad_levels_single, Random(d[4])); end if;
+end for;
+
+pos_bad_curves_single := [**];
+for d in pos_bad_levels_single do
+   bad_curves_d :={}; 
+    for c in pot_false_data do 
+        if c[4] eq {d} then Include(~bad_curves_d, <c[1],c[2]>); end if;
+    end for;
+            Append(~pos_bad_curves_single, <bad_curves_d, d>);
+end for;
+
+bad_more_places := {};
+for d in pot_false_data do 
+    if #d[4] ne 1 then Include(~bad_more_places, <d[1], d[2], d[4]>);
+    end if;
+end for;
+
+IsFromBelow := function(a, b)
+    if b[1] gt  a[1] then c := a; a:= b; b:=c; end if;
+    if IsDivisibleBy(a[1],b[1]) then
+			c:=a[1] div b[1];
+			
+			deg:=c^2*&*[Rationals() | 1-1/p^2 : p in PrimeDivisors(a[1]) | p
+                notin PrimeDivisors(b[1])];
+			if deg eq a[2] div b[2] then return true; else return false; end if;
+		end if;
+    return false;
+end function;
+
+find_min := function(a)
+    min := 1000000;
+    min_deg := 0;
+    for d in a do 
+        if d[1] le min then min:= d[1]; min_deg := d[2]; end if;
+    end for;
+        return <min, min_deg>;
+end function;
+
+
+ 
+
+arrange_bad_more_places := function(a)
+    bad_more_places_dummy :=[**];
+   for d in a do 
+      r := d[3];
+      dif := [**]; 
+     while #r ne 0 do 
+        r_temp :=r;
+        arrising_from_min := {};
+        min := find_min(r);
+        for x in r_temp do 
+           if IsFromBelow(x, min) then Include(~arrising_from_min,x); 
+              Exclude(~r, x); 
+           end if;
+        end for; 
+        Append(~dif, arrising_from_min);
+     end while;
+     Append(~bad_more_places_dummy, [*d[1], d[2], dif*]);
+   end for;
+       return bad_more_places_dummy;
+end function;
+         
+bad_more_places := arrange_bad_more_places(bad_more_places);
+
+pos_bad_levels_mult:={};
+
[…]

### 2023-03-17 isolated_points/NotIsolated.m
rearrangements and updates to parallelize big computation

@@ -1,6 +1,6 @@
-AttachSpec("~/ModularCurves/equations/equations.spec");//change if you have 
+AttachSpec("/usr/people/hashimot/ModularCurves/equations/equations.spec");//change if you have 
                                                        //different path to the spec file
-path := OpenImageContext("~/ModularCurves/equations/OpenImage/data-files"); //change if you have 
+path := OpenImageContext("/usr/people/hashimot/ModularCurves/equations/OpenImage/data-files"); //change if you have 
                                                                             //different path to 
                                                                             //data-files.
 
@@ -195,7 +195,7 @@ if assigned seq then
     SetColumns(0);
     SetAutoColumns(false);
     seq := eval seq;
-    inputs := Split(Read("Curves.txt"), "\n");
+    inputs := Split(Read("isolated_refined.txt"), "\n");
     input := eval inputs[seq];
     output := NotIsolated(input);
     output := [*input*] cat output;

### 2023-03-17 isolated_points/NotIsolated.m
fix not isolated code to work with input

@@ -136,7 +136,7 @@ end function;
 
 
 //main function to check if a j invariant is sporadic.
-NotIsolated:=function(a);
+NotIsolated:=function(a, j);
 	E:=EllipticCurve(a);
 	G,n,S:=FindOpenImage(path, E);
 	G0:=ReducedLevel(G);
@@ -183,9 +183,9 @@ end for;
     //bad but not in remove can be handled using gonality arguments.
     if bad ne remove then 
         supbad := bad diff remove;
-        return [*jInvariant(E), a, false, supbad*];
+        return [*j, a, false, supbad*]; //return j-invariant we already have
     end if;
-    return [*jInvariant(E), a, true*];    
+    return [*j, a, true*];    
 end function;
 
 
@@ -196,9 +196,12 @@ if assigned seq then
     SetAutoColumns(false);
     seq := eval seq;
     inputs := Split(Read("isolated_refined.txt"), "\n");
-    input := eval inputs[seq];
-    output := NotIsolated(input);
-    output := [*input*] cat output;
+    input := inputs[seq];
+    i := Index(s, ")");
+    jinv := s[1..18]; //construct j-invariant
+    ainv := eval  s[i+2 .. #s];
+    output := NotIsolated(ainv, jinv);
+    output := [*ainv*] cat output;
     print Join([Sprint(elt) : elt in output], ":");
     exit;
 end if;

### 2023-03-17 isolated_points/NotIsolated.m
fixed typos

@@ -197,9 +197,9 @@ if assigned seq then
     seq := eval seq;
     inputs := Split(Read("isolated_refined.txt"), "\n");
     input := inputs[seq];
-    i := Index(s, ")");
-    jinv := s[1..18]; //construct j-invariant
-    ainv := eval  s[i+2 .. #s];
+    i := Index(input, ")");
+    jinv := input[1..18]; //construct j-invariant
+    ainv := eval  input[i+2 .. #input];
     output := NotIsolated(ainv, jinv);
     output := [*ainv*] cat output;
     print Join([Sprint(elt) : elt in output], ":");

### 2023-03-18 isolated_points/NotIsolated.m
typo

@@ -198,7 +198,7 @@ if assigned seq then
     inputs := Split(Read("isolated_refined.txt"), "\n");
     input := inputs[seq];
     i := Index(input, ")");
-    jinv := input[1..18]; //construct j-invariant
+    jinv := input[1..i]; //construct j-invariant
     ainv := eval  input[i+2 .. #input];
     output := NotIsolated(ainv, jinv);
     output := [*ainv*] cat output;

### 2023-03-18 isolated_points/NotIsolated.m
delete redundant data

@@ -201,7 +201,6 @@ if assigned seq then
     jinv := input[1..i]; //construct j-invariant
     ainv := eval  input[i+2 .. #input];
     output := NotIsolated(ainv, jinv);
-    output := [*ainv*] cat output;
     print Join([Sprint(elt) : elt in output], ":");
     exit;
 end if;

### 2023-03-19 isolated_points/find_pot_isolated.py
python processing

@@ -1,0 +1,18 @@
+#code to find the potentially isolated points from all the data
+
+data_files = ['1to100000.out', '100001to200000.out', '200001to300000.out', '300001to400000.out', '400001to500000.out', '500001to534299.out']
+
+for name in data_files:
+    file = open(name, 'r')
+    data = file.readlines()
+    bad_curves = []
+    for line in data:
+        jinv, ainv, b = line.split(':')
+        if b.strip() != 'true':
+            bad_curves.append(line)
+    file.close()
+
+fileout = open('potentially_isolated.txt', 'w')
+for curve in bad_curves:
+    fileout.write(curve)
+fileout.close()

### 2023-03-20 isolated_points/deleteduplicates.py
Split isolated.txt into two
This is because of overleaf, which refuses to sync (it turns out) when
there is a file larger than 50mb. I also updated the refinement script
so that it still runs with this split.

@@ -1,23 +1,37 @@
-#code to get isolated_refined.txt from isolated.txt
-
-file = open('isolated.txt', 'r')
-data = file.readlines()
+# code to get isolated_refined.txt from isolated1.txt and isolated2
 from collections import defaultdict
+
+
+with open('isolated1.txt', 'r', encoding="utf8") as file1:
+    data1 = file1.readlines()
+with open('isolated2.txt', 'r', encoding="utf8") as file2:
+    data2 = file2.readlines()
+
+data = data1 + data2
+
+# remove comments at start of file
+data = [datum for datum in data if datum[0] != "#"]
+ndata = len(data)
+
+
+print("Parsing isolated1 and isolated2 files...")
 dict = defaultdict(list)
-for line in data:
+for idx, line in enumerate(data):
     jinv, ainv = line.split('","')
-    a,b =jinv[1:].split(',')
-    j = (eval(a[1:]),eval(b[:-1]))
-    ainv = ainv[:-2].replace('{','[')
+    a, b = jinv[1:].split(',')
+    j = (eval(a[1:]), eval(b[:-1]))
+    ainv = ainv[:-2].replace('{', '[')
     ainv = ainv.replace('}', ']')
     ainvs = eval(ainv)
     dict[j].append(ainv)
-file.close()
+    print(f"\r{idx:10}/{ndata}", end="")
+print("Done.")
 
-fileout = open('isolated_refined.txt', 'w')
-for j in dict.keys():
-    fileout.write(str(j))
-    fileout.write(',')
-    fileout.write(str(dict[j][0]))
-    fileout.write('\n')
-fileout.close()
+
+with open("isolated_refined.txt", 'w', encoding="utf8") as fileout:
+    for j in dict.keys():
+        fileout.write(str(j))
+        fileout.write(',')
+        fileout.write(str(dict[j][0]))
+        fileout.write('\n')
+print("Refined output written to isolated_refined.txt")

### 2023-03-20 isolated_points/find_pot_isolated.py
Don't write empty potentially_isolated file.

@@ -12,7 +12,10 @@ for name in data_files:
             bad_curves.append(line)
     file.close()
 
-fileout = open('potentially_isolated.txt', 'w')
-for curve in bad_curves:
-    fileout.write(curve)
-fileout.close()
+if bad_curves:
+    fileout = open('potentially_isolated.txt', 'w')
+    for curve in bad_curves:
+        fileout.write(curve)
+    fileout.close()
+else:
+    print("No potentially isolated curves were found.")

### 2023-03-20 TeX/author_info.tex
Updates from Overleaf

@@
 
+\author[Hashimoto]{Sachi Hashimoto}
+\address{%
+  Sachi Hashimoto,
+  Max Planck Institut für Mathematik in den Naturwissenschaften,
+  Inselstraße 22,
+  04103 Leipzig
+}
+\email{\url{sachi.hashimoto@mis.mpi.de}}
+\urladdr{\url{sachihashimoto.github.io/}}
+
 \author[Keller]{Timo Keller}
@@
 }
+
+\author[Shukla]{Himanshu Shukla}
+\address{Himanshu Shukla, Mathematisches Institut, Uiversit\"{a}t Bayreuth, Universit\"{a}tstrasse 30, 95444 Bayreuth, Germany}
+\email{Himanshu.Shukla@uni-bayreuth.de}
+\urladdr{\url{https://www.mathe2.uni-bayreuth.de/hishukla/}}
+\thanks{HS is supported by the DFG-grant STO 299/17-1}

### 2023-03-20 TeX/draft.tex

@@
 
-\noindent Since any CM elliptic curve is known to produce sproadic points on infinitely many modular curves of the form $X_1(N)$, it follows conversely that every $j$-invariant in this set is sporadic.
+\noindent Since any CM elliptic curve is known to produce sporadic points on infinitely many modular curves of the form $X_1(N)$, it follows conversely that every $j$-invariant in this set is sporadic.
 
@@
 \begin{theorem}
-Let $x=[E,P]\in X_1(N)$ be a non-CM sporadic point with $j(E) \in \Q$. Fix an equation of $E/\Q$, and let $N_E$ denote its conductor. Suppose
+Let $x=[E,P]\in X_1(N)$ be a non-CM sporadic point with $j(E) \in \Q$.
+Fix an equation for $E/\Q$ and let $N_E$ denote its conductor.
+Suppose that one of the following holds:
 \begin{itemize}
     \item$N_E \leq 500{,}000$,
-\item $N_E$ is only divisible prime primes $p \leq 7$, or
+    \item $N_E$ is only divisible by primes $p \leq 7$, or
     \item $N_E=p \leq 200{,}000{,}000$ for some prime number $p$.
@@
     \item For all $12 < b \mid M$ compute the minimum degree of the field of definition of a point with respect to $G \mod b$, the image of $G$ in $\GL_2(\Z/b\Z)$.
-(For that, compute the orbits of $\langle G, -G \rangle \mod b$ on $\bP^1(\Z/b\Z)$.
+(For that, compute the orbits of $\langle G, -G \rangle \mod b$ on the elements of $(\Z/b\Z)^2$ of order $b$.
 Sort the orbits by size.
-Return ) \filip{We need to look at the orbits of $\langle G, -G \rangle \mod b$ on $(\Z/b\Z)^2$, not $\bP^1(\Z/b\Z)$.
+Return )
+    %\filip{We need to look at the orbits of $\langle G, -G \rangle \mod b$ on $(\Z/b\Z)^2$, not $\bP^1(\Z/b\Z)$.
 If we consider the action on $\bP^1(\Z/b\Z)$, the orbits might be too small and hence the degree we get.

### 2023-03-29 isolated_points/NotIsolated.m
add all potentially isolated degrees when min degree < g+1, fix whitespace

@@ -24,14 +24,14 @@ end function;
 
 /*
 NotSporadic:=procedure(a);
-	E:=EllipticCurve(a);
-	G,n,S:=FindOpenImage(path, E);
-	G0:=ReducedLevel(G);
-	G0t := sub<GL(2,Integers(#BaseRing(G0))) | [Transpose(g):g in Generators(G0)]>;
-	k:=#BaseRing(G0t);
-	for b in Divisors(k) do
-	if b gt 12 then
-	   bool:=MinDegreeOfPoint(ChangeRing(G0t,Integers(b))) ge (Genus(Gamma1(b))+1); 
+    E:=EllipticCurve(a);
+    G,n,S:=FindOpenImage(path, E);
+    G0:=ReducedLevel(G);
+    G0t := sub<GL(2,Integers(#BaseRing(G0))) | [Transpose(g):g in Generators(G0)]>;
+    k:=#BaseRing(G0t);
+    for b in Divisors(k) do
+    if b gt 12 then
+       bool:=MinDegreeOfPoint(ChangeRing(G0t,Integers(b))) ge (Genus(Gamma1(b))+1); 
        print bool,b,MinDegreeOfPoint(ChangeRing(G0t,Integers(b))); 
     end if;
 end for;
@@ -96,22 +96,22 @@ end function;
 
 //Level reduction from the output of Zywina's algorithm
 ReducedLevel:=function(G)
-        m:=Modulus(BaseRing(G));
-        NS:=Set(NonSurjectivePrimes(G));
-        sE:={2,3} join NS;
-        m0:=&*[p^Valuation(m,p):p in sE];
-        G:=ChangeRing(G,Integers(m0));
-        for p in PrimeFactors(m0) do
-                while Valuation(m0,p) gt 1 and #G/#ChangeRing(G,Integers(m0 div p)) eq p^4 do
-                        m0:=m0 div p;
-                        G:=ChangeRing(G,Integers(m0));
-                end while;
-                if not p in NS and Valuation(m0,p) eq 1 and #G/#ChangeRing(G,Integers(m0 div p)) eq #GL(2,GF(p)) then
-                        m0:=m0 div p;
-                        G:=ChangeRing(G,Integers(m0));
-                end if;
-        end for;
-        return G,m0;
+    m:=Modulus(BaseRing(G));
+    NS:=Set(NonSurjectivePrimes(G));
+    sE:={2,3} join NS; 
[…]

### 2023-03-29 TeX/notes/meeting_notes_29Mar2023.tex
Meeting notes

\documentclass[11pt,reqno]{amsart}
% We ain't got no time for eq. nums. on the left

% Enable UTF-8 encodings for input, to enter é instead of \'{e}.
\usepackage[utf8]{inputenc}

\usepackage{amsmath,amsthm,amssymb}

% Presented to you by Technicolor, and the number 3
\usepackage{graphics}
\usepackage{hyperref}
\usepackage[usenames, dvipsnames]{xcolor}

% For full page usage, shockingly
\usepackage{fullpage}

% Don't worry about starred environments. YOU are the star!
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}

% For ease in writing labels and references
%\usepackage{showkeys}
\usepackage[square,sort,comma,numbers]{natbib}

% For pretty hyperlinks
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
  linkcolor=darkblue,urlcolor=darkblue,
anchorcolor=darkblue,citecolor=darkblue}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}%[section]
\newtheorem*{theorem*}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem*{proposition*}{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem*{corollary*}{Corollary}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{question}[theorem]{Question}
\theoremstyle{definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}

%\numberwithin{equation}{section}

% Nongross real and imaginary parts
\renewcommand{\Im}{\operatorname{Im}}
\renewcommand{\Re}{\operatorname{Re}}
\DeclareMathOperator{\SL}{SL}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator*{\Res}{Res}

\newcommand{\DLD}[1]{\textcolor{Plum}{DLD:\@ #1}}

\usepackage{minted}
\usemintedstyle{lovelace}
\definecolor{mintbf}{gray}{0.95}
\setminted{bgcolor=mintbf}

% Don't have subsections appear in TOC
%\setcounter{tocdepth}{1}

% This uses a hacky but reasonable parser that is not actually public
% \renewcommand{\MintedPygmentize}{./magma.py}

\title{Meeting notes}
\author{DLD}
\date{\today}

\begin{document}

\maketitle

We (Abbey, Travis, David, Sachi, and Himanshu) had a meeting
from today (29 March 2023) where we talked about
\texttt{NotIsolated.m}.
I annotated our code with notes from this meeting, which I show
here.

\vspace*{0.2cm}
\begin{quote}
  Pseudocode is the sort of code that compiles on a human, not on a computer.

  --- Travis
\end{quote}

This is all a description of \texttt{NotIsolated.m}. Note that this does
not include Filip's more recent enhancements --- that remains to be explained.

\section{\texttt{NotIsolated} function}\label{sec:notisolated}

The main function is \texttt{NotIsolated}, which is how we frame our code
examination.

\begin{minted}[mathescape, linenos, samepage]{c}
/* First half of NotIsolated function, which determines if j
 * can't give isolated points. */
NotIsolated:=function(a, j);             // #1
    E:=EllipticCurve(a);
    G,n,S:=FindOpenImage(path, E);       // #2
    G0:=ReducedLevel(G);                 // #3 (Things to be proved!)
    G0t := sub<
      GL(2,Integers(#BaseRing(G0))) | [Transpose(g):g in Generators(G0)]
    >;                                   // #4
    k:=#BaseRing(G0t);
    good:=[];                            // "not isolated"
    bad:=[];                             // "potentially isolated"
    for b in Divisors(k) do
        if b gt 12 then                  // #5
            ww:=MinDegreeOfPoint(ChangeRing(G0t,Integers(b)));
                                         // #6
            // if the min degree >= g+1 then the dimension of the Reimann-Roch
            // space associated to the point of min degree is at least 2 hence it
            // is not sporadic.
            if  ww ge (Genus(Gamma1(b))+1) then
                Append(~good,<b, ww>);   // #7
            else
                // otherwise we need to check if gonality/degree reduction
                // arguments can be used
                Append(~bad,<b, ww>);
            end if;
        end if;
    end for;
\end{minted}

Along the side, I've indicated several annotation points. We address these in
turn. The numbers of each point in the following list align with an annotation
point in the code above.

\begin{enumerate}
  \item The function \texttt{NotIsolated} takes the coefficients \texttt{a =
  \{a\_1, \ldots, a\_6\}} of the Weierstrass equation of an elliptic curve and a
  $j$-invariant \texttt{j}. Ultimately, this function will try to show that $j$
  doesn't give an isolated point, and will either report that it was successful
  --- or that it couldn't show that $j$ doesn't give isolated points.

  Note the double negatives here. The algorithm confirms that an elliptic curve
  $E$ with $j$-invariant $j(E)$ \emph{doesn't} give sporadic points, or fails
  and gives partial information.

  \item \texttt{FindOpenImage} is Zywina's code. It returns three things: the
  image \texttt{G}, the index \texttt{n} of \texttt{G} in $\GL(2, \widehat{Z})$,
  and the intersection \texttt{S} of \texttt{G} with $\SL(2, \widehat{Z})$.

  \item\label{item:reduced_level_lemma} \texttt{ReducedLevel} is a function we
  define. There are many things to prove about it. I defer the individual
  description until \S\ref{sec:reducedlevel}. But the content of this line is
  the following:

  Zywina's code identifies an adelic level of the image of $G$. But to
  determine if a point is isolated, we don't need to consider the entire level.
  We can reduce the level to be more manageable. We (need to) prove that we can
  do this in Lemma~\ref{lemma:reduced_level} in \S\ref{sec:reducedlevel}.

  \item Note the transpose in this line! This confused us before. But this is
  because Magma things of vectors as row vectors, and thus matrices naturally
  act on the right.

  \item\label{item:b_geq_12} For each $b$, we assert that it is sufficient to
  consider only $b > 12$. We (need to) prove that this is sufficient in
  Lemma~\ref{lemma:b_geq_12}.
\end{enumerate}

% This Lemma corresponds to item~\ref{item:b_geq_12}.

\begin{lemma}\label{lemma:b_geq_12}
  (Roughly, we can restrict to $b > 12$).
\end{lemma}

\begin{enumerate}\setcounter{enumi}{5}
  \item\label{item:min_degree} \texttt{MinDegreeOfPoint} is a function we
  define. It returns the minimum degree of the field of definition of a point.
  We calculate this in a nice way, but I defer the individual description until
  \S\ref{sec:mindegreeofpoint}.

  \item\label{item:min_deg_genus} This is very simple, but we need a citation for the claim that if
  $\mathrm{mindeg}(b) \geq \mathrm{genus}(\Gamma_1(b)) + 1$, then the point is
  not isolated. We call this Lemma~\ref{lemma:min_deg_genus}.
\end{enumerate}

% This Lemma corresponds to item~\ref{item:min_deg_genus}.

\begin{lemma}\label{lemma:min_deg_genus}
  If $\deg(b) \geq \mathrm{genus}(\Gamma_1(b)) + 1$, then $b$ is not sporadic.
\end{lemma}

At the end of this half of the main function, we have accumulated two lists of
points, \texttt{good} and \texttt{bad}. Here, \emph{good} means that the point
is not isolated for the simple reasons from Lemma~\ref{lemma:min_deg_genus};
\emph{bad} simply means that we don't yet know.

The second half of the main function implements an idea based
on~\cite{Bourdon2019} to further eliminate points.

\begin{minted}[mathescape, linenos, firstnumber=last, samepage]{c}
    /* continuing from before */
    // Refuting levels and degrees based on the level reduction theorem of BELOV.
    // If j is a sporadic point of degree d in level m then it becomes a point of
    // d/deg(f) in level n where f:X1(m)-->X1(n) is the natural projection map.
    remove:={};                          // #8 START
    for x in bad do
        for y in good do
            if IsDivisibleBy(x[1],y[1]) then
                b:=x[1] div y[1];
                deg:=b^2*&*[Rationals()
                              | 1-1/p^2 : p in PrimeDivisors(x[1])
                              | p notin PrimeDivisors(y[1]) ];
                if deg eq x[2] div y[2] then Include(~remove,x); end if;
            end if;
        end for;
    end for;                             // #8 END

    // Now we check using gonality arguments if the levels, degrees in the set
    // bad but not in remove can be handled using gonality arguments.
    bad := SequenceToSet(bad);
    if bad ne remove then                // #9
        supbad := bad diff remove;
        return [*j, a, false, supbad*]; //return j-invariant we already have
    end if;
    return [*j, a, true*];
end function;
\end{minted}

This code does two things.

The region surrounded by \texttt{\#8 START} and
\texttt{\#8 END} is an implementation of~\cite{Bourdon2019}.

\begin{enumerate}\setcounter{enumi}{7}
  \item\label{item:belov} The region surrounded by \texttt{\#8 START} and
  \texttt{\#8 END} is an implementation of~\cite{Bourdon2019}. Conceptually, we
  can think of this region as a function (creating \texttt{remove} from
  \texttt{good} and \texttt{bad}) that is a concrete code function on its own.
  We describe this implementation further in Proposition~\ref{prop:belov}.

  \item Finally, we see if there is anything left after trying to remove
  as much as possible using Proposition~\ref{prop:belov}. If there are, then we
  return the remaining elements of uncertainty (which we call \texttt{supbad},
  presumably short for \emph{super bad}).
\end{enumerate}

\begin{proposition}\label{prop:belov}
  The algorithm in \#8 correctly determines \ldots
\end{proposition}

\begin{theorem}\label{thm:main}
  The algorithm in \texttt{NotIsolated} either confirms that a $j$-invariant doesn't
  give rise to sporadic points or indicates that additional information is
  necessary. (There is a lot to be said here, and it will incorporate each
  other intermediate result).
\end{theorem}

\clearpage
\section{\texttt{ReducedLevel} function}\label{sec:reducedlevel}

We now consider \texttt{ReducedLevel}, which is a rather important piece of
code. Despite how quickly we wrote it (almost entirely written in the first
day), a lot of things are happening.

\begin{minted}[mathescape, linenos, samepage]{c}
/* NOTE: We explicitly check those primes dividing m when G doesn't surject to
 * GL2FP. */
NonSurjectivePrimes:=function(G)                     // #1
    m:=Modulus(BaseRing(G));
    return [p:p in PrimeFactors(m)|#ChangeRing(G,GF(p)) ne #GL(2,GF(p))];
end function;

// Level reduction from the output of Zywina's algorithm
ReducedLevel:=function(G)
    m:=Modulus(BaseRing(G));
    NS:=Set(NonSurjectivePrimes(G));
    sE:={2,3} join NS;                    // always consider 2 and 3
    m0:=&*[p^Valuation(m,p):p in sE];
    G:=ChangeRing(G,Integers(m0));
    for p in PrimeFactors(m0) do                     // #2
        while Valuation(m0,p) gt 1                   // #3
                and #G/#ChangeRing(G,Integers(m0 div p)) eq p^4 do
            m0:=m0 div p;
            G:=ChangeRing(G,Integers(m0));
        end while;
        if not p in NS and Valuation(m0,p) eq 1      // #4
               and #G/#ChangeRing(G,Integers(m0 div p)) eq #GL(2,GF(p)) then
            m0:=m0 div p;
            G:=ChangeRing(G,Integers(m0));
        end if;
    end for;
    return G,m0;
end function;
\end{minted}

Along the side, I've indicated several annotation points. We address these in
turn. The numbers of each point in the following list align with an annotation
point in the code above.

\begin{enumerate}
  \item \texttt{NonSurjectivePrimes} is almost pseudocode as is, representing
  almost exactly a definition.

  \item In our meeting, we had a couple of thoughts about the relationship
  between \texttt{NS}, \texttt{sE}, \texttt{m0}, and
  \texttt{PrimeFactors(m0)}. We briefly talked about whether it was inefficient
  to compute the prime factors of \texttt{m0} again in this line, as in some
  sense we already know the primes from just above.

  \item The moral story of this line is that we check to make sure that the
  index when passing from $G(m_0)$ to $G(m_0/p)$ is as large as possible. If it
  is, then nothing is lost by removing a power of $p$.

  We had a lot of discussion about this when $p = 2$. See Proposition 3.5
  of~\cite{Bourdon2019} (or other places) for the idea. But note that $2$ needs
  to be handled differently in principle.

  \item The purpose of this line is to possibly consider removing the factors
  of $2$ and $3$ that we (forcibly) added above.
  Notice that \texttt{p in PrimeFactors(m0)} and \texttt{not p in NS} implies
  that $p \in \{2, 3\}$.

  It might be possible that this portion of code could be simplified.
\end{enumerate}

The primary claim about what this code for is contained in the Level Reduction
Lemma, Lemma~\ref{lemma:reduced_level}. But we need to guarantee that this
implementation is correct.

\begin{lemma}\label{lemma:reduced_level}[Level Reduction Lemma]
  Suppose that $E/\mathbb{Q}$ has adelic image $G$ in $\GL(2, \widehat{Z})$ and
  $G$ has level $M$. To determine if $E$ gives rise to a sporadic, it suffices
  to consider level $N$ \ldots (where $N$ consists essentially of nonsurjective
  primes, and also $2$ and $3$).
\end{lemma}

\begin{proposition}
  The algorithm in \texttt{ReducedLevel} correctly reduces level.
\end{proposition}

I note that this will probably use Proposition 3.5 of~\cite{Bourdon2019} (or
other places) for the idea, and should pay close attention to what happens for
the prime $2$.

\section{\texttt{MinDegreeOfPoint} function}\label{sec:mindegreeofpoint}

We now consider \texttt{MinDegreeOfPoint}.

\begin{minted}[mathescape, linenos, samepage]{c}
VectorOrder:=function(v)
    m:=#Parent(v[1]);
    g:=GCD([m, Integers()!v[2], Integers()!v[1]]);
    return m div g;
end function;

//compute min degree of a point i.e. the min degree of the field of definition
//of a point expressed as a 1 x 2  vector.
MinDegreeOfPoint:=function(G)
    m:=Modulus(BaseRing(G));
    H:=sub<GL(2,Integers(m))|G,-G!1>;           // #1
    orb:=Orbits(H);                             // #2
    sorb:=Sort(orb,func<o1,o2|#o1-#o2>);        // #3
    s2:=[x: x in sorb| VectorOrder(x[1]) eq m]; // #4
    return (#s2[1]) div 2;                      // #5
end function;
\end{minted}

Along the side, I've indicated several annotation points. We address these in
turn. The numbers of each point in the following list align with an annotation
point in the code above.

\begin{enumerate}
  \item When finding the minimum degree of a point, we deliberately include
  $-1$ in the group.

  \item \texttt{Orbits} is a standard magma command that outputs the orbits as
  a list of lists of row-vectors. It's very fast, and led to radical speed
  improvements when we began to use it instead of our earlier code.

  \item This defines a sorting function. The effect is that \texttt{sorb}
  contains sorted orbits, sorted in increasing order of size.

  \item We isolate to those elements with compatible \texttt{VectorOrder}s.

  \item As we included $-1$, we can always divide by $2$ when we return the
  elements. Since the orbits are sorted, the first element will be the
  smallest, which is why we return the first element.
\end{enumerate}

I think there are perhaps two things to show here.

\begin{lemma}
  The algorithm in \texttt{VectorOrder} correctly returns \ldots
\end{lemma}

\begin{proposition}
  The algorithm in \texttt{MinDegreeOfPoint} correctly returns the minimum
  degree of the field of definition.

  Either in this proposition or in an additional lemma, describe why we can
  divide the resulting degree by $2$ \emph{always}, including when $-1 \in G$
  already. \DLD{I only note this because I can't remember why this is true.}
\end{proposition}

\section{Additional notes}

In the process of writing these descriptions, we will probably rewrite parts of
the code. As we're going to make the code public, we will also need to make a
\emph{sanitized} version that we stand by.

There is also a consideration of what we're phrasing. Initially, we thought
about sporadic $j$-invariants. But we're moving on from that.

Finally, there are additional components of processing that we've done but
which aren't incorporated here. These include

\begin{enumerate}
  \item The basic gonality processing, and
  \item The other things that Filip wrote about in zulip.
\end{enumerate}

\vspace{20 mm}
\bibliographystyle{alpha}
\bibliography{bibliofile}

\end{document}

### 2023-03-29 TeX/notes/magma.py

@@ -1,0 +1,129 @@
+#!/usr/bin/python3.9
+
+import argparse
+import sys
+import pygments.cmdline as _cmdline
+
+def main(args):
+  parser = argparse.ArgumentParser()
+  parser.add_argument('-l', dest='lexer', type=str)
+  opts, rest = parser.parse_known_args(args[1:])
+  if str(opts.lexer).lower() == 'magma':
+    args = [__file__, '-l', __file__ + ':Magma', '-x', *rest]
+  _cmdline.main(args)
+
+if __name__ == '__main__':
+  main(sys.argv)
+
+# ----------------------------------------------------------------------
+# -- here's the actual MagmaLexer:
+
+from pygments.lexer import RegexLexer, include, words, bygroups, using, this
+from pygments.token import Comment, Operator, Keyword, Name, String, Number,\
+                           Punctuation, Whitespace, Text, Generic, Error
+
+class Magma(RegexLexer):
+  name = 'Magma'
+  aliases = ['magma']
+  filenames = ['*.m', '*.mag']
+
+  # the following categories came from an Emacs Magma-mode package
+  keywords =       """ _ by default do is select then to where end until
+                       catch elif else when case for function if intrinsic
+                       procedure repeat try while """
+  operators =      """ adj and cat cmpeq cmpne diff div eq ge gt in join
+                       le lt meet mod ne notadj notin notsubset or sdiff
+                       subset xor not """
+  extra_keywords = """ assert assert2 assert3 break clear continue declare delete
+                       error error if eval exit
+                       forward fprintf freeze iload import load local print
+                       printf quit random read readi require requirege
+                       requirerange restore return save time vprint vprintf vtime
+                       assigned exists forall """
+  constructors =   """ car case cop elt ext func hom ideal lideal map
+                       ncl pmap proc quo rec recformat rideal sub """
+  block_open =     """ try catch case when then else do repeat
+                       function procedure intrinsic """
+  block_close =    """ until end when elif else catch """
+
[…]

### 2023-04-03 TeX/draft.tex
Updates from Overleaf

@@
 \newtheorem{algorithm}[theorem]{Algorithm}
-
+\DeclareMathOperator{\gon}{gon}
 %\numberwithin{equation}{section}
@@
 \newcommand{\Z}{\bZ}
+\newcommand{\PP}{\mathbb P}
 \newcommand{\filip}[1]{{\color{cyan} \textsf{$\sun\sun\sun$ Filip: [#1]}}}
@@
 
+\section{Genus 0 adelic images do not produce isolated points}
+
+Let $E/ \Q$ be an elliptic curve and $G\in \GL_2(\hat \Z)$ its adelic image.
+By $G(n)$ denote the image of its mod $n$ representation.
+Denote by $B_1(n)$ the subgroup of $\GL_2(\Z /n \Z)$ consisting of the upper triangular matrices with a $1$ in the upper left entry.
+Note that $X_{B_1(n)}=X_1(n)$.
+We say that a congruence group $\Gamma$ is of genus $g$ if $X_\Gamma$ is of genus $g$.
+We say that a point $P$ corresponds to an elliptic curve $E$ if $j(P)=j(E)$.
+
+\begin{proposition}
+Let $E/\Q$ be an elliptic curve with adelic image of genus $0$. Then there does not exist an $n$ such that a point corresponding to $E$ on $X_1(n)$ is sporadic.
+\end{proposition}
+\begin{proof}
+Since $G$ is by assumption of genus $0$, it follows that so is $G(n)$. Let $P$ be a $\Q$-rational point on $X_{G(n)}$ corresponding to $E$.
+
+%Let $B$ be the group generated by $G(n)$ and a conjugate of $B_1(n)$ in $\GL_2(\Z/n\Z)$; this is again a group of genus $0$ on which the image $P'$ of $P$ under the map $X_{G(n)}\rightarro X_B$ is $\Q$-rational.
+The inclusion of subgroups $B\subset B_1(n)$ induces a map $X_1(n)\rightarrow  X_B$.
+
+The minimal degree of a point on $X_1(n)$ corresponding to $E$ is the minimal index of $B:=c(B_1(n))\cap G(n)$ in $G(n)$, where $c$ denotes conjugation in $\GL_2(\Z /n \Z)$. 
+Call this (minimal) index $d$ and let $f:X_{B}\rightarrow X_{G(n)}$ be the corresponding map of modular curves.
+By construction, all the points in $f^{-1}(P)$ are of degree $d$ and obviously $\gon_\Q X_{B}\leq d.$ Let $P'\in f^{-1}(P) \subseteq X_{B}$ be a point corresponding to $E$, and let $g:X_{B}\rightarrow X_1(n)$ be the map induced by the inclusion $B_1(n) \subseteq B$.
+Then by the argument above we have that $g(P')$ is of degree $d$ (as this is the minimal degree of a point on $X_1(n)$ corresponding to $E$), and on the other hand we have that $\gon_\Q X_1(n)\leq d$ by \cite[Proposition A.1 (vii)]{Poonen:gonality}.
+\end{proof}
+
 \vspace{20 mm}

### 2023-04-03 TeX/notes/meeting_notes_29Mar2023.tex
Updates from Overleaf

@@
 
-\usepackage{minted}
-\usemintedstyle{lovelace}
-\definecolor{mintbf}{gray}{0.95}
-\setminted{bgcolor=mintbf}
+% Don't use minted, b/c overleaf
+% \usepackage{minted}
+% \usemintedstyle{lovelace}
+% \definecolor{mintbf}{gray}{0.95}
+% \setminted{bgcolor=mintbf}
 
@@
 
-\begin{minted}[mathescape, linenos, samepage]{c}
+\begin{verbatim}
 /* First half of NotIsolated function, which determines if j
@@
     end for;
-\end{minted}
+\end{verbatim}
 
@@
 
-\begin{minted}[mathescape, linenos, firstnumber=last, samepage]{c}
+\begin{verbatim}
     /* continuing from before */
@@
 end function;
-\end{minted}
+\end{verbatim}
 
@@
 
-\begin{minted}[mathescape, linenos, samepage]{c}
+\begin{verbatim}
 /* NOTE: We explicitly check those primes dividing m when G doesn't surject to
@@
 
-\begin{minted}[mathescape, linenos, samepage]{c}
+\begin{verbatim}
 VectorOrder:=function(v)

### 2023-04-05 TeX/draft.tex
Updates from Overleaf

@@
 \usepackage{amsmath,amsthm,amssymb}
+% \usepackage{algorithm2e}
 
@@
 \renewcommand{\theta}{\vartheta}
-
+\newcommand{\Supp}{\operatorname{Supp}}
 \renewcommand\labelenumi{(\theenumi)}
@@
 
+\section{Reduce Level}
+\noindent \textbf{Input:} Non-CM elliptic curve $E/\Q$\\
+\textbf{Output:} Finite set of positive integers $\mathcal{I}_1$ such that any isolated point $x \in X_1(n)$ with $j(x) =j(E)$ maps under the natural projection map to an isolated point on $X_1(d)$ for $d \in \mathcal{I}_1$.
+\begin{theorem}
+Let $E/\Q$ be a non-CM elliptic curve, and let $\rho_E$ denote the adelic Galois representation of $E$. Let $M_E$ be any positive integer such that 
+\[
+\im \rho_E=\pi^{-1}(\im \rho_{E, M_E}).
+\]
+Then for any $x \in X_1(n)$ with $j(x)=j(E)$ we have $\deg(x)=\deg(f)\cdot \deg(f(x))$, where $f: X_1(n) \rightarrow X_1(\gcd(n,M_E))$ denotes the natural map. It follows that:
+\begin{enumerate}
+\item If $x$ is $\mathbb{P}^1$-isolated, then $f(x)$ is $\mathbb{P}^1$-isolated.
+\item If $x$ is AV-isolated, then $f(x)$ is AV-isolated.
+\item If $x$ is sporadic, then $f(x)$ is sporadic.
+\end{enumerate}
+\end{theorem}
+
+\begin{proof}
+This follows from the arguments in Section 5.3 of BELOV (see Remark 5.5 in particular) and Theorem 4.3.
+\end{proof}
+
+Let $S_E=\{2,3\} \cup \{\ell : \rho_{E,\ell^{\infty}}(\Gal_{\Q}) \neq \GL_2(\Z_{\ell})\}$. Let $M_E=M_1\cdot M_2$ where $\Supp(M_1) \subseteq S_E$ and $\Supp(M_2) \cap S_E =\emptyset$.
+
+\begin{corollary}
+Let $E/\Q$ be a non-CM elliptic curve, and let $\rho_E$ denote the adelic Galois representation of $E$. 
+Then for any $x \in X_1(n)$ with $j(x)=j(E)$ we have $\deg(x)=\deg(f)\cdot \deg(f(x))$, where $f: X_1(n) \rightarrow X_1(\gcd(n,M_1))$ denotes the natural map. It follows that:
+\begin{enumerate}
+\item If $x$ is $\mathbb{P}^1$-isolated, then $f(x)$ is $\mathbb{P}^1$-isolated.
+\item If $x$ is AV-isolated, then $f(x)$ is AV-isolated.
+\item If $x$ is sporadic, then $f(x)$ is sporadic.
+\end{enumerate}
+\end{corollary}
+
+\begin{proof}
+This should follow from BELOV Proposition 5.7.
+\end{proof}
+
+Main idea beyond this: Let $m$ be the product of the primes in $\Supp(M_1)$.
+By Proposition 5.8 in BELOV, it suffices to replace $M_1$ in the corollary above with the level of the $m$-adic Galois representation.
+This should be the main point of the ``ReducedLevel" operation: to compute this level.
+Note in particular we do not need to add in 2 and 3 if they were not already in $\Supp(M_E)$.
+
+\section{Compute Degree}
+
+\noindent \textbf{Input:} $\mathcal{I}_1$ from step 1\\
+\textbf{Output:} For each $d \in \mathcal{I}_1$, compute degree(s) of closed point on $X_1(n)$ associated to $E$. Return ???
+
+\begin{proposition}
+Let $E/\Q$ be a non-CM elliptic curve and $n \in \mathbb{Z}^+$. If $\im \rho_{E,n} \cong G \leq \GL_2(\Z/n\Z)$, then ...
+\end{proposition}
+
+\section{Riemann-Roch}
+
+\noindent \textbf{Input:} Output from step 2\\
+\textbf{Output:} Smaller list of pairs to check
+
+\begin{lemma}
+Let $C$ be a curve over a number field $k$ with genus $g$. If $x \in C(\overline{k})$ is a closed point with degree
+$\geq g+1$, then $x$ is not $\mathbb{P}^{1}$-isolated.
+\end{lemma}
+
+\begin{proof}
+This is Lemma 13 in revision of B., Gill, Rouse, Watson.
+\end{proof}
+
+\section{Remaining Cases}
+
+Filip's arguemnts
+
 \section{Genus 0 adelic images do not produce isolated points}

### 2023-04-05 isolated_points/isolatedpoints.m
convert to intrinsics, add spec file

@@ -1,28 +1,11 @@
-AttachSpec("/usr/people/hashimot/ModularCurves/equations/equations.spec");//change if you have 
-                                                       //different path to the spec file
-path := OpenImageContext("/usr/people/hashimot/ModularCurves/equations/OpenImage/data-files"); //change if you have 
-                                                                            //different path to 
-
-/*#################################################################################################
-The following program checks given an elliptic curve with rational j-invariant if it represents an 
-isolated point of any degree and any level. The flow of execution is as follows:
-
-Input curve (Cremona label or with coefficient array) -> Zywina's algorithm -> Level reduction -> compute min degree for all divisors of reduced level -> refute using genus/Reiman-Roch
-arguments -> refute by pushing down to lower levels using BELOV -> Output 
-(True if everything is refuted / false with left over levels/degrees, otherwise).
-
-This program was written during COUNT at CIRM.
-#################################################################################################*/
-
-
-NonSurjectivePrimes:=function(G)
+intrinsic NonSurjectivePrimes(G::GrpMat) -> SeqEnum[RngIntElt]
+    {Given G the adelic image of the Galois representation, compute the non-surjective primes}
         m:=Modulus(BaseRing(G));
         return [p:p in PrimeFactors(m)|#ChangeRing(G,GF(p)) ne #GL(2,GF(p))];
-end function;
+end intrinsic;
 
-
-//Level reduction from the output of Zywina's algorithm
-ReducedLevel:=function(G)
+intrinsic ReducedLevel(G::GrpMat) -> GrpMat, RngIntElt
+    {Level reduction from the output of Zywina's algorithm}
     m:=Modulus(BaseRing(G));
     NS:=Set(NonSurjectivePrimes(G));
     sE:={2,3} join NS; 
@@ -39,29 +22,28 @@ ReducedLevel:=function(G)
         end if;
     end for;
     return G,m0;
-end function;
+end intrinsic;
 
-
-VectorOrder:=function(v)
+intrinsic VectorOrder(v::ModTupRngElt) -> RngIntElt
+    {Order of a vector with entries in Z/mZ}
     m:=#Parent(v[1]);
[…]

### 2023-04-05 isolated_points/test.m

@@ -1,0 +1,18 @@
+AttachSpec("/Users/sachihashimoto/Repos/ModularCurves/equations/equations.spec");                                                      //different path to the spec file
+path := OpenImageContext("/Users/sachihashimoto/Repos/ModularCurves/equations/OpenImage/data-files");                                                                           
+AttachSpec("isolated.spec");
+
+if assigned seq then
+    SetColumns(0);
+    SetAutoColumns(false);
+    seq := eval seq;
+    inputs := Split(Read("isolated_refined.txt"), "\n");
+    input := inputs[seq];
+    i := Index(input, ")");
+    jinv := input[1..i]; //construct j-invariant
+    ainv := eval input[i+2 .. #input];
+    output := NotIsolated(ainv, jinv, path);
+    print Join([Sprint(elt) : elt in output], ":");
+    exit;
+end if;
+

### 2023-04-06 isolated_points/isolatedpoints.m
meeting changes updates to code

@@ -53,43 +53,24 @@ intrinsic DegreesOfPotIsolatedPoints(G::GrpMat, g::RngIntElt) -> SeqEnum[RngIntE
     return degrees;
 end intrinsic;
 
-intrinsic NotIsolated(a::SeqEnum[RngIntElt], j::MonStgElt, path::Assoc) -> List
-    {main function to check if a j invariant is sporadic}
-    E:=EllipticCurve(a);
-    G,n,S:=FindOpenImage(path, E);
-    G0:=ReducedLevel(G);
-    G0t := sub<GL(2,Integers(#BaseRing(G0))) | [Transpose(g):g in Generators(G0)]>;
-    k:=#BaseRing(G0t);
-    good:=[];
-    bad:=[];
-    for b in Divisors(k) do
-        if b gt 12 then //X1(11) is a rank 0 elliptic curve with non noncuspidal rational pts
-            ww:=MinDegreeOfPoint(ChangeRing(G0t,Integers(b)));
-            //if the min degree >= g+1 then the dimension of the Riemann-Roch
-            //space associated to the point of min degree is at least 2 hence it
-            //is not sporadic.
-            genusGamma1bplus1 := (Genus(Gamma1(b))+1);
-            if  ww ge genusGamma1bplus1 then 
-                Append(~good,<b, ww>); //not isolated
-            else 
-            //otherwise we need to check if gonality/degree reduction 
-            //arguments can be used
-            //then we return all of the orbit sizes / 2 as long as degree < g+1
-            wws := DegreesOfPotIsolatedPoints(ChangeRing(G0t,Integers(b)), genusGamma1bplus1);
-            for ww in wws do
-                Append(~bad,<b, ww>); //potentially isolated
-            end for;
-            end if;
-        end if;
-    end for;
-    remove:={};
+intrinsic DegreesOfPoints(G::GrpMat) -> SeqEnum[RngIntElt]
+    {compute all degrees of points without doing Riemann-Roch}
+    m := Modulus(BaseRing(G));
+    H := sub<GL(2,Integers(m))|G,-G!1>;
+    orb := Orbits(H);
+    orbm := [#x div 2 : x in orb | VectorOrder(x[1]) eq m]; 
+    degrees := SetToSequence(Set(orbm)); //remove duplicates
+    return degrees;
+end intrinsic;
 
-//Refuting levels and degrees based on the level reduction theorem of BELOV.
-//If j is a sporadic point of degree d in level m then it becomes a point of
[…]

### 2023-04-06 isolated_points/isolatedpoints.m
changes with amazing tabs

@@ -68,7 +68,7 @@ intrinsic RefuteLevel(potisolated::SeqEnum[Tup], allpts::SeqEnum[Tup]) -> SeqEnu
     {Refuting levels and degrees based on the level reduction theorem of BELOV.
     If j is a sporadic point of degree d in level m then it becomes a point of
     d/deg(f) in level n where f:X1(m)-->X1(n) is the natural projection map.}
-
+	remove := {};
     for x in potisolated do 
         for y in allpts do
             if IsDivisibleBy(x[1],y[1]) then
@@ -98,20 +98,20 @@ intrinsic NotIsolated(a::SeqEnum[RngIntElt], j::MonStgElt, path::Assoc) -> List
         if l gt 12 then //X1(11) is a rank 0 elliptic curve with non noncuspidal rational pts
 
             listofdeg := DegreesOfPoints(ChangeRing(G0t,Integers(l)));
-            for d in listofdeg do
+	genusGamma1lplus1 := Genus(Gamma1(l))+1;
+            for deg in listofdeg do
                 Append(~allpoints,<l, deg>);
-            end for;
-            genusGamma1lplus1 := (Genus(Gamma1(l))+1);
-
-            if deg ge genusGamma1lplus1 then
-                Append(~potisolated, <l, deg>); //"easy" Riemann--Roch condition
-            end if;
+            	if deg ge genusGamma1lplus1 then
+                	Append(~potisolated, <l, deg>); //"easy" Riemann--Roch condition
+            	end if;
+	end for;
    
         end if;
     end for;
 
-    remove := RefuteLevel(potisolated, allpts);
-    potisolated := potisolated diff remove; //the remaining potentially isolated
+    remove := RefuteLevel(potisolated, allpoints);
+	potisolated := SequenceToSet(potisolated);
+	potisolated := potisolated diff remove; //the remaining potentially isolated
 
     if #potisolated gt 0 then
         return [*j, a, false, potisolated*]; 

### 2023-04-06 isolated_points/isolatedpoints.m
git rid of excess code, fix tabs

@@ -31,28 +31,6 @@ intrinsic VectorOrder(v::ModTupRngElt) -> RngIntElt
     return m div g;
 end intrinsic;
 
-intrinsic MinDegreeOfPoint(G::GrpMat) -> RngIntElt
-    {compute min degree of a point i.e. the min degree of the field of definition
-    of a point expressed as a 1 x 2  vector}
-    m:=Modulus(BaseRing(G));
-    H:=sub<GL(2,Integers(m))|G,-G!1>;
-    orb:=Orbits(H);
-    sorb:=Sort(orb,func<o1,o2|#o1-#o2>);
-    s2:=[x: x in sorb| VectorOrder(x[1]) eq m]; //equivalently Minimum([x: x in orb| VectorOrder(x[1]) eq m]);
-    return (#s2[1]) div 2;
-end intrinsic;
-
-intrinsic DegreesOfPotIsolatedPoints(G::GrpMat, g::RngIntElt) -> SeqEnum[RngIntElt]
-    {compute all degrees of points, and returns the ones that are greater than g}
-    m := Modulus(BaseRing(G));
-    H := sub<GL(2,Integers(m))|G,-G!1>;
-    orb := Orbits(H);
-    orbm := [x : x in orb | VectorOrder(x[1]) eq m]; 
-    orbmg := [#x div 2 : x in orbm | (#x div 2) ge g];
-    degrees := SetToSequence(Set(orbmg)); //remove duplicates
-    return degrees;
-end intrinsic;
-
 intrinsic DegreesOfPoints(G::GrpMat) -> SeqEnum[RngIntElt]
     {compute all degrees of points without doing Riemann-Roch}
     m := Modulus(BaseRing(G));
@@ -68,12 +46,11 @@ intrinsic RefuteLevel(potisolated::SeqEnum[Tup], allpts::SeqEnum[Tup]) -> SeqEnu
     {Refuting levels and degrees based on the level reduction theorem of BELOV.
     If j is a sporadic point of degree d in level m then it becomes a point of
     d/deg(f) in level n where f:X1(m)-->X1(n) is the natural projection map.}
-	remove := {};
+    remove := {};
     for x in potisolated do 
         for y in allpts do
             if IsDivisibleBy(x[1],y[1]) then
                 b:=x[1] div y[1];
-                
                 deg:=b^2*&*[Rationals() | 1-1/p^2 : p in PrimeDivisors(x[1]) | p notin PrimeDivisors(y[1])];
[…]

### 2023-04-06 isolated_points/isolatedpoints.m
incorporate RR into refute level

@@ -42,10 +42,23 @@ intrinsic DegreesOfPoints(G::GrpMat) -> SeqEnum[RngIntElt]
 end intrinsic;
 
 //TODO: rename this function
-intrinsic RefuteLevel(potisolated::SeqEnum[Tup], allpts::SeqEnum[Tup]) -> SeqEnum[Tup]
+intrinsic RefuteLevel(allpts::SeqEnum[Tup]) -> SeqEnum[Tup]
     {Refuting levels and degrees based on the level reduction theorem of BELOV.
     If j is a sporadic point of degree d in level m then it becomes a point of
     d/deg(f) in level n where f:X1(m)-->X1(n) is the natural projection map.}
+   
+    function easyRiemannRoch(listofpts)
+        for pt in listofpts do
+            l, deg := Explode(pt);
+            genusGamma1lplus1 := Genus(Gamma1(l))+1;
+            if deg ge genusGamma1lplus1 then
+                Append(~potisolated, <l, deg>); //"easy" Riemann--Roch condition
+            end if;
+        end for;
+    end function;
+
+    potisolated := easyRiemannRoch(allpts);
+
     remove := {};
     for x in potisolated do 
         for y in allpts do
@@ -61,6 +74,7 @@ intrinsic RefuteLevel(potisolated::SeqEnum[Tup], allpts::SeqEnum[Tup]) -> SeqEnu
 
 end intrinsic;
 
+
 intrinsic NotIsolated(a::SeqEnum[RngIntElt], j::MonStgElt, path::Assoc) -> List
     {main function to check if a j invariant is sporadic}
     E:=EllipticCurve(a);
@@ -74,14 +88,7 @@ intrinsic NotIsolated(a::SeqEnum[RngIntElt], j::MonStgElt, path::Assoc) -> List
     for l in Divisors(k) do
         if l gt 12 then //X1(11) is a rank 0 elliptic curve with non noncuspidal rational pts
             listofdeg := DegreesOfPoints(ChangeRing(G0t,Integers(l)));
-            genusGamma1lplus1 := Genus(Gamma1(l))+1;
-            for deg in listofdeg do
-                Append(~allpoints,<l, deg>);
-                if deg ge genusGamma1lplus1 then
-                    Append(~potisolated, <l, deg>); //"easy" Riemann--Roch condition
-                end if;
-            end for;
-   
+            allpoints := [<l, deg> : deg in listofdeg];
         end if;
     end for;
 

### 2023-04-06 isolated_points/isolatedpoints.m
typos

@@ -48,6 +48,7 @@ intrinsic RefuteLevel(allpts::SeqEnum[Tup]) -> SeqEnum[Tup]
     d/deg(f) in level n where f:X1(m)-->X1(n) is the natural projection map.}
    
     function easyRiemannRoch(listofpts)
+        potisolated := [];
         for pt in listofpts do
             l, deg := Explode(pt);
             genusGamma1lplus1 := Genus(Gamma1(l))+1;
@@ -55,6 +56,7 @@ intrinsic RefuteLevel(allpts::SeqEnum[Tup]) -> SeqEnum[Tup]
                 Append(~potisolated, <l, deg>); //"easy" Riemann--Roch condition
             end if;
         end for;
+        return potisolted;
     end function;
 
     potisolated := easyRiemannRoch(allpts);

### 2023-04-06 isolated_points/isolatedpoints.m
typo...

@@ -56,7 +56,7 @@ intrinsic RefuteLevel(allpts::SeqEnum[Tup]) -> SeqEnum[Tup]
                 Append(~potisolated, <l, deg>); //"easy" Riemann--Roch condition
             end if;
         end for;
-        return potisolted;
+        return potisolated;
     end function;
 
     potisolated := easyRiemannRoch(allpts);

### 2023-04-06 isolated_points/isolatedpoints.m
fixed problem...

@@ -72,7 +72,10 @@ intrinsic RefuteLevel(allpts::SeqEnum[Tup]) -> SeqEnum[Tup]
         end for;
     end for;
 
-    return remove;
+    potisolated := SequenceToSet(potisolated);
+    potisolated := potisolated diff remove; //the remaining potentially isolated
+
+    return potisolated;
 
 end intrinsic;
 
@@ -86,7 +89,6 @@ intrinsic NotIsolated(a::SeqEnum[RngIntElt], j::MonStgElt, path::Assoc) -> List
     k:=#BaseRing(G0t);
 
     allpoints := []; //generate a list of <l, deg> such that E is a non CM point on X1(l) of degree deg 
-    potisolated := [];
     for l in Divisors(k) do
         if l gt 12 then //X1(11) is a rank 0 elliptic curve with non noncuspidal rational pts
             listofdeg := DegreesOfPoints(ChangeRing(G0t,Integers(l)));
@@ -94,9 +96,7 @@ intrinsic NotIsolated(a::SeqEnum[RngIntElt], j::MonStgElt, path::Assoc) -> List
         end if;
     end for;
 
-    remove := RefuteLevel(potisolated, allpoints);
-    potisolated := SequenceToSet(potisolated);
-    potisolated := potisolated diff remove; //the remaining potentially isolated
+    potisolated := RefuteLevel(allpoints);
 
     if #potisolated gt 0 then
         return [*j, a, false, potisolated*]; 

### 2023-04-06 isolated_points/isolatedpoints.m
fix another problem

@@ -92,7 +92,9 @@ intrinsic NotIsolated(a::SeqEnum[RngIntElt], j::MonStgElt, path::Assoc) -> List
     for l in Divisors(k) do
         if l gt 12 then //X1(11) is a rank 0 elliptic curve with non noncuspidal rational pts
             listofdeg := DegreesOfPoints(ChangeRing(G0t,Integers(l)));
-            allpoints := [<l, deg> : deg in listofdeg];
+            for deg in listofdeg do
+                Append(~allpoints, <l, deg>);
+            end for;
         end if;
     end for;
 

### 2023-04-12 TeX/draft.tex

--- 2023-04-03 TeX/draft.tex
@@
 \usepackage{amsmath,amsthm,amssymb}
+\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
+
+\usepackage{colonequals}
 
@@
 \newtheorem{exercise}[theorem]{Exercise}
-\newtheorem{algorithm}[theorem]{Algorithm}
+% \newtheorem{algorithm}[theorem]{Algorithm}
 \DeclareMathOperator{\gon}{gon}
@@
 \newcommand{\filip}[1]{{\color{cyan} \textsf{$\sun\sun\sun$ Filip: [#1]}}}
-\newcommand{\davidnote}[1]{\marginpar{\footnotesize{\textcolor{Plum}{David: #1}}}}
+\newcommand{\davidnote}[1]{\textcolor{Plum}{David: #1}}
+
+\newcommand{\abbey}[1]{\textcolor{blue}{Abbey: #1}}
+
+\newcommand{\sachi}[1]{\textcolor{purple}{Sachi: #1}}
+% \newcommand{\travis}[1]{\textcolor{chartreuse}{Travis: #1}}
 
@@
 
+\section{Background}
+
+\begin{theorem}
+Let $E/\Q$ be a non-CM elliptic curve, and let $\rho_E$ denote the adelic Galois representation of $E$. Let $M_E$ be any positive integer such that 
+\[
+\im \rho_E=\pi^{-1}(\im \rho_{E, M_E}).
+\]
+Then for any $x \in X_1(n)$ with $j(x)=j(E)$ we have $\deg(x)=\deg(f)\cdot \deg(f(x))$, where $f: X_1(n) \rightarrow X_1(\gcd(n,M_E))$ denotes the natural map. It follows that:
+\begin{enumerate}
+\item If $x$ is $\mathbb{P}^1$-isolated, then $f(x)$ is $\mathbb{P}^1$-isolated.
+\item If $x$ is AV-isolated, then $f(x)$ is AV-isolated.
+\item If $x$ is sporadic, then $f(x)$ is sporadic.
+\end{enumerate}
+\end{theorem}
+
+\begin{proof}
+This follows from the arguments \cite[$\S5.3$]{BELOV} and \cite[Theorem 4.3]{BELOV}.
+\abbey{This is mentioned in Remark 5.5 of \cite{BELOV} in particular.
+I'm not sure if we should include more details here.}
+\end{proof}
+
 \section{Proving that a point is not sporadic}
@@
 \begin{algorithm}
-\textbf{Input:} A non-CM $j$-invariant $j = j(E) \in \Q$.
-
-\textbf{Output:} \textsc{False} if $j$ is not a sporadic $j$-invariant.
-
-\begin{enumerate}
-    \item Compute the adelic image $G$ of $E/\Q$ as a subgroup of $\GL_2(\hat{\Z})$ using Zywina's algorithm.
-Represent the output as some \emph{level} $M$ together with a subgroup $G$ of $\GL_2(\Z/M\Z)$.
-
-    \item Reduce level.
-
-    \item For all $12 < b \mid M$ compute the minimum degree of the field of definition of a point with respect to $G \mod b$, the image of $G$ in $\GL_2(\Z/b\Z)$.
-(For that, compute the orbits of $\langle G, -G \rangle \mod b$ on the elements of $(\Z/b\Z)^2$ of order $b$.
-Sort the orbits by size.
-Return )
+\KwIn{A non-CM $j$-invariant $j = j(E) \in \Q$.}
+\KwOut{\textsc{False} if $j$ is not a sporadic $j$-invariant.
+\abbey{Update: Finite list of curves, degrees such that any isolated point on $X_1(n)$ associated to $E$ maps down under the natural projection map to a point in this list.
+If empty, $j$ is not isolated.)}}
+Compute the adelic image $G$ of $E/\Q$ as a subgroup of $\GL_2(\hat{\Z})$ using Zywina's algorithm. Represent the output as some \emph{level} $N$ together with a subgroup $G$ of $\GL_2(\Z/N\Z)$\;
+Reduce level\;
+For all $12 < b \mid N$, using Algorithm~\ref{alg:compute_degree} compute the minimum degree of the field of definition of a point with respect to $G \mod b$, the image of $G$ in $\GL_2(\Z/b\Z)$\;
+\Return{?} \;
     %\filip{We need to look at the orbits of $\langle G, -G \rangle \mod b$ on $(\Z/b\Z)^2$, not $\bP^1(\Z/b\Z)$.
@@
 Furthermore, it is necessary to consider only the elements of $(\Z/b\Z)^2$ of order $b$.}
-\end{enumerate}
 \end{algorithm}
@@
 (In the \texttt{Magma} implementation, we have to be careful that \texttt{Magma} uses right actions, but in our mathematics, we use left action.
-We therefore use the transposes of the matrices in $\GL_2(\Z/M\Z)$.)
+We therefore use the transposes of the matrices in $\GL_2(\Z/N\Z)$.)
+
+\section{Reduce Level}
+
+\abbey{Travis,Sachi, Abbey}
+
+\begin{theorem}[\cite{BELOV}]\label{BELOVthm}
+Let $E/\Q$ be a non-CM elliptic curve, and let $m$ be the product of 2, 3, and all primes $\ell$ where the $\ell$-adic Galois representation of $E$ is not surjective.
+Let $m_0$ be the level of the $m$-adic Galois representation associated to $E$ and let $f: X_1(n) \rightarrow X_1(\gcd(n,m_0))$ denote the natural map.
+If $x\in X_1(n)$ is an isolated point with $j(x)=j(E)$, then $f(x)\in X_1(\gcd(n,m_0))$ is an isolated point.
+\end{theorem}
+
+Using Zywina's algorithm for the level of the adelic Galois representation as a starting point, we may obtain the level of the $m$-adic Galois representation associated to $E$ as in Theorem \ref{BELOVthm}.
+
+\begin{algorithm}[H]
+  \KwIn{$G\subseteq \GL_2(\Z/N\Z)$ such that $\im\rho_E=\pi^{-1}(G)$ and $N$ is the level}
+  \KwOut{$G\subseteq \GL_2(\Z/m_0\Z)$ such that $G=\im\rho_{E,m_0}$ and $\im\rho_{E,m^{\infty}}=\pi^{-1}(\im\rho_{E,m_0})$ where $m$ is the product of the non-surjective primes and $2$ and $3$ (if they do not already divide $m$), and $m_0$ is minimal \abbey{Don't we need to include 2 and 3 in our definition of $m$?
+It is possible 2 and 3 may divide $m_0$ even if they are not surjective primes.
+If they are not necessary, then 2 and 3 need not divide $m_0$ in the final output.} }
+  \caption{Reduce level}%
+  \label{alg:reduce_level}
+  Let $N_E = \{\ell|N \text{ prime} \colon \rho_{E,\ell} \text{ is non-surjective} \}$\;
+  Let $S_E= N_E \cup \{ 2, 3\}$\;
+  Let $m_0 = \prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$\;
+  \For{$\ell \in \{ \ell | m_0 \colon \ell_0 \text{ prime} \}$}{
+  \While{$\ell|m_0$ and $\#G/\#(G \pmod{m_0/p}) = p^4$}{
+    $m_0 = m_0/p$\;
+    $G = G \pmod{m_0}$\;
+  }
+  \If{not $p$ in $N_E$ and $\ord_p(m_0) = 1$ and $\#G/\#(G \pmod{m_0/p}) = \#\GL_2(\Z/p\Z)$}{
+  $m_0 = m_0/p$\;
+   $G = G \pmod{m_0}$\;}}
+  \Return{$G,m_0$}
+\end{algorithm}
+
+  \begin{proposition}
+    Algorithm~\ref{alg:reduce_level} is correct.
+  \end{proposition}
+  \begin{proof}
+    Since $N$ is the level of the adelic representation and both $m$ and $m_0$ divides $N$, we must have that $\im\rho_{E, m^\infty} = \pi^{-1}(\im \rho_{E,m_0})$.
+This property is an invariant of the for-loop.
+The for-loop
+    terminates once as many powers of $\ell$ have been removed from $m_0$ 
+    as possible while maintaining this invariant. Thus $m_0$ is the minimal such integer and is thus the level. 
+  \end{proof}
+
+\section{Compute Degree}
+
+\noindent \textbf{Input:} $\mathcal{I}_1$ from step 1 \\
+\textbf{Output:} For each $d \in \mathcal{I}_1$, compute degree(s) of closed point on $X_1(N)$ associated to $E$. Return ??? \abbey{update algorithm description}
+
+\begin{algorithm}[H]\label{alg:compute_degree}
+  \KwIn{$G\subseteq \GL_2(\Z/N\Z)$ such that $\im\rho_E=\pi^{-1}(G)$ and $N$ is the level; a bound $g \in \Z$}
+  \KwOut{all degrees of $x$-coordinates of points that are $\geq g$} 
+  Let $H \colonequals \langle G, -I_2\rangle \leq \GL_2(\Z/N\Z)$\;
+  Compute the orbits of $H$ acting on $(\Z/N\Z)^2$\label{Inc-1}\;
+  Filter the orbit representatives that have order equal to $N$\;
+  Compute the orbit sizes ``degrees'' $s$ such that $s/2 \geq g$\label{DivBy2}\;
+  Remove duplicates\label{RemDup}\;
+  \Return{degrees}
+\end{algorithm}
+
+Note that only working with orbit(s) (representatives) significantly speeds up the implementation. The computation of the orbits of $G$ acting on $(\Z/N\Z)^2$ is efficiently implemented in Magma.
+
+\begin{proposition}
+Let $E/\Q$ be a non-CM elliptic curve and $N \in \Z_{>0}$.
+If $\im \rho_{E,N} \cong G \leq \GL_2(\Z/N\Z)$, then the Algorithm \ref{alg:compute_degree} outputs the sequence consisting of all possible degrees of $x(P)$, where $P\in E[N]$ is a point of order $N$.
+\end{proposition}
+\begin{proof}
+    We begin by noting that $(E, P)$ and $(E, -P)$ denote the same point on $X_1(N)$, for $P \in E[N]$. Therefore, the degree of 
+    a point represented by $(E, P)$, when
+    $E$ is defined over $\Q$ depends only on $x(P)$. 
+    If $E[N]$ is identified with $(\Z/N\Z)^2$, then $\deg(P)=\# (G. P)$, where $P$ on the left hand side is considered as an element of $(\Z/N\Z)^2$
+    and on right hand side as an element of $E[N]$.
+    If $P$ and $-P$ are in the same Galois orbit, i.e., $-I_2\in G$, then $[\Q(x(P)):\Q]=[\Q(P):\Q]/2$. On the other hand, one has $[\Q(x(P)):\Q]=[\Q(P):\Q]$, when 
+    $-I_2\notin G$. 
+    Therefore, computing the orbit sizes with respect to the 
+    group $H\coloneqq \langle G, -I_2 \rangle$ (step~\ref{Inc-1} in Algorithm \ref{alg:compute_degree}) and dividing
+    by $2$ (step~\ref{DivBy2}) handles both the cases, because in the later case (i.e., when $-I_2\notin G$) the orbit sizes will be doubled. 
+    Finally, step~\ref{RemDup} makes sure that every degree occurs only once in the output sequence.
+\end{proof}
+
+\section{Riemann-Roch}
+
+\noindent \textbf{Input:} Output from step 2\\
+\textbf{Output:} Smaller list of pairs to check
+
+\begin{lemma}
+Let $C$ be a curve over a number field $k$ with genus $g$. If $x \in C(\overline{k})$ is a closed point with degree
+$\geq g+1$, then $x$ is not $\mathbb{P}^{1}$-isolated.
+\end{lemma}
+
+\begin{proof}
+This is Lemma 13 in revision of B., Gill, Rouse, Watson.
+\end{proof}
+
+\section{Remaining Cases}
+\abbey{Filip? Abbey?}
+Filip's arguments.
 
@@
 By $G(n)$ denote the image of its mod $n$ representation.
-Denote by $B_1(n)$ the subgroup of $\GL_2(\Z /n \Z)$ consisting of the upper triangular matrices with a $1$ in the upper left entry.
+Denote by $B_1(n)$ the subgroup of $\GL_2(\Z/n\Z)$ consisting of the upper triangular matrices with a $1$ in the upper left entry.
 Note that $X_{B_1(n)}=X_1(n)$.

### 2023-04-12 isolated_points/isolatedpoints.m
update

@@ -60,10 +60,11 @@ intrinsic RefuteLevel(allpts::SeqEnum[Tup]) -> SeqEnum[Tup]
     end function;
 
     potisolated := easyRiemannRoch(allpts);
+    nonisolated :=  Set(allpts) diff Set(potisolated);
 
     remove := {};
-    for x in potisolated do 
-        for y in allpts do
+    for x in potisolated do //<l, deg> a point of degree deg on X1(l) 
+        for y in nonisolated do 
             if IsDivisibleBy(x[1],y[1]) then
                 b:=x[1] div y[1];
                 deg:=b^2*&*[Rationals() | 1-1/p^2 : p in PrimeDivisors(x[1]) | p notin PrimeDivisors(y[1])];
@@ -90,8 +91,8 @@ intrinsic NotIsolated(a::SeqEnum[RngIntElt], j::MonStgElt, path::Assoc) -> List
 
     allpoints := []; //generate a list of <l, deg> such that E is a non CM point on X1(l) of degree deg 
     for l in Divisors(k) do
-        if l gt 12 then //X1(11) is a rank 0 elliptic curve with non noncuspidal rational pts
-            listofdeg := DegreesOfPoints(ChangeRing(G0t,Integers(l)));
+        if l gt 12 then //X1(11) is a rank 0 elliptic curve with no non noncuspidal rational pts
+            listofdeg := DegreesOfPoints(ChangeRing(G0t,Integers(l))); //MAJOR CHANGE!!
             for deg in listofdeg do
                 Append(~allpoints, <l, deg>);
             end for;

### 2023-04-12 isolated_points/isolatedpoints.m
fix syntax

@@ -60,7 +60,7 @@ intrinsic RefuteLevel(allpts::SeqEnum[Tup]) -> SeqEnum[Tup]
     end function;
 
     potisolated := easyRiemannRoch(allpts);
-    nonisolated :=  Set(allpts) diff Set(potisolated);
+    nonisolated := SequenceToSet(allpts) diff SequenceToSet(potisolated);
 
     remove := {};
     for x in potisolated do //<l, deg> a point of degree deg on X1(l) 

### 2023-04-12 Old Code/NotIsolated.m
reorganizing files

@@ -1,0 +1,147 @@
+AttachSpec("/usr/people/hashimot/ModularCurves/equations/equations.spec");//change if you have 
+                                                       //different path to the spec file
+path := OpenImageContext("/usr/people/hashimot/ModularCurves/equations/OpenImage/data-files"); //change if you have 
+                                                                            //different path to 
+
+/*#################################################################################################
+The following program checks given an elliptic curve with rational j-invariant if it represents an 
+isolated point of any degree and any level. The flow of execution is as follows:
+
+Input curve (Cremona label or with coefficient array) -> Zywina's algorithm -> Level reduction -> compute min degree for all divisors of reduced level -> refute using genus/Reiman-Roch
+arguments -> refute by pushing down to lower levels using BELOV -> Output 
+(True if everything is refuted / false with left over levels/degrees, otherwise).
+
+This program was written during COUNT at CIRM.
+#################################################################################################*/
+
+
+NonSurjectivePrimes:=function(G)
+        m:=Modulus(BaseRing(G));
+        return [p:p in PrimeFactors(m)|#ChangeRing(G,GF(p)) ne #GL(2,GF(p))];
+end function;
+
+
+//Level reduction from the output of Zywina's algorithm
+ReducedLevel:=function(G)
+    m:=Modulus(BaseRing(G));
+    NS:=Set(NonSurjectivePrimes(G));
+    sE:={2,3} join NS; 
+    m0:=&*[p^Valuation(m,p):p in sE];
+    G:=ChangeRing(G,Integers(m0));
+    for p in PrimeFactors(m0) do 
+        while Valuation(m0,p) gt 1 and #G/#ChangeRing(G,Integers(m0 div p)) eq p^4 do
+            m0:=m0 div p;
+            G:=ChangeRing(G,Integers(m0));
+        end while;
+        if not p in NS and Valuation(m0,p) eq 1 and #G/#ChangeRing(G,Integers(m0 div p)) eq #GL(2,GF(p)) then //this #G/#ChangeRing(G,Integers(m0 div p)) eq #GL(2,GF(p)) is implied by other two conditions
+            m0:=m0 div p;
+            G:=ChangeRing(G,Integers(m0));
+        end if;
+    end for;
+    return G,m0;
+end function;
+
+
[…]

### 2023-04-12 Old Code/NotSporadic.m

@@ -1,0 +1,228 @@
+AttachSpec("~/ModularCurves/equations/equations.spec");//change if you have 
+                                                       //different path to the spec file
+path := OpenImageContext("~/ModularCurves/equations/OpenImage/data-files"); //change if you have 
+                                                                            //different path to 
+                                                                            //data-files.
+load "gon_data.m"; //gonality data file
+
+
+/*
+PrimitiveVectors:=function(m)
+        V:=RSpace(Integers(m),2);
+        W:=[V![d,a]:d in Divisors(m), a in [1..m]|GCD(a,d) eq 1];
+        return W;
+end function;
+*/
+
+//MinDegreeOfPoint:=function(G)
+        //m:=Modulus(BaseRing(G));
+        //H:=sub<GL(2,Integers(m))|G,-G!1>;
+        //W:=PrimitiveVectors(m);
+        //c:=Min({Integers()!(#H/(2*#Stabilizer(H,v))):v in W});
+        //return c;
+//end function;
+
+
+/*
+NotSporadic:=procedure(a);
+	E:=EllipticCurve(a);
+	G,n,S:=FindOpenImage(path, E);
+	G0:=ReducedLevel(G);
+	G0t := sub<GL(2,Integers(#BaseRing(G0))) | [Transpose(g):g in Generators(G0)]>;
+	k:=#BaseRing(G0t);
+	for b in Divisors(k) do
+	if b gt 12 then
+	   bool:=MinDegreeOfPoint(ChangeRing(G0t,Integers(b))) ge (Genus(Gamma1(b))+1); 
+       print bool,b,MinDegreeOfPoint(ChangeRing(G0t,Integers(b))); 
+    end if;
+end for;
+end procedure;
+*/
+
+/*
+function form_p1_data(M);
+    grid := Matrix(M,M,[<1,1,0>]);
+    list:=[];
+    counter:=0;
+    for r in [1..M-1] do
+        for c in [0..M-1] do
+            if (Gcd(Gcd(r,c),M) eq 1) then
+                if grid[r+1,c+1] eq 0 then
+                    counter:=counter + 1;
+                    grid[r+1,c+1]:=counter;
+                    list := list cat [[r,c]];
+                    for a in [1..M] do
+                        if Gcd(a,M) eq 1 then
+                            rr := (r * a) mod M;
+                            cc := (c * a) mod M;
+                            grid[rr+1,cc+1]:=grid[r+1,c+1];
+                        end if;
+                    end for;
+                end if;
+            else
[…]

### 2023-04-12 Old Code/PotentiallyBadCurves.m

@@ -1,0 +1,95 @@
+pot_false_data:= [[*[ 1, 1, 0, -5288002736, 148005943305472 ],1542085860252894509103949/6408896512,[ 1, 1, 0, -5288002736, 148005943305472 ],{ <25, 10> }*],
+[*[ 1, 0, 1, -32031834244, -2116511967284374 ],3634704740957616196378170215513091769/168224880645019054412841796875000,[ 1, 0, 1, -32031834244, -2116511967284374 ],{ <24, 4> }*],
+[*[ 0, -1, 0, -120245445, -507477469907 ],-52893159101157376/11,[ 0, -1, 0, -120245445, -507477469907 ],{ <25, 10> }*],
+[*[ 1, 0, 0, -49095400, 132402324032 ],13087181362848921857775657601/10116926999101440000,[ 1, 0, 0, -49095400, 132402324032 ],{ <16, 2> }*],
+[*[ 1, 1, 1, -1431633920, 20849998282145 ],-324503698618794407582644992737281/19342794667089993085747200,[ 1, 1, 1, -1431633920, 20849998282145 ],{ <32, 8> }*],
+[*[ 0, 0, 0, -7164300, 7378058000 ],13619385906841/6048000,[ 0, 0, 0, -7164300, 7378058000 ],{ <24, 4> }*],
+[*[ 1, 0, 1, -190891, -36002922 ],-882216989/131072,[ 1, 0, 1, -190891, -36002922 ],{ <68, 48>, <136, 192>, <34, 12>, <17, 4> }*],
+[*[ 1, 0, 0, -1773878330125, -909355979228841397 ],-617298465273089376571121350031405627538001/165066,[ 1, 0, 0, -1773878330125, -909355979228841397 ],{ <25, 10> }*],
+[*[ 1, -1, 1, -1478148863, 21873679573767 ],10414276373665867414321/301547812500000,[ 1, -1, 1, -1478148863, 21873679573767 ],{ <30, 8> }*],
+[*[ 1, 0, 0, -298010, 293238372 ],-2926956820564562516641/35459588343029760000,[ 1, 0, 0, -298010, 293238372 ],{ <16, 2> }*],
+[*[ 0, -1, 0, -17059856, 27486338496 ],-1139466686381936641/17587891077120,[ 0, -1, 0, -17059856, 27486338496 ],{ <32, 8> }*],
[…]

### 2023-04-12 deleteduplicates.py

@@ -1,0 +1,37 @@
+# code to get isolated_refined.txt from isolated1.txt and isolated2
+from collections import defaultdict
+
+
+with open('isolated1.txt', 'r', encoding="utf8") as file1:
+    data1 = file1.readlines()
+with open('isolated2.txt', 'r', encoding="utf8") as file2:
+    data2 = file2.readlines()
+
+data = data1 + data2
+
+# remove comments at start of file
+data = [datum for datum in data if datum[0] != "#"]
+ndata = len(data)
+
+
+print("Parsing isolated1 and isolated2 files...")
+dict = defaultdict(list)
+for idx, line in enumerate(data):
+    jinv, ainv = line.split('","')
+    a, b = jinv[1:].split(',')
+    j = (eval(a[1:]), eval(b[:-1]))
+    ainv = ainv[:-2].replace('{', '[')
+    ainv = ainv.replace('}', ']')
+    ainvs = eval(ainv)
+    dict[j].append(ainv)
+    print(f"\r{idx:10}/{ndata}", end="")
+print("Done.")
+
+
+with open("isolated_refined.txt", 'w', encoding="utf8") as fileout:
+    for j in dict.keys():
+        fileout.write(str(j))
+        fileout.write(',')
+        fileout.write(str(dict[j][0]))
+        fileout.write('\n')
+print("Refined output written to isolated_refined.txt")

### 2023-04-12 find_pot_isolated.py

@@ -1,0 +1,21 @@
+#code to find the potentially isolated points from all the data
+
+data_files = ['1to100000.out', '100001to200000.out', '200001to300000.out', '300001to400000.out', '400001to500000.out', '500001to534299.out']
+
+for name in data_files:
+    file = open(name, 'r')
+    data = file.readlines()
+    bad_curves = []
+    for line in data:
+        jinv, ainv, b = line.split(':')
+        if b.strip() != 'true':
+            bad_curves.append(line)
+    file.close()
+
+if bad_curves:
+    fileout = open('potentially_isolated.txt', 'w')
+    for curve in bad_curves:
+        fileout.write(curve)
+    fileout.close()
+else:
+    print("No potentially isolated curves were found.")

### 2023-04-12 isolated_points/NotIsolated.m

@@ -1,147 +1,0 @@
-AttachSpec("/usr/people/hashimot/ModularCurves/equations/equations.spec");//change if you have 
-                                                       //different path to the spec file
-path := OpenImageContext("/usr/people/hashimot/ModularCurves/equations/OpenImage/data-files"); //change if you have 
-                                                                            //different path to 
-
-/*#################################################################################################
-The following program checks given an elliptic curve with rational j-invariant if it represents an 
-isolated point of any degree and any level. The flow of execution is as follows:
-
-Input curve (Cremona label or with coefficient array) -> Zywina's algorithm -> Level reduction -> compute min degree for all divisors of reduced level -> refute using genus/Reiman-Roch
-arguments -> refute by pushing down to lower levels using BELOV -> Output 
-(True if everything is refuted / false with left over levels/degrees, otherwise).
-
-This program was written during COUNT at CIRM.
-#################################################################################################*/
-
-
-NonSurjectivePrimes:=function(G)
-        m:=Modulus(BaseRing(G));
-        return [p:p in PrimeFactors(m)|#ChangeRing(G,GF(p)) ne #GL(2,GF(p))];
-end function;
-
-
-//Level reduction from the output of Zywina's algorithm
-ReducedLevel:=function(G)
-    m:=Modulus(BaseRing(G));
-    NS:=Set(NonSurjectivePrimes(G));
-    sE:={2,3} join NS; 
-    m0:=&*[p^Valuation(m,p):p in sE];
-    G:=ChangeRing(G,Integers(m0));
-    for p in PrimeFactors(m0) do 
-        while Valuation(m0,p) gt 1 and #G/#ChangeRing(G,Integers(m0 div p)) eq p^4 do
-            m0:=m0 div p;
-            G:=ChangeRing(G,Integers(m0));
-        end while;
-        if not p in NS and Valuation(m0,p) eq 1 and #G/#ChangeRing(G,Integers(m0 div p)) eq #GL(2,GF(p)) then //this #G/#ChangeRing(G,Integers(m0 div p)) eq #GL(2,GF(p)) is implied by other two conditions
-            m0:=m0 div p;
-            G:=ChangeRing(G,Integers(m0));
-        end if;
-    end for;
-    return G,m0;
-end function;
-
-
[…]

### 2023-04-12 isolated_points/arrangement.m

@@ -1,99 +1,0 @@
-
-
-
-
-
-load "PotentiallyBadCurves.m";
-pos_bad_levels_single := {};
-for d in pot_false_data do
-    if #d[4] eq 1 then Include(~pos_bad_levels_single, Random(d[4])); end if;
-end for;
-
-pos_bad_curves_single := [**];
-for d in pos_bad_levels_single do
-   bad_curves_d :={}; 
-    for c in pot_false_data do 
-        if c[4] eq {d} then Include(~bad_curves_d, <c[1],c[2]>); end if;
-    end for;
-            Append(~pos_bad_curves_single, <bad_curves_d, d>);
-end for;
-
-bad_more_places := {};
-for d in pot_false_data do 
-    if #d[4] ne 1 then Include(~bad_more_places, <d[1], d[2], d[4]>);
-    end if;
-end for;
-
-IsFromBelow := function(a, b)
-    if b[1] gt  a[1] then c := a; a:= b; b:=c; end if;
-    if IsDivisibleBy(a[1],b[1]) then
-			c:=a[1] div b[1];
-			
-			deg:=c^2*&*[Rationals() | 1-1/p^2 : p in PrimeDivisors(a[1]) | p
-                notin PrimeDivisors(b[1])];
-			if deg eq a[2] div b[2] then return true; else return false; end if;
-		end if;
-    return false;
-end function;
-
-find_min := function(a)
-    min := 1000000;
-    min_deg := 0;
-    for d in a do 
-        if d[1] le min then min:= d[1]; min_deg := d[2]; end if;
-    end for;
-        return <min, min_deg>;
-end function;
-
-
- 
-
-arrange_bad_more_places := function(a)
-    bad_more_places_dummy :=[**];
-   for d in a do 
-      r := d[3];
-      dif := [**]; 
-     while #r ne 0 do 
-        r_temp :=r;
-        arrising_from_min := {};
-        min := find_min(r);
-        for x in r_temp do 
-           if IsFromBelow(x, min) then Include(~arrising_from_min,x); 
-              Exclude(~r, x); 
-           end if;
-        end for; 
-        Append(~dif, arrising_from_min);
-     end while;
-     Append(~bad_more_places_dummy, [*d[1], d[2], dif*]);
-   end for;
-       return bad_more_places_dummy;
-end function;
-         
-bad_more_places := arrange_bad_more_places(bad_more_places);
-
-pos_bad_levels_mult:={};
-
[…]

### 2023-04-12 isolated_points/deleteduplicates.py

@@ -1,37 +1,0 @@
-# code to get isolated_refined.txt from isolated1.txt and isolated2
-from collections import defaultdict
-
-
-with open('isolated1.txt', 'r', encoding="utf8") as file1:
-    data1 = file1.readlines()
-with open('isolated2.txt', 'r', encoding="utf8") as file2:
-    data2 = file2.readlines()
-
-data = data1 + data2
-
-# remove comments at start of file
-data = [datum for datum in data if datum[0] != "#"]
-ndata = len(data)
-
-
-print("Parsing isolated1 and isolated2 files...")
-dict = defaultdict(list)
-for idx, line in enumerate(data):
-    jinv, ainv = line.split('","')
-    a, b = jinv[1:].split(',')
-    j = (eval(a[1:]), eval(b[:-1]))
-    ainv = ainv[:-2].replace('{', '[')
-    ainv = ainv.replace('}', ']')
-    ainvs = eval(ainv)
-    dict[j].append(ainv)
-    print(f"\r{idx:10}/{ndata}", end="")
-print("Done.")
-
-
-with open("isolated_refined.txt", 'w', encoding="utf8") as fileout:
-    for j in dict.keys():
-        fileout.write(str(j))
-        fileout.write(',')
-        fileout.write(str(dict[j][0]))
-        fileout.write('\n')
-print("Refined output written to isolated_refined.txt")

### 2023-04-12 isolated_points/find_pot_isolated.py

@@ -1,21 +1,0 @@
-#code to find the potentially isolated points from all the data
-
-data_files = ['1to100000.out', '100001to200000.out', '200001to300000.out', '300001to400000.out', '400001to500000.out', '500001to534299.out']
-
-for name in data_files:
-    file = open(name, 'r')
-    data = file.readlines()
-    bad_curves = []
-    for line in data:
-        jinv, ainv, b = line.split(':')
-        if b.strip() != 'true':
-            bad_curves.append(line)
-    file.close()
-
-if bad_curves:
-    fileout = open('potentially_isolated.txt', 'w')
-    for curve in bad_curves:
-        fileout.write(curve)
-    fileout.close()
-else:
-    print("No potentially isolated curves were found.")

### 2023-04-12 isolated_points/isolatedpoints.m

@@ -1,110 +1,0 @@
-intrinsic NonSurjectivePrimes(G::GrpMat) -> SeqEnum[RngIntElt]
-    {Given G the adelic image of the Galois representation, compute the non-surjective primes}
-        m:=Modulus(BaseRing(G));
-        return [p:p in PrimeFactors(m)|#ChangeRing(G,GF(p)) ne #GL(2,GF(p))];
-end intrinsic;
-
-intrinsic ReducedLevel(G::GrpMat) -> GrpMat, RngIntElt
-    {Level reduction from the output of Zywina's algorithm}
-    m:=Modulus(BaseRing(G));
-    NS:=Set(NonSurjectivePrimes(G));
-    sE:={2,3} join NS; 
-    m0:=&*[p^Valuation(m,p):p in sE];
-    G:=ChangeRing(G,Integers(m0));
-    for p in PrimeFactors(m0) do 
-        while Valuation(m0,p) gt 1 and #G/#ChangeRing(G,Integers(m0 div p)) eq p^4 do
-            m0:=m0 div p;
-            G:=ChangeRing(G,Integers(m0));
-        end while;
-        if not p in NS and Valuation(m0,p) eq 1 and #G/#ChangeRing(G,Integers(m0 div p)) eq #GL(2,GF(p)) then //this #G/#ChangeRing(G,Integers(m0 div p)) eq #GL(2,GF(p)) is implied by other two conditions
-            m0:=m0 div p;
-            G:=ChangeRing(G,Integers(m0));
-        end if;
-    end for;
-    return G,m0;
-end intrinsic;
-
-intrinsic VectorOrder(v::ModTupRngElt) -> RngIntElt
-    {Order of a vector with entries in Z/mZ}
-    m:=#Parent(v[1]);
-    g:=GCD([m, Integers()!v[2], Integers()!v[1]]);
-    return m div g;
-end intrinsic;
-
-intrinsic DegreesOfPoints(G::GrpMat) -> SeqEnum[RngIntElt]
-    {compute all degrees of points without doing Riemann-Roch}
-    m := Modulus(BaseRing(G));
-    H := sub<GL(2,Integers(m))|G,-G!1>;
-    orb := Orbits(H);
-    orbm := [#x div 2 : x in orb | VectorOrder(x[1]) eq m]; 
-    degrees := SetToSequence(Set(orbm)); //remove duplicates
-    return degrees;
-end intrinsic;
-
-//TODO: rename this function
[…]

### 2023-04-12 isolated_points/test.m

@@ -1,18 +1,0 @@
-AttachSpec("/usr/people/hashimot/ModularCurves/equations/equations.spec");                                                      //different path to the spec file
-path := OpenImageContext("/usr/people/hashimot/ModularCurves/equations/OpenImage/data-files");                                                                           
-AttachSpec("isolated.spec");
-
-if assigned seq then
-    SetColumns(0);
-    SetAutoColumns(false);
-    seq := eval seq;
-    inputs := Split(Read("isolated_refined.txt"), "\n");
-    input := inputs[seq];
-    i := Index(input, ")");
-    jinv := input[1..i]; //construct j-invariant
-    ainv := eval input[i+2 .. #input];
-    output := NotIsolated(ainv, jinv, path);
-    print Join([Sprint(elt) : elt in output], ":");
-    exit;
-end if;
-

### 2023-04-12 isolatedpoints.m

@@ -1,0 +1,111 @@
+intrinsic NonSurjectivePrimes(G::GrpMat) -> SeqEnum[RngIntElt]
+    {Given G the adelic image of the Galois representation, compute the non-surjective primes}
+        m:=Modulus(BaseRing(G));
+        return [p:p in PrimeFactors(m)|#ChangeRing(G,GF(p)) ne #GL(2,GF(p))];
+end intrinsic;
+
+intrinsic ReducedLevel(G::GrpMat) -> GrpMat, RngIntElt
+    {Level reduction from the output of Zywina's algorithm}
+    m:=Modulus(BaseRing(G));
+    NS:=Set(NonSurjectivePrimes(G));
+    sE:={2,3} join NS; 
+    m0:=&*[p^Valuation(m,p):p in sE];
+    G:=ChangeRing(G,Integers(m0));
+    for p in PrimeFactors(m0) do 
+        while Valuation(m0,p) gt 1 and #G/#ChangeRing(G,Integers(m0 div p)) eq p^4 do
+            m0:=m0 div p;
+            G:=ChangeRing(G,Integers(m0));
+        end while;
+        if not p in NS and Valuation(m0,p) eq 1 and #G/#ChangeRing(G,Integers(m0 div p)) eq #GL(2,GF(p)) then //this #G/#ChangeRing(G,Integers(m0 div p)) eq #GL(2,GF(p)) is implied by other two conditions
+            m0:=m0 div p;
+            G:=ChangeRing(G,Integers(m0));
+        end if;
+    end for;
+    return G,m0;
+end intrinsic;
+
+intrinsic VectorOrder(v::ModTupRngElt) -> RngIntElt
+    {Order of a vector with entries in Z/mZ}
+    m:=#Parent(v[1]);
+    g:=GCD([m, Integers()!v[2], Integers()!v[1]]);
+    return m div g;
+end intrinsic;
+
+intrinsic DegreesOfPoints(G::GrpMat) -> SeqEnum[RngIntElt]
+    {compute all degrees of points without doing Riemann-Roch}
+    m := Modulus(BaseRing(G));
+    H := sub<GL(2,Integers(m))|G,-G!1>;
+    orb := Orbits(H);
+    orbm := [#x div 2 : x in orb | VectorOrder(x[1]) eq m]; 
+    degrees := SetToSequence(Set(orbm)); //remove duplicates
+    return degrees;
+end intrinsic;
+
+//TODO: rename this function
[…]

### 2023-04-12 TeX/draft.tex
Updates from Overleaf

@@
   Let $m_0 = \prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$\;
-  \For{$\ell \in \{ \ell | m_0 \colon \ell_0 \text{ prime} \}$}{
-  \While{$\ell|m_0$ and $\#G/\#(G \pmod{m_0/p}) = p^4$}{
+  \For{$p \in \{ \ell | m_0 \colon \ell \text{ prime} \}$}{
+  \While{$p |m_0$ and $\#G/\#(G \pmod{m_0/p}) = p^4$}{
     $m_0 = m_0/p$\;
@@
   Filter the orbit representatives that have order equal to $N$\;
-  Compute the orbit sizes ``degrees'' $s$ such that $s/2 \geq g$\label{DivBy2}\;
+  Compute the orbit sizes $s$ and``degrees'' as $s/2$ \label{DivBy2}\;
   Remove duplicates\label{RemDup}\;

### 2023-04-12 TeX/draft.tex
Update draft to better reflect rewritten code

@@
 \newcommand{\abbey}[1]{\textcolor{blue}{Abbey: #1}}
-
+\newcommand{\dld}[1]{\textcolor{Plum}{dld: #1}}
 \newcommand{\sachi}[1]{\textcolor{purple}{Sachi: #1}}
@@
 
-\begin{theorem}[\cite{BELOV}]\label{BELOVthm}
-Let $E/\Q$ be a non-CM elliptic curve, and let $m$ be the product of 2, 3, and all primes $\ell$ where the $\ell$-adic Galois representation of $E$ is not surjective.
-Let $m_0$ be the level of the $m$-adic Galois representation associated to $E$ and let $f: X_1(n) \rightarrow X_1(\gcd(n,m_0))$ denote the natural map.
-If $x\in X_1(n)$ is an isolated point with $j(x)=j(E)$, then $f(x)\in X_1(\gcd(n,m_0))$ is an isolated point.
-\end{theorem}
-
 Using Zywina's algorithm for the level of the adelic Galois representation as a starting point, we may obtain the level of the $m$-adic Galois representation associated to $E$ as in Theorem \ref{BELOVthm}.
@@
 
-\section{Riemann-Roch}
+\section{Filtering by Level Mapping}
 
-\noindent \textbf{Input:} Output from step 2\\
-\textbf{Output:} Smaller list of pairs to check
+\begin{theorem}[\cite{BELOV}]\label{BELOVthm}
+Let $E/\Q$ be a non-CM elliptic curve, and let $m$ be the product of 2, 3, and all primes $\ell$ where the $\ell$-adic Galois representation of $E$ is not surjective.
+Let $m_0$ be the level of the $m$-adic Galois representation associated to $E$ and let $f: X_1(n) \rightarrow X_1(\gcd(n,m_0))$ denote the natural map.
+If $x\in X_1(n)$ is an isolated point with $j(x)=j(E)$, then $f(x)\in X_1(\gcd(n,m_0))$ is an isolated point.
+\end{theorem}
+
+\dld{This is \texttt{FilterByLevelMapping}, which used to be called
+\texttt{RefuteLevel}. It acts as a filter. We feed in a list, and the output is
+a (hopefully smaller) list guaranteed to contain all isolated points. If the
+list is empty, then we have shown that the curve doesn't give rise to an
+isolated point! If not, then perhaps other work is necessary.}
+
+\dld{I imagine other filters being potentially applied afterwards, each
+removing some set of non-isolated points.}
+
+\begin{algorithm}[H]\label{alg:level_mapping}
+  \KwIn{A list of pairs $(N, d)$ such that $E$ gives a nonCM point on $X_1(N)$
+  of degree $d$.}
+  \KwOut{A list of pairs $(N, d)$ containing all isolated points.}
+  (sketch)\;
+  create list of guaranteed nonisolated points using easy Riemann--Roch\;
+  filter potentially isolated points via Theorem~\ref{BELOVthm}\;
+  \Return{remaining $(N, d)$ pairs.}
+\end{algorithm}
+
+\dld{I collect the ingredients for use. The easy Riemann--Roch argument we use
+is from the following lemma. In principle, we could use any source of
+guaranteed nonisolated points.}
 
@@
 
-\section{Remaining Cases}
+\dld{For the filter, we apply (the contrapositive of) Theorem~\ref{BELOVthm}.
+We also use the degree of the natural map as in Proposition~2.2 of BELOV.}
+
+\section{Remaining Filters}
 \abbey{Filip? Abbey?}

### 2023-04-12 isolatedpoints.m

@@ -8,10 +8,10 @@ intrinsic ReducedLevel(G::GrpMat) -> GrpMat, RngIntElt
     {Level reduction from the output of Zywina's algorithm}
     m:=Modulus(BaseRing(G));
     NS:=Set(NonSurjectivePrimes(G));
-    sE:={2,3} join NS; 
+    sE:={2,3} join NS;
     m0:=&*[p^Valuation(m,p):p in sE];
     G:=ChangeRing(G,Integers(m0));
-    for p in PrimeFactors(m0) do 
+    for p in PrimeFactors(m0) do
         while Valuation(m0,p) gt 1 and #G/#ChangeRing(G,Integers(m0 div p)) eq p^4 do
             m0:=m0 div p;
             G:=ChangeRing(G,Integers(m0));
@@ -36,17 +36,16 @@ intrinsic DegreesOfPoints(G::GrpMat) -> SeqEnum[RngIntElt]
     m := Modulus(BaseRing(G));
     H := sub<GL(2,Integers(m))|G,-G!1>;
     orb := Orbits(H);
-    orbm := [#x div 2 : x in orb | VectorOrder(x[1]) eq m]; 
+    orbm := [#x div 2 : x in orb | VectorOrder(x[1]) eq m];
     degrees := SetToSequence(Set(orbm)); //remove duplicates
     return degrees;
 end intrinsic;
 
-//TODO: rename this function
-intrinsic RefuteLevel(allpts::SeqEnum[Tup]) -> SeqEnum[Tup]
-    {Refuting levels and degrees based on the level reduction theorem of BELOV.
+intrinsic FilterByLevelMapping(allpts::SeqEnum[Tup]) -> SeqEnum[Tup]
+    {Filtering levels and degrees based on the level reduction theorem of BELOV.
     If j is a sporadic point of degree d in level m then it becomes a point of
     d/deg(f) in level n where f:X1(m)-->X1(n) is the natural projection map.}
-   
+
     function easyRiemannRoch(listofpts)
         potisolated := [];
         for pt in listofpts do
@@ -63,8 +62,8 @@ intrinsic RefuteLevel(allpts::SeqEnum[Tup]) -> SeqEnum[Tup]
     nonisolated := SequenceToSet(allpts) diff SequenceToSet(potisolated);
 
     remove := {};
-    for x in potisolated do //<l, deg> a point of degree deg on X1(l) 
-        for y in nonisolated do 
+    for x in potisolated do //<l, deg> a point of degree deg on X1(l)
[…]

### 2023-04-19 TeX/draft.tex
Updates from Overleaf

@@
 \section{Proving that a point is not sporadic}
+The following algorithm is the main procedure for determining a $j$-invariant is not sporadic. It gives an overview of the structure.
 
-\begin{algorithm}
-\KwIn{A non-CM $j$-invariant $j = j(E) \in \Q$.}
-\KwOut{\textsc{False} if $j$ is not a sporadic $j$-invariant.
-\abbey{Update: Finite list of curves, degrees such that any isolated point on $X_1(n)$ associated to $E$ maps down under the natural projection map to a point in this list.
-If empty, $j$ is not isolated.)}}
+\begin{algorithm}[h!]
+\caption{Main Algorithm}\label{alg:mainalgorithm}
+\KwIn{A non-CM $j$-invariant $j = j(E) \in \Q$ and $a$-invariants for $E$ with $j$-invariant $j$.}
+\KwOut{Finite list of pairs $(n,d)$ such that any isolated point on $X_1(n)$ associated to $E$ maps down under the natural projection map to a point of degree $d$ in this list.
+\sachi{is this better?} \abbey{Don't we mean ``Finite list of pairs $(n_i,d_i)$ such that any isolated point on $X_1(n)$ associated to $E$ maps down under the natural projection map to a point of degree $d_i$ on $X_1(n_i)$ for some $n_i \mid n$ and $(n_i,d_i)$ in this list.
+But maybe with better notation.}}
 Compute the adelic image $G$ of $E/\Q$ as a subgroup of $\GL_2(\hat{\Z})$ using Zywina's algorithm. Represent the output as some \emph{level} $N$ together with a subgroup $G$ of $\GL_2(\Z/N\Z)$\;
-Reduce level\;
-For all $12 < b \mid N$, using Algorithm~\ref{alg:compute_degree} compute the minimum degree of the field of definition of a point with respect to $G \mod b$, the image of $G$ in $\GL_2(\Z/b\Z)$\;
-\Return{?} \;
+Using Algorithm \ref{alg:reduce_level}, reduce the level to $G, m_0$\; 
+Define $L \colonequals \{\}$\;
+\For{all $12 < b \mid m_0$}{
+Using Algorithm~\ref{alg:compute_degree} compute the set $D$ of degrees of all fields of definition of a point with respect to $G \mod b$, the image of $G$ in $\GL_2(\Z/b\Z)$\;
+Set $L \colonequals L \cup \{ (b, d) : d \in D\}$ \;}
+Using Algorithm \ref{alg:level_mapping} filter the list $L$ to obtain a refined list $L'$\;
+\Return{the list $L'$ } \;
     %\filip{We need to look at the orbits of $\langle G, -G \rangle \mod b$ on $(\Z/b\Z)^2$, not $\bP^1(\Z/b\Z)$.
@@
 \end{algorithm}
+
+\begin{theorem}
+ Algorithm \ref{alg:mainalgorithm} is correct. 
+\end{theorem}
+\begin{corollary}
+If Algorithm \ref{alg:mainalgorithm} outputs an empty set on some $j$-invariant $j = j(E)$ and $a$-invariants $a$ for $E$, then $j$ is not a  $\mathbf{P}^1$-isolated point on $X_1(N)$.
+\end{corollary}
+\abbey{Zywina said the results returned from his adelic image algrithm are guaranteed to be correct and that ``errors will always occur if $E$ gives rise to an unknown exceptional rational point on certain high genus modular curves." Since an error in his algorithm will result in an error in our algorithm, I don't know what should be said about this in our writeup.} \sachi{maybe the easiest thing is just to add a remark saying that the results are guaranteed to be correct, and getting an error instead of a result is possible but that we did not encounter it?}
 
@@
   \label{alg:reduce_level}
-  Let $N_E = \{\ell|N \text{ prime} \colon \rho_{E,\ell} \text{ is non-surjective} \}$\;
+  Let $P_E = \{\ell|N \text{ prime} \colon \rho_{E,\ell} \text{ is non-surjective} \}$\;
   Let $S_E= N_E \cup \{ 2, 3\}$\;
@@
   }
-  \If{not $p$ in $N_E$ and $\ord_p(m_0) = 1$ and $\#G/\#(G \pmod{m_0/p}) = \#\GL_2(\Z/p\Z)$}{
+  \If{not $p$ in $P_E$ and $\ord_p(m_0) = 1$ and $\#G/\#(G \pmod{m_0/p}) = \#\GL_2(\Z/p\Z)$}{
   $m_0 = m_0/p$\;
@@
 
-\noindent \textbf{Input:} $\mathcal{I}_1$ from step 1 \\
-\textbf{Output:} For each $d \in \mathcal{I}_1$, compute degree(s) of closed point on $X_1(N)$ associated to $E$. Return ??? \abbey{update algorithm description}
+The following algorithm computes the degrees of closed points on $X_1(N)$ associated to $E$.
 
-\begin{algorithm}[H]\label{alg:compute_degree}
-  \KwIn{$G\subseteq \GL_2(\Z/N\Z)$ such that $\im\rho_E=\pi^{-1}(G)$ and $N$ is the level; a bound $g \in \Z$}
-  \KwOut{all degrees of $x$-coordinates of points that are $\geq g$}
+% \noindent \textbf{Input:} $\mathcal{I}_1$ from step 1 \\
+% \textbf{Output:} For each $d \in \mathcal{I}_1$, compute degree(s) of closed point on $X_1(N)$ associated to $E$. Return ??? \abbey{update algorithm description}
+
+\begin{algorithm}[H] \caption{Compute Degree}\label{alg:compute_degree}
+  \KwIn{$G\subseteq \GL_2(\Z/N\Z)$ such that $\im\rho_E=\pi^{-1}(G)$ and $N$ is the level}
+  \KwOut{all degrees of $x$-coordinates of points}
   Let $H \colonequals \langle G, -I_2\rangle \leq \GL_2(\Z/N\Z)$\;
   Compute the orbits of $H$ acting on $(\Z/N\Z)^2$\label{Inc-1}\;
-  Filter the orbit representatives that have order equal to $N$\;
+  Filter the orbit representatives for orbits that have order equal to $N$\;
   Compute the orbit sizes $s$ and``degrees'' as $s/2$ \label{DivBy2}\;
@@
 \begin{proof}
-    We begin by noting that $(E, P)$ and $(E, -P)$ denote the same point on $X_1(N)$, for $P \in E[N]$. Therefore, the degree of
+    We begin by noting that $(E, P)$ and $(E, -P)$ \abbey{induce the same closed} point on $X_1(N)$, for $P \in E[N]$. Therefore, the degree of
     a point represented by $(E, P)$, when
@@
 
-\begin{algorithm}[H]\label{alg:level_mapping}
+\begin{algorithm}[H]\caption{Filter by Level Mapping}\label{alg:level_mapping}
   \KwIn{A list of pairs $(N, d)$ such that $E$ gives a nonCM point on $X_1(N)$
@@
 
-\section{Genus 0 adelic images do not produce isolated points}
+\section{Genus 0 adelic images do not produce sporadic points}
 

### 2023-04-20 isolatedpoints.m
Correct easy Riemann Roch

@@ -47,19 +47,19 @@ intrinsic FilterByLevelMapping(allpts::SeqEnum[Tup]) -> SeqEnum[Tup]
     d/deg(f) in level n where f:X1(m)-->X1(n) is the natural projection map.}
 
     function easyRiemannRoch(listofpts)
-        potisolated := [];
+        nonisolated := [];
         for pt in listofpts do
             l, deg := Explode(pt);
             genusGamma1lplus1 := Genus(Gamma1(l))+1;
             if deg ge genusGamma1lplus1 then
-                Append(~potisolated, <l, deg>); //"easy" Riemann--Roch condition
+                Append(~nonisolated, <l, deg>); //"easy" Riemann--Roch condition
             end if;
         end for;
-        return potisolated;
+        return nonisolated;
     end function;
 
-    potisolated := easyRiemannRoch(allpts);
-    nonisolated := SequenceToSet(allpts) diff SequenceToSet(potisolated);
+    nonisolated := easyRiemannRoch(allpts);
+    potisolated := SequenceToSet(allpts) diff SequenceToSet(nonisolated);
 
     remove := {};
     for x in potisolated do //<l, deg> a point of degree deg on X1(l)

### 2023-04-25 TeX/draft.tex
Updates from Overleaf

@@
 
-% For pretty hyperlinks
-\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
+% For pretty hyperlinks (I changed this because I cannot see what is a ref/link and what is not, sorry! - Sachi)
+\definecolor{darkblue}{rgb}{0.0,0.0,1}
 \hypersetup{colorlinks,breaklinks,
@@
 \newcommand{\sachi}[1]{\textcolor{purple}{Sachi: #1}}
+\newcommand{\timo}[1]{\textcolor{red}{Timo: #1}}
 % \newcommand{\travis}[1]{\textcolor{chartreuse}{Travis: #1}}
@@
 \begin{enumerate}
-\item If $x$ is $\mathbb{P}^1$-isolated, then $f(x)$ is $\mathbb{P}^1$-isolated.
+\item If $x$ is $\mathbf{P}^1$-isolated, then $f(x)$ is $\mathbf{P}^1$-isolated.
 \item If $x$ is AV-isolated, then $f(x)$ is AV-isolated.
@@
 \KwIn{A non-CM $j$-invariant $j = j(E) \in \Q$ and $a$-invariants for $E$ with $j$-invariant $j$.}
-\KwOut{Finite list of pairs $(n,d)$ such that any isolated point on $X_1(n)$ associated to $E$ maps down under the natural projection map to a point of degree $d$ in this list.
-\sachi{is this better?} \abbey{Don't we mean ``Finite list of pairs $(n_i,d_i)$ such that any isolated point on $X_1(n)$ associated to $E$ maps down under the natural projection map to a point of degree $d_i$ on $X_1(n_i)$ for some $n_i \mid n$ and $(n_i,d_i)$ in this list.
-But maybe with better notation.}}
+\KwOut{Finite list of pairs $(n,d)$ such that any isolated point on $X_1(N)$ associated to $E$ maps down under the natural projection map to an isolated point of degree $d$ on $X_1(n)$ in the list. }
 Compute the adelic image $G$ of $E/\Q$ as a subgroup of $\GL_2(\hat{\Z})$ using Zywina's algorithm. Represent the output as some \emph{level} $N$ together with a subgroup $G$ of $\GL_2(\Z/N\Z)$\;
@@
 \end{corollary}
-\abbey{Zywina said the results returned from his adelic image algrithm are guaranteed to be correct and that ``errors will always occur if $E$ gives rise to an unknown exceptional rational point on certain high genus modular curves." Since an error in his algorithm will result in an error in our algorithm, I don't know what should be said about this in our writeup.} \sachi{maybe the easiest thing is just to add a remark saying that the results are guaranteed to be correct, and getting an error instead of a result is possible but that we did not encounter it?}
+\abbey{Zywina said the results returned from his adelic image algrithm are guaranteed to be correct and that ``errors will always occur if $E$ gives rise to an unknown exceptional rational point on certain high genus modular curves." Since an error in his algorithm will result in an error in our algorithm, I don't know what should be said about this in our writeup.} \sachi{maybe the easiest thing is just to add a remark saying that the results are guaranteed to be correct, and getting an error instead of a result is possible but that we did not encounter it?} \timo{I second that.} \abbey{alternatively, separate Zywina's algorithm from ours in this paper}
 
@@
   \KwIn{$G\subseteq \GL_2(\Z/N\Z)$ such that $\im\rho_E=\pi^{-1}(G)$ and $N$ is the level}
-  \KwOut{$G\subseteq \GL_2(\Z/m_0\Z)$ such that $G=\im\rho_{E,m_0}$ and $\im\rho_{E,m^{\infty}}=\pi^{-1}(\im\rho_{E,m_0})$ where $m$ is the product of the non-surjective primes and $2$ and $3$ (if they do not already divide $m$), and $m_0$ is minimal \abbey{Don't we need to include 2 and 3 in our definition of $m$?
-It is possible 2 and 3 may divide $m_0$ even if they are not surjective primes.
-If they are not necessary, then 2 and 3 need not divide $m_0$ in the final output.} }
+  \KwOut{$G\subseteq \GL_2(\Z/m_0\Z)$ such that $G=\im\rho_{E,m_0}$ and $\im\rho_{E,m^{\infty}}=\pi^{-1}(\im\rho_{E,m_0})$ where $m$ is the product of the non-surjective primes and $2$ and $3$ (if they do not already divide $m$), and $m_0$ is minimal }
   \caption{Reduce level}%
@@
   Let $P_E = \{\ell|N \text{ prime} \colon \rho_{E,\ell} \text{ is non-surjective} \}$\;
-  Let $S_E= N_E \cup \{ 2, 3\}$\;
+  Let $S_E= P_E \cup \{ 2, 3\}$\;
   Let $m_0 = \prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$\;
@@
 
-\section{Compute Degree}
+\abbey{give example}
+
+\section{Compute Degrees}
 
@@
   Filter the orbit representatives for orbits that have order equal to $N$\;
-  Compute the orbit sizes $s$ and``degrees'' as $s/2$ \label{DivBy2}\;
+  Compute the orbit sizes $s$ and ``degrees'' as $s/2$ \label{DivBy2}\;
   Remove duplicates\label{RemDup}\;
@@
 \begin{algorithm}[H]\caption{Filter by Level Mapping}\label{alg:level_mapping}
-  \KwIn{A list of pairs $(N, d)$ such that $E$ gives a nonCM point on $X_1(N)$
+  \KwIn{A list of pairs $(N, d)$ such that $E$ gives a non-CM point on $X_1(N)$
   of degree $d$.}
@@
 
+\abbey{give example}
+
 \begin{lemma}
@@
 \begin{proof}
-This is Lemma 13 in revision of B., Gill, Rouse, Watson.
+This is Lemma 13 in revision of B., Gill, Rouse, Watson. \cite{OddDeg}
 \end{proof}

### 2023-04-26 isolatedpoints.m
code fixes, test data set

@@ -73,7 +73,6 @@ intrinsic FilterByLevelMapping(allpts::SeqEnum[Tup]) -> SeqEnum[Tup]
     end for;
     //See https://arxiv.org/pdf/1808.04520.pdf Prop 2.2
 
-    potisolated := SequenceToSet(potisolated);
     potisolated := potisolated diff remove; //the remaining potentially isolated
 
     return potisolated;
@@ -81,8 +80,12 @@ intrinsic FilterByLevelMapping(allpts::SeqEnum[Tup]) -> SeqEnum[Tup]
 end intrinsic;
 
 
-intrinsic NotIsolated(a::SeqEnum[RngIntElt], j::MonStgElt, path::Assoc) -> List
+intrinsic NotIsolated(j::FldRatElt, path::Assoc: a:=[]) -> List
     {main function to check if a j invariant is sporadic}
+    if #a eq 0 then
+        a := [1,0,0,-36/(j-1728),-1/(j-1728)];
+        assert jInvariant(EllipticCurve(a)) eq j;
+    end if;
     E:=EllipticCurve(a);
     G,n,S:=FindOpenImage(path, E);
     G0:=ReducedLevel(G);
@@ -102,9 +105,9 @@ intrinsic NotIsolated(a::SeqEnum[RngIntElt], j::MonStgElt, path::Assoc) -> List
     potisolated := FilterByLevelMapping(allpoints);
 
     if #potisolated gt 0 then
-        return [*j, a, false, potisolated*];
+        return [*Sprint(j), false, potisolated*];
     else
-        return [*j, a, true, potisolated*];
+        return [*Sprint(j), true, potisolated*];
     end if;
 
 end intrinsic;

### 2023-04-26 testalvaro.m

@@ -1,0 +1,11 @@
+AttachSpec("/Users/sachihashimoto/repos/ModularCurves/equations/equations.spec");                                                      
+path := OpenImageContext("/Users/sachihashimoto/repos/ModularCurves/equations/OpenImage/data-files");                                                                           
+AttachSpec("isolated.spec");
+
+
+inputs := Split(Read("alvarodata.txt"), "\n");
+for  input in inputs do
+    jinv := Rationals()!(eval input);
+    output := NotIsolated(jinv, path);
+    print Join([Sprint(elt) : elt in output], ":");
+end for;

### 2023-04-28 isolatedpoints.m
update reducedlevel

@@ -4,7 +4,7 @@ intrinsic NonSurjectivePrimes(G::GrpMat) -> SeqEnum[RngIntElt]
         return [p:p in PrimeFactors(m)|#ChangeRing(G,GF(p)) ne #GL(2,GF(p))];
 end intrinsic;
 
-intrinsic ReducedLevel(G::GrpMat) -> GrpMat, RngIntElt
+intrinsic ReducedLevel(G::GrpMat) -> RngIntElt
     {Level reduction from the output of Zywina's algorithm}
     m:=Modulus(BaseRing(G));
     NS:=Set(NonSurjectivePrimes(G));
@@ -16,12 +16,15 @@ intrinsic ReducedLevel(G::GrpMat) -> GrpMat, RngIntElt
             m0:=m0 div p;
             G:=ChangeRing(G,Integers(m0));
         end while;
-        if not p in NS and Valuation(m0,p) eq 1 and #G/#ChangeRing(G,Integers(m0 div p)) eq #GL(2,GF(p)) then //this #G/#ChangeRing(G,Integers(m0 div p)) eq #GL(2,GF(p)) is implied by other two conditions
-            m0:=m0 div p;
-            G:=ChangeRing(G,Integers(m0));
+        if not p in NS and Valuation(m0,p) eq 1 then
+            if m0 eq p and #G eq #GL(2,GF(p)) then
+                return 1;
+            elif #G/#ChangeRing(G,Integers(m0 div p)) eq #GL(2,GF(p)) then 
+                m0:=m0 div p;
+            end if;
         end if;
     end for;
-    return G,m0;
+    return m0;
 end intrinsic;
 
 intrinsic VectorOrder(v::ModTupRngElt) -> RngIntElt
@@ -88,7 +91,13 @@ intrinsic NotIsolated(j::FldRatElt, path::Assoc: a:=[]) -> List
     end if;
     E:=EllipticCurve(a);
     G,n,S:=FindOpenImage(path, E);
-    G0:=ReducedLevel(G);
+    m0:=ReducedLevel(G);
+    
+    if m0 eq 1 then
+        return [*Sprint(j), true, {}*];
+    end if;
+
+    G0:=ChangeRing(G,Integers(m0));
     G0t := sub<GL(2,Integers(#BaseRing(G0))) | [Transpose(g):g in Generators(G0)]>;
     k:=#BaseRing(G0t);
 

### 2023-04-28 extrafilters.m
upload code from Filip

@@ -1,0 +1,85 @@
+//Special cases / more filters
+
+
+function mptoP1(Z);
+    j:=0;
+    k:=0;
+    N:=[];
+    for i:=1 to #Z do
+        add:=true;
+        B:=SetToSequence(Z[i,4]);
+        m,t:=Min([a[1]: a in B]);
+        E:=EllipticCurve(Z[i,1]);
+        G:=FindOpenImage(E);
+        G0:=ChangeRing(G,Integers(m));
+        if GL2Genus(G0) eq 0 then
+            Gx:=GL2Borel1(BaseRing(G0));
+            G1:=sub<GL(2,BaseRing(G0))|Gx,-Gx!1>;
+            G0:=sub<GL(2,BaseRing(G0))|G0,-G0!1>;
+             if IsConjugateSubgroup(GL(2,BaseRing(G0)), G0, G1) then
+                print "Degree of the map to P1 is:", #G0 div #G1;
+                print "While the input is:", B[t];
+                print "";
+                j:=j+1;
+                add:=false;
+            else
+                check_el:=false;
+                S:=Conjugates(GL(2,BaseRing(G0)),G1);
+                for a in S do
+                    Gb:=sub<GL(2,BaseRing(G0))|Generators(a) join Generators(G0)>;
+                    tr, g:=IsConjugateSubgroup(GL(2,BaseRing(G0)),Gb,G1);
+                    assert tr;
+                    if (#Gb div #G1) eq  B[t,2] then
+                        print "We have obtained an element we can eliminate!";
+                        check_el:=true;
+                        print "Degree of the map to P1 is:", #Gb div #G1;
+                        print "While the input is:", B[t];
+                        print "";
+                    add:=false;
+                    end if;
+                end for;
+                if check_el then k:=k+1; end if;
+            end if;
+        end if;
+    if add then N:=Append(N,Z[i]); end if;
+    end for;
+    j;
+    k;
+    return N;
+end function;
+
+
+function gen1cases(Z);
+    N:=[];
+    for i:=1 to #Z do
+        add:=true;
+        B:=SetToSequence(Z[i,4]);
+        m,t:=Min([a[1]: a in B]);
+        E:=EllipticCurve(Z[i,1]);
+        G:=FindOpenImage(E);
+        G0:=ChangeRing(G,Integers(m));
+        if GL2Genus(G0) eq 1 then
[…]

### 2023-05-18 TeX/draft.tex
Updates from Overleaf

@@
 % We ain't got no time for eq. nums. on the left
+\usepackage{soul}%added for \st
 
@@
 \usepackage{graphics}
+%\usepackage{ulem}
 \usepackage{hyperref}
+\usepackage{cleveref}
 \usepackage[usenames, dvipsnames]{xcolor}
@@
 \newcommand{\Q}{\bQ}
+\newcommand{\C}{\bC}
 \newcommand{\Z}{\bZ}
-\newcommand{\PP}{\mathbb P}
-\newcommand{\filip}[1]{{\color{cyan} \textsf{$\sun\sun\sun$ Filip: [#1]}}}
+\newcommand{\PP}{\mathbf P}
+\newcommand{\Jac}{\operatorname{Jac}}
+\newcommand{\proj}{\operatorname{proj}}
+
 \newcommand{\davidnote}[1]{\textcolor{Plum}{David: #1}}
-
+\newcommand{\filip}[1]{{\textcolor{cyan}{Filip: [#1]}}}
 \newcommand{\abbey}[1]{\textcolor{blue}{Abbey: #1}}
@@
 \newcommand{\timo}[1]{\textcolor{red}{Timo: #1}}
-% \newcommand{\travis}[1]{\textcolor{chartreuse}{Travis: #1}}
-
+\newcommand{\travis}[1]{\textcolor{orange}{Travis: #1}}
+\newcommand{\abedit}[1]{{\color{blue} #1}}
+\newcommand{\fedit}[1]{{\color{cyan} #1}}
 % Don't have subsections appear in TOC
@@
 
-\title{Towards a Classification of Sporadic $j$-invariants}
+\title{Towards a Classification of Isolated $j$-invariants}
 \input{author_info.tex}
@@
 \begin{document}
-\begin{abstract}
+\begin{abstract} \abbey{will update once we re-run the code}
 We develop an algorithm to test whether a non-CM elliptic curve $E/\Q$ gives rise to a sporadic point of any degree on any modular curve of the form $X_1(N)$.
 This builds on prior work of Zywina which gives a method for computing the image of the adelic Galois representation associated to $E$.
-Running this algorithm on all elliptic curves presetly in the LMFDB yields strong evidence for the fact that $E$ gives rise to a sporadic point if and only if $j(E)=-140625/8$ or $-9317$.
+Running this algorithm on all elliptic curves presetly in the LMFDB yields strong evidence for the conjecture that $E$ gives rise to a sporadic point if and only if $j(E)=-140625/8$ or $-9317$.
     \end{abstract}
 \maketitle
+\abbey{will update once we re-run the code}
 
@@
 We are interested in studying \textbf{sporadic} points $x \in X_1(N)$, which are points for which there are only finitely many points on $X_1(N)$ of degree at most $\deg(x)$.
-Hence a non-cuspidal sporadic point corresponds to an elliptic curve with a point of order $N$ in ``usually low degree." Elliptic curves with complex multiplication (CM) provide many natural examples of sporadic points, as the extra endomorphisms of a CM elliptic curve give constraints on the size of the image of the associated Galois representation.
+Hence a non-cuspidal sporadic point corresponds to an elliptic curve with a point of order $N$ in ``unusually low degree." Elliptic curves with complex multiplication (CM) provide many natural examples of sporadic points, as the extra endomorphisms of a CM elliptic curve give constraints on the size of the image of the associated Galois representation.
 Indeed, there exist sporadic CM points on $X_1(N)$ for all $N\geq 721$; see \cite[Theorem 8.2]{CGPS2022}.
@@
 
+\section*{Acknowledgments}
+We thank Pete Clark, Jeremy Rouse, and David Zureick-Brown for helpful conversations.
+
 \section{Background}
+\subsection{Isolated Points on Curves}
+Let $C$ be a curve, by which we will mean a nonsingular projective geometrically integral 1-dimensional scheme defined over a number field $k$; we suppose all curves satisfy these assumptions throughout the paper.
+To streamline our exposition, we assume $P_0 \in C(k)$, but this is not required; see \cite[$\S4$]{BELOV}.
+Throughout, we consider closed points of the curve $C$, which correspond to $\Gal_k$-orbits of points in $C(\overline{k})$.
+The degree of $x$ is defined to be the degree of the residue field $k(x)$ over $k$, or alternatively, to be the length of the $\Gal_k$-orbit of points in $C(\overline{k})$ corresponding to $x$.
 
+To any closed point $x \in C$ of degree $d$ we associate the $k$-rational effective divisor 
+\[
+ x=P_1+ \cdots +P_{d},
+\]
+where $P_1, \dots, P_{d}$ are the points in the $\Gal_{k}$-orbit associated to $x$.
+With this identification, we can study the image of $x$ under the natural map from the $d$th symmetric power of $C$ to the curve's Jacobian
+\[
+\Phi_d: C^{(d)} \rightarrow \Jac(C)
+\]
+which sends the effective divisor $D$ of degree $d$ to the class $[D - dP_0]$, where $P_0 \in C(k)$.
+If $\Phi_d(x)=\Phi_d(y)$ for some other point $y \in C^{(d)}(k)$, then there exists a non-constant function $f \in k(C)^{\times}$ with $\text{div}(f)=x-y$.
+Since $x$ is a degree $d$ point and $x\not=y$, $x$ and $y$ have distinct support so $f: C \rightarrow \mathbb{P}^1_{k}$ is a dominant morphism of degree $d$.\footnote{In particular, this shows $\Phi_d$ is injective if $d$ is less than the $k$-gonality of $C$, which is the least degree of a non-constant rational map to $\mathbb{P}^1$.} By Hilbert's irreducibility theorem \cite[Chapter 9]{serre97}, $f^{-1}(\mathbb{P}^{1}(k))$ will contain infinitely many closed points of degree $d$.
+On the other hand, if $\Phi_d$ is injective on closed points of degree $d$, then by Faltings' Theorem \cite{faltings} there can exist infinitely many such points only if all but finitely many are parametrized by translates of positive rank abelian subvarieties of $\Jac(C)$.
+This inspires the following:
+
+\begin{definition} Let $C$ be a curve defined over a number field $k$.
+\begin{enumerate}
+\item []
+\item A closed point $x \in C$ of degree $d$ is $\PP^1$\textbf{-parametrized} if there exists a point $x' \in C^{(d)}(k)$ such that $\Phi_d(x)=\Phi_d(x')$.
+\item A closed point $x \in C$ of degree $d$ is \textbf{AV-parametrized} if there exists a positive rank abelian subvariety $A/k$ with  $A \subset \Jac(C)$ such that $\Phi_d(x)+A \subset \im(\Phi_d)$.
+\item A closed point $x \in C$ of degree $d$ is \textbf{isolated} if it is neither $\mathbb{P}^1$-parametrized nor AV-parametrized.
+\item A closed point $x \in C$ of degree $d$ is \textbf{sporadic} if there are only finitely many closed points of $C$ of degree at most $\deg(x)$.
+\end{enumerate}
+\end{definition}
+
+If $C$ has genus $g\geq 2$, then the collection of all points on $C$ with coordinates in $k$ is finite by Faltings's theorem \cite{faltings83}.
+In general, the set $C(k)$ sits inside a larger finite set of points, namely, the set of all isolated points of $C$.
+    \begin{theorem}[{Bourdon, Ejder, Liu, Odumodu, Viray, \cite[Theorem 4.2]{BELOV}}]\label{thm:FiniteIsolated}
+        Let $C$ be a curve over a number field.
+        \begin{enumerate}
+            \item There are infinitely many degree $d$ points on $C$ if and only if there is a degree $d$ point on $C$ that is \emph{not} isolated.
+            \item There are only finitely many isolated points on $C$.
+        \end{enumerate}
+    \end{theorem}
+It follows from Theorem \ref{thm:FiniteIsolated} that every sporadic point is isolated, but the converse need not hold.
+
+\subsection{Modular Curves}
+For any subgroup $H \leq \GL_2(\Z/N\Z)$, we define the modular curve $X_H$ to be the coarse space of the stack $\mathcal{M}_H$, as defined in Deligne--Rapoport \cite{DR}.
+\abbey{Describe interpretation of $K$-rational points.} The curve $X_H$ is a scheme over $\text{Spec }\Z[1/N]$ and parametrises generalized elliptic curves with $H$-level structure.
+See, for example, \cite[$\S2.3$]{RSZB2022} for details.
+In particular, if we take
+\[
+B_1(N) =\left\{ \begin{pmatrix}
+1 & * \\
+0 & *
+\end{pmatrix} \right \} \leq \GL_2(\Z/N\Z),
+\]
+then $X_{B_1(N)}=X_1(N)$, the modular curve whose noncuspidal points parametrize  elliptic curves with a distinguished point of order $N$.
+There is an analytic isomorphism between $X_1(N)(\mathbb{C})$ and the Riemann surface constructed as a quotient of the extended upper-half plane by the congruence subgroup
+\[
+\Gamma_1(N) \coloneqq\left\{ \begin{pmatrix}
+a & b \\
+c & d 
+\end{pmatrix} \in \SL_2(\Z) \, : \, c \equiv 0 \pmod{N} \text{ and } a \equiv d \equiv 1 \pmod{N} \right \}, 
+\]
+with matrices acting via linear fractional transformations.
+If $N \geq 4$, then $\mathcal{M}_{B_1(N)}$ is its own coarse moduli space, and so noncuspidal $k$-rational points of $X_1(N)$ classify pairs $(E,P)$, where $E/k$ is an elliptic curve and $P\in E(k)$, up to $k$-isomorphism.
+\abbey{I decided not to define the modular curve by its moduli problem as in \cite[$\S2$]{RouseDZB}, since the construction yields a stack in general...
+so it seems confusing to call it a modular *curve*.
+I've opted to go with the conventions of \cite[$\S2.3$]{RSZB2022}.}
+
+\abbey{maybe define $X_G$ for general open subgroup $G \leq \GL_2(\widehat{\Z})$ here instead of in later section on maps between modular curves}
+
+\subsection{Closed Points on Modular Curves} To discuss isolated points on modular curves, we must consider closed points on $X_1(N)$, viewed always as a scheme over $\Q$.
+\fedit{Let $k$ be a number field and fix an embedding of $k$ into $\overline \Q$}.
+Given an elliptic curve $E/k$ with $P \in E(k)$ of order $N$, the pair $(E,P)$ induces a $k$-valued point on $X_1(N)$ via the moduli interpretation described above.
+We denote this $k$-valued point by $(E,P)_k$.
+%\abedit{and it corresponds to a morphism of $\Q$-schemes from $\text{Spec } k$ to $X_1(N)$.
+\fedit{The $\Gal_\Q$-orbit of $(E,P)_k$ corresponds bijectively to a closed point on $X_1(N)$ over $\Q$, and we call this the \textbf{closed point} $x \in X_1(N)$} associated to $(E,P)$ \abbey{I much prefer the earlier definition -- the bijection of closed points with Galois orbits is something that requires proof, whereas what I wrote originally comes directly from the definition of $k$-valued point, i.e, a morphism from $\text{Spec }k$ to $X$.
+This makes me disagree with your later edits to this section.} \filip{I think the bijection is obvious and can in any case easily be cited, e.g.
+from \cite[Proposition 2.4.6]{Poonen_RPV} and makes everything clearer.
+But if you insist, feel free to revert to what you previously wrote},  and we define the \textbf{degree} of $x$ to be the degree of the residue field $\Q(x)$ over $\Q$.
+
+We note in particular that $\deg(x)$ may be strictly less than the degree of $k$.
+However, there always exists $E'/\Q(x)$ with $j(E')=j(E)$ and $P' \in E'(\Q(x))$, where the point $P' \in E'$ maps to $P \in E$ under a $\overline \Q$-isomoprhism sending $E$ to $E'$.
+See \cite[p.
+274, Proposition VI.3.2]{DR}.
+\fedit{The pair $(E',P')$ gives a $\Q(x)$-valued point \st{associated to the closed point $x$}, and it is the unique $\Q(x)$-valued point such that $(E,P)_{k}=(E',P')_{k}.$}
+
+In applications where such a property is important, it is sometimes useful to work with the \textbf{geometric point} associated to $(E,P)$, which we define to be the point $(E,P)_{\overline{\Q}}$.
+Note $(E,P)_{\overline{\Q}}$ induces the same closed point as $(E,P)_k$.
+
+Let $E/k$ be an elliptic curve and $P \in E(k)$ a point of order $N$.
+Note that for any $\xi \in \Aut(E)$, the pair $(E,\xi P)$ induces the same closed point $x \in X_1(N)$, since $\xi$ provides the necessary isomorphism.\footnote{ \abbey{Add footnote about connection with $X_{\pm B_1(N)}$.
+``If you take the moduli space of the set of closed points associated to pairs $(E,P)$ as above, you in fact get exactly $X_{\pm B_1(N)}$ (i.e the moduli functor will correspond exactly to this)!" Does this still hold for $j=0,1728$?}} This can be used to obtain a more explicit description of the residue field $\Q(x)$.
+
+\begin{lemma}\label{ResidueFieldLemma}
+Let $E$ be an elliptic curve defined over $\Q(j(E))$, and let $P \in E$ be a point of order $N$. Then the residue field of the closed point $x \in X_1(N)$ associated to $(E,P)$ is given by
+\[
+\Q(x)=\Q(j(E),\mathfrak{h}(P)),
+\]
+where $\mathfrak{h} \rightarrow E/\Aut(E) \cong \mathbb{P}^1$ is a Weber function for $E$. \abbey{Need to clarify statement to match conventions about $k$-valued pts/closed points}
+\end{lemma}
+
+\begin{proof}
+See, for example, \cite[Lemma 2.5]{OddDegQCurve}. 
+\end{proof}
+
+\begin{remark} In particular, if $E/\Q(j(E))$ does not have complex multiplication and $P=(x_0,y_0)$, then one can take $\Q(x)=\Q(j(E),x_0)$. See \cite[p. 107]{shimura}.
+\end{remark}
+\begin{example}
+Let $E_1:y^2+xy+y=x^3-x^2-3x+3$ and $P_1=(-1,2)$ a point of order 7.
+Then $(E_1,P_1)$ gives a $\Q$-valued point on $X_1(7)/\Q$ and also a closed point $x\in X_1(7)$ of degree 1.
+On the other hand, let $E_2:y^2=x^3-43x-166$ and $P_2=(5,i\sqrt{256})$ a point of order 7.
+Then $(E_2,P_2)$ gives a $\Q(i)$-valued point on $X_1(7)/\Q$ and also a closed point $x\in X_1(7)$ of degree 1 by Lemma \ref{ResidueFieldLemma} \abedit{since $\Aut(E) = \{\pm1\}$}.
+In fact, both $(E_1,P_1)$ and $(E_2,P_2)$ induce the same geometric point on $X_1(7)$ since $(E_1,P_1)_{\overline{\Q}}=(E_2,P_2)_{\overline{\Q}}$.
+One could alternatively compute the Kubert-Tate normal form associated to $E_2/\Q(i)$, with $P_2=(5,i\sqrt{256})$:
+\[E_3: y^2-xy-4y=x^3-4x^2,\, \, P_3=(0,0).
+\]
+We can check that $(E_1,P_1)_{\Q}=(E_3,P_3)_{\Q}$ and $(E_2,P_2)_{\Q(i)} =(E_3,P_3)_{\Q(i)}$.
+Thus it is fair to say that $(E_2,P_2)$ induces a $\Q$-valued point, even though it is not itself a $\Q$-valued point.
+\end{example}
+
+\begin{example}
+The distinction between closed points and geometric points can be seen when counting the number of points of a particular degree.
+For example, let $E$ be the elliptic curve with LMFDB label \href{https://www.lmfdb.org/EllipticCurve/Q/162/c/3}{162.c3}.
+Then $E$ possesses a unique $\Q$-rational subgroup of order 21 with generator $P$.
+For each $a \in (\Z/21\Z)^{\times}$, we consider the geometric point on $X_1(21)$ associated to $(E,aP)$.
+Since $(E,aP)_{\overline{\Q}}=(E,-aP)_{\overline{\Q}}$, we find there are six distinct geometric points corresponding to $(E,aP)$ for $a \in (\Z/21\Z)^{\times}$.
+However, these six $\overline{\Q}$-points lie in two Galois orbits, each of size 3.
+Thus we would say there are two closed points of degree 3, and the cardinality of the Galois orbit equals the degree.
+\end{example}
+
+%\begin{example}
+%\emph{To add; could also talk about $f^*(j(E))$}
+%\end{example}
+
+\subsection{Maps Between Modular Curves} We say an open subgroup $G$ of $\GL_2(\widehat{\Z})$ has \textbf{level} $N$ if $G=\pi^{-1}(\overline{G})$, where $\pi:\GL_2(\widehat{\Z}) \rightarrow \GL_2(\Z/N\Z)$ is the natural projection map and $\overline{G}=\pi(G)$.
+\timo{and $N$ is minimal with respect to this property} If $\det(G)=\widehat{\Z}^{\times}$, we define the modular curve $X_G \coloneqq X_{\overline{G}}$.
+If $G=\GL_2(\widehat{\Z})$, then we identify $X_G \cong \mathbb{P}^1$ with the $j$-line.
+\begin{proposition} \label{prop:mapdegree}
+If $G \subseteq G' \subseteq \GL_2(\widehat{\Z})$ are two open subgroups with surjective determinant, then there is a natural $\Q$-rational morphism $X_G \rightarrow X_{G'}$ of degree $[\pm G': \pm G]$.
+\timo{where $\pm G$ is the subgroup generated by $G$ and $-I_2$}
+\end{proposition}
+\begin{proof} This comes from the inclusion of function fields $\Q(X_G) \supseteq \Q(X_{G'})$.
+\abbey{ Is there a good citation for this?
+Zywina's paper just states it, and other papers give a more precise justification, but work with subgroups of $\GL_2(\Z/N\Z)/\{\pm 1\}$.
+We should also mention why surjective determinant is needed here...
+my understanding is that if the determinant is not surjective, then the function field construction will not result in a curve over $\Q$, but what we define to be $X_H$ is always a scheme over $\Q$.
+So the two constructions only coincide exactly when the determinant is surjective.
+I think it's worth mentioning this somewhere, since Zywina's paper uses the function field construction.} \timo{My guess is that it would follow from the construction of $X_G$ as a quotient, probably with additional work for going from the fine to the coarse moduli space.}\\
+\filip{Here's a  proof: Let $N$ be the level of $G$.
+For any subgroup $H$ of $\GL_2(\Z /N\Z)$, we have $\Q(X_H)=\Q(X(N))^H$.
+Now by Galois theory it follows that $\Q(X_G) \supseteq \Q(X_{G'})$, so we conclude that there exists a $\Q$-rational morphism $f:X_G \rightarrow X_{G'}$.\\ To determine its degree, let $\Gamma$ and $\Gamma'$ be the intersection with $\SL_2(\Z)$ of the inverse image of $G$ and $G'$ in $\GL_2(\Z)$.
+Over $\bC$, the morphism $f$ is the quotient map $\Gamma \backslash \mathcal{H} \rightarrow \Gamma' \backslash \mathcal{H}$.
+Since the kernel of the action of $\SL_2(\Z)$ on $\mathcal H$ is $\pm I$, the degree of $f$ is as claimed.}
+    \end{proof}
+Taking $G=\pi^{1}(B_1(ab))$ and $G'=\pi^{-1}(B_1(a))$ gives the following corollary, which under the moduli interpretation corresponds to sending $(E,P)$ to $(E,bP)$.    \begin{corollary}
+                For positive integers $a$ and $b$, the natural $\Q$-rational map $f\colon X_1(ab) \rightarrow X_1(a)$ has
+                \[
+                    \deg(f)=
+                    c_{f}\cdot b^2 \prod_{p \mid b,\, p \nmid a}
+                    \left(1-\frac{1}{p^2}\right),
+                \]
+                where $c_{f}=1/2$ if $a \leq 2$ and $ab>2$ and $c_{f}=1$ otherwise. 
+    \end{corollary}
+
+\subsection{Galois Representations} \abbey{still need to add}
+\[
+\rho_{E,m^{\infty}}: \Gal_k \xrightarrow{\rho_E} \GL_2(\widehat{\Z}) \cong  \prod_{p \text{ prime}} \GL_2(\Z_{p}) \xrightarrow{\proj} \prod_{p \mid m} \GL_2(\Z_{p}),
+\]
+
+\section{Isolated Points on Modular Curves: Prior Results}
+\abbey{Not sure which results need to be included, or if they should be discussed in the introduction.}\\
+\abbey{Need to define isolated/sporadic $j$-invariant; maybe in intro}
 \begin{theorem}
@@
 \]
-Then for any $x \in X_1(n)$ with $j(x)=j(E)$ we have $\deg(x)=\deg(f)\cdot \deg(f(x))$, where $f: X_1(n) \rightarrow X_1(\gcd(n,M_E))$ denotes the natural map. It follows that:
+Then for any $x \in X_1(n)$ with $j(x)=j(E)$ we have $\deg(x)=\deg(f)\cdot \deg(f(x))$, where $f: X_1(n) \rightarrow X_1(\gcd(n,M_E))$ denotes the natural map.
+\timo{Separate this into a corollary:?} It follows that:
 \begin{enumerate}
@@
 
-\section{Proving that a point is not sporadic}
-The following algorithm is the main procedure for determining a $j$-invariant is not sporadic. It gives an overview of the structure.
+\section{Proving that a $j$-invariant is not isolated}
+The following algorithm is the main procedure for determining a $j$-invariant is not isolated. It gives an overview of the structure.
 
@@
 \caption{Main Algorithm}\label{alg:mainalgorithm}
-\KwIn{A non-CM $j$-invariant $j = j(E) \in \Q$ and $a$-invariants for $E$ with $j$-invariant $j$.}
-\KwOut{Finite list of pairs $(n,d)$ such that any isolated point on $X_1(N)$ associated to $E$ maps down under the natural projection map to an isolated point of degree $d$ on $X_1(n)$ in the list. }
+\KwIn{A non-CM $j$-invariant $j = j(E) \in \Q$.}
+\KwOut{A finite list of pairs $(n,d)$ such that any isolated point on $X_1(N)$ associated to $E$ maps down under the natural projection map to an isolated point of degree $d$ on $X_1(n)$ in the list.}
 Compute the adelic image $G$ of $E/\Q$ as a subgroup of $\GL_2(\hat{\Z})$ using Zywina's algorithm. Represent the output as some \emph{level} $N$ together with a subgroup $G$ of $\GL_2(\Z/N\Z)$\;
 Using Algorithm \ref{alg:reduce_level}, reduce the level to $G, m_0$\; 
-Define $L \colonequals \{\}$\;
+Set $L \colonequals \{\}$\;
 \For{all $12 < b \mid m_0$}{
 Using Algorithm~\ref{alg:compute_degree} compute the set $D$ of degrees of all fields of definition of a point with respect to $G \mod b$, the image of $G$ in $\GL_2(\Z/b\Z)$\;
-Set $L \colonequals L \cup \{ (b, d) : d \in D\}$ \;}
-Using Algorithm \ref{alg:level_mapping} filter the list $L$ to obtain a refined list $L'$\;
-\Return{the list $L'$ } \;
-    %\filip{We need to look at the orbits of $\langle G, -G \rangle \mod b$ on $(\Z/b\Z)^2$, not $\bP^1(\Z/b\Z)$.
-If we consider the action on $\bP^1(\Z/b\Z)$, the orbits might be too small and hence the degree we get.
-Furthermore, it is necessary to consider only the elements of $(\Z/b\Z)^2$ of order $b$.}
+Set $L \colonequals L \cup \{ (b, d) : d \in D\}$\;}
+Using Algorithm \ref{alg:level_mapping} filter the list $L$ to obtain a refined \timo{reduced?} list $L'$\;
+\Return{the list $L'$ }\; \abbey{Appears to also return true/false.
+I think the false output is misleading since false does not mean ``not isolated," only that we cannot rule it out} \sachi{Perhaps this is a case where it's clearer if our code and our paper do not match completely.
+For me the true/false was so that I can easily parse the data and find out which ones need extra work.
+False just meant ``not done with this yet''.
+But I can see an argument also that it's misleading to the user to return a boolean on a function called notisolated...
+where the boolean does not indicate whether the point is isolated/not.}
 \end{algorithm}
@@
 \end{theorem}
+\abbey{proof needed somewhere -- should it go at the end after the other parts of the algorithm have been described?}
 \begin{corollary}
-If Algorithm \ref{alg:mainalgorithm} outputs an empty set on some $j$-invariant $j = j(E)$ and $a$-invariants $a$ for $E$, then $j$ is not a  $\mathbf{P}^1$-isolated point on $X_1(N)$.
+If Algorithm \ref{alg:mainalgorithm} outputs an empty set on some $j$-invariant $j = j(E)$, then $j$ is not a  $\mathbf{P}^1$-isolated point on $X_1(N)$.
+\abbey{Actually, can conclude not isolated $j$-invariant}
 \end{corollary}
@@
 \section{Reduce Level}
+\abbey{I updated this section to match the revised code and implement other expository changes.}
+Let $E/\Q$ be a non-CM elliptic curve, and define the set 
+\[
+S_E\coloneqq \{2,3\} \cup \{ \ell: \rho_{E,\ell^{\infty}}(\Gal_{\Q}) \neq \GL_2(\Z_{\ell}) \}.
+\] For $m \coloneqq \prod_{\ell \in S_E} \ell$, we give an algorithm to obtain the level of the $m$-adic Galois representation associated to $E$ from the image of the adelic representation of $E$.
+In practice, we can obtain $\im \rho_E$ from Zywina's algorithm \cite{ZywinaAlgorithm}.
 
-\abbey{Travis,Sachi, Abbey}
-
-Using Zywina's algorithm for the level of the adelic Galois representation as a starting point, we may obtain the level of the $m$-adic Galois representation associated to $E$ as in Theorem \ref{BELOVthm}.
+\abbey{Rewrite algorithm description to be less technical?
+Could say the algorithm finds the smallest $m \mid N$ such that $\#G=\#G_m \cdot \#\ker(\GL_2(\Z/mn\Z) \rightarrow \GL_2(\Z/m\Z))$ and returns $m=m0$.}
 
 \begin{algorithm}[H]
-  \KwIn{$G\subseteq \GL_2(\Z/N\Z)$ such that $\im\rho_E=\pi^{-1}(G)$ and $N$ is the level}
-  \KwOut{$G\subseteq \GL_2(\Z/m_0\Z)$ such that $G=\im\rho_{E,m_0}$ and $\im\rho_{E,m^{\infty}}=\pi^{-1}(\im\rho_{E,m_0})$ where $m$ is the product of the non-surjective primes and $2$ and $3$ (if they do not already divide $m$), and $m_0$ is minimal }
+  \KwIn{$G\leq \GL_2(\Z/N\Z)$ such that $\im\rho_E=\pi^{-1}(G)$ and $N$ is the level} 
+  \KwOut{Smallest $m_0 \in \Z^+$ such that $\im\rho_{E,m^{\infty}}=\pi^{-1}(\im\rho_{E,m_0})$ where $m= \prod_{\ell \in S_E} \ell$}
   \caption{Reduce level}%
   \label{alg:reduce_level}
-  Let $P_E = \{\ell|N \text{ prime} \colon \rho_{E,\ell} \text{ is non-surjective} \}$\;
+  Let $P_E = \{\ell \mid N \text{ prime} \colon \rho_{E,\ell} \text{ is non-surjective} \}$\;
   Let $S_E= P_E \cup \{ 2, 3\}$\;
   Let $m_0 = \prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$\;
-  \For{$p \in \{ \ell | m_0 \colon \ell \text{ prime} \}$}{
-  \While{$p |m_0$ and $\#G/\#(G \pmod{m_0/p}) = p^4$}{
+  \For{$p \in \{ \ell \mid  m_0 \colon \ell \text{ prime} \}$}{
+  \While{$p \mid m_0$ and $\#G/\#(G \pmod{m_0/p}) = p^4$}{
     $m_0 = m_0/p$\;
@@
   }
-  \If{not $p$ in $P_E$ and $\ord_p(m_0) = 1$ and $\#G/\#(G \pmod{m_0/p}) = \#\GL_2(\Z/p\Z)$}{
+  \If{not $p$ in $P_E$ and $\ord_p(m_0) = 1$}{\If{$m_0=p$ and $\#G=\#\GL_2(\Z/p\Z)$}{\Return{1}}\ElseIf{$\#G/\#(G \pmod{m_0/p}) = \#\GL_2(\Z/p\Z)$}{
     $m_0 = m_0/p$\;
-   $G = G \pmod{m_0}$\;}}
-  \Return{$G,m_0$}
+  } }
+}
+  %   \If{not $p$ in $P_E$ and $\ord_p(m_0) = 1$ and $\#G/\#(G \pmod{m_0/p}) = \#\GL_2(\Z/p\Z)$}{$m_0 = m_0/p$\;$G = G \pmod{m_0}$\;}
+  \Return{$m_0$}
 \end{algorithm}
@@
   \end{proposition}
+
   \begin{proof}
-    Since $N$ is the level of the adelic representation and both $m$ and $m_0$ divides $N$, we must have that $\im\rho_{E, m^\infty} = \pi^{-1}(\im \rho_{E,m_0})$.
+    Since $N$ is the level of the adelic representation and both $m$ and $m_0$ divides $N$ \abbey{It is not true that $m$ must $N$ since $m$ is always divisible by 2 and 3.
+But if $2$ does not divide $N$, for example, then it does not divide the level of the $m$-adic representation.}, we must have that $\im\rho_{E, m^\infty} = \pi^{-1}(\im \rho_{E,m_0})$.
 This property is an invariant of the for-loop.
@@
 
+      \abbey{Perhaps we should have a proposition statement and proof that is independent of the algorithm writeup, and refer to this in the proof of the algorithm.
+A statement along the lines of: ``Let $G \leq \GL_2(\Z/mn\Z)$ and $G_m \coloneqq G \pmod{m}$.
+Suppose
+  \[
+\#G=\#G_m \cdot \#\ker(\GL_2(\Z/mn\Z) \rightarrow \GL_2(\Z/m\Z)).
+  \] Then $G= \pi^{-1}(G_m),$ where $\pi \rightarrow \GL_2(\Z/mn\Z) \rightarrow \GL_2(\Z/m\Z)$." But we'll need to address what's going on with 2 and 3 in particular.}
+
 \abbey{give example}
@@
 
-The following algorithm computes the degrees of closed points on $X_1(N)$ associated to $E$.
+The following algorithm computes the degrees of closed points on $X_1(N)$ associated to a \abedit{non-CM elliptic curve $E/\Q$}.
 
@@
 \begin{algorithm}[H] \caption{Compute Degree}\label{alg:compute_degree}
-  \KwIn{$G\subseteq \GL_2(\Z/N\Z)$ such that $\im\rho_E=\pi^{-1}(G)$ and $N$ is the level}
+  \KwIn{$G\subseteq \GL_2(\Z/N\Z)$ such that $\im\rho_E=\pi^{-1}(G)$ and $N$ is the level \abbey{code actually takes in transpose of image}}
   \KwOut{all degrees of $x$-coordinates of points}
   Let $H \colonequals \langle G, -I_2\rangle \leq \GL_2(\Z/N\Z)$\;
-  Compute the orbits of $H$ acting on $(\Z/N\Z)^2$\label{Inc-1}\;
-  Filter the orbit representatives for orbits that have order equal to $N$\;
-  Compute the orbit sizes $s$ and ``degrees'' as $s/2$ \label{DivBy2}\;
-  Remove duplicates\label{RemDup}\;
-  \Return{degrees}
+  Compute the orbits $O$ of $H$ acting on $(\Z/N\Z)^2$\label{Inc-1}\;
+  Filter the orbit representatives $R$ for orbits $O$ \travis{representatives?} that have order equal to $N$ in $(\Z/N)^2$\;
+  For each element of $R$, compute the orbit sizes $s$ and their ``degrees'' as $s/2$; store the degees in $D$\label{DivBy2}\;
+  Remove duplicates in $D$\label{RemDup}\;
+  \Return{degrees $D$}
 \end{algorithm}
@@
 \begin{proof}
-    We begin by noting that $(E, P)$ and $(E, -P)$ \abbey{induce the same closed} point on $X_1(N)$, for $P \in E[N]$. Therefore, the degree of
+    We begin by noting that $(E, P)$ and $(E, -P)$ \abedit{induce the same closed} point on $X_1(N)$, for $P \in E[N]$. Therefore, the degree of
     a point represented by $(E, P)$, when
@@
     If $E[N]$ is identified with $(\Z/N\Z)^2$, then $\deg(P)=\# (G. P)$, where $P$ on the left hand side is considered as an element of $(\Z/N\Z)^2$
-    and on right hand side as an element of $E[N]$.
+    and on right hand side as an element of $E[N]$\travis{should this be right/left instead of left/right? what is the degree of a point in $(\Z/N)^2$?}.
     If $P$ and $-P$ are in the same Galois orbit, i.e., $-I_2\in G$, then $[\Q(x(P)):\Q]=[\Q(P):\Q]/2$. On the other hand, one has $[\Q(x(P)):\Q]=[\Q(P):\Q]$, when
-    $-I_2\notin G$.
+    $-I_2\notin G$ \abbey{I don't think this last sentence is true.
+(Filip, didn't you orginally have a comment here?) Consider an elliptic curve with Galois image 7Ns.2.1, which does not contain $-I$.
+There is a $P$ such that $\Q(P)$ has degree 18 but $\Q(x(P))$ has degree 9.
+Alternatively, one can note that if $-I \notin G$, then there exists a twist $E'$ of $E/\Q$ such that $\im \rho_{E',N}=\langle G, -I \rangle$ by \cite[Corollary 5.25]{sutherland}, and we can divide by 2 b/c of your first argument.
+Degrees of (closed) points on $X_1(N)$ are not impacting by replacing a curve by its twist.} \filip{Yes, I had written that it should be the other way round, then got confused during the Zoom talk and deleted it.
+It should in fact be the other way round.}
     Therefore, computing the orbit sizes with respect to the
@@
 Let $E/\Q$ be a non-CM elliptic curve, and let $m$ be the product of 2, 3, and all primes $\ell$ where the $\ell$-adic Galois representation of $E$ is not surjective.
-Let $m_0$ be the level of the $m$-adic Galois representation associated to $E$ and let $f: X_1(n) \rightarrow X_1(\gcd(n,m_0))$ denote the natural map.
+Let $m_0$ be the level of the $m$-adic Galois representation associated to $E$ and let $f\colon X_1(n) \rightarrow X_1(\gcd(n,m_0))$ denote the natural map.
 If $x\in X_1(n)$ is an isolated point with $j(x)=j(E)$, then $f(x)\in X_1(\gcd(n,m_0))$ is an isolated point.
@@
   (sketch)\;
-  create list of guaranteed nonisolated points using easy Riemann--Roch\;
-  filter potentially isolated points via Theorem~\ref{BELOVthm}\;
+  Create list $L$ of guaranteed nonisolated points using easy Riemann--Roch \timo{elaborate}\;
+  Filter potentially isolated points in $L$ via Theorem~\ref{BELOVthm}\;
   \Return{remaining $(N, d)$ pairs.}
@@
 Let $C$ be a curve over a number field $k$ with genus $g$. If $x \in C(\overline{k})$ is a closed point with degree
-$\geq g+1$, then $x$ is not $\mathbb{P}^{1}$-isolated.
+$\geq g+1$, then $x$ is not $\PP^{1}$-isolated.
 \end{lemma}
@@
 \section{Remaining Filters}
-\abbey{Filip? Abbey?}
-Filip's arguments.
+In this section we describe additional criteria which can prove that there are no isolated points on $X_1(N)$ for a fixed $N$ corresponding to a given $j$-invariant.
+
+Let $E/\Q$ be given and let $G_0$ be the image mod $N$ Galois representation attached to $E$ (in $\GL_2(\Z/N\Z)$ after some choice of basis for $E[N]$) and let $y=(E,P)$ correspond to a degree $d$ point on $X_1(N)$ for some $P\in E[N]$.
+Suppose there is a conjugate $c(B_1(N))$ of $B_1(N)$ such that $B:=\langle c(B_1(N)), G_0 \rangle \leq \GL_2(\Z/N\Z)$ and $X_B$ is of genus 0 and such that $[\pm B: \pm c(B_1(N))]=d$.
+By \Cref{prop:mapdegree} it follows that there exists a degree $d$ map $f\colon X_1(N)\rightarrow X_B\simeq \PP^1$ of degree $d$.
+Since $G_0$ is contained in $B$, it follows that $E$ corresponds to a  $x\in X_B(\Q)$ such that $f(y)=x$, hence $y$ is not $\PP^1$-isolated.
+
+\subsection{Special cases}
+We now explain how we dealt with cases that passed all the filters.
+
+\subsubsection{Degree $4$ point on $X_1(17)$ corresponding to $j=-882216989/131072$}
+To show that this point is not isolated we compute the coordinates of the degree $4$ point $x$ corresponding to our curve on a model of $X_1(17)$.
+The point $x$ is defined over a cyclic quartic field.
+Let $\sigma_i$, for $i=1,\ldots, 4$ be the automorphisms of $K$ and $D=\sum_{i=1}^4\sigma_i(x)$.
+We compute $\ell(D)=2$, which implies that $x$ is not $\PP^1$-isolated.
+
+The fact that this point is not $\PP^1$-isolated also follows from the results of \cite{DerickxMazurKamienny}, where it is shown that there are no $\PP^1$-isolated quartic points on $X_1(17)$.
+
+\subsubsection{Degree $18$ point on $X_1(37)$ corresponding to $j=-162677523113838677$}
+
+We show that the points $x\in X_1(37)(K)$, where $K$ is a degree 18 number field, and $j(x)=-162677523113838677$ is $\PP^1$-isolated.
+We explicitly compute the coordinates of $x$ on a model of $X_1(37)$ and define  $\sigma_i$, for $i=1,\ldots, 18$ to be the automorphisms of $K$ and $D=\sum_{i=1}^{18}\sigma_i(x)$.
+Reducing everything modulo $3$ and denoting the reduction of $D$ modulo $3$ by $\overline{D}$, we obtain $\ell(\overline{D})=1$, which shows that the reduction
+$\overline{x}$ of $x$ modulo 3 is not $\PP^1$-isolated, it follows that $x$ cannot be $\PP^1$-isolated.
+
+\filip{I did not go into much details here, as I think more details would entail just writing a bunch of equations, and the code where all the compuitations are dove, will be supplied.}
 
@@
 
-Let $E/ \Q$ be an elliptic curve and $G\in \GL_2(\hat \Z)$ its adelic image.
+Let $E/\Q$ be an elliptic curve and $G\in \GL_2(\hat \Z)$ its adelic image.
 By $G(n)$ denote the image of its mod $n$ representation.
@@
 
-The minimal degree of a point on $X_1(n)$ corresponding to $E$ is the minimal index of $B:=c(B_1(n))\cap G(n)$ in $G(n)$, where $c$ denotes conjugation in $\GL_2(\Z /n \Z)$.
-Call this (minimal) index $d$ and let $f:X_{B}\rightarrow X_{G(n)}$ be the corresponding map of modular curves.
-By construction, all the points in $f^{-1}(P)$ are of degree $d$ and obviously $\gon_\Q X_{B}\leq d.$ Let $P'\in f^{-1}(P) \subseteq X_{B}$ be a point corresponding to $E$, and let $g:X_{B}\rightarrow X_1(n)$ be the map induced by the inclusion $B_1(n) \subseteq B$.
-Then by the argument above we have that $g(P')$ is of degree $d$ (as this is the minimal degree of a point on $X_1(n)$ corresponding to $E$), and on the other hand we have that $\gon_\Q X_1(n)\leq d$ by \cite[Proposition A.1 (vii)]{Poonen:gonality}.
+The minimal degree of a point on $X_1(n)$ corresponding to $E$ is the minimal index of $B \colonequals c(B_1(n))\cap G(n)$ in $G(n)$, where $c$ denotes conjugation in $\GL_2(\Z /n \Z)$.
+Call this (minimal) index $d$ and let $f\colon X_{B}\rightarrow X_{G(n)}$ be the corresponding map of modular curves.
+By construction, all the points in $f^{-1}(P)$ are of degree $d$ and obviously $\gon_\Q X_{B}\leq d$.
+Let $P'\in f^{-1}(P) \subseteq X_{B}$ be a point corresponding to $E$, and let $g\colon X_{B}\rightarrow X_1(n)$ be the map induced by the inclusion $B_1(n) \supseteq B$.
+Then by the argument above we have that $g(P')$ is of degree $d$ (as this is the minimal degree of a point on $X_1(n)$ corresponding to $E$), and on the other hand we have that $\gon_\Q X_1(n)\leq d$ by \cite[Proposition~A.1\,(vii)]{Poonen:gonality}.
 \end{proof}
+
+\abbey{I think if we are just interested in sporadic points, this is almost immediate.
+If $E/\Q$ has adelic image of genus 0, then there are infinitely many non-isomorphic elliptic curves over $\Q$ with the same image.
+If $E$ gives a point on $X_1(n)$ of degree $d$, then so will all the other infinitely many elliptic curves...
+so there are infinitely many degree $d$ points on $X_1(n)$, and the point is not sporadic.\\
+To still think about: Is there a version of this for isolated points? }
+\filip{I remember what the issue was: we construct maps $X_B\rightarrow X_{G(n)}$ and $f:X_B\rightarrow X_1(n)$, and show that the point associated to $E$ on $X_B$ is not $\PP^1$-isolated.
+But I don't know how to show that this would imply that the image of this point under $f$ is not $\PP^1$-isolated.
+}\\
+\filip{This is I think a more general group theoretic problem: we have a subgroup $A$ of $G(n)$ of index $d$, i.e.
+$[G(n):A]=d$, where $A\leq B_1(N)$ (or some conjugate of $B_1(n)$).
+Then we ask what is the index of $B_1(N)$ in the group generated by $G(n)$ and $B_1(n)$.
+If the answer is again necessarily $d$ (or we can always choose a conjugate of $B_1(n)$) such that the index is $d$, then we are good.}
 

### 2023-05-20 isolatedpoints.m
update descriptions

@@ -1,17 +1,20 @@
 intrinsic TransposeMatrixGroup(G::GrpMat) -> GrpMat
-    {Return the transpose}
+    {Return the transpose of G}
     Gt := sub<GL(2,BaseRing(G)) | [Transpose(g):g in Generators(G)]>;
     return Gt;
 end intrinsic;
 
 intrinsic NonSurjectivePrimes(G::GrpMat) -> SeqEnum[RngIntElt]
-    {Given G the adelic image of the Galois representation, compute the non-surjective primes}
-        m:=Modulus(BaseRing(G));
-        return [p:p in PrimeFactors(m)|#ChangeRing(G,GF(p)) ne #GL(2,GF(p))];
+    {Given G the mod N reduction of the adelic Galois image of a non-CM elliptic curve, 
+    where N is the level, return the non-surjective primes}
+    m:=Modulus(BaseRing(G));
+    return [p:p in PrimeFactors(m)|#ChangeRing(G,GF(p)) ne #GL(2,GF(p))];
 end intrinsic;
 
 intrinsic ReducedLevel(G::GrpMat) -> RngIntElt
-    {Level reduction from the output of Zywina's algorithm}
+    {Given G the mod N reduction of the adelic Galois image of a non-CM elliptic curve, 
+    where N is the level, return the level of the m-adic Galois representation, 
+    where m is the product of 2, 3, and any larger primes which are non-surjective}
     m:=Modulus(BaseRing(G));
     NS:=Set(NonSurjectivePrimes(G));
     sE:={2,3} join NS;
@@ -23,7 +26,7 @@ intrinsic ReducedLevel(G::GrpMat) -> RngIntElt
             G:=ChangeRing(G,Integers(m0));
         end while;
         if not p in NS and Valuation(m0,p) eq 1 then
-            if m0 eq p and #G eq #GL(2,GF(p)) then
+            if m0 eq p then
                 return 1;
             elif #G/#ChangeRing(G,Integers(m0 div p)) eq #GL(2,GF(p)) then 
                 m0:=m0 div p;
@@ -40,9 +43,9 @@ intrinsic VectorOrder(v::ModTupRngElt) -> RngIntElt
     return m div g;
 end intrinsic;
 
-//This is obsolete
+//This function is not called
 intrinsic DegreesOfPoints(G::GrpMat) -> SetMulti
-    {compute all degrees of points without doing Riemann--Roch}
[…]

### 2023-07-20 TeX/author_info.tex

@@
-\author[Doe]{Your Name Here}
-\address{
-  John Doe,
-  Monsters University,
-  Department of Mathematics,
-  123 Main Street,
-  Anywhere, CA
-  United States of America
-}
-\email{\url{foobar@example.com}}
-\thanks{JD is supported by the Imaginary Friend association}
-
 \author[Bourdon]{Abbey Bourdon}
@@
 \email{\url{sachi.hashimoto@mis.mpi.de}}
-\urladdr{\url{sachihashimoto.github.io/}}
+\urladdr{\url{https://sachihashimoto.github.io/}}
 
@@
 \urladdr{\url{https://www.timo-keller.de}}
+
+\author[Klagsbrun]{Zev Klagsbrun}
+\address{Zev Klagsbrun, Center for Communications Research, San Diego, CA}
+\email{zdklags@ccr-lajolla.org}
 
@@
 }
+\author[Morrison]{Travis Morrison}
+\address{Travis Morrison, 
+Virginia Tech Department of Mathematics, 
+226 Stanger Street, 
+24061 Blacksburg, VA USA}
+\email{\url{tmo@vt.edu}}
+\urladdr{\url{https://travismo.github.io/}}
+
+\author[Najman]{Filip Najman}
+\address{
+Filip Najman, University of Zagreb, Bijeni\v{c}ka Cesta 30, 10000 Zagreb, Croatia
+}
+\email{\url{fnajman@math.hr}}
+\urladdr{\url{https://web.math.pmf.unizg.hr/~fnajman/}}
 

### 2023-07-20 TeX/draft.tex

--- 2023-04-25 TeX/draft.tex
@@
 \usepackage[utf8]{inputenc}
-
+\usepackage[all,cmtip]{xy}
 \usepackage{amsmath,amsthm,amssymb}
 \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
-
+\usepackage{verbatim}
 \usepackage{colonequals}
@@
 \usepackage{graphics}
+%\usepackage{ulem}
 \usepackage{hyperref}
+\usepackage{cleveref}
 \usepackage[usenames, dvipsnames]{xcolor}
+\usepackage{tikz}
 
@@
 % Nongross real and imaginary parts
+\DeclareMathOperator{\lcm}{lcm}
 \renewcommand{\Im}{\operatorname{Im}}
@@
 \begin{abstract} 
-We develop an algorithm to test whether a non-CM elliptic curve $E/\Q$ gives rise to a sporadic point of any degree on any modular curve of the form $X_1(N)$.
+We develop an algorithm to test whether a non-CM elliptic curve $E/\Q$ gives rise to an isolated point of any degree on any modular curve of the form $X_1(N)$.
 This builds on prior work of Zywina which gives a method for computing the image of the adelic Galois representation associated to $E$.
-Running this algorithm on all elliptic curves presetly in the LMFDB yields strong evidence for the fact that $E$ gives rise to a sporadic point if and only if $j(E)=-140625/8$ or $-9317$.
+Running this algorithm on all elliptic curves presently in the $L$-functions and Modular Forms Database yields strong evidence for the conjecture that $E$ gives rise to a $\PP^1$-isolated point on $X_1(N)$ if and only if $j(E)=-140625/8, -9317,$ $351/4$, or $-162677523113838677$.
     \end{abstract}
@@
 
+\section{Introduction}
+\label{sec:intro}
+\abbey{Updated to account for isolated points.}
 The modular curve $X_1(N)$ is an algebraic curve over $\Q$ whose non-cuspidal points parametrize elliptic curves with a distinguished point of order $N$.
-We are interested in studying \textbf{sporadic} points $x \in X_1(N)$, which are points for which there are only finitely many points on $X_1(N)$ of degree at most $\deg(x)$.
-Hence a non-cuspidal sporadic point corresponds to an elliptic curve with a point of order $N$ in ``usually low degree." Elliptic curves with complex multiplication (CM) provide many natural examples of sporadic points, as the extra endomorphisms of a CM elliptic curve give constraints on the size of the image of the associated Galois representation.
-Indeed, there exist sporadic CM points on $X_1(N)$ for all $N\geq 721$; see \cite[Theorem 8.2]{CGPS2022}.
+We are interested in studying isolated points on $X_1(N)$.
+Roughly speaking these are points of degree $d$ not belonging to an infinite family of degree $d$ points parametrized by a geometric object.
+For example, if $f: X_1(N) \rightarrow \PP^1$ is a rational map of degree $d$, then $f^{-1}(\PP^1(\Q))$ contains infinitely many closed points of degree $d$ by Hilbert's irreducibility theorem \cite[Chapter 9]{serre97}.
+We say a degree $d$ point \emph{not} arising from such a map is \textbf{$\PP^1$-isolated}.
+Other infinite families of degree $d$ points correspond to positive rank abelian subvarieties of the curve's Jacobian; see Section \ref{sec:background} for details.
+A point which is not thus parametrized is \textbf{AV-isolated}.
+If a closed point $x\in X_1(N)$ is both $\PP^1$- and AV-isolated, then we say $x$ is \textbf{isolated}.
+Isolated points can be thought of as those points whose existence is not explained by a geometric construction.
+The lack of control of isolated points in infinite families of modular curves lies at the heart of several important open problems.
+See, for example, \cite[Question 1]{MazurNote} and \cite[Theorem 1.3]{BourdonNajman2021}.
 
-Non-CM sporadic points on $X_1(N)$ remain much more mysterious.
-One recent line of investigation has focused on the class of sporadic points associated to non-CM elliptic curves with $j$-invariant in $\Q$.
-To date, there are only two known examples of such curves, up to isomorphism over $\overline{\Q}$:
+One special class of isolated points is \textbf{sporadic} points, which are $x \in X_1(N)$ such that there are only finitely many points on $X_1(N)$ of degree at most $\deg(x)$.
+Hence a non-cuspidal sporadic point corresponds to an elliptic curve with a point of order $N$ in ``usually low degree." Elliptic curves with complex multiplication (CM) provide many natural examples of sporadic points, since the extra endomorphisms of a CM elliptic curve constrain the size of the image of the associated Galois representation.
+Indeed, as shown in \cite[Theorem 8.2]{CGPS2022}, there exist sporadic CM points on $X_1(N)$ for all $N\geq 721$.
+
+Non-CM isolated points on $X_1(N)$ remain much more mysterious.
+One recent line of investigation has focused on the class of isolated points associated to non-CM elliptic curves with $j$-invariant in $\Q$.
+To date, there are only three known examples of such curves, up to isomorphism over $\overline{\Q}$:
 \begin{itemize}
-\item The elliptic curve with $j$-invariant $-140625/8$ corresponds to points of degree 3 on $X_1(21)$.
-As there are only finitely many points of degree at most 3 on this modular curve, these are sporadic.
+\item The elliptic curve with $j$-invariant $-140625/8$ corresponds to two points of degree 3 on $X_1(21)$.
+Since there are only finitely many points of degree at most 3 on this modular curve, these are sporadic (and hence isolated) points.
 This example was first discovered by Najman \cite{najman16}.
 In fact, this is the unique elliptic curve giving a sporadic point of degree at most 3 on \emph{any} modular curve of the form $X_1(N)$, as shown in recent work of Derickx, Etropolski, van Hoeij, Morrow, and Zureick-Brown \cite{DEvHMZB2021}.
-\item The elliptic curve with $j$-invariant $-9317$ gives a degree 6 point on $X_1(37)$, as in work of van Hoeij \cite{vanHoeij}.
-Since this degree is less than half the $\Q$-gonality of $X_1(37)$, as computed in \cite{DerickxVanHoeij2014}, the point is necessarily sporadic by work of Frey \cite{frey}.
+\item The elliptic curve with $j$-invariant $-9317$ gives three degree 6 points on $X_1(37)$, as in work of van Hoeij \cite{vanHoeij}.
+Since 6 is less than half the $\Q$-gonality of $X_1(37)$, as computed in \cite{DerickxVanHoeij2014}, the point is necessarily sporadic by work of Frey \cite{frey}.
+\item The elliptic curve with $j$-invariant $351/4$ gives an isolated point of degree 9 on $X_1(28)$; see \cite[Theorem 2]{OddDeg}.
+There are infinitely many points on $X_1(28)$ of degree 6, as shown in \cite{DerickxVanHoeij2014}, so this point is isolated but not sporadic.
 \end{itemize}
 
-We say these are \textbf{sporadic $j$-invariants} since they are the image of a sporadic point on $X_1(N)$.
-We have good reason to believe that the collection of all sporadic $j$-invariants in $\Q$ is finite.
+If $x \in X_1(N)$ is a sporadic (resp.
+isolated) point, we say $j(x) \in X_1(1) \cong \mathbf{P}^1$ is a \textbf{sporadic} (resp.
+\textbf{isolated}) \textbf{$j$-invariant}.
+Thus the three $j$-invariants listed above are isolated $j$-invariants, while $-140625/8$  and $-9317$ are also sporadic $j$-invariants.
+We have good reason to believe that the set of all isolated $j$-invariants in $\Q$ is finite.
 \begin{theorem}[Bourdon, Ejder, Liu, Odumodu, Viray \cite{BELOV}]
+\label{BELOVfiniteness}
 Suppose there exists a constant $C$ such that the mod $\ell$ Galois representation of any non-CM elliptic curve over $\Q$ is surjective for primes $\ell>C$.
-Then there are only finitely many sporadic $j$-invariants in $\Q$.
+Then there are only finitely many isolated $j$-invariants in $\Q$.
 \end{theorem}
 
-\noindent The assumption about Galois representations stated in Theorem 1 was originally asked as a question by Serre \cite{serre72}, and it has now been formally conjectured by both Sutherland \cite{sutherland} and Zywina \cite{ZywinaImages}.
+\noindent The assumption about Galois representations stated in Theorem \ref{BELOVfiniteness} was originally asked as a question by Serre \cite{serre72}, and it has now been formally conjectured by both Sutherland \cite{sutherland} and Zywina \cite{ZywinaImages}.
 It is even suspected that $C=37$.
-Theorem 1 is known unconditionally for points of odd degree \cite{OddDeg}: indeed, $j=-140625/8$ is the only non-CM $j$-invariant in $\Q$ giving a sporadic point of odd degree on $X_1(N)$, even as $N$ ranges over all positive integers.
+Theorem \ref{BELOVfiniteness} is known unconditionally for points of odd degree \cite{OddDeg}: indeed, $j=-140625/8$ and $j=351/4$ are the only non-CM $j$-invariants in $\Q$ giving an isolated point of odd degree on $X_1(N)$, even as $N$ ranges over all positive integers.
 
-In \cite{BELOV}, they ask whether one can explicitly determine the set of sporadic $j$-invariants in $\Q$, and this is the motivation for the present work.
-In particular, we conjecture that the two non-CM sporadic $j$-invariants identified above are in fact the \emph{only} sporadic $j$-invariants in $\Q$ associated to non-CM elliptic curves.
+In \cite{BELOV}, they ask whether one can explicitly determine the set of isolated $j$-invariants in $\Q$.
+This is the motivation for the present work.
+We develop an algorithm which can be used to determine whether a given non-CM $j$-invariant $j\in \Q$ is isolated.
+Starting with the adelic image of the adelic Galois representation associated $E/\Q$ with $j(E)=j(x)$, as computed by Zywina \cite{ZywinaAlgorithm}, we apply various filters inspired by \cite{BELOV} to determine whether there exists an isolated point on $x \in X_1(N)$ with $j(x)=j$.
 
-\begin{conjecture}
-If $x\in X_1(N)$ is a sporadic point with $j(x) \in \Q$, then $j(x)=-140625/8$ or $-9317$ or is one of the 13 CM $j$-invariants in $\Q$.
-\end{conjecture}
+\begin{algorithm}[h!]
+\caption{Main Algorithm}
+\KwIn{A non-CM $j$-invariant $j \in \Q$.}
+\KwOut{A list $[j,\{\langle a_1,d_1\rangle, \dots, \langle a_k,d_k\rangle \}]$ such that any isolated point $x \in X_1(N)$ with $j(x)=j$ maps down under the natural projection map to an isolated point of degree $d_i$ on $X_1(a_i)$ for some $1 \leq i \leq k$.}
+\end{algorithm}
 
-\noindent Since any CM elliptic curve is known to produce sporadic points on infinitely many modular curves of the form $X_1(N)$, it follows conversely that every $j$-invariant in this set is sporadic.
+\noindent In particular, if the output of Algorithm \ref{alg:mainalgorithm} is the empty set, then $j$ is not an isolated $j$-invariant.
+We give an overview of the main algorithm in Section \ref{alg:mainalgorithm}, with key sub-algorithms described in detail in Sections \ref{sec:madicrep} and \ref{sec:primitivedeg}.
+We address the validity of Algorithm \ref{alg:mainalgorithm} in Section \ref{sec:validity}.
 
-The basis for this conjecture is the following result.
+Running Algorithm \ref{alg:mainalgorithm} on all elliptic curves currently in the $L$-functions and Modular Forms Database (LMFDB) \cite{LMFDB} gives a list of 95 $j$-invariants which require further consideration; see the Appendix.
+After applying certain additional filters to address special cases, as discussed in Section~\ref{sec:remainingfilters}, we arrive at the following result.
 
-\begin{theorem}
-Let $x=[E,P]\in X_1(N)$ be a non-CM sporadic point with $j(E) \in \Q$.
+\begin{theorem}\label{LMFDBoutputThm}
+Let $x=[E,P]\in X_1(N)$ be a non-CM isolated point with $j(E) \in \Q$.
 Fix an equation for $E/\Q$ and let $N_E$ denote its conductor.
@@
 \end{itemize}
-Then $j(E) =-140625/8$ or $-9317$.
+Then $j(E) \in \{-140625/8,-9317,351/4, -162677523113838677\}$.
+Moreover, each of these $j$-invariants corresponds to a $\PP^1$-isolated point on $X_1(21)$, $X_1(37)$, $X_1(28)$, and $X_1(37)$, respectively.
 \end{theorem}
 
-Since both known examples of sporadic points on $X_1(N)$ associated to non-CM rational $j$-invariants lie above exceptional rational points on $X_0(N)$ -- that is, they correspond to rational points in cases where the set of all such rational points is finite -- is natural to ask whether this construction might yield other examples of sporadic points.
-Our work shows that the answer is no.
+Based on these results, we conjecture that the four non-CM isolated $j$-invariants identified above are in fact the \emph{only} $j$-invariants in $\Q$ associated to non-CM elliptic curves which give rise to $\PP^1$-isolated points.
+
+\begin{conjecture}
+If $x\in X_1(N)$ is a $\PP^1$-isolated point with $j(x) \in \Q$, then $j(x)=-140625/8$,$-9317$, $351/4$, $-162677523113838677$, or one of the 13 CM $j$-invariants in $\Q$.
+\end{conjecture}
+
+\noindent Since any CM elliptic curve is known to produce sporadic points on infinitely many modular curves of the form $X_1(N)$ by \cite[Theorem 7.1]{BELOV}, it follows conversely that every $j$-invariant in this set is isolated.
+
+It is worth noting that the sporadic points on $X_1(21)$ associated to $j=-140625/8$ and the sporadic points on $X_1(37)$ associated to $j=-9317$ lie above exceptional rational points on $X_0(21)$ and $X_0(37)$, respectively.
+We say a point $x \in X_0(N)(\Q)$ is \textbf{exceptional} if $X_0(N)(\Q)$ is finite and $x$ corresponds to a non-CM elliptic curve over $\Q$.
+Thus it is natural to ask whether there exist other sporadic points on $X_1(N')$ lying above such exceptional rational points.
+Running Algorithm~\ref{alg:mainalgorithm} on the 14 $j$-invariants corresponding to exceptional rational points on $X_0(N)$ (see, for example, \cite[Table 4]{LRAnn}) shows that there are no additional sporadic $j$-invariants in this set.
+\begin{theorem}
+Let $E$ be an elliptic curve corresponding to an exceptional rational point on $X_0(N)$. If there exists a sporadic point $x \in X_1(N')$ with $j(x)=j(E)$, then $j(E) =-140625/8$ or $-9317$.
+\end{theorem}
+
+It is still an open problem to determine all sporadic points $x \in \cup_{N \in \Z^+} X_1(N)$ with $j(x) =-140625/8$ or $-9317$.
+
+\section*{Acknowledgments}
+We thank Pete Clark, Maarten Derickx, Jeremy Rouse, and David Zureick-Brown for helpful conversations.
+
+\section{Background}
+\label{sec:background}
+\subsection{Isolated Points on Curves}
+Let $C$ be a curve, by which we will mean a nonsingular projective geometrically integral 1-dimensional scheme defined over a number field $k$; we suppose all curves satisfy these assumptions throughout the paper.
+To streamline our exposition, we assume there exists a point $P_0 \in C(k)$, but this is not required; see \cite[$\S4$]{BELOV}.
+Throughout, we consider closed points of the curve $C$, which correspond to $\Gal_k$-orbits of points in $C(\overline{k})$.
+The degree of $x$ is defined to be the degree of the residue field $k(x)$ over $k$, or alternatively, to be the length of the $\Gal_k$-orbit of points in $C(\overline{k})$ corresponding to $x$.
+
+To any closed point $x \in C$ of degree $d$ we associate the $k$-rational effective divisor 
+\[
+ x=P_1+ \cdots +P_{d},
+\]
+where $P_1, \dots, P_{d}$ are the points in the $\Gal_{k}$-orbit associated to $x$.
+With this identification, we can study the image of $x$ under the natural map from the $d$th symmetric power of $C$ to the curve's Jacobian
+\begin{align}
+\label{eqn:phid}
+\Phi_d: C^{(d)} \rightarrow \Jac(C)
+\end{align}
+which sends the effective divisor $D$ of degree $d$ to the class $[D - dP_0]$, where $P_0 \in C(k)$.
+If $\Phi_d(x)=\Phi_d(y)$ for some other point $y \in C^{(d)}(k)$, then there exists a non-constant function $f \in k(C)^{\times}$ with $\text{div}(f)=x-y$.
+Since $x$ is a degree $d$ point and $x\not=y$, $x$ and $y$ have distinct support so $f: C \rightarrow \mathbf{P}^1_{k}$ is a dominant morphism of degree $d$.\footnote{In particular, this shows $\Phi_d$ is injective if $d$ is less than the $k$-gonality of $C$, which is the least degree of a non-constant rational map to $\mathbf{P}^1$.} By Hilbert's irreducibility theorem \cite[Chapter 9]{serre97}, $f^{-1}(\mathbf{P}^{1}(k))$ will contain infinitely many closed points of degree $d$.
+On the other hand, if $\Phi_d$ is injective on closed points of degree $d$, then by Faltings' Theorem \cite{faltings} there can exist infinitely many such points only if all but finitely many are parametrized by translates of positive rank abelian subvarieties of $\Jac(C)$.
+\sachi{or maybe: Suppose $\Phi_d$ is injective on closed points of degree $d$.
+Then Faltings' theorem \cite{faltings} implies all but finitely many such points are parametrized by translates of positive rank abelian subvarieties of $\Jac(C)$.}
+This inspires the following:
+
+\begin{definition} Let $C$ be a curve defined over a number field $k$. Let $\Phi_d$ be the map in \eqref{eqn:phid}.
+\begin{enumerate}
+\item []
+\item A closed point $x \in C$ of degree $d$ is $\PP^1$\textbf{-parametrized} if there exists a point $x' \in C^{(d)}(k)$ such that $\Phi_d(x)=\Phi_d(x')$.
+Otherwise, we say $x$ is $\PP^1$\textbf{-isolated}.
+\item A closed point $x \in C$ of degree $d$ is \textbf{AV-parametrized} if there exists a positive rank abelian subvariety $A/k$ with  $A \subset \Jac(C)$ such that $\Phi_d(x)+A \subset \im(\Phi_d)$.
+Otherwise, we say $x$ is \textbf{AV-isolated}.
+\item A closed point $x \in C$ of degree $d$ is \textbf{isolated} if it is both $\PP^1$-isolated and AV-isolated.
+\item A closed point $x \in C$ of degree $d$ is \textbf{sporadic} if there are only finitely many closed points of $C$ of degree at most $\deg(x)$.
+\end{enumerate}
+\end{definition}
+
+If $C$ has genus $g\geq 2$, then the collection of all points on $C$ with coordinates in $k$ is finite by Faltings's theorem \cite{faltings83}.
+In general, the set $C(k)$ sits inside a larger finite set of points, namely, the set of all isolated points of $C$.
+    \begin{theorem}[{Bourdon, Ejder, Liu, Odumodu, Viray, \cite[Theorem 4.2]{BELOV}}]\label{thm:FiniteIsolated}
+        Let $C$ be a curve over a number field.
+        \begin{enumerate}
+            \item There are infinitely many degree $d$ points on $C$ if and only if there is a degree $d$ point on $C$ that is \emph{not} isolated.
+            \item There are only finitely many isolated points on $C$.
+        \end{enumerate}
+    \end{theorem}
+It follows from Theorem \ref{thm:FiniteIsolated} that every sporadic point is isolated, but the converse need not hold.
+
+\subsection{Modular Curves}
+For any subgroup $H \leq \GL_2(\Z/N\Z)$, we define the modular curve $X_H$ to be the coarse space of the stack $\mathcal{M}_H$, as defined in Deligne--Rapoport \cite{DR}.
+The curve $X_H$ is a scheme over $\text{Spec }\Z[1/N]$ and parametrises generalized elliptic curves with $H$-level structure.
+\abedit{In particular, its $k$-rational points roughly classify elliptic curves over $k$ whose mod $N$ image is contained in $H$}; see, for example, \cite[$\S2.3$]{RSZB2022} for details.
+If we take
+\[
+B_1(N) =\left\{ \begin{pmatrix}
+1 & * \\
+0 & *
+\end{pmatrix} \right \} \leq \GL_2(\Z/N\Z),
+\]
+then $X_{B_1(N)}=X_1(N)$, the modular curve whose noncuspidal points parametrize  elliptic curves with a distinguished point of order $N$.
+There is an analytic isomorphism between $X_1(N)(\mathbb{C})$ and the Riemann surface constructed as a quotient of the extended upper-half plane by the congruence subgroup
+\[
+\Gamma_1(N) \coloneqq\left\{ \begin{pmatrix}
+a & b \\
+c & d 
+\end{pmatrix} \in \SL_2(\Z) \, : \, c \equiv 0 \pmod{N} \text{ and } a \equiv d \equiv 1 \pmod{N} \right \}, 
+\]
+with matrices acting via linear fractional transformations.
+If $N \geq 4$, then $\mathcal{M}_{B_1(N)}$ is its own coarse moduli space, and so noncuspidal $k$-rational points of $X_1(N)$ classify pairs $(E,P)$, where $E/k$ is an elliptic curve and $P\in E(k)$, up to $k$-isomorphism.
+%\abbey{I decided not to define the modular curve by its moduli problem as in \cite[$\S2$]{RouseDZB}, since the construction yields a stack in general...
+so it seems confusing to call it a modular *curve*.
+I've opted to go with the conventions of \cite[$\S2.3$]{RSZB2022}.}
+
+\abedit{We may also define a modular curve associated to an open subgroup $G$ of $\GL_2(\widehat{\Z})$.
+For any $N \in \Z^+$, let $\pi:\GL_2(\widehat{\Z}) \rightarrow \GL_2(\Z/N\Z)$ be the natural projection map, and define $G(N) \coloneqq \pi(G)$.
+We say $G$ has \textbf{level} $N$ if $G=\pi^{-1}(G(N))$ and $N$ is minimal with respect to this property.} If $\det(G)=\widehat{\Z}^{\times}$, we define the modular curve $X_G \coloneqq X_{G(N)}$.
+If $G=\GL_2(\widehat{\Z})$, then we identify $X_G \cong \PP^1$ with the $j$-line.
+
+\subsection{Closed Points on Modular Curves}\abbey{I updated the first 2 paragraphs of this section.} To discuss isolated points on modular curves, we must consider closed points on $X_1(N)$, viewed always as a scheme over $\Q$.
+Let $k$ be a field with an embedding of $k$ into $\overline \Q$.
+Given an elliptic curve $E/k$ with $P \in E(k)$ of order $N$, the pair $(E,P)$ induces a $k$-valued point on $X_1(N)$ via the moduli interpretation described above.
+We denote this $k$-valued point by $(E,P)_k$, and by definition it corresponds to a morphism of $\Q$-schemes $f:\text{Spec } k \rightarrow X_1(N)$.
+The map $f$ sends the unique point of $\text{Spec } k$ to a point $x \in X$, and we call $x$ the \textbf{closed point} associated to $(E,P)$.\footnote{Note $x$ is indeed closed since $\Q(x)/\Q$ is finite; see, for example, \cite[Exercise 5.9, p.76] {Liu2002}.} We define the \textbf{degree} of $x$ to be the degree of the residue field $\Q(x)$ over $\Q$.
+Since there are many scheme-valued points which induce the same closed point, it is sometimes preferable to consider Galois orbits of points in $X_1(N)(\overline{\Q})$, which are in bijection with the set of closed points.
+Thus one could alternatively define the closed point associated to $(E,P)$ as the $\Gal_\Q$-orbit of $(E,P)_{\overline{\Q}}$.
+\sachi{I think the difference between $k$-valued points and $k$-rational points is confusing, since the names are so similar.
+It would be nice to explicitly point out what is meant by $k$-rationality somewhere (in constrast to $k$-valued).} \abbey{They are all the same thing for a scheme over a field.
+I used the term $k$-valued b/c it's the term used in Qing Liu's book \cite{Liu2002}, but it matches what Poonen calls a $k$-rational point or a $k$-point of a scheme over a field in \emph{Rational points on varieties}, for example.
+The definition is actually already above --- it's a morphism of $\Q$-schemes $f:\text{Spec} k \rightarrow X_1(N)$.
+If you say $k$-rational point, I imagine most people just think of points with coordinates in $k$, rather than this scheme-theoretic definition.
+These two notions coincide, but it's something to prove, for example, as in Prop.
+2.18 in Section 3.2.3 of \cite{Liu2002}.}
+
+\begin{remark} Given a $k$-valued point $(E,P)_k$, we note that the degree of the associated closed point $x$ may be strictly less than the degree of $k$.
+However, there always exists $E'/\Q(x)$ with $j(E')=j(E)$ and $P' \in E'(\Q(x))$, where the point $P' \in E'$ maps to $P \in E$ under a $\overline \Q$-isomorphism sending $E$ to $E'$.
+See \cite[p.
+274, Proposition VI.3.2]{DR}.
+The pair $(E',P')$ gives a $\Q(x)$-valued point, and it is the unique $\Q(x)$-valued point such that $(E,P)_{k}=(E',P')_{k}.$
+\end{remark}
+
+Let $E/k$ be an elliptic curve and $P \in E(k)$ a point of order $N$.
+Note that for any $\xi \in \Aut(E)$, the pair $(E,\xi P)$ induces the same closed point $x \in X_1(N)$, since $\xi$ provides the necessary isomorphism.
+This can be used to obtain a more explicit description of the residue field $\Q(x)$.
+%\footnote{ \abbey{Add footnote about connection with $X_{\pm B_1(N)}$.
+``If you take the moduli space of the set of closed points associated to pairs $(E,P)$ as above, you in fact get exactly $X_{\pm B_1(N)}$ (i.e the moduli functor will correspond exactly to this)!" Does this still hold for $j=0,1728$?}}
+
+\begin{lemma}\label{ResidueFieldLemma}
+Let $E$ be an elliptic curve defined over $\Q(j(E))$, and let $P \in E$ be a point of order $N$. Then the residue field of the closed point $x \in X_1(N)$ associated to $(E,P)$ is given by
+\[
+\Q(x)\cong\Q(j(E),\mathfrak{h}(P)),
+\]
+where $\mathfrak{h} \rightarrow E/\Aut(E) \cong \mathbf{P}^1$ is a Weber function for $E$. 
+\end{lemma}
+
+\begin{proof}
+See, for example, \cite[Lemma 2.5]{BourdonNajman2021}.%{OddDegQCurve}. 
+\end{proof}
+
+\abbey{Add Shimura definition of $\mathfrak{h}$.}
+
+\begin{remark}\label{ResidueFieldRmk} In particular, if $E/\Q(j(E))$ does not have complex multiplication and $P=(x_0,y_0)$, then one can take $\Q(x)\cong\Q(j(E),x_0)$. See \cite[p. 107]{shimura}.
+\end{remark}
+\begin{example}
+Let $E_1:y^2+xy+y=x^3-x^2-3x+3$ and $P_1=(-1,2)$ a point of order 7.
+Then $(E_1,P_1)$ gives a $\Q$-valued point on $X_1(7)/\Q$ and also a closed point $x\in X_1(7)$ of degree 1.
+On the other hand, let $E_2:y^2=x^3-43x-166$ and $P_2=(5,i\sqrt{256})$ a point of order 7.
+Then $(E_2,P_2)$ gives a $\Q(i)$-valued point on $X_1(7)/\Q$ and also a closed point $x\in X_1(7)$ of degree 1 by \abedit{Remark \ref{ResidueFieldRmk}} \sachi{(and therefore a $\Q$-rational point)} \abbey{We want to think of it as \emph{inducing} a $\Q$-rational point---as explained in the paragraph below, or in Remark 7 above---rather than $(E_2,P_2)$ itself being $\Q$-rational.
+The non-cuspidal $\Q$-rational points of $X_1(7)(\Q)$ correspond to $\Q$-isomorphism classes of elliptic curves $E/\Q$ with a point $P\in E(\Q)$ of order 7, where this comes from the curve being a fine moduli space.
+So the representative $E_2,P_2$ does not show up here, since $P_2$ is not in $\Q$.}.
+In fact, both $(E_1,P_1)$ and $(E_2,P_2)$ induce the same geometric point on $X_1(7)$ since $(E_1,P_1)_{\overline{\Q}}=(E_2,P_2)_{\overline{\Q}}$.
+
+One could alternatively compute the Kubert--Tate normal form associated to $E_2/\Q(i)$, with $P_2=(5,i\sqrt{256})$:
+\[E_3: y^2-xy-4y=x^3-4x^2,\, \, P_3=(0,0).
+\]
+We can check that $(E_1,P_1)_{\Q}=(E_3,P_3)_{\Q}$ and $(E_2,P_2)_{\Q(i)} =(E_3,P_3)_{\Q(i)}$.
+Thus it is fair to say that $(E_2,P_2)$ induces a $\Q$-valued point, even though it is not itself a $\Q$-valued point.
+\end{example}
+
+\begin{example}
+The distinction between closed points and geometric points can be seen when counting the number of points of a particular degree.
+For example, let $E$ be the elliptic curve with LMFDB label \href{https://www.lmfdb.org/EllipticCurve/Q/162/c/3}{162.c3}.
+Then $E$ possesses a unique $\Q$-rational subgroup of order 21 with generator $P$.
+For each $a \in (\Z/21\Z)^{\times}$, we consider the geometric point on $X_1(21)$ associated to $(E,aP)$.
+Since $(E,aP)_{\overline{\Q}}=(E,-aP)_{\overline{\Q}}$, we find there are six distinct geometric points corresponding to $(E,aP)$ for $a \in (\Z/21\Z)^{\times}$.
+However, these six $\overline{\Q}$-points lie in two Galois orbits, each of size 3.
+Thus we would say there are two closed points of degree 3, and the cardinality of the Galois orbit equals the degree.
+\end{example}
+
+%\begin{example}
+%\emph{To add; could also talk about $f^*(j(E))$}
+%\end{example}
+
+\subsection{Maps Between Modular Curves}
+
+\begin{proposition} \label{prop:mapdegree}
+If $G \subseteq G' \subseteq \GL_2(\widehat{\Z})$ are two open subgroups with surjective determinant, then there is a natural $\Q$-rational morphism $X_G \rightarrow X_{G'}$ of degree $[\pm G': \pm G]$.
+Here, $\pm G$ denotes the subgroup generated by $G$ and $-I_2$.
+\end{proposition}
+\begin{proof}
+Let $N$ be the level of $G$.
+For any subgroup $H$ of $\GL_2(\Z /N\Z)$, we have $\Q(X_H)=\Q(X(N))^H$.
+Now by Galois theory it follows that $\Q(X_G) \supseteq \Q(X_{G'})$, so we conclude that there exists a $\Q$-rational morphism $f:X_G \rightarrow X_{G'}$.
+
+To determine its degree, let $\Gamma$ and $\Gamma'$ be the intersection with $\SL_2(\Z)$ of the inverse image of $G$ and $G'$ in $\GL_2(\Z)$.
+Over $\bC$, the morphism $f$ is the quotient map $\Gamma \backslash \mathcal{H} \rightarrow \Gamma' \backslash \mathcal{H}$.
+Since the kernel of the action of $\SL_2(\Z)$ on $\mathcal H$ is $\pm I$, the degree of $f$ is as claimed.
+    \end{proof}
+Let $a$ and $b$ be positive integers.
+Taking $G=\pi^{-1}(B_1(ab))$ and $G'=\pi^{-1}(B_1(a))$ gives the following corollary, which under the moduli interpretation corresponds to sending $(E,P)$ to $(E,bP)$.
 \begin{corollary}
-Let $X_0(N)$ have genus greater than 0, and let $E$ be a non-CM elliptic curve corresponding to a rational point on $X_0(N)$.
-If there exists a sporadic point $x \in X_1(N')$ with $j(x)=j(E)$, then $j(E) =-140625/8$ or $-9317$.
+                For positive integers $a$ and $b$, the natural $\Q$-rational map $f\colon X_1(ab) \rightarrow X_1(a)$ has
+                \[
+                    \deg(f)=
+                    c_{f}\cdot b^2 \prod_{p \mid b,\, p \nmid a}
+                    \left(1-\frac{1}{p^2}\right),
+                \]
+                where $c_{f}=1/2$ if $a \leq 2$ and $ab>2$ and $c_{f}=1$ otherwise. 
     \end{corollary}
 
-\section{Background}
+\subsection{Galois Representations}\abbey{Recently added section.} If $E$ is an elliptic curve defined over a number field $k$, then $\Gal_k$ acts naturally on the points of $E$.
+On torsion points, this action is described by the \textbf{adelic Galois representation} associated to $E/k$,
+\[
+\rho_{E}: \Gal_k \rightarrow \Aut(E(\overline{k})_{\text{tors}}) \cong \GL_2(\widehat{\Z}). 
+\]
+From this we can obtain two other Galois representations.
+On the one hand, fixing a positive integer $m$, we can choose to record the action of $\Gal_k$ on points \abedit{whose order is divisible only by those primes dividing $m$}.
+This is the \textbf{$m$-adic Galois representation} associated to $E$:
+\[
+\rho_{E,m^{\infty}}\colon \Gal_k \xrightarrow{\rho_E} \GL_2(\widehat{\Z}) \cong  \prod_{p \text{ prime}} \GL_2(\Z_{p}) \xrightarrow{\proj} \prod_{p \mid m} \GL_2(\Z_{p}).
+\]
+In particular, if $m=\ell$ is a prime number, we recover the standard $\ell$-adic representation associated to $E$.
+Alternatively, we may wish to record Galois action only on points of order dividing $m$; we use $E[m]$ to denote the finite subgroup of such points.
+This gives the \textbf{mod $m$ Galois representation} associated to $E$,
+\[
+\rho_{E,m}\colon \Gal_k \rightarrow \Aut(E[m]) \cong \GL_2(\Z/m\Z).
+\]
+Note that $\rho_{E,m}$ agrees with the reduction of $\rho_E$ mod $m$.
 
-\begin{theorem}
-Let $E/\Q$ be a non-CM elliptic curve, and let $\rho_E$ denote the adelic Galois representation of $E$. Let $M_E$ be any positive integer such that
-\[
-\im \rho_E=\pi^{-1}(\im \rho_{E, M_E}).
-\]
-Then for any $x \in X_1(n)$ with $j(x)=j(E)$ we have $\deg(x)=\deg(f)\cdot \deg(f(x))$, where $f: X_1(n) \rightarrow X_1(\gcd(n,M_E))$ denotes the natural map. It follows that:
+If $E/k$ is a non-CM elliptic curve, we define the \textbf{level} of $\rho_E$ to be the smallest positive integer $N$ such that $\im \rho_E=\pi^{-1}(\im \rho_{E,N})$, where $\pi:\GL_2(\widehat{\Z}) \rightarrow \GL_2(\Z/N\Z)$ is the natural reduction map; that such an $N$ exists is a consequence of Serre's Open Image Theorem \cite{serre72}.
+The level of $\rho_{E,m^{\infty}}$ may be defined in an analogous way.
+We take the convention that $\GL_2(\Z/1\Z)$ denotes the trivial group, so level 1 corresponds to the associated Galois representation being surjective.
+Though $\rho_E$ is never surjective when $k=\Q$, this can occur for elliptic curves defined over number fields of higher degree \cite[Theorem 1.2]{Greicius2010}.
+
+%\section{Isolated Points on Modular Curves: Prior Results}
+
+%\begin{theorem}
+%Let $E/\Q$ be a non-CM elliptic curve, and let $\rho_E$ denote the adelic Galois representation of $E$. Let $M_E$ be any positive integer such that
+%\[
+%\im \rho_E=\pi^{-1}(\im \rho_{E, M_E}).
+%\]
+%Then for any $x \in X_1(n)$ with $j(x)=j(E)$ we have $\deg(x)=\deg(f)\cdot \deg(f(x))$, where $f: X_1(n) \rightarrow X_1(\gcd(n,M_E))$ denotes the natural map.
+\timo{Separate this into a corollary:?} It follows that:
+%\begin{enumerate}
+%\item If $x$ is $\mathbf{P}^1$-isolated, then $f(x)$ is $\mathbf{P}^1$-isolated.
+%\item If $x$ is AV-isolated, then $f(x)$ is AV-isolated.
+%\item If $x$ is sporadic, then $f(x)$ is sporadic.
+%\end{enumerate}
+%\end{theorem}
+
+%\begin{proof}This follows from the arguments \cite[$\S5.3$]{BELOV} and \cite[Theorem 4.3]{BELOV}. \abbey{This is mentioned in Remark 5.5 of \cite{BELOV} in particular.}\end{proof}
+
+\section{Genus 0 adelic images do not produce isolated points}
+
+\abbey{I moved this from the end.}
+\label{sec:genus0}
+Let $E/\Q$ be an elliptic curve and $G\in \GL_2(\hat \Z)$ its adelic image.
+By $G(N)$ denote the image of its mod $N$ representation.
+Denote by $B_1(N)$ the subgroup of $\GL_2(\Z/N\Z)$ consisting of the upper triangular matrices with a $1$ in the upper left entry.
+Note that $X_{B_1(N)}=X_1(N)$.
+We say that a congruence group $\Gamma$ is of genus $g$ if $X_\Gamma$ is of genus $g$.
+We say that a point $P$ corresponds to an elliptic curve $E$ if $j(P)=j(E)$.
+
+\begin{lemma} \label{lem:map to Symd}
+Let $f\colon X \to Y$ be a finite morphism of curves of degree $d$. Then $f$ induces a non-constant morphism $f^*\colon Y \to X^{(d)}$.
+\end{lemma}
+\begin{proof}
+    See~\cite[Theorem~3.13]{MilneJV}. The morphism is non-constant since fibers above different points are mapped to different points.
+\end{proof}
+
+Note that a rational map from $\PP^1$ to a smooth variety of degree $1$ extends uniquely to a morphism (by the valuative criterion of properness) and is an isomorphism onto its image since a genus $0$ curve cannot have singularities.
+The symmetric powers of a smooth projective curve are smooth~\cite[Proposition~3.2]{MilneJV}.
+
+\begin{lemma} \label{lem:iso1}
+Let $X$ be a curve with a copy of $\bP^1$ inside $X^{(d)}$ and let $x\in X^{(d)}(\Q)$ be irreducible and lying on the image of $\PP^1$ inside of $X^{(d)}$. Then $x$ is not $\PP^1$-isolated.
+\end{lemma}
+\begin{proof}
+The restriction of the map $\Phi_d:X^{(d)}\rightarrow \Jac (X)$ to the image of $\PP^1$ inside $X^{(d)}$ factors through $\Jac(\PP^1)=\{0 \}$ by the Albanese property of the Jacobian, so it contracts the $\PP^1$ to a point on $\Jac(X)$.\footnote{Or because abelian varieties contain no positive dimensional rational varieties~\cite[Corollary~3.9]{MilneAV}.} Hence $\Phi_d(y) = \Phi_d(x)$ for any $y$ lying on this image of $\PP^1$.
+\end{proof}
+
+\begin{lemma} \label{lem:iso2}
+Let $f: X\rightarrow Y$ be a finite morphism of curves and $x$ a point on $X$, and assume  $\deg x = \deg f(x)$. If $x$ is not $\PP^1$-isolated, then neither is $f(x)$.
+\end{lemma}
+\begin{proof}
+If $x$ is not $\bP^1$-isolated (i.e., $x$ is $\bP^1$-parametrized), then 
+by Lemmas \ref{lem:iso1} and \ref{lem:iso2} $x$ lies on a $\PP^1$ inside of $X^{(d)}$ and $f(x)$ lies on the image of this $\PP^1$ (which is again a $\PP^1$ by \Cref{lem:map to Symd} or because the induced morphism on the $d$-th symmetric power is again finite) inside of $Y^{(d)}$.
+Now the conclusion follows by \Cref{lem:iso1}.
+\end{proof}
+
+\begin{proposition} \label{Genus0Prop}
+Let $E/\Q$ be an elliptic curve with mod $N$ image $G(N)$ of genus $0$ and $N$ a positive integer. Then there does not exist a point corresponding to $E$ on $X_1(N)$ that is $\PP^1$-isolated.
+\end{proposition}
+\begin{proof}
+Let $x$ be a $\Q$-rational point on $X_{G(N)}$ corresponding to $E$.
+
+%Let $B$ be the group generated by $G(n)$ and a conjugate of $B_1(n)$ in $\GL_2(\Z/n\Z)$; this is again a group of genus $0$ on which the image $P'$ of $P$ under the map $X_{G(n)}\rightarro X_B$ is $\Q$-rational.
+The inclusion of subgroups $B\subset B_1(n)$ induces a map $X_1(n)\rightarrow  X_B$.
+
+Let $(E,P)=\abedit{y} \in X_1(N)$ correspond to $E$.
+Let $B \colonequals B_1(N) \cap c(G(N))$ in $c(G(N))$, where $c$ denotes the appropriate choice of conjugation in $\GL_2(\Z/N\Z)$ such that $P$ is an element of the basis inducing the mod $N$ representation.
+Let $d \colonequals [\pm c(G(N)) : \pm B]$.
+%\abbey{Seems like we'd want to take the conjugate of $G(N)$ such that $P$ is the first basis element, but keep $B_1(N)$ as is.
+Also, we want the index of $\pm B$ in $\pm G(N)$.} \filip{Yes, fixed.}
+
+Let $f\colon X_{B}\rightarrow X_{G(N)} \simeq \PP^1$ be the corresponding degree $d$ map of modular curves.
+%\timo{One has $\deg(x) = \deg(f(x))$ [yes, but this is not what we need]: $B$ is the exact stabilizer of $x$ in $G(N)$, so the fiber above $f(x)$ is completely split, working with quotients $f\colon X/H \to X/G$ by finite groups $H \leq G$ such that $H = G_x$ because $f(x) = Gx = G/Hx$ has $\#G/H = \deg(f)$ preimages.}
+\Cref{lem:map to Symd} yields a non-constant morphism $f^*\colon X_{G(N)} \to X_{B}^{(d)}$ such that $f^*(x)$ lies on a $\PP^1 \simeq X_{G(N)}$.
+Hence $x \in X_B$ is not $\PP^1$-isolated by \Cref{lem:iso1} [irreducible].
+Consider the morphism $g\colon X_B \to X_1(N)$ corresponding to $B \leq B_1(N)$.
+It is totally ramified above $g(x)$ because $B_1(N)$ stabilizes $g(x) = y$ and so does $B$, so the decomposition group of $x$ equals its inertia subgroup.
+Hence it satisfies $\deg(g(x)) = \deg(x)$, so $g(x)$ is not $\PP^1$-isolated by \Cref{lem:iso2}.
+%\abbey{How do we know $f^{-1}(x)$ is irreducible, in order to apply \Cref{lem:iso1}?} \filip{Well because the mod $N$ image is equal to $G(N)$ (and not a subgroup).
+So to get the image to reduce to $B$, we need to go to an extension of the index of $B$ in $G(N)$.
+This is a more general result: if $G\geq H$ are congruence groups of level $N$ and $f:X_H\rightarrow X_G$ and $x$ corresponds to an elliptic curve whose mod $N$ image is $G$ over $\Q$, then the degree of $f^{-1}(x)$ is $\deg f$.} \abbey{Oh, right -- that makes sense.
+Thanks.}
+\end{proof}
+
+\begin{corollary}
+Let $E/\Q$ be an elliptic curve with adelic image $G$ of genus $0$ and $n$ a positive integer. Then there does not exist an $n$ such that a point corresponding to $E$ on $X_1(n)$ is $\PP^1$-isolated.
+\end{corollary}
+\begin{proof}
+Since $G$ is by assumption of genus $0$, it follows that so is $G(n)$. The result then follows from Proposition \ref{Genus0Prop}.
+\end{proof}
+
+\begin{comment}
+are of degree $d$. 
+Let $x'\in f^{-1}(x) \subseteq X_{B}$ be a point corresponding to $E$, and let $g\colon X_{B}\rightarrow X_1(n)$ be the map induced by the inclusion $B_1(N) \supseteq B$.
+The point $x'$ lies on a $\PP^1$ inside $X_B^{(d)}$ and hence $g(x')$ lies on a $\PP^1$ inside $X_1(n)^{(d)}$.
+Since no Abelian variety has $\PP^1$ as a subvariety, $\Phi_d$ contracts this $\PP^1$ inside $X_1(n)^{(d)}$ to a single point; it follows that $g(x')$ is not $\PP^1$-isolated.
+
+We have the following commutative diagram:
+
+$$
+\xymatrix{
+& X_B \ar[r]^{g} \ar[d]^{f} & X_1(N) \ar[d]^{q} \\
+&X_{G(N)} \ar[r]^{h} & X_{G'},
+}
+$$
+where $G'$ is defined to be the subgroup of $\GL_2(\Z/N\Z)$ generated by the union of $B_1(N)$ and $G(N)$, and the maps $q:X_1(N) \rightarrow X_{G'}$ and $h:X_G(N) \rightarrow X_{G'}$ are induced by the inclusion of the corresponding subgroups.
+The curve $X_{G'}$ is obviously of genus $0$ as it is covered by $X_{G(N)}$ of genus 0.
+
+As $g(x')$ is of degree $d$ and $q(g(x'))=h(x)\in X_{G'}(\Q)$, it follows $\deg q\geq d$. Alternatively, the same conclusion follows from $\deg q=[\pm G':\pm B_1(N)]\geq [\pm G':\pm B]=d. $
+
+\filip{Work in progress.
+If we prove $\deg q=d$, we are done.
+There's a more general question here, which I think is interesting: given a morphism $f:X\rightarrow \PP^1$ over $\Q$, with genus of $X$ at least 2, is it possible that there's infinitely many points of degree $<d$ in $f^{-1}(\PP^1(\Q))$.
+For $d=2$, the answer is no, and I think this might be the case in general.
+If anyone knows of a reference (or proof) of this, let me know; this would complete the proof of this lemma.
+} \abbey{Seems like you'd want some sort of strong form of Hilbert's irreducibility for this?
+I hadn't thought of this before...
+I believe there are infinitely many $c\in\Q$ such that $f-c$ is irreducible, which gives infinitely many degree $d$ points.
+So you want to know whether there are only finitely many $c$ such that $f-c$ is reducible?
+It looks like in some cases something like this is true (e.g., ``Finiteness results for Hilbert's irreducibility theorem" by M\"{u}ller), but not in general.}
+\filip{Yes, this would be some strong form of Hilbert's irreducibility.
+Is there a single example, of an $X$ of genus $\geq 2$ and $f$, where $f$ does not factor as $f=f_1\circ f_2$  with $\deg f_i>1$ (otherwise there can be many counterexamples), where this is not true?}
+\end{comment}
+
+%\filip{I remember what the issue was: we construct maps $X_B\rightarrow X_{G(n)}$ and $f:X_B\rightarrow X_1(n)$, and show that the point associated to $E$ on $X_B$ is not $\PP^1$-isolated.
+But I don't know how to show that this would imply that the image of this point under $f$ is not $\PP^1$-isolated.
+}\\
+%\filip{This is I think a more general group theoretic problem: we have a subgroup $A$ of $G(n)$ of index $d$, i.e.
+$[G(n):A]=d$, where $A\leq B_1(N)$ (or some conjugate of $B_1(n)$).
+Then we ask what is the index of $B_1(N)$ in the group generated by $G(n)$ and $B_1(n)$.
+If the answer is again necessarily $d$ (or we can always choose a conjugate of $B_1(n)$) such that the index is $d$, then we are good.}
+
+\section{Primitive Points on Modular Curves}
+\abbey{New section which answers Zev's question about the PrimitiveDegreesOfPoints algorithm in the affirmative.}
+At a high level, our algorithm to decide whether a given $E$ defined over $\Q$ is \abedit{gives rise to} an isolated point on $X_1(N)$ for some $N\geq 1$ proceeds in two steps.
+First, we reduce this to a finite computation by computing a level $n$ associated to the adelic image of $E$ so that we need only consider levels $m|n$.
+Next, we try to reduce the  levels $m|n$ which we need to check: our filters for non-isolated points work better for points of lower level, in general.
+In this section, we introduce a notion of a primitive point on a modular curve.
+For a computable integer $m$ \abbey{We don't need any restrictions here -- $m$ doesn't have to correspond to the level.
+The point is that any isolated point on $X_1(n)$ for $n \mid m$ will map down under the natural projection map to a primitive point which is isolated by \cite[Theorem 4.3]{BELOV}.
+So I think it's better to postpone discussion of the level until later sections.} associated to the adelic image of $E$, the $m$-primitive points above $E$ of degree $d$ on $X_1(a)$ will have the property that any isolated point on $X_1(N)$ for any $N$ will map, under the natural map, to some primitive  point \abedit{which is isolated}.
+
+Let $m\geq 1$ be an integer.
+We now define the $m$-primitive points above a given elliptic curve $E$ defined over $\Q$.
+We begin by defining a directed graph $G=G(E,m)$ on the points of $X_1(n)$ \abedit{corresponding to $E$} for $n|m$.
+The vertices of $G(E,m)$ are tuples $(x,n,d)$ where:
 \begin{enumerate}
-\item If $x$ is $\mathbf{P}^1$-isolated, then $f(x)$ is $\mathbf{P}^1$-isolated.
-\item If $x$ is AV-isolated, then $f(x)$ is AV-isolated.
-\item If $x$ is sporadic, then $f(x)$ is sporadic.
+    \item $n|m$,
+    \item $x$ is a degree $d$ point on $X_1(n)$, and 
+    \item $j(x)=j(E)$.
 \end{enumerate}
-\end{theorem}
+We connect $(x,n,d)$ with an arrow to $(x',n',d')$ if: 
+\begin{enumerate}
+    \item $n'$ is a proper divisor of $n$,
+    \item $x'=f(x)$ where $f\colon X_1(n)\to X_1(n')$ is the natural map, and
+    \item $d=d'\cdot \deg f$.
+\end{enumerate}
+
+This is a directed acyclic graph. A \textbf{sink} in a directed acyclic graph is a vertex with no outgoing edges, and a \textbf{source} is a vertex with no incoming edges.
+
+\begin{definition}\label{def:mprimitive}
+    Let $E$ be an elliptic curve over $\Q$ and let $m\geq 1$ be an integer.
+The \textbf{$m$-primitive points} above $E$ are the sinks \abedit{of} $G(E,m)$.
+The \textbf{$m$-primitive degrees} are the tuples $(n,d)$, where $(x,n,d)$ is $m$-primitive for $E$.
+\travis{multiplicity?}
+\end{definition}
+In Section~\ref{sec:primitivedeg}, we give an algorithm for enumerating the sinks of $G(E,m)$. 
+\begin{remark}
+Suppose $n'' | n' | n | m$ and that $(x,n,d), (x',n',d'), (x'',n'',d'')$ are vertices.
+This graph is \textbf{transitive}, meaning that if there is an arrow from $(x,n,d)$ $(x',n',d')$ and from $(x',n',d')$ to $(x'',n'',d''),$ then
+there is also an arrow from $(x,n,d)$ to $(x'',n'',d'')$.
+\travis{Moreover, if there is an arrow from $(x,n,d)$ to $(x'',n'',d''),$ then we  claim there \abedit{is} an arrow from $(x,n,d)$ to $(x',n',d')$, \abedit{where $x'$ is the image of $x$ on $X_1(n')$ and $n'$ properly divides $n$}.
+Intuitively, if the degree grows as much as possible from level $n''$ to level $n$ then it also grows as much as possible from level $n'$ to level $n$.
+Indeed: let $g_1:X_1(n) \rightarrow X_1(n')$ and $g_2:X_1(n') \rightarrow X_1(n'')$.
+Suppose for the sake of contradiction that  $\abedit{d}<\abedit{d'}\cdot\deg g_1$.
+But since $\abedit{d'} \leq \abedit{d''} \cdot \deg g_2$, this would imply $\abedit{d}<\abedit{d''} \cdot\deg g_1\cdot \deg g_2 $.
+This contradicts our assumption that there is an arrow from $(x,n,d)$ to $(x'',n'',d'')$.}
+\end{remark}
+
+Now fix a vertex $(x,n,d)$ and consider its \textbf{descendants}, i.e.
+all vertices $(x',n',d')$ reachable by a path from $(x,n,d)$.
+This is a directed acyclic graph with a single source, $(x,n,d)$.
+\abedit{In this section, we will show that this graph has a single sink as well.}    \abbey{Is there standard notation for this?
+I use $D(v)$ below.}
+
+\begin{proposition}\label{Prop:single_sink}
+    Let $m\geq 1$ be an integer and let $E/\Q$ be an elliptic curve. Fix $v=(x,m,d)$ in $G(E,m)$, and consider the subgraph $D(v)$ of all its descendants. Then $D(v)$ has a single sink.
+\end{proposition}
+
+\subsection{Preliminary Results}
+
+\begin{lemma}\label{lem:LCM}
+Let $n_1,n_2 \in \Z^+$ and define $n \coloneqq \lcm(n_1,n_2)$.
+If $g=\gcd(n_1,n_2)$, we let $n_1=g\cdot n_1'$ and $n_2=g\cdot n_2'$.
+Suppose $E/F$ is an elliptic curve, and $P \in E(\overline{F})$ is a point of order $n$.
+If $n_2'P\in E(F)$ and $n_1'P \in E(F)$, then $P \in E(F)$.
+\end{lemma}
 
 \begin{proof}
-This follows from the arguments \cite[$\S5.3$]{BELOV} and \cite[Theorem 4.3]{BELOV}.
-\abbey{This is mentioned in Remark 5.5 of \cite{BELOV} in particular.
-I'm not sure if we should include more details here.}
+Note $n_2'P \in E(F)$ is a point of order $n_1$, and $n_1'P \in E(F)$ is a point of order $n_2$.  Thus there is an element $Q$ of order $n$ in
+\[
+\langle n_2'P, n_1' P \rangle \subseteq E(F).
+\] Since $\langle n_2'P, n_1' P \rangle \subseteq \langle P \rangle$, it follows that the $F$-rational point $Q$ is a generator of $\langle P \rangle$.
+In particular, $P\in \langle Q \rangle$, and so $P\in E(F)$, as desired.
 \end{proof}
 
-\section{Proving that a point is not sporadic}
-The following algorithm is the main procedure for determining a $j$-invariant is not sporadic. It gives an overview of the structure.
+\begin{lemma} \label{lem:compositum_res_fields}
+Let $n_1,n_2 \in \Z^+$ and define $n \coloneqq \lcm(n_1,n_2)$.
+If $g=\gcd(n_1,n_2)$, we let $n_1=g\cdot n_1'$ and $n_2=g\cdot n_2'$.
+Let $x=[E,P] \in X_1(n)$ for an elliptic curve $E$ with $j(E) \neq 0,1728$, and define $x_1=[E,n_2'P] \in X_1(n_1)$ and $x_2=[E,n_1'P] \in X_1(n_2)$.
+The residue field $\Q(x)$ is at most a quadratic extension of the compositum $\Q(x_1)\Q(x_2)$.
+Moreover:
+\begin{enumerate}
+\item If $g>2$, then $\Q(x_1)\Q(x_2)=\Q(x)$.
+\item If $n_1=2$ or if $n_2=2$, then $\Q(x_1)\Q(x_2)=\Q(x)$.
+\end{enumerate}
+\end{lemma}
 
+\begin{proof}
+Since $F_1=\Q(x_1)$ and $F_2=\Q(x_2)$ are both subfields of $F=\Q(x)$, it follows that $F_1F_2$ is as well.
+We will show the degree of $F/F_1F_2$ is at most 2.
+If $n_1=2$ or $n_2=2$, we may assume without loss of generality that $n_2=2$.
+Fix a Weierstrass equation for $E/\Q(j(E))$ so we may take $F_1=\Q(j(E),\mathfrak{h}(n_2'P))$, $F_2=\Q(j(E),\mathfrak{h}(n_1'P))$, and $F=\Q(j(E),\mathfrak{h}(P))$ by Lemma \ref{ResidueFieldLemma}.
+
+There exists $E'/F_1$ such that $\varphi:E \rightarrow E'$ is an isomorphism and $\varphi(n_2'P) \in E'(F_1)$; see, for example, \cite[p.
+274, Proposition VI.3.2]{DR}.
+Moreover, we have $F_2= \Q(j(E),\mathfrak{h}(n_1'P))=\Q(j(E),\mathfrak{h}(\varphi(n_1'P)))$ by \cite[p.
+107]{shimura}.
+In particular, the explicit formulas for $\mathfrak{h}$ as in \cite[p.
+107]{shimura} show that the $x$-coordinate of $\varphi(n_1'P)$ is rational over $F_1F_2$.
+The $y$-coordinate of $\varphi(n_1'P)$ is defined over at worst a quadratic extension $L/F_1F_2$, and $L=F_1F_2$ if $n_2=2$.
+Then $\varphi(P) \in E'(L)$ by Lemma \ref{lem:LCM}.
+Since $\mathfrak{h}(\varphi(P))=\mathfrak{h}(P)$, it follows that $F \subseteq L$.
+
+Suppose that $F/F_1F_2$ is a quadratic extension.
+Then consider $E'/F_1F_2$, and let $\{\varphi(P),Q\}$ be a basis for $E'[n]$.
+Recall that if $\rho_{E',n}(\sigma)=M \in \GL_2(\Z/n\Z)$ with respect to this basis, then $M \pmod{n_1}$ gives $\rho_{E',n_1}(\sigma)$ with respect to the basis $\{n_2'\varphi(P),n_2'Q\}$.
+Similarly, $M\pmod{n_2}$ gives $\rho_{E',n_2}(\sigma)$ with respect to the basis $\{n_1'\varphi(P),n_1'Q\}$.
+Since $n_2'(\varphi(P))$ is $F_1F_2$-rational and only the $x$-coordinate of $n_1'\varphi(P)$ is defined over $F_1F_2$, there is $\sigma\in \Gal_{F_1F_2}$ such that $\sigma(n'\varphi(P))=-n_1\varphi(P)$ and $\sigma(n_2'(\varphi(P))=n_2'\varphi(P)$.
+Thus $\sigma(\varphi(P))=\alpha \varphi(P)+\beta Q$ where $\alpha \equiv 1 \pmod{n_1}$ and $\alpha \equiv -1 \pmod{n_2}$.
+If $g>2$, then $1 \equiv -1 \pmod{g}$, and we have a contradiction.
+\end{proof}
+
+\subsection{Proof of Proposition \ref{Prop:single_sink}}
+The proof of Proposition \ref{Prop:single_sink} will appear as a corollary to the following more general result.
+
+\begin{proposition}\label{Prop:gcd}
+Let $m\geq 1$ be an integer and let $E/\Q$ be an elliptic curve. In $G(E,m)$,
+suppose $(x,n,d)$ is connected by a path to both $(x_1,n_1,d_1)$ and $(x_2,n_2,d_2)$, where $n=\lcm(n_1,n_2)$.
+Then \abedit{if $\gcd(n_1,n_2) \neq n_1,n_2$}, it follows that both $(x_1,n_1,d_1)$ and $(x_2,n_2,d_2)$ connect to $(x_3, \gcd(n_1,n_2),d_3)$.
+
+\end{proposition}
+
+%    \begin{figure}[h] 
+%        \begin{center}
+%        \begin{tikzpicture}[node distance=2cm]
+%        
+%        \node (n){$X_1(n)$};
+%        \node (n1)[below left of=n, node distance=3cm]{$X_1(n_1)$};
+%        \node (n2)[below right of=n, node distance=3cm]{$X_1(n_2)$};
+%        \node (gcd)[below of=n, node distance=4.5cm]{$X_1(\gcd(n_1,n_2))$};
+%        \draw[-] (n) edge node [left]{$f_1$}(n1);
+%        \draw[-] (n) edge node [right]{$f_2$}(n2);
+%        \draw[-] (n1) edge node [left]{}(gcd);
+%        \draw[-] (n2) edge node [left]{}(gcd);
+%
+%        \end{tikzpicture}
+%        \end{center}
+%        \caption{Maps of Modular Curves}
+%    \end{figure}
+
+        \begin{figure}[h] 
+        \begin{center}
+        \begin{tikzpicture}[node distance=1.5cm]
+
+	\node (n){$\Q(x)$};
+        \node (comp)[below of=n]{$\Q(x_1)\Q(x_2)$};
+        \node (n1)[below left of=comp, node distance=2.2cm]{$\Q(x_1)$};
+        \node (n2)[below right of=comp, node distance=2.2cm]{$\Q(x_2)$};
+        \node (gcd)[below of=comp, node distance=3.2cm]{$\Q(x_3)$};
+        \node (Q)[below of=gcd]{$\Q$};
+        \draw[-] (comp) edge node [left]{$\deg(f_1)$ or $\deg(f_1)/2$}(n1);
+        \draw[-] (comp) edge node [right]{$\deg(f_2)$ or $\deg(f_2)/2$}(n2);
+        \draw[-] (n1) edge node [left]{$d_1/d_3$}(gcd);
+        \draw[-] (n2) edge node [right]{$d_2/d_3$}(gcd);
+        \draw[-] (n) edge node [left]{1 or 2}(comp);
+        \draw[-] (gcd) edge node [left]{$d_3$}(Q);
+        \end{tikzpicture}
+        \end{center}
+        \caption{Degrees of Residue Fields}
+    \end{figure}
+
+    \begin{proof}  By assumption, the integer $g=\gcd(n_1,n_2)$ is a proper divisor of both $n_1=gn_1'$ and $n_2=gn_2'$.
+
+    Let $f_1: X_1(n) \rightarrow X_1(n_1)$ and let $f_2: X_1(n) \rightarrow X_1(n_2)$. We consider two cases.
+    \begin{enumerate}
+    \item Suppose $ g>2$, or if $g=1$, that exactly one of $n_1$ or $n_2$ is greater than 2.
+In the latter case, without loss of generality we may assume $n_1>2$, and $n_2=2$.
+Then $\Q(x_1)\Q(x_2)=\Q(x)$ by Lemma \ref{lem:compositum_res_fields}, and so by assumption
+    \begin{align*}
+    [\Q(x_1)\Q(x_2):\Q(x_1)]=\deg(f_1),\\
+    [\Q(x_1)\Q(x_2):\Q(x_2)]=\deg(f_2).
+    \end{align*}
+        It follows from properties of composite fields that $\deg(f_1) \leq \frac{d_2}{d_3}$ and $\deg(f_2) \leq \frac{d_1}{d_3}$; see Figure 1.
+Note that for a prime $p \mid n_1'$, we have $p \nmid g$ if and only if $p \nmid n_2$.
+Similarly, for a prime $p \mid n_2'$, we have $p \nmid g$ if and only if $p \nmid n_1$.
+Thus
+    \begin{align*}
+    \frac{d_1}{d_3} \leq \deg(X_1(n_1) \rightarrow X_1(g))=\deg(f_2),\\
+        \frac{d_2}{d_3} \leq \deg(X_1(n_2) \rightarrow X_1(g))=\deg(f_1).
+    \end{align*}
+    Putting this together, we find that $\frac{d_1}{d_3}=\deg(f_2)$ and $\frac{d_2}{d_3}=\deg(f_1)$, and the conclusion holds.
+    \item Suppose $g=2$ or, if $g=1$, that $n_1,n_2>2$.
+It follows from Lemma \ref{lem:compositum_res_fields} and the same argument as above that $\frac{\deg(f_2)}{2} \leq \frac{d_1}{d_3}$ and $\frac{\deg(f_1)}{2} \leq \frac{d_2}{d_3}$.
+However, since $n_1,n_2>2$ by assumption, we have
+    \begin{align*}
+    \frac{d_1}{d_3} \leq \deg(X_1(n_1) \rightarrow X_1(g))=\frac{1}{2}(\deg(f_2)),\\
+       \frac{ d_2}{d_3} \leq \deg(X_1(n_2) \rightarrow X_1(g))=\frac{1}{2}(\deg(f_1)).
+    \end{align*}
+   Thus $\frac{d_1}{d_3}=\frac{\deg(f_2)}{2}$ and $\frac{d_2}{d_3}=\frac{\deg(f_1)}{2}$, and the conclusion follows. \qedhere
+      \end{enumerate}
+    \end{proof}
+
+\begin{corollary}
+Let $m\geq 1$ be an integer and let $E/\Q$ be an elliptic curve. Fix $v=(x,m,d)\in G(E,m)$, and consider the subgraph $D(v)$ of all its descendants. Then $D(v)$ has a single sink.
+\end{corollary}
+
+\begin{proof}
+Suppose for the sake of contradiction that $D(v)$ has two distinct sinks, $v_1=(x_1,n_1,d_1)$ and $v_2=(x_2,n_2,d_2)$.
+But having a path from $(x,n,d)$ to each of $v_1,v_2$ implies there is a path from $(x',\text{lcm}(n_1,n_2),d')$ to each of $v_1,v_2$.
+But then both $v_1,v_2$ map to $(x_3,\text{gcd}(n_1,n_2),d_3)$ by Proposition \ref{Prop:gcd}, contradicting the fact that they were both sinks.
+
+\abbey{need to rule out case where $\gcd=n_1$ or $n_2$ since removed from proposition}
+%If $n_1 \mid n_2$, then the claim holds since the natural map $X_1(n) \rightarrow X_1(n_1)$ factors through $X_1(n_2)$ in this case \abbey{Add more details.
+Also, this is allowing for a vertex to (trivially) connect to itself...
+modify definition to allow?}; similarly, the claim holds if $n_2 \mid n_1$.
+\end{proof}
+
+\section{Overview of the Main Algorithm}
+\label{sec:mainalg}
+\abbey{Section updated to match revised algorithm; added examples.} The following algorithm is the main procedure for determining whether a given non-CM $j$-invariant in $\Q$ is the image of a $\PP^1$-isolated point on $X_1(N)$ for some $N$ based on results in \cite{BELOV,ZywinaAlgorithm}.
+We note that for any CM $j$-invariant $j$, there exists infinitely many $N\in\Z^+$ for which there is a sporadic point $x\in X_1(N)$ with $j(x)=j$ by \cite[Theorem 7.1]{BELOV}, so it is not necessary to consider them in this algorithm.
+The outline below gives an overview of the structure, while the algorithms to perform particular steps are described in detail in Sections \ref{sec:madicrep} and \ref{sec:primitivedeg}.
+We will prove a theorem on the validity of Algorithm \ref{alg:mainalgorithm} in Section \ref{sec:validity}.
+
+\setcounter{algocf}{0}
 \begin{algorithm}[h!]
 \caption{Main Algorithm}\label{alg:mainalgorithm}
-\KwIn{A non-CM $j$-invariant $j = j(E) \in \Q$ and $a$-invariants for $E$ with $j$-invariant $j$.}
-\KwOut{Finite list of pairs $(n,d)$ such that any isolated point on $X_1(N)$ associated to $E$ maps down under the natural projection map to an isolated point of degree $d$ on $X_1(n)$ in the list. }
-Compute the adelic image $G$ of $E/\Q$ as a subgroup of $\GL_2(\hat{\Z})$ using Zywina's algorithm. Represent the output as some \emph{level} $N$ together with a subgroup $G$ of $\GL_2(\Z/N\Z)$\;
-Using Algorithm \ref{alg:reduce_level}, reduce the level to $G, m_0$\; 
-Define $L \colonequals \{\}$\;
-\For{all $12 < b \mid m_0$}{
-Using Algorithm~\ref{alg:compute_degree} compute the set $D$ of degrees of all fields of definition of a point with respect to $G \mod b$, the image of $G$ in $\GL_2(\Z/b\Z)$\;
-Set $L \colonequals L \cup \{ (b, d) : d \in D\}$ \;}
-Using Algorithm \ref{alg:level_mapping} filter the list $L$ to obtain a refined list $L'$\;
-\Return{the list $L'$ } \;
-    %\filip{We need to look at the orbits of $\langle G, -G \rangle \mod b$ on $(\Z/b\Z)^2$, not $\bP^1(\Z/b\Z)$.
-If we consider the action on $\bP^1(\Z/b\Z)$, the orbits might be too small and hence the degree we get.
-Furthermore, it is necessary to consider only the elements of $(\Z/b\Z)^2$ of order $b$.}
+\KwIn{A non-CM $j$-invariant $j \in \Q$.}
+\KwOut{A list $[j,\{\langle a_1,d_1\rangle, \dots, \langle a_k,d_k\rangle \}]$ such that any isolated point $x \in X_1(N)$ with $j(x)=j$ maps down under the natural projection map to an isolated point of degree $d_i$ on $X_1(a_i)$ for some $1 \leq i \leq k$.}
+Construct an elliptic curve $E/\Q$ with $j(E)=j$.\\
+Compute the adelic image $G$ of $E/\Q$ as a subgroup of $\GL_2(\hat{\Z})$ using Zywina's algorithm \cite{ZywinaAlgorithm}.
+Represent the output as the level $N$ and the subgroup $G(N)$ of $\GL_2(\Z/N\Z)$.\\
+Apply Algorithm \ref{alg:reduce_level} to $G(N)$ to obtain the level $m_0$ of the $m$-adic Galois representation associated to $E$, where $m$ is the product of 2, 3, and all non-surjective primes.\\
+Using Algorithm \ref{alg:compute_prim_degree}, return a multiset $D$ with entries $\langle n, \{\langle a_1, d_1\rangle ,  \dots,  \langle a_r, d_r\rangle \} \rangle$
+    for all positive divisors $n$ of $m_0$ such that the degree of the corresponding 
+    closed point on $X_1(n)$ is as large as possible given that its image on $X_1(a_i) $
+    has degree $d_i$.\\
+Construct the multiset $D' \subseteq D$ containing only those elements $\langle n, \{\langle a_1, d_1\rangle ,  \dots,  \langle a_r, d_r\rangle \} \rangle$ for which $d_i \leq \text{genus}(X_1(a_i))+1$ for all $1 \leq i \leq r$.\\
+Create the multiset $M$ consisting of all pairs $\langle a_i,d_i\rangle $ appearing in $D'$, where $\langle a_i,d_i\rangle $ has multiplicity $\mu$ if and only if $X_1(a_i)$ has $\mu$ distinct closed points of degree $d_i$.\\
+\Return{$[j,M]$}
+
 \end{algorithm}
 
-\begin{theorem}
- Algorithm \ref{alg:mainalgorithm} is correct. 
-\end{theorem}
-\begin{corollary}
-If Algorithm \ref{alg:mainalgorithm} outputs an empty set on some $j$-invariant $j = j(E)$ and $a$-invariants $a$ for $E$, then $j$ is not a  $\mathbf{P}^1$-isolated point on $X_1(N)$.
-\end{corollary}
-\abbey{Zywina said the results returned from his adelic image algrithm are guaranteed to be correct and that ``errors will always occur if $E$ gives rise to an unknown exceptional rational point on certain high genus modular curves." Since an error in his algorithm will result in an error in our algorithm, I don't know what should be said about this in our writeup.} \sachi{maybe the easiest thing is just to add a remark saying that the results are guaranteed to be correct, and getting an error instead of a result is possible but that we did not encounter it?} \timo{I second that.} \abbey{alternatively, separate Zywina's algorithm from ours in this paper}
+In particular, note that if Algorithm \ref{alg:mainalgorithm} outputs $[j,\{\}]$, then $j$ is not the image of any $\mathbf{P}^1$-isolated point on $X_1(N)$, even as $N$ ranges over all positive integers.
+See Corollary \ref{cor:P1_isolated}.
 
-(In the \texttt{Magma} implementation, we have to be careful that \texttt{Magma} uses right actions, but in our mathematics, we use left action.
-We therefore use the transposes of the matrices in $\GL_2(\Z/N\Z)$.)
+\begin{example}
+If $j=-9317$, then Algorithm \ref{alg:mainalgorithm} returns $[j, \{\langle 37,6\rangle ^3\}]$.
+This means that any isolated point $x\in X_1(N)$ with $j(x)=j$ and $N \in \Z^+$ maps down under the natural projection map to one of the 3 closed points of degree 6 on $X_1(37)$.
+In fact, these points are all sporadic by \cite[Proposition 2]{frey}, since $6 < \frac{1}{2} \gon_{\Q}(X_1(37)) = 18$.
+Here, the gonality computation is a result of \cite{DerickxVanHoeij2014}.
+Thus $j$ is a sporadic --- and hence isolated --- $j$-invariant.
+\end{example}
 
-\section{Reduce Level}
+\begin{example}
+If $j=-121$, then Algorithm \ref{alg:mainalgorithm} returns $[j, \{\}]$. This means that there are no isolated points on $X_1(N)$ associated to this $j$-invariant. 
+\end{example}
 
-\abbey{Travis,Sachi, Abbey}
+\begin{example}
+If $j=-882216989/131072$, then Algorithm \ref{alg:mainalgorithm} returns  $[j,\{\langle 17,4\rangle ^2\}]$.
+This means that $j$ is associated to an isolated point on a modular curve of the form $X_1(N)$ if and only if there exists a degree 4 isolated point $x \in X_1(17)$ with $j(x)=j$.
+In Section \ref{sec:remainingfilters}, we will show that no such isolated point exists, from which we can conclude that $j$ is not an isolated $j$-invariant.
+\end{example}
 
-Using Zywina's algorithm for the level of the adelic Galois representation as a starting point, we may obtain the level of the $m$-adic Galois representation associated to $E$ as in Theorem \ref{BELOVthm}.
+\section{\texorpdfstring{Computing the level of the $m$-adic representation}{Computing the level of the m-adic representation}}
+\label{sec:madicrep}
+\abbey{Updated the algorithm description to be less technical; added math proposition to justify; added examples.}
+Let $E/\Q$ be a non-CM elliptic curve, and define the set 
+\[
+S_E\coloneqq \{2,3\} \cup \{ \ell: \rho_{E,\ell^{\infty}}(\Gal_{\Q}) \neq \GL_2(\Z_{\ell}) \}.
+\] For $m \coloneqq \prod_{\ell \in S_E} \ell$, we give an algorithm to obtain the level of the $m$-adic Galois representation associated to $E$ from the image of the adelic representation of $E$.
+In practice, we can obtain $\im \rho_E$ from Zywina's algorithm \cite{ZywinaAlgorithm}.\\
 
 \begin{algorithm}[H]
-  \KwIn{$G\subseteq \GL_2(\Z/N\Z)$ such that $\im\rho_E=\pi^{-1}(G)$ and $N$ is the level}
-  \KwOut{$G\subseteq \GL_2(\Z/m_0\Z)$ such that $G=\im\rho_{E,m_0}$ and $\im\rho_{E,m^{\infty}}=\pi^{-1}(\im\rho_{E,m_0})$ where $m$ is the product of the non-surjective primes and $2$ and $3$ (if they do not already divide $m$), and $m_0$ is minimal }
-  \caption{Reduce level}%
+  \KwIn{$G(N)\leq \GL_2(\Z/N\Z)$ where $\im\rho_E=G$ and $N$ is the level.} 
+  \KwOut{$m_0 \in \Z^+$ the level of $\rho_{E,m^{\infty}}$ for $m= \prod_{\ell \in S_E} \ell$.}
+  \caption{Reduced level}%
   \label{alg:reduce_level}
-  Let $P_E = \{\ell|N \text{ prime} \colon \rho_{E,\ell} \text{ is non-surjective} \}$\;
-  Let $S_E= P_E \cup \{ 2, 3\}$\;
-  Let $m_0 = \prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$\;
-  \For{$p \in \{ \ell | m_0 \colon \ell \text{ prime} \}$}{
-  \While{$p |m_0$ and $\#G/\#(G \pmod{m_0/p}) = p^4$}{
-    $m_0 = m_0/p$\;
-    $G = G \pmod{m_0}$\;
-  }
-  \If{not $p$ in $P_E$ and $\ord_p(m_0) = 1$ and $\#G/\#(G \pmod{m_0/p}) = \#\GL_2(\Z/p\Z)$}{
-  $m_0 = m_0/p$\;
-   $G = G \pmod{m_0}$\;}}
-  \Return{$G,m_0$}
+  Let $n = \prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$.\\
+Compute smallest $m_0$ dividing $n$ such that \[\#G(n)=\#G(m_0) \cdot \#\ker(\GL_2(\Z/n\Z) \rightarrow \GL_2(\Z/m_0\Z)).\]\\
+  \Return{$m_0$}
 \end{algorithm}
@@
   \begin{proposition}
-    Algorithm~\ref{alg:reduce_level} is correct.
+  Let $E/\Q$ be a non-CM elliptic curve, and let $\im \rho_E=G \leq \GL_2(\widehat{\Z})$ be a subgroup of level $N$.
+Define $n \coloneqq \prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$.
+If $m_0$ is the smallest positive integer dividing $n$ such that \[\#G(n)=\#G(m_0) \cdot \#\ker(\GL_2(\Z/n\Z) \rightarrow \GL_2(\Z/m_0\Z)),\] then $m_0$ is the level of the $m$-adic Galois representation associated to $E$ for $m= \prod_{\ell \in S_E} \ell$.
   \end{proposition}
   \begin{proof}
-    Since $N$ is the level of the adelic representation and both $m$ and $m_0$ divides $N$, we must have that $\im\rho_{E, m^\infty} = \pi^{-1}(\im \rho_{E,m_0})$.
-This property is an invariant of the for-loop.
-The for-loop
-    terminates once as many powers of $\ell$ have been removed from $m_0$
-    as possible while maintaining this invariant. Thus $m_0$ is the minimal such integer and is thus the level.
+  First we will show that $\im \rho_{E,m^{\infty}}=\pi_1^{-1}(G(n))$, where $\pi_1:\prod_{\ell \in S_E} \GL_2(\Z_{\ell}) \rightarrow \GL_2(\Z/n\Z)$ is the natural reduction map.
+It suffices to show that $\ker \pi_1 \subseteq \im \rho_{E,m^{\infty}}$.
+We have $N=n\cdot n'$ with $(n,n')=1$, and so we may identify $G(N)$ as a subgroup of $\GL_2(\Z/n\Z) \times \GL_2(\Z/n'\Z)$.
+Under this identification, let $H$  be the intersection of $G(N)$ with the subgroup $\{I\} \times \GL_2(\Z/n'\Z)$.
+Then since $G$ has level $N$,
+  \[
+  \pi^{-1}(H) \subseteq \im \rho_E,
+  \]
+  where $\pi: \GL_2(\widehat{\Z}) \rightarrow \GL_2(\Z/N\Z)$ is the natural reduction map.
+The image of this subset relation under the natural projection map  $\GL_2(\widehat{\Z}) \cong \prod_{\ell} \GL_2(\Z_{\ell}) \rightarrow  \prod_{\ell \in S_E} \GL_2(\Z_{\ell}) $ gives
+  \[
+  \ker(\pi_1) \subseteq \im \rho_{E,m^{\infty}},
+  \]
+  as desired.
+
+Let $\pi_2: \GL_2(\Z/n\Z) \rightarrow \GL_2(\Z/m_0\Z)$ be the natural reduction map.
+The assumption on $m_0$ implies that $\ker(\pi_2) \subseteq G(n)$, so it follows that $G(n) = \pi_2^{-1}(G(m_0))$.
+Thus if $\pi_3: \prod_{\ell \in S_E} \GL_2(\Z_{\ell}) \rightarrow \GL_2(\Z/m_0\Z)$ denotes the reduction map, we have
+  \begin{align*}
+  \pi_3^{-1}(G(m_0))&=\pi_1^{-1}(\pi_2^{-1}(G(m_0))\\
+  &=\pi_1^{-1}(G(n))\\
+  &=\im \rho_{E,m^{\infty}}.
+  \end{align*}
+By construction $m_0$ is the smallest positive integer with this property.
   \end{proof}
 
-\abbey{give example}
+  \begin{corollary}
+  Algorithm \ref{alg:reduce_level} is correct.
+  \end{corollary}
 
-\section{Compute Degrees}
+  \begin{example}
+Suppose $E/\Q$ is a non-CM elliptic curve such that $\rho_{E}$ has level $N$.
+As above, define $n=\prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$ and let $m_0$ be the level of $\rho_{E,m^{\infty}}$ for $m= \prod_{\ell \in S_E} \ell$.
+It follows that $m_0| n$ and $n | N$.
+Each of these divisibilities can be proper.
+For example, if $E=75072.bc2$, we see that $\rho_E$ has level $N=4682=2^2 \cdot 3 \cdot 17 \cdot 23$.
+Since 2 is the only non-surjective prime, $n=2^2$.
+However, the level of the $m$-adic Galois representation associated to $E$ is 2.
+On the other hand, it can also happen that $N=m_0$.
+For example, if $E=54.b2$, we see that $\rho_E$ has level 72, and this is also the level of the $m$-adic Galois representation associated to $E$.
+\end{example}
 
-The following algorithm computes the degrees of closed points on $X_1(N)$ associated to $E$.
+\section{Compute Primitive Degrees}
+\label{sec:primitivedeg}
+% \abbey{Travis is working to update this section; I updated input/output description to match that in our isolatedpoints.m file}
+% (In the \texttt{Magma} implementation, we have to be careful that \texttt{Magma} uses right actions, but in our mathematics, we use left action.
+We therefore use the transposes of the matrices in $\GL_2(\Z/m\Z)$.) \sachi{maybe the previous sentence is too technical for the start of the section / can be cut?} \travis{agreed}
+
+Let $E$ be an elliptic curve over $\Q$ and let $m\geq1$ be an integer.
+In this section, we discuss an algorithm for computing the list  of $m$-primitive degrees.
+At a high level, we are simply traversing the graph $G(E,m)$, always beginning at a source, until finding a sink.
+The sinks are the $m$-primitive points, and we record the associated $m$-primitive degree.
+We only retain the level $n$ and degree $d$ of a $m$-primitive point $(x,n,d)$ since, in our main algorithm, we will often try show that $X_1(n)$ has no isolated points of degree $d$ at all.
+The input to the algorithm is $G=\im \rho_{E,m}\leq \GL_2(\Z/m\Z)$.
+We represent $m$-primitive degrees as tuples $( a,d)$ where $a$ is the level of the point $x\in X_1(a)$ and $d=\deg x$.
+% , meaning a list whose entries are lists of tuples $\{ \langle a_1,d_1\rangle,\ldots\}$ with the following properties: 
+% \begin{enumerate}
+%     \item if there is $N\in \Z_{>0}$ and a point $x$ on $X_1(N)$ above $j(E)$ which is isolated, then there exists some $\{\langle a_1,d_1\rangle,\ldots\}$ in $L$ and a tuple $\langle a_i,d_i\rangle$ such that $a_i|N$ and there is an isolated point $y=f(x)$ of degree $d_i$ on $X_1(a_i)$ above $j(E)$, where $f\colon X_1(N)\to X_1(a_i)$ is the natural map;
+%     \item for a given entry $\{\langle a_1,d_1\rangle,\ldots\}$ in $L$, there are no $i,j$ such that $a_i|a_j$. 
+% \end{enumerate} 
+% We call the entries of $L$ primitive degrees because any isolated point on any modular curve $X_1(N)$ will map to a point of degree $d_i$ on $X_1(a_i)$ where $\langle a_i,d_i\rangle$ occurs as a tuple in some entry of $L$, and the levels $a_i$ are minimal (with respect to divisibility) with this property.
+% The following algorithm computes a primitive degrees $\langle a,d\rangle$ for isolated points on $X_1(a)$ of degree $d$ above a non-CM curve $E$.
+Let $m$ be the level of the $m_0$-adic representation where $m_0$ is divisible by $2$, $3$, and the non-surjective primes.
+The points produced by this algorithm are primitive in the sense that the image under the natural map $X_1(m)\to X_1(a)$ of any isolated point above $E$ on $X_1(n)$ will be an isolated point on $X_1(a)$.
+% the degrees of closed points on $X_1(m)$ associated to a \abedit{non-CM elliptic curve $E/\Q$}.
 
@@
 
-\begin{algorithm}[H] \caption{Compute Degree}\label{alg:compute_degree}
-  \KwIn{$G\subseteq \GL_2(\Z/N\Z)$ such that $\im\rho_E=\pi^{-1}(G)$ and $N$ is the level}
-  \KwOut{all degrees of $x$-coordinates of points}
-  Let $H \colonequals \langle G, -I_2\rangle \leq \GL_2(\Z/N\Z)$\;
-  Compute the orbits of $H$ acting on $(\Z/N\Z)^2$\label{Inc-1}\;
-  Filter the orbit representatives for orbits that have order equal to $N$\;
-  Compute the orbit sizes $s$ and ``degrees'' as $s/2$ \label{DivBy2}\;
-  Remove duplicates\label{RemDup}\;
-  \Return{degrees}
+\begin{algorithm}[H] \caption{Compute Primitive Degrees}\label{alg:compute_prim_degree}
+  \KwIn{$G\leq \GL_2(\Z/m\Z)$ such that $\im\rho_{E,m}=G$}
+  \KwOut{The multiset of $m$-primitive degrees for $E$}
+  % multiset with entries $\langle n, \{\langle a_1, d_1\rangle,  ...
+\}\rangle$ for all positive divisors $n$ of $m$ such that the degree of the corresponding closed point on $X_1(n)$ is as large as possible given that its image on $X_1(a_i)$ has degree $d_i$ \abedit{and no $a_i \mid a_j$ for $i \neq j$}}
+  % \travis{I think this should say something like: A multiset with entries $\langle n, \{\langle a_1, d_1\rangle,  ... \}\rangle$ 
+  % in bijection with the closed points $(E,P)$ in $X_1(n)$ above $E$, where $n$ divides $m$ and $(E,P)$ maps down to a point $(E,\frac{m}{n}P)$ on $X_1(n)$ of degree }\abbey{But it's not returning all divisors $a_i$ of $n$.}\travis{right the code appends
+  % one element to the output per orbit, i.e.
+per point in X1m above E, i think?}\abbey{I think in theory it could return $a_1,a_2$ if a certain divisibility condition is not satisfied (the ``b mod a ne 0" part of the code).
+I don't think there are any examples of this, but this is interesting in its own right.}
+  Let $H \colonequals \langle G, -I_2\rangle \leq \GL_2(\Z/m\Z)$\;
+  Compute the orbits $O$ of $H$ acting on $(\Z/m\Z)^2$\label{Inc-1}\;
+  Let $D= \{\}$\;
+  \For{each orbit $vH\in O$}{ \label{alg:compute_primitive_degrees:minimal_levels}
+  Let $n$ be the order of $v$ in $(\Z/m\Z)^2$\;
+  Let $L= \{\}$\;
+  \For{$a|n$}{
+  \If{$\deg x = \deg y \cdot \deg f$, where $x$ corresponds to $vG$, 
+  $f\colon X_1(n)\to X_1(n/a)$ is the natural map, and $y=f(x)$}{
+  Append $(n/a,\deg y)$ to $L$\;
+  }
+  }
+  Remove all $( a,d)\in L$ such that there exists $(a',d')\in L$ with $a'$ properly dividing $a$\; 
+  Append $L$ to $D$\;
+  } 
+  % compute all tuples $\langle a,d\rangle$ such that $a|n$, the point $x=(E,P)\in X_1(n)$ corresponding to $vH$ maps to $y=(E,\frac{n}{a}P)\in X_1(a)$ with $\deg y = d$, $\deg x = (\deg f)(\deg y)$, and $a$ is minimal with respect to the divisibility ordering\;
+
+  % Filter the orbit representatives $R$ for orbits $O$ \travis{representatives?} that have order equal to $N$ in $(\Z/N)^2$\;
+  % For each element of $R$, compute the orbit sizes $s$ and their ``degrees'' as $s/2$; store the degees in $D$\label{DivBy2}\;
+  % Remove duplicates in $D$\label{RemDup}\;
+  \Return{$D$}
 \end{algorithm}
 
-Note that only working with orbit(s) (representatives) significantly speeds up the implementation. The computation of the orbits of $G$ acting on $(\Z/N\Z)^2$ is efficiently implemented in Magma.
+\abbey{In practice, it appeared that for an element $\langle n, \{\langle a_1, d_1\rangle,  \ldots \}\rangle$ in the output of this algorithm, the set $\#\{\langle a_1, d_1\rangle,  \ldots \}$ contains only 1 element.
+(Zev's observation) See section 4 for a proof of this.}
 
-\begin{proposition}
-Let $E/\Q$ be a non-CM elliptic curve and $N \in \Z_{>0}$.
-If $\im \rho_{E,N} \cong G \leq \GL_2(\Z/N\Z)$, then the Algorithm \ref{alg:compute_degree} outputs the sequence consisting of all possible degrees of $x(P)$, where $P\in E[N]$ is a point of order $N$.
+We briefly discuss how we execute the loop in Step~\ref{alg:compute_primitive_degrees:minimal_levels} in Algorithm~\ref{alg:compute_prim_degree}.
+The orbits of $H$ acting on $(\Z/m\Z)^2$ are in bijection with the elements in the multiset output by Algorithm~\ref{alg:compute_prim_degree}.
+We discuss how we build the list in $L$ corresponding to an orbit orbit $x=vH$, where $v\in (\Z/m\Z)^2$ is a representative $x$.
+We initialize $L$ to the empty list.
+Let $n$ be the order of $v$ in $(\Z/m\Z)^2$.
+For a divisor $a$ of $n$, we compute the orbit $y=avH$ of $av$ under the action of $H$.
+These orbits $x$ and $y$ correspond to points $(E,P)$ and $(E,aP)$ on $X_1(n)$ and $X_1(\frac{n}{a})$.
+Proposition~\ref{prop:compute_degrees} below allows us to compute $\deg x$ and $\deg y$ from $n,n/a,\#vH$, and $\#avH$.
+If  $\deg(x)/\deg(y)=\deg(f)$ then we include $( \frac{n}{a},\deg y)$  in the list $L$.
+% ($\deg y$ is computed as $c\#dvH$ where $c=\frac{1}{2}$ if $ed\leq 2$ and $c=1$ otherwise). 
+After repeating this procedure for each divisor of $n$,  we remove every element $( a,d)$ of $L$ such that there exists $( a',d') $ with $a'|a$ and $a'\not=a$. This corresponds to identifying the 
+sinks in the subgraph $G(E,m)$ consisting of vertices reachable by a path from the point $(x,n,\deg x)$: we simply enumerate every vertex reachable from $(x,n,d)$, and remove every vertex which is not a sink.
+
+The following proposition allows us to calculate the degrees of $x$ and $y$ from the data $n,n/a,\#vH$ and $\#avH$.
+
+\begin{proposition}\label{prop:compute_degrees}
+Let $E/\Q$ be a non-CM elliptic curve and $m \in \Z_{>0}$.
+Let $\im \rho_{E,m} \cong G \leq \GL_2(\Z/m\Z)$ and let $H=\langle G,-I\rangle$.
+Let $v\in (\Z/m\Z)^2$ have order $n|m$ and let $(E,P)$ be a representative of the point $x$ of $X_1(n)$  corresponding to $vG$.
+If $n>2$, the degree of $x$ is $\#vH/2$.
+If $n\leq 2$, the degree of $x$ is
+$\#vH=\#vG$. 
 \end{proposition}
+
 \begin{proof}
-    We begin by noting that $(E, P)$ and $(E, -P)$ \abbey{induce the same closed} point on $X_1(N)$, for $P \in E[N]$. Therefore, the degree of
-    a point represented by $(E, P)$, when
-    $E$ is defined over $\Q$ depends only on $x(P)$.
-    If $E[N]$ is identified with $(\Z/N\Z)^2$, then $\deg(P)=\# (G. P)$, where $P$ on the left hand side is considered as an element of $(\Z/N\Z)^2$
-    and on right hand side as an element of $E[N]$.
-    If $P$ and $-P$ are in the same Galois orbit, i.e., $-I_2\in G$, then $[\Q(x(P)):\Q]=[\Q(P):\Q]/2$. On the other hand, one has $[\Q(x(P)):\Q]=[\Q(P):\Q]$, when
-    $-I_2\notin G$.
-    Therefore, computing the orbit sizes with respect to the
-    group $H\coloneqq \langle G, -I_2 \rangle$ (step~\ref{Inc-1} in Algorithm \ref{alg:compute_degree}) and dividing
-    by $2$ (step~\ref{DivBy2}) handles both the cases, because in the later case (i.e., when $-I_2\notin G$) the orbit sizes will be doubled.
-    Finally, step~\ref{RemDup} makes sure that every degree occurs only once in the output sequence.
+    We begin by noting that $(E, P)$ and $(E, -P)$ induce the same closed point $x$ on $X_1(n)$. Therefore, since $E$ is defined over $\Q$, the degree of
+    $x$ depends only on $x(P)$ and is equal to $[\Q(x(P)):\Q]$. 
+    % Indeed: assuming $E$ is given by $y^2=f(x)$, if $d=f(x(P))$ is not a square in $\Q(x(P))$, then the quadratic twist $E^{(d)}:dy^2=f(x)$ has the $\Q(x(P))$-rational point $P'=(x(P),1)$ of order $n$, and $(E^{(d)},P')$ represents the same point as $(E,P)$.
+    We next observe that $[\Q(P):\Q]=\#vG$.
+Assume that $n>2$.
+When $-I\in G$, the points $P$ and $-P$ are distinct and in the same Galois orbit so $[\Q(x(P)):\Q]=[\Q(P):\Q]/2$ and $\#vH=\#vG$.
+We conclude that
+    \[
+    \deg x = [\Q(x(P)):\Q] = [\Q(P):\Q]/2 = \frac{1}{2}\#vG = \frac{1}{2}\#vH. 
+    \]
+    % To see this: let $L$ be the Galois closure of $\Q(P)/\Q$. We have that 
+    % \[
+    % \#vG = \#\Gal_{\Q} P = \#\Gal(L/\Q) P = \frac{\Gal(L/\Q)}{\#\{\sigma\in \Gal(L/\Q):\sigma(P)=P)\}} = \frac{[L:\Q]}{\#\Gal(L/\Q(P))}=\frac{[L:\Q]}{[\Q(P):\Q]}=[\Q(P):\Q].
+    % \]
+    If $-I \notin G$, then $\#vH=2\#vG$.
+There exists a twist $E'$ of $E/\Q$ such that $\im \rho_{E',n}=\langle G, -I \rangle$ by \cite[Corollary 5.25]{sutherland}.
+The point $(E,P)$ is also represented by $(E',P')$ for some $P'\in E'[n]$, and the same argument from above  implies
+    \[
+    2\#vG=\#vH = [\Q(P'):\Q] = 2[\Q(x(P')):\Q] = 2[\Q(x(P)):\Q],
+    \]
+    so we again have that the degree of the point represented by $(E,P)$ is $\#vH/2$.
+
+    Now assume $n\leq 2$. Then $-I=I$ in $\GL_2(\Z/n\Z)$ so $G=H$, and $\Q(x(P))=\Q(P)$. We conclude 
+    \[
+    \deg x = [\Q(x(P)):\Q] = [\Q(P):\Q] = \#vG = \#vH. \qedhere
+    \]
 \end{proof}
 
-\section{Filtering by Level Mapping}
+% Clearly the output of Algorithm~\ref{alg:compute_prim_degree} satisfies property (ii), since we simply remove entries $\langle a_i,d_i\rangle$ if there is some other entry $\langle a_j,d_j\rangle$ with $a_j|a_i$.
+The following proposition implies that the output is correct, i.e.
+the output satisfies property (i).
+% \begin{proposition}\label{prop:primitve_degrees}
+%     Let $E$ be a non-CM elliptic curve over $\Q$ with associated $m$-adic Galois representation $G=\im\rho_{E,m}\subseteq \GL_2(\Z/m_0\Z)$, where $m$ is the product of $2,3,$ and non-surjective primes and $m_0$ is the level of the representation.
 
-\begin{theorem}[\cite{BELOV}]\label{BELOVthm}
+%     On input $G$, Algorithm~\ref{alg:compute_prim_degree} returns a list $L$ of lists of tuples $\langle a,d\rangle$ with the following property: if there exists some $N\geq 1$ and isolated point $x\in X_1(N)$ with $j(x)=j(E)$, then there exists a tuple $\langle a,d\rangle$ in $L$ such that $a|N$ and $f(x)\in X_1(a)$ is isolated, where $f\colon X_1(N)\to X_1(a)$ is the natural map.
+% \end{proposition}
+
+% \begin{proof}
+%     This follows from Theorems~\ref{thm:PushingForwardSporadicIsolated} and \ref{BELOVthm}.
+\travis{these appear in the next section.
+We can move them up before this section, mention that Proposition~\ref{prop:primitve_degrees} will be proven in the next section in the proof of Theorem~\ref{thm:validity_main_algorithm}, or just omit the proposition and mention that we will prove the correctness of Algorithm~\ref{alg:compute_prim_degree} while we prove correctness of Algorithm~\ref{alg:mainalgorithm}.}
+% \end{proof}
+% Note that only working with orbit(s) (representatives) significantly speeds up the implementation. The computation of the orbits of $G$ acting on $(\Z/N\Z)^2$ is efficiently implemented in Magma.
+
+% \begin{proposition}
+% Let $E/\Q$ be a non-CM elliptic curve and $N \in \Z_{>0}$.
+If $\im \rho_{E,N} \cong G \leq \GL_2(\Z/N\Z)$, then the Algorithm \ref{alg:compute_degree} outputs the sequence consisting of all possible degrees of $x(P)$, where $P\in E[N]$ is a point of order $N$.
+% \end{proposition}
+% \begin{proof}
+%     We begin by noting that $(E, P)$ and $(E, -P)$ \abedit{induce the same closed} point on $X_1(N)$, for $P \in E[N]$. Therefore, the degree of
+%     a point represented by $(E, P)$, when
+%     $E$ is defined over $\Q$ depends only on $x(P)$.
+%     If $E[N]$ is identified with $(\Z/N\Z)^2$, then $\deg(P)=\# (G. P)$, where $P$ on the left hand side is considered as an element of $(\Z/N\Z)^2$
+%     and on right hand side as an element of $E[N]$\travis{should this be right/left instead of left/right? what is the degree of a point in $(\Z/N)^2$?}.
+%     If $P$ and $-P$ are in the same Galois orbit, i.e., $-I_2\in G$, then $[\Q(x(P)):\Q]=[\Q(P):\Q]/2$. On the other hand, one has $[\Q(x(P)):\Q]=[\Q(P):\Q]$, when
+%     $-I_2\notin G$ \abbey{I don't think this last sentence is true.
+(Filip, didn't you orginally have a comment here?) Consider an elliptic curve with Galois image 7Ns.2.1, which does not contain $-I$.
+There is a $P$ such that $\Q(P)$ has degree 18 but $\Q(x(P))$ has degree 9.
+Alternatively, one can note that if $-I \notin G$, then there exists a twist $E'$ of $E/\Q$ such that $\im \rho_{E',N}=\langle G, -I \rangle$ by \cite[Corollary 5.25]{sutherland}, and we can divide by 2 b/c of your first argument.
+Degrees of (closed) points on $X_1(N)$ are not impacting by replacing a curve by its twist.} \filip{Yes, I had written that it should be the other way round, then got confused during the Zoom talk and deleted it.
+It should in fact be the other way round.}
+%     Therefore, computing the orbit sizes with respect to the
+%     group $H\coloneqq \langle G, -I_2 \rangle$ (step~\ref{Inc-1} in Algorithm \ref{alg:compute_degree}) and dividing
+%     by $2$ (step~\ref{DivBy2}) handles both the cases, because in the later case (i.e., when $-I_2\notin G$) the orbit sizes will be doubled.
+%     Finally, step~\ref{RemDup} makes sure that every degree occurs only once in the output sequence.
+% \end{proof}
+
+\section{Validity of Main Algorithm}
+\label{sec:validity}
+
+\abbey{New section.} In this section, we will prove results on the validity of our Main Algorithm as stated in Section \ref{sec:mainalg}.
+After recording preliminary results in Section \ref{sec:prelimresult}, we will give the proof in Section \ref{sec:proofvalidity}.
+The section concludes with an additional example.
+
+\subsection{Preliminary Results}
+\label{sec:prelimresult}
+One of the key strategies of our algorithm is to exploit instances where the image of an isolated point is isolated. A prototypical result of this nature is the following.
+\begin{theorem}[\cite{BELOV}, Theorem 4.3]
+\label{thm:PushingForwardSporadicIsolated}
+    Let $f\colon C \to D$ be a finite map of curves, let $x\in C$ be a closed point, and let $y = f(x) \in D$.  Assume that $\deg(x) = \deg(y)\cdot\deg(f)$.
+    \begin{enumerate}
+        \item If $x$ is $\PP^1$-isolated, then $y$ is $\PP^1$-isolated.
+                \item If $x$ is $AV$-isolated, then $y$ is $AV$-isolated.
+        \item If $x$ is sporadic, then $y$ is sporadic.
+    \end{enumerate}
+\end{theorem}
+
+In the case where $C$ is a modular curve, this condition can be translated into one involving arithmetic properties of the corresponding elliptic curves.
+Though result stated below is formulated for more general elliptic curves in \cite{BELOV}, we record here the version for elliptic curves over $\Q$.
+
+\begin{theorem}[\cite{BELOV}, Theorem 1.1]\label{BELOVthm}
 Let $E/\Q$ be a non-CM elliptic curve, and let $m$ be the product of 2, 3, and all primes $\ell$ where the $\ell$-adic Galois representation of $E$ is not surjective.
-Let $m_0$ be the level of the $m$-adic Galois representation associated to $E$ and let $f: X_1(n) \rightarrow X_1(\gcd(n,m_0))$ denote the natural map.
+Let $m_0$ be the level of the $m$-adic Galois representation associated to $E$ and let $f\colon X_1(n) \rightarrow X_1(\gcd(n,m_0))$ denote the natural map.
 If $x\in X_1(n)$ is an isolated point with $j(x)=j(E)$, then $f(x)\in X_1(\gcd(n,m_0))$ is an isolated point.
@@
 
-\dld{This is \texttt{FilterByLevelMapping}, which used to be called
-\texttt{RefuteLevel}. It acts as a filter. We feed in a list, and the output is
-a (hopefully smaller) list guaranteed to contain all isolated points. If the
-list is empty, then we have shown that the curve doesn't give rise to an
-isolated point! If not, then perhaps other work is necessary.}
+\subsection{Validity of Main Algorithm}
+\label{sec:proofvalidity}
+\begin{theorem}\label{thm:validity_main_algorithm}
+Let $j\in\Q$ be a non-CM $j$-invariant.
+If Algorithm \ref{alg:mainalgorithm} returns $[j,\{\langle n_1,d_1\rangle, \dots, \langle n_k,d_k\rangle \}]$, then any isolated point $x\in X_1(N)$ for $N \in \Z^+$ with $j(x)=j$ maps under the natural projection map to an isolated point of degree $d_i$ on $X_1(n_i)$ for some  $1 \leq i \leq k$.
+\end{theorem}
 
-\dld{I imagine other filters being potentially applied afterwards, each
-removing some set of non-isolated points.}
+\begin{remark}
+Since our algorithm builds on that of Zywina \cite{ZywinaAlgorithm}, it is possible that our algorithm give an error if the adelic image cannot be computed.
+See Zywina \cite{ZywinaImagesGit} for details.
+In particular, he notes that ``errors will always occur if $E$ gives rise to an unknown exceptional rational point on certain high genus modular curves." We are not aware of any instances when this error occurs.
+\end{remark}
 
-\begin{algorithm}[H]\caption{Filter by Level Mapping}\label{alg:level_mapping}
-  \KwIn{A list of pairs $(N, d)$ such that $E$ gives a non-CM point on $X_1(N)$
-  of degree $d$.}
-  \KwOut{A list of pairs $(N, d)$ containing all isolated points.}
-  (sketch)\;
-  create list of guaranteed nonisolated points using easy Riemann--Roch\;
-  filter potentially isolated points via Theorem~\ref{BELOVthm}\;
-  \Return{remaining $(N, d)$ pairs.}
-\end{algorithm}
-
-\dld{I collect the ingredients for use. The easy Riemann--Roch argument we use
-is from the following lemma. In principle, we could use any source of
-guaranteed nonisolated points.}
-
-\abbey{give example}
-
-\begin{lemma}
-Let $C$ be a curve over a number field $k$ with genus $g$. If $x \in C(\overline{k})$ is a closed point with degree
-$\geq g+1$, then $x$ is not $\mathbb{P}^{1}$-isolated.
-\end{lemma}
+\begin{remark} 
+The range of the moduli to which \texttt{PrimitiveDegreesOfPoints} is applicable is restricted by the amount of memory Magma can use.
+The input of very large matrix groups may result in a runtime error.
+Because we take preliminary steps to reduce the modulus of the matrix group (i.e., Section \ref{sec:madicrep}), this error did not occur when running our full algorithm on all elliptic curves currently in the LMFDB.
+\abbey{New remark; incorporates Timo's suggestion}
+\end{remark}
 
 \begin{proof}
-This is Lemma 13 in revision of B., Gill, Rouse, Watson. \cite{OddDeg}
+Let $E/\Q$ be a non-CM elliptic curve with $j(E)=j$.
+We may compute $\im \rho_E=G$ via Zywina's algorithm \cite{ZywinaAlgorithm}, and represent the output as $G(N) \leq \GL_2(\Z/N\Z)$ where $N$ is the level.
+By Algorithm \ref{alg:reduce_level}, we may use $G(N)$ to compute the level $m_0$ of the $m$-adic Galois representation associated to $E$, where $m$ is the product of 2, 3, and all non-surjective primes.
+Let $x\in X_1(N)$ be an isolated point with $j(x)=j$ and $N\in \Z^+$.
+By Theorem \ref{BELOVthm}, it follows that $f(x)\in X_1(\gcd(N,m_0))$ is an isolated point, where $f\colon X_1(N) \rightarrow X_1(\gcd(N,m_0))$ is the natural map.
+Thus it suffices to search for isolated points on $X_1(n)$ where $n \mid m_0$.
+
+By Algorithm \ref{alg:compute_prim_degree}, we may compute the multiset $D$ with entries $\langle n, \{\langle a_1, d_1\rangle ,  \dots,  \langle a_r, d_r\rangle \} \rangle$ for all positive divisors $n$ of $m_0$ such that the degree of the corresponding closed point on $X_1(n)$ is as large as possible given that its image on $X_1(a_i) $ has degree $d_i$.
+Suppose $x \in X_1(n)$ is isolated.
+Then by Theorem \ref{thm:PushingForwardSporadicIsolated}, for all $1\leq i \leq r$ the point $f_i(x) \in X_1(a_i)$ is an isolated point of degree $d_i$, where $f_i: X_1(n) \rightarrow X_1(a_i)$ is the natural map.
+If there exists $i$ such that $\deg(f_i(x))>\text{genus}(X_1(a_i))+1$, then $f(x_i)$ is not $\PP^1$-isolated since its associated Riemann--Roch space has dimension at least 2 by the Riemann--Roch Theorem.
+This gives a contradiction.
+Thus we need only consider the multiset $D' \subseteq D$ containing only those elements $\langle n, \{\langle a_1, d_1\rangle ,  \dots,  \langle a_r, d_r\rangle \} \rangle$ for which $d_i \leq \text{genus}(X_1(a_i))+1$ for all $1 \leq i \leq r$.
+Moreover, since the image $f_i(x) \in X_1(a_i)$ is isolated and is the image of $x$ under the natural projection map, we may in fact record only the multiset $M$ containing of all pairs $\langle a_i,d_i\rangle $ appearing in $D'$.
+We include the element $\langle a_i,d_i\rangle $ in $M$ with multiplicity $\mu$ if and only if $X_1(a_i)$ has $\mu$ distinct closed points of degree $d_i$.
+Since Algorithm \ref{alg:mainalgorithm} returns $[j,M]$, we are done.
 \end{proof}
 
-\dld{For the filter, we apply (the contrapositive of) Theorem~\ref{BELOVthm}.
-We also use the degree of the natural map as in Proposition~2.2 of BELOV.}
+\begin{corollary}\label{cor:P1_isolated}
+If Algorithm \ref{alg:mainalgorithm} outputs an empty set on some $j$-invariant $j = j(E)$, then $j$ is not the image of an  isolated point on $X_1(N)$ for any positive integer $N$. 
+\end{corollary}
+
+\subsection{Additional Example}
+
+We end this section with an extended example to illustrate the impact of each step in Algorithm \ref{alg:mainalgorithm}.
+Let $E=1225.b1$, a non-CM elliptic curve over $\Q$, and let $m$ denote the product of 2, 3, and all non-surjective primes.
+Here, one can check that $m=162$.
+\begin{enumerate}
+\item Zywina's algorithm shows the adelic image of $E$ is of level $N=5180$. Let $G(N) \coloneqq \im \rho_{E,N}$.
+\item Algorithm \ref{alg:reduce_level} shows that the level of the $m$-adic Galois representation of $E$ is 148.
+\item Algorithm \ref{alg:compute_prim_degree} shows that it suffices to consider points on $X_1(n)$ where $n \mid 37$.
+In particular, it is not necessary to consider points on $X_1(74)$ or $X_1(148)$ since any will map under the natural projection map to a modular curve of lower level.
+There is a single point of degree 1 on $X_1(1)$ and 4 points on $X_1(37)$ --- one of degree 18 and 3 of degree 222.
+\item We compute that $\text{genus}(X_1(37))=40$ and  $\text{genus}(X_1(1))=0$. Thus no point of degree 222 on $X_1(37)$ can be isolated, and neither is the rational point on $X_1(1)$.
+\item The algorithm returns $[j, \{\langle 37, 18 \rangle\}]$.
+\end{enumerate}
 
 \section{Remaining Filters}
-\abbey{Filip? Abbey?}
-Filip's arguments.
+\label{sec:remainingfilters}
 
-\section{Genus 0 adelic images do not produce sporadic points}
+\sachi{Swap this section with the next section?} \abbey{I moved the last section way earlier -- what do you think?}
 
-Let $E/ \Q$ be an elliptic curve and $G\in \GL_2(\hat \Z)$ its adelic image.
-By $G(n)$ denote the image of its mod $n$ representation.
-Denote by $B_1(n)$ the subgroup of $\GL_2(\Z/n\Z)$ consisting of the upper triangular matrices with a $1$ in the upper left entry.
-Note that $X_{B_1(n)}=X_1(n)$.
-We say that a congruence group $\Gamma$ is of genus $g$ if $X_\Gamma$ is of genus $g$.
-We say that a point $P$ corresponds to an elliptic curve $E$ if $j(P)=j(E)$.
+\abedit{Suppose $E/\Q$ is non-CM elliptic curve such that one of the following holds:
+\begin{itemize}
+    \item$N_E \leq 500{,}000$,
+    \item $N_E$ is only divisible by primes $p \leq 7$, or
+    \item $N_E=p \leq 200{,}000{,}000$ for some prime number $p$.
+\end{itemize} Then running Algorithm 1 on $E$ results in the empty set, aside from the output for those $j$-invariants given in the Appendix.}
+In this section we describe additional criteria which can prove that there are no isolated points on $X_1(N)$ for a fixed $N$ corresponding to a given $j$-invariant \abedit{$j \notin \{-140625/8,-9317,351/4, -162677523113838677\}$, proving Theorem \ref{LMFDBoutputThm}}.
 
-\begin{proposition}
-Let $E/\Q$ be an elliptic curve with adelic image of genus $0$. Then there does not exist an $n$ such that a point corresponding to $E$ on $X_1(n)$ is sporadic.
+\begin{proposition} \abbey{New plan is to use result about genus 0 mod $N$ images in place of this Proposition (instead of working to correct it).}
+    Let $E/\Q$ be an elliptic curve and let $G_0$ be the image mod $N$ Galois representation attached to $E$, viewed as a subgroup of $\GL_2(\Z/N\Z)$ after some choice of basis for $E[N]$.
+Let $y=(E,P)$ be a degree $d$ point on $X_1(N)$.
+Suppose there is a conjugate $c(B_1(N))$ of $B_1(N)$ such that $B:=\langle c(B_1(N)), G_0 \rangle \leq \GL_2(\Z/N\Z)$ and $X_B$ is of genus 0.
+If $[\pm B: \pm c(B_1(N))]=d$, then $y$ is not $\PP^1$-isolated.
 \end{proposition}
+
+\abbey{We need some sort of compatibility criterion here.
+For example, suppose $G_0$ is the full Borel subgroup, so $X_B=X_0(N)$.
+Then for $y$ on $X_1(N)$ of degree $d$, it does not necessarily follow that $f(y)$ is in $X_0(N)(\Q).$ We would need to know that $\langle P \rangle$ is actually $\Q$-rational.
+I think we need to choose a conjugate of $G_0$ so that $P$ is the first basis element, and then work with $B_1(N)$ and not $c(B_1(N))$.}
+
 \begin{proof}
-Since $G$ is by assumption of genus $0$, it follows that so is $G(n)$. Let $P$ be a $\Q$-rational point on $X_{G(n)}$ corresponding to $E$.
-
-%Let $B$ be the group generated by $G(n)$ and a conjugate of $B_1(n)$ in $\GL_2(\Z/n\Z)$; this is again a group of genus $0$ on which the image $P'$ of $P$ under the map $X_{G(n)}\rightarro X_B$ is $\Q$-rational.
-The inclusion of subgroups $B\subset B_1(n)$ induces a map $X_1(n)\rightarrow  X_B$.
-
-The minimal degree of a point on $X_1(n)$ corresponding to $E$ is the minimal index of $B:=c(B_1(n))\cap G(n)$ in $G(n)$, where $c$ denotes conjugation in $\GL_2(\Z /n \Z)$.
-Call this (minimal) index $d$ and let $f:X_{B}\rightarrow X_{G(n)}$ be the corresponding map of modular curves.
-By construction, all the points in $f^{-1}(P)$ are of degree $d$ and obviously $\gon_\Q X_{B}\leq d.$ Let $P'\in f^{-1}(P) \subseteq X_{B}$ be a point corresponding to $E$, and let $g:X_{B}\rightarrow X_1(n)$ be the map induced by the inclusion $B_1(n) \subseteq B$.
-Then by the argument above we have that $g(P')$ is of degree $d$ (as this is the minimal degree of a point on $X_1(n)$ corresponding to $E$), and on the other hand we have that $\gon_\Q X_1(n)\leq d$ by \cite[Proposition A.1 (vii)]{Poonen:gonality}.
+    By \Cref{prop:mapdegree} it follows that there exists a degree $d$ map $f\colon X_1(N)\rightarrow X_B\simeq \PP^1$ of degree $d$.
+Since $G_0$ is contained in $B$, it follows that $E$ corresponds to  $x\in X_B(\Q)$ such that $f(y)=x$ \abbey{I don't think we necessarily have $f(y)=x$; see comment directly above proof.}.
+Hence $y$ is not $\PP^1$-isolated.
 \end{proof}
 
+\subsection{Special cases}
+We now explain how we dealt with cases that passed all the filters.
+
+\subsubsection{Degree $4$ point on $X_1(17)$ corresponding to $j=-882216989/131072$}
+To show that this point is not isolated we compute the coordinates of \fedit{a} degree $4$ point $x$ corresponding to our curve on a model of $X_1(17)$.
+\abbey{Does this construction depend on which closed point of degree 4 we choose?
+There are 2.} \filip{I didn't check, but it probably shouldn't.
+I changed "the" to "a" in the previous sentence.} The point $x$ is defined over a cyclic quartic field.
+Let $\sigma_i$, for $i=1,\ldots, 4$ be the automorphisms of $K$ and $D=\sum_{i=1}^4\sigma_i(x)$.
+We compute $\ell(D)=2$, which implies that $x$ is not $\PP^1$-isolated.
+
+The fact that this point is not $\PP^1$-isolated also follows from the results of \cite[Proposition 6.7]{DerickxMazurKamienny}, where it is shown that there are no $\PP^1$-isolated quartic points on $X_1(17)$.
+
+\subsubsection{Degree $18$ point on $X_1(37)$ corresponding to $j=-162677523113838677$}
+
+We show that the points $x\in X_1(37)(K)$, where $K$ is a degree 18 number field, and $j(x)=-162677523113838677$ is $\PP^1$-isolated.
+We explicitly compute the coordinates of $x$ on a model of $X_1(37)$ and define  $\sigma_i$, for $i=1,\ldots, 18$ to be the automorphisms of $K$ and $D=\sum_{i=1}^{18}\sigma_i(x)$.
+Reducing everything modulo $3$ and denoting the reduction of $D$ modulo $3$ by $\overline{D}$, we obtain $\ell(\overline{D})=1$, which shows that the reduction
+$\overline{x}$ of $x$ modulo 3 is $\PP^1$-isolated, and hence it follows that $x$ is $\PP^1$-isolated.  %\abbey{I believe we mean that it \emph{is} $\PP^1$-isolated.} \filip{Yes, fixed.}
+
+\filip{I did not go into much details here, as I think more details would entail just writing a bunch of equations, and the code where all the computations are dove, will be supplied.}
+
+\newpage
+\section*{Appendix}
+\label{appendix}
+\abbey{Added output of Algorithm 1.}
+Suppose $E/\Q$ is non-CM elliptic curve such that one of the following holds:
+\begin{itemize}
+    \item$N_E \leq 500{,}000$,
+    \item $N_E$ is only divisible by primes $p \leq 7$, or
+    \item $N_E=p \leq 200{,}000{,}000$ for some prime number $p$.
+\end{itemize}
+If the output of Algorithm 1 is non-empty, then $j(E)$ and the output appear in the list below.
+\scriptsize{
+\begin{align*}
+&-1/15:\{<32, 8>^2\}\\
+&-1139466686381936641/17587891077120:\{<32, 8>^2 \}\\
+&-13123858413236228917847770385659606286401/20767600023946451721766482684226058876:\{ <25, 10> \}\\
+&-1376562883316985524655287925404037121/1193272631368179777536:\{ <25, 5>^2 \}\\
+&-12757618324042173549858425461682176/1823806051450564693130128615083:\{ <25, 10> \}\\
+&-1415127831921321522248426938217281/3666855487972497940063476562500:\{ <32, 16>^2 \}\\
+&-140625/8:\{ <21, 3>^2 \}\\
+&-162677523113838677:\{ <37, 18> \}\\
+&-19328649688935739391016961/18446462598732840960:\{ <32, 16>^2 \}\\
+&-19465109/22:\{ <25, 10> \}\\
+&-18975420587737213095292649/255881160051786:\{<25, 10> \}\\
+&-225741686871429146260559062081/146211902909299839467520000:\{ <16, 2>^4 \}\\
+&-24680042791780949/369098752:\{ <25, 5>^2 \}\\
+&-2926956820564562516641/35459588343029760000:\{ <16, 2>^4 \}\\
+&-279328676638409/15200157696:\{ <25, 10> \}\\
+&-324503698618794407582644992737281/19342794667089993085747200:\{ <32, 8>^2 \}\\
+&-326573981641149886485204481/194520794324722008975:\{ <32, 8>^2 \}\\
+&-1638541430081273024/26265946892733:\{ <25, 10> \}\\
+&-353498371667659682101/113715890591105024:\{ <25, 10> \}\\
+&-3545733621855029067330337757367361/9094574488699436187744140625:\{ <32, 8>^2 \}\\
+&-3552277140342294754589991537894721/568432733416557312011718750:\{ <32, 16>^2 \}\\
+&-36703062611518813711084873444252734518401/397925291030084608863799302120300:\{ <32, 16>^2 \}\\
+&-4033422215926741/404:\{ <25, 10> \}\\
+&-4096/11:\{ <25, 5>^2 \}\\
+&-488162845931504468669161001/502:\{<25, 10> \}\\
+&-49019660417634625566551535616/52295500263431403:\{ <25, 5>^2 \}\\
+&-5107501047547200669121/186932676651373720080:\{ <32, 16>^2 \}\\
+&-52893159101157376/11:\{ <25, 10> \}\\
+&-56667352321/16711680:\{ <32, 16>^2 \}\\
+&-60627540058019895893705412918183361/10979320318525440000000000000000:\{ <16, 2>^4 \}\\
+&-60698457/40960:\{ <13, 2>^3 \}\\
+&-617298465273089376571121350031405627538001/165066:\{ <25, 10> \}\\
+&-70809965983288820433601/12128017136035299345:\{ <32, 8>^2 \}\\
+&-79184385609230668294081/759738277429254810:\{ <32, 16>^2 \}
+\end{align*}
+\begin{align*}
+&-882216989/131072: \{ <17, 4>^2\}\\
+&-460815199424/93:\{ <25, 10> \}\\
+&-9317:\{ <37, 6>^3 \}\\
+&1023887723039/928972800:\{ <16, 2>^4 \}\\
+&1139466686381936641/4080:\{ <32, 16>^2 \}\\
+&1144081181272479239133643526834383042983361/757051842880264964991840000:\{ <16, 2>^4 \}\\
+&115099000398621243971890559/78239096930039062500000000:\{ <16, 2>^4 \}\\
+&1259954716599707317761635279/782145653991396014555136:\{ <25, 5>^2 \}\\
+&128394017933147245660796166417119/493274390082338961058364010000:\{ <16, 2>^4 \}\\
+&13087181362848921857775657601/10116926999101440000:\{ <16, 2>^4 \}\\
+&13527956825588849127121/25701087819771000:\{ <24, 4>^2 \}\\
+&13619385906841/6048000:\{ <24, 4>^2 \}\\
+&13831657260716704136482954281709863361/17374959614531090376562500:\{ <32, 16>^2 \}\\
+&14551803469961881301880007324200000001/9536718750:\{ <32, 16>^2 \}\\
+&150336917982741967163778998756395764357350401/2077057800300:\{ <32, 16>^2 \}\\
+&1542085860252894509103949/6408896512:\{ <25, 10> \}\\
+&164711681450297281/8097103872000:\{ <24, 4>^2 \}\\
+&1663986362115498724215359/108912513076663261593600:\{ <32, 16>^2 \}\\
+&1663986362115498724215359/1169329859973065744640:\{ <32, 8>^2 \}\\
+&16778985534208729/81000:\{ <24, 4>^2 \}\\
+&178296503348692983836197044001/1342:\{ <25, 10> \}\\
+&1815401516599/8422162432:\{ <25, 10> \}\\
+&190705121216/71:\{ <25, 10> \}\\
+&19328649688935739391016961/1048320:\{ <32, 8>^2 \}\\
+&20250020461466473637047669654178374039681/501531896655344498219343780249600:\{ <32, 8>^2 \}\\
+&2119184381004022710620128465357091164489/26664780077208000:\{ <24, 4>^2 \}\\
+&2366200373628880151/2612420149248000:\{ <24, 4>^2 \}\\
+&236979190359324065638429091444161/447618521651352874905600:\{ <32, 16>^2 \}\\
+&291546910741641055583105024/382127162858793:\{ <25, 5>^2 \}\\
+&297106512928238351998640242081/3977028808593750000:\{ <16, 2>^4 \}\\
+&300872095888141441/22515023872:\{ <25, 5>^2 \}\\
+&324503698618794407582644992737281/268431360:\{ <32, 16>^2 \}\\
+&326573981641149886485204481/2690010:\{ <32, 16>^2 \}\\
+&3358085834636749/382:\{ <25, 10> \}\\
+&351/4:\{ <28, 9>^2 \}\\
+&3552277140342294754589991537894721/152581640625:\{ <32, 8>^2 \}\\
+&3634704740957616196378170215513091769/168224880645019054412841796875000:\{ <24, 4>^2 \}\\
+&364421318680576777174674911/450962301637624725000000:\{ <24, 4>^2 \}\\
+&36546944013036856482908761/14157275332658039712000:\{ <24, 4>^2 \}\\
+&378499465220294881/120530818800:\{ <16, 2>^4 \}\\
+&3922540634246430781376/71:\{ <25, 10> \}\\
+&44992447464066442427196092139811199/65124493101588450372219085693359375:\{ <32, 8>^2 \}\\
+&45960438227854760543785319/46920791622800342016000000:\{ <24, 4>^2 \}\\
+&5107501047547200669121/69461926257623040:\{ <32, 8>^2 \}\\
+&52300395461270777993673352489/30181158775846600704000000:\{ <24, 4>^2 \}\\
+&5345287166085790635663218704920974401/226978257155929261920000:\{ <16, 2>^4 \}
+\end{align*}
+\begin{align*}
+&5444502293860223539938743709179943321601/68719411200:\{ <32, 8>^2 \}\\
+&546397111960658404325211701139833360188801/209323126216982833463548776182030859375:\{<32, 8>^2 \}\\
+&5481351580593489628916345933548801/688740975:\{ <32, 8>^2 \}\\
+&56667352321/15:\{ <32, 8>^2 \}\\
+&56868272654707881404486749117441/10748658652923870314496000:\{ <24, 4>^2 \}\\
+&573007087724441463649920782881/67058993610000000000000000:\{ <16, 2>^4 \}\\
+&591720065532918583239955136329/116891407012939453125000000:\{ <24, 4>^2 \}\\
+&628284678908027418152998936285681/19884708881378173828125000:\{ <24, 4>^2 \}\\
+&6271688643866537984/1353:\{ <25, 10> \}\\
+&68699533290471196810719174361/268409217024000:\{ <24, 4>^2 \}\\
+&70809965983288820433601/2711034593280:\{ <32, 16>^2 \}\\
+&79184385609230668294081/42941745:\{ <32, 8>^2 \}\\
+&818546927584539194367471866449/14273634375000:\{ <24, 4>^2 \}\\
+&8827236347661221188886967161105287201/46539238473000000:\{ <24, 4>^2 \}\\
+&96653256179049031824319796125471784879999/341359290480134366830343600487545241600:\{ <32, 8>^2 \}
+\end{align*}}
 \vspace{20 mm}

### 2023-07-25 extrafilters2.m
add code from Filip

@@ -1,0 +1,33 @@
+//code for degree 4 point on X1(24)
+
+coords_jK := function(X,j,jinv,K);
+    PP := Codomain(j);
+    pt := PP ! [jinv];
+    base_scheme := BaseScheme(j);
+    pullback_scheme := Pullback(j,pt);
+    difference := Difference(pullback_scheme, base_scheme);
+    differenceK := BaseChange(difference,K);
+    points := Points(differenceK);
+    return points;
+end function;
+
+N:=24;
+_<x,y>:=PolynomialRing(Rationals(),2);
+p:=(x^2 - 3)*y^4 + x*(x^4 + 2*x^3 + 2*x^2 + 2*x - 3)*y^2 - x^4 - x^2;
+A<a,b>:=AffineSpace(Rationals(),2);
+X:=Curve(A,p);
+q:=y;
+t:=(4*x*y + 4*y^3)/(x*y^4 - 4*x*y^2 - x - 2*y^4 - 2*y^2);
+E:=EllipticCurve([0,t^2-2*q*t-2,0,-(t^2-1)*(q*t+1)^2,0]);
+num:=Numerator(jInvariant(E));
+denom:=Denominator(jInvariant(E));
+jmap := map<X -> ProjectiveSpace(Rationals(),1) | [num, denom] >;
+jinv:=16778985534208729/81000;
+R<x> := PolynomialRing(Rationals()); K<a> := NumberField(x^4 - 8*x^2 + 10);
+pts:=coords_jK(X,jmap,jinv,K);
+Xk:=BaseChange(X,K);
+P1:=Xk![pts[1,1], pts[1,2]];
+P2:=Xk![pts[2,1], pts[2,2]];
+P3:=Xk![pts[3,1], pts[3,2]];
+P4:=Xk![pts[4,1], pts[4,2]];
+Dimension(RiemannRochSpace(Divisor(P1)+Divisor(P2)+Divisor(P3)+Divisor(P4)));

### 2023-07-27 TeX/draft.tex

@@
 \usepackage{colonequals}
+
+%for tables
+\usepackage{tabularx}
+\usepackage{booktabs}
 
@@
 \newcommand{\fedit}[1]{{\color{cyan} #1}}
+\newcommand{\sedit}[1]{{\color{purple} #1}}
+
 % Don't have subsections appear in TOC
@@
 \label{sec:intro}
-\abbey{Updated to account for isolated points.}
+
 The modular curve $X_1(N)$ is an algebraic curve over $\Q$ whose non-cuspidal points parametrize elliptic curves with a distinguished point of order $N$.
@@
 Roughly speaking these are points of degree $d$ not belonging to an infinite family of degree $d$ points parametrized by a geometric object.
-For example, if $f: X_1(N) \rightarrow \PP^1$ is a rational map of degree $d$, then $f^{-1}(\PP^1(\Q))$ contains infinitely many closed points of degree $d$ by Hilbert's irreducibility theorem \cite[Chapter 9]{serre97}.
+For example, if $f: X_1(N) \rightarrow \PP^1$ is a rational map of degree $d$, then $f^{-1}(\PP^1(\Q))$ contains infinitely many closed points of degree $d$ by Hilbert's irreducibility theorem \cite[Chapter~9]{serre97}.
 We say a degree $d$ point \emph{not} arising from such a map is \textbf{$\PP^1$-isolated}.
@@
 The lack of control of isolated points in infinite families of modular curves lies at the heart of several important open problems.
-See, for example, \cite[Question 1]{MazurNote} and \cite[Theorem 1.3]{BourdonNajman2021}.
+See, for example, \cite[Question~1]{MazurNote} and \cite[Theorem~1.3]{BourdonNajman2021}.
 
@@
 Hence a non-cuspidal sporadic point corresponds to an elliptic curve with a point of order $N$ in ``usually low degree." Elliptic curves with complex multiplication (CM) provide many natural examples of sporadic points, since the extra endomorphisms of a CM elliptic curve constrain the size of the image of the associated Galois representation.
-Indeed, as shown in \cite[Theorem 8.2]{CGPS2022}, there exist sporadic CM points on $X_1(N)$ for all $N\geq 721$.
+Indeed, as shown in \cite[Theorem~8.2]{CGPS2022}, there exist sporadic CM points on $X_1(N)$ for all $N\geq 721$.
 
@@
 In fact, this is the unique elliptic curve giving a sporadic point of degree at most 3 on \emph{any} modular curve of the form $X_1(N)$, as shown in recent work of Derickx, Etropolski, van Hoeij, Morrow, and Zureick-Brown \cite{DEvHMZB2021}.
+
     \item The elliptic curve with $j$-invariant $-9317$ gives three degree 6 points on $X_1(37)$, as in work of van Hoeij \cite{vanHoeij}.
 Since 6 is less than half the $\Q$-gonality of $X_1(37)$, as computed in \cite{DerickxVanHoeij2014}, the point is necessarily sporadic by work of Frey \cite{frey}.
+
     \item The elliptic curve with $j$-invariant $351/4$ gives an isolated point of degree 9 on $X_1(28)$; see \cite[Theorem 2]{OddDeg}.
@@
 We develop an algorithm which can be used to determine whether a given non-CM $j$-invariant $j\in \Q$ is isolated.
-Starting with the adelic image of the adelic Galois representation associated $E/\Q$ with $j(E)=j(x)$, as computed by Zywina \cite{ZywinaAlgorithm}, we apply various filters inspired by \cite{BELOV} to determine whether there exists an isolated point on $x \in X_1(N)$ with $j(x)=j$.
+Starting with the adelic image of the adelic Galois representation associated $E/\Q$ with $j(E)=j(x)$, as computed by Zywina \cite{ZywinaAlgorithm}, we apply various filters to determine whether there exists an isolated point on $x \in X_1(N)$ with $j(x)=j$.
 
@@
     \KwIn{A non-CM $j$-invariant $j \in \Q$.}
-\KwOut{A list $[j,\{\langle a_1,d_1\rangle, \dots, \langle a_k,d_k\rangle \}]$ such that any isolated point $x \in X_1(N)$ with $j(x)=j$ maps down under the natural projection map to an isolated point of degree $d_i$ on $X_1(a_i)$ for some $1 \leq i \leq k$.}
+    \KwOut{A \abedit{finite} list $[j,\{\langle a_1,d_1\rangle, \dots, \langle a_k,d_k\rangle \}]$ such that any isolated point $x \in X_1(N)$ with $j(x)=j$ maps down under the natural projection map to an isolated point of degree $d_i$ on $X_1(a_i)$ for some $1 \leq i \leq k$.}
 \end{algorithm}
@@
 \noindent In particular, if the output of Algorithm \ref{alg:mainalgorithm} is the empty set, then $j$ is not an isolated $j$-invariant.
-We give an overview of the main algorithm in Section \ref{alg:mainalgorithm}, with key sub-algorithms described in detail in Sections \ref{sec:madicrep} and \ref{sec:primitivedeg}.
-We address the validity of Algorithm \ref{alg:mainalgorithm} in Section \ref{sec:validity}.
+
+One of the key filters we use is based on \cite[Theorem 4.3]{BELOV}.
+
+\begin{theorem}[\cite{BELOV}]
+Let $f: C \rightarrow D$ be a finite map of curves, let $x \in C$ be a closed point, and let $y=f(x)\in D$. Assume that $\deg(x)=\deg(y)\cdot \deg(f)$.
+\begin{enumerate}
+\item If $x$ is $\PP^1$-isolated, then $y$ is $\PP^1$-isolated.
+\item If $x$ is AV-isolated, then $y$ is AV-isolated.
+\item $x$ is sporadic, then $y$ is sporadic.
+\end{enumerate}
+\end{theorem}
+
+\noindent Since the image of the adelic Galois representation of a non-CM elliptic curve $E/\Q$ has finite level, this theorem reduces the problem of determining whether $j(E)$ is isolated to the problem of determining whether $E$ gives rise to an isolated point on a finite number of modular curves.
+While a sufficient finite list can be deduced directly from the adelic level as found by Zywina \cite{ZywinaAlgorithm}, our output works to reduce this list to its minimal size.
+This inspires the notion of \textbf{primitive points} on modular curves, as studied in Section \ref{sec:PrimitivePoints}.
+In particular, $j(E)$ is isolated if and only if there exists an isolated primitive point corresponding to $E$.
+Moreover, any point $x\in X_1(N)$ with $j(x)=j(E)$ corresponds to a \emph{unique} primitive point (Proposition \ref{Prop:single_sink}).
+
+The second part of Algorithm \ref{alg:mainalgorithm} works to show the primitive points corresponding to $E$ are \emph{not} isolated.
+For example, if the Riemann-Roch space associated to $x \in X_1(N)$ with $j(x)=j(E)$ has dimension at least 2, then $x$ is not $\PP^1$-isolated (and hence not isolated).
+In other cases, we can show $x \in X_1(N)$ is not isolated by applying the following result.
+
+\begin{proposition} \label{Prop:Genus0Intro}
+Let $E/\Q$ be an elliptic curve, and let $H \leq \GL_2(\Z/N\Z)$ be the image of the mod $N$ Galois representation of $E$, after some choice of basis.
+If the modular curve $X_H$ has genus 0, then there are no isolated points on $X_1(N)$ associated to $E$.
+\end{proposition}
+
+\noindent In particular, this result implies any elliptic curve with adelic image of genus 0 does not give rise to any isolated points on $X_1(N)$, even as $N$ ranges over all positive integers.
+However, even when the adelic image of $E$ has positive genus, it can still be that $\im \rho_{E,N}$ has genus 0 for all $N$ corresponding to primitive points.
+This makes Proposition \ref{Prop:Genus0Intro} more broadly applicable.
 
 Running Algorithm \ref{alg:mainalgorithm} on all elliptic curves currently in the $L$-functions and Modular Forms Database (LMFDB) \cite{LMFDB} gives a list of 95 $j$-invariants which require further consideration; see the Appendix.
-After applying certain additional filters to address special cases, as discussed in Section~\ref{sec:remainingfilters}, we arrive at the following result.
+\abbey{I think we should build Prop.
+\ref{Prop:Genus0Intro} into the algorithm.
+Would need to update to mention only Table 1 instead.} After applying certain additional filters to address special cases, as discussed in Section~\ref{sec:remainingfilters}, we arrive at the following result.
 
@@
 \begin{itemize}
-    \item$N_E \leq 500{,}000$,
+    \item $N_E \leq 500{,}000$,
     \item $N_E$ is only divisible by primes $p \leq 7$, or
@@
 Then $j(E) \in \{-140625/8,-9317,351/4, -162677523113838677\}$.
-Moreover, each of these $j$-invariants corresponds to a $\PP^1$-isolated point on $X_1(21)$, $X_1(37)$, $X_1(28)$, and $X_1(37)$, respectively.
+Moreover, each one of these $j$-invariants corresponds to a $\PP^1$-isolated point on $X_1(21)$, $X_1(37)$, $X_1(28)$, and $X_1(37)$, respectively.
 \end{theorem}
@@
 Based on these results, we conjecture that the four non-CM isolated $j$-invariants identified above are in fact the \emph{only} $j$-invariants in $\Q$ associated to non-CM elliptic curves which give rise to $\PP^1$-isolated points.
-
-\begin{conjecture}
-If $x\in X_1(N)$ is a $\PP^1$-isolated point with $j(x) \in \Q$, then $j(x)=-140625/8$,$-9317$, $351/4$, $-162677523113838677$, or one of the 13 CM $j$-invariants in $\Q$.
+Since any CM elliptic curve is known to produce sporadic points on infinitely many modular curves of the form $X_1(N)$ by \cite[Theorem 7.1]{BELOV}, it follows conversely that every $j$-invariant in this set is isolated.
+
+\begin{conjecture}\label{conj}
+If $x\in X_1(N)$ is a $\PP^1$-isolated point with $j(x) \in \Q$, then $j(x)=-140625/8$, $-9317$, $351/4$, $-162677523113838677$, or one of the 13 CM $j$-invariants in $\Q$.
 \end{conjecture}
-
-\noindent Since any CM elliptic curve is known to produce sporadic points on infinitely many modular curves of the form $X_1(N)$ by \cite[Theorem 7.1]{BELOV}, it follows conversely that every $j$-invariant in this set is isolated.
-
-It is worth noting that the sporadic points on $X_1(21)$ associated to $j=-140625/8$ and the sporadic points on $X_1(37)$ associated to $j=-9317$ lie above exceptional rational points on $X_0(21)$ and $X_0(37)$, respectively.
+\begin{remark}
+\filip{New remark.}
+Let $x\in X_1(N)$ be a $\PP^1$-isolated point with $j(x) \in \Q$.
+One expects that the square-free part of the conductor of any $E$ with $j(E)=j(x)$ will be very small.
+The reason for this is that any such isolated point will necessarily have small mod $p$ image for some $p$ dividing $N$.
+This in turn forces potentially good reduction on $E$ in all primes, except possibly for $p=2$, see \cite[Corollary 4.4]{Mazur1978} for one (out of many) example of this phenomenon.
+Indeed this is the case for all the curves appearing in \Cref{conj}; their conductors are either a square, or twice a square.
+
+Hence one might except to find most or all of the $\PP^1$-isolated points among elliptic curves with relatively small conductor (and hence in the LMFDB).
+This observation perhaps makes the computational evidence supporting \Cref{conj} more convincing.
+\end{remark}
+
 We say a point $x \in X_0(N)(\Q)$ is \textbf{exceptional} if $X_0(N)(\Q)$ is finite and $x$ corresponds to a non-CM elliptic curve over $\Q$.
-Thus it is natural to ask whether there exist other sporadic points on $X_1(N')$ lying above such exceptional rational points.
+It is worth noting that the sporadic points on $X_1(21)$ associated to $j=-140625/8$ and the sporadic points on $X_1(37)$ associated to $j=-9317$ lie above exceptional points on $X_0(21)$ and $X_0(37)$, respectively.
+Thus it is natural to ask whether there exist other sporadic \abedit{$j$-invariants corresponding to} exceptional rational points on $X_0(N)$.
 Running Algorithm~\ref{alg:mainalgorithm} on the 14 $j$-invariants corresponding to exceptional rational points on $X_0(N)$ (see, for example, \cite[Table 4]{LRAnn}) shows that there are no additional sporadic $j$-invariants in this set.
 \begin{theorem}
-Let $E$ be an elliptic curve corresponding to an exceptional rational point on $X_0(N)$. If there exists a sporadic point $x \in X_1(N')$ with $j(x)=j(E)$, then $j(E) =-140625/8$ or $-9317$.
+Let $E$ be an elliptic curve corresponding to an exceptional rational point on $X_0(N)$ for some positive integer $N$. \abedit{If $j(E)$ is sporadic, then $j(E)=-140625/8$ or $-9317$.}
 \end{theorem}
@@
 It is still an open problem to determine all sporadic points $x \in \cup_{N \in \Z^+} X_1(N)$ with $j(x) =-140625/8$ or $-9317$.
+
+\subsection{Outline}
+After providing relevant background material in Section \ref{sec:background}, we establish  preliminary mathematical results on genus 0 adelic images ($\S$\ref{sec:genus0}) and primitive points on modular curves ($\S$\ref{sec:PrimitivePoints}).
+We give an overview of the main algorithm in Section \ref{sec:mainalg}, with key sub-algorithms described in detail in Sections \ref{sec:madicrep} and \ref{sec:primitivedeg}.
+We address the validity of Algorithm \ref{alg:mainalgorithm} in Section \ref{sec:validity}.
+The output of the algorithm and its final analysis is discussed in Section \ref{sec:remainingfilters}.
 
@@
 For any subgroup $H \leq \GL_2(\Z/N\Z)$, we define the modular curve $X_H$ to be the coarse space of the stack $\mathcal{M}_H$, as defined in Deligne--Rapoport \cite{DR}.
-The curve $X_H$ is a scheme over $\text{Spec }\Z[1/N]$ and parametrises generalized elliptic curves with $H$-level structure.
+The curve $X_H$ is a scheme over $\text{Spec }\Z[1/N]$ and parametrizes generalized elliptic curves with $H$-level structure.
 \abedit{In particular, its $k$-rational points roughly classify elliptic curves over $k$ whose mod $N$ image is contained in $H$}; see, for example, \cite[$\S2.3$]{RSZB2022} for details.
@@
 Thus one could alternatively define the closed point associated to $(E,P)$ as the $\Gal_\Q$-orbit of $(E,P)_{\overline{\Q}}$.
-\sachi{I think the difference between $k$-valued points and $k$-rational points is confusing, since the names are so similar.
-It would be nice to explicitly point out what is meant by $k$-rationality somewhere (in constrast to $k$-valued).} \abbey{They are all the same thing for a scheme over a field.
-I used the term $k$-valued b/c it's the term used in Qing Liu's book \cite{Liu2002}, but it matches what Poonen calls a $k$-rational point or a $k$-point of a scheme over a field in \emph{Rational points on varieties}, for example.
-The definition is actually already above --- it's a morphism of $\Q$-schemes $f:\text{Spec} k \rightarrow X_1(N)$.
-If you say $k$-rational point, I imagine most people just think of points with coordinates in $k$, rather than this scheme-theoretic definition.
-These two notions coincide, but it's something to prove, for example, as in Prop.
-2.18 in Section 3.2.3 of \cite{Liu2002}.}
 
@@
 On the other hand, let $E_2:y^2=x^3-43x-166$ and $P_2=(5,i\sqrt{256})$ a point of order 7.
-Then $(E_2,P_2)$ gives a $\Q(i)$-valued point on $X_1(7)/\Q$ and also a closed point $x\in X_1(7)$ of degree 1 by \abedit{Remark \ref{ResidueFieldRmk}} \sachi{(and therefore a $\Q$-rational point)} \abbey{We want to think of it as \emph{inducing} a $\Q$-rational point---as explained in the paragraph below, or in Remark 7 above---rather than $(E_2,P_2)$ itself being $\Q$-rational.
-The non-cuspidal $\Q$-rational points of $X_1(7)(\Q)$ correspond to $\Q$-isomorphism classes of elliptic curves $E/\Q$ with a point $P\in E(\Q)$ of order 7, where this comes from the curve being a fine moduli space.
-So the representative $E_2,P_2$ does not show up here, since $P_2$ is not in $\Q$.}.
+Then $(E_2,P_2)$ gives a $\Q(i)$-valued point on $X_1(7)/\Q$ and also a closed point $x\in X_1(7)$ of degree 1 by \abedit{Remark \ref{ResidueFieldRmk}}.
 In fact, both $(E_1,P_1)$ and $(E_2,P_2)$ induce the same geometric point on $X_1(7)$ since $(E_1,P_1)_{\overline{\Q}}=(E_2,P_2)_{\overline{\Q}}$.
@@
 Taking $G=\pi^{-1}(B_1(ab))$ and $G'=\pi^{-1}(B_1(a))$ gives the following corollary, which under the moduli interpretation corresponds to sending $(E,P)$ to $(E,bP)$.
-\begin{corollary}
+\begin{corollary}\label{Cor:DegreeFormula}
                 For positive integers $a$ and $b$, the natural $\Q$-rational map $f\colon X_1(ab) \rightarrow X_1(a)$ has
@@
 
-\subsection{Galois Representations}\abbey{Recently added section.} If $E$ is an elliptic curve defined over a number field $k$, then $\Gal_k$ acts naturally on the points of $E$.
+\subsection{Galois Representations} If $E$ is an elliptic curve defined over a number field $k$, then $\Gal_k$ acts naturally on the points of $E$.
 On torsion points, this action is described by the \textbf{adelic Galois representation} associated to $E/k$,
@@
 \section{Genus 0 adelic images do not produce isolated points}
+\label{sec:genus0images}
 
@@
 Let $E/\Q$ be an elliptic curve and $G\in \GL_2(\hat \Z)$ its adelic image.
-By $G(N)$ denote the image of its mod $N$ representation.
+Let $G(N)$ denote the image of its mod $N$ representation.
 Denote by $B_1(N)$ the subgroup of $\GL_2(\Z/N\Z)$ consisting of the upper triangular matrices with a $1$ in the upper left entry.
@@
 We say that a point $P$ corresponds to an elliptic curve $E$ if $j(P)=j(E)$.
+\sedit{In this section, we show that elliptic curves with genus $0$ mod $N$ image  do not correspond to $\PP^1$-isolated points on $X_1(N)$.}
+
+\abbey{Do we want to add a check for this as part of our main algorithm?
+That is, if $\langle a, d\rangle$ appears in our list indicating that $E$ gives a possibly isolated point on $X_1(a)$ of degree $d$, should we check whether $X_{\im \rho_{E,a}}$ has genus 0?
+If so, $\langle a, d\rangle$ can be removed from the list.
+Then the long list currently in the appendix could be removed, since Table 1 would suffice.}
 
@@
 \section{Primitive Points on Modular Curves}
+\label{sec:PrimitivePoints}
+
 \abbey{New section which answers Zev's question about the PrimitiveDegreesOfPoints algorithm in the affirmative.}
-At a high level, our algorithm to decide whether a given $E$ defined over $\Q$ is \abedit{gives rise to} an isolated point on $X_1(N)$ for some $N\geq 1$ proceeds in two steps.
-First, we reduce this to a finite computation by computing a level $n$ associated to the adelic image of $E$ so that we need only consider levels $m|n$.
+At a high level, our algorithm to decide whether a given $E/\Q$ gives rise to an isolated point on $X_1(N)$ for some $N\geq 1$ proceeds in two steps.
+First, we reduce this to a finite computation by computing a level $n$ associated to the adelic image of $E$, so that we need only consider levels $m|n$.
 Next, we try to reduce the  levels $m|n$ which we need to check: our filters for non-isolated points work better for points of lower level, in general.
@@
 Let $m\geq 1$ be an integer. 
-We now define the $m$-primitive points above a given elliptic curve $E$ defined over $\Q$.
-We begin by defining a directed graph $G=G(E,m)$ on the points of $X_1(n)$ \abedit{corresponding to $E$} for $n|m$.
-The vertices of $G(E,m)$ are tuples $(x,n,d)$ where:
+%We now define the $m$-primitive points above a given elliptic curve $E/\Q$. 
+We begin by defining a directed graph $G(E,m)$ on the points of $X_1(n)$ corresponding to $E$ for all $n|m$. The vertices of $G(E,m)$ are tuples $(x,n,d)$ where:
 \begin{enumerate}
@@
 \end{enumerate}
-We connect $(x,n,d)$ with an arrow to $(x',n',d')$ if: 
+We connect $(x,n,d)$ with an arrow \sachi{a directed edge} to $(x',n',d')$ if: 
 \begin{enumerate}
@@
 \end{definition}
+
+\abedit{
+\begin{theorem}
+    Let $E/\Q$ be a non-CM elliptic curve.
+Then there are only finitely many primitive points associated to $E$.
+Moreover, $j(E)$ is isolated if and only if one of the primitive points associated to $E$ is isolated.
+\end{theorem}
+
+}
 In Section~\ref{sec:primitivedeg}, we give an algorithm for enumerating the sinks of $G(E,m)$. 
-\begin{remark}
+\begin{remark}\label{Remark:Transitivity}
 Suppose $n'' | n' | n | m$ and that $(x,n,d), (x',n',d'), (x'',n'',d'')$ are vertices.
-This graph is \textbf{transitive}, meaning that if there is an arrow from $(x,n,d)$ $(x',n',d')$ and from $(x',n',d')$ to $(x'',n'',d''),$ then
-there is also an arrow from $(x,n,d)$ to $(x'',n'',d'')$.
-\travis{Moreover, if there is an arrow from $(x,n,d)$ to $(x'',n'',d''),$ then we  claim there \abedit{is} an arrow from $(x,n,d)$ to $(x',n',d')$, \abedit{where $x'$ is the image of $x$ on $X_1(n')$ and $n'$ properly divides $n$}.
+This graph is \textbf{transitive}, meaning that if there is an arrow \sedit{edge} from $(x,n,d)$ \sedit{to} $(x',n',d')$ and from $(x',n',d')$ to $(x'',n'',d''),$ then
+there is also an arrow \sedit{edge} from $(x,n,d)$ to $(x'',n'',d'')$.
+\travis{Moreover, if there is an arrow from $(x,n,d)$ to $(x'',n'',d''),$ then we  claim there \abedit{is} an arrow from $(x,n,d)$ to $(x',n',d')$, \abedit{where $x'$ is the image of $x$ on $X_1(n')$ and $n'$ is any multiple of $n''$ which properly divides $n$}.
 Intuitively, if the degree grows as much as possible from level $n''$ to level $n$ then it also grows as much as possible from level $n'$ to level $n$.
-Indeed: let $g_1:X_1(n) \rightarrow X_1(n')$ and $g_2:X_1(n') \rightarrow X_1(n'')$.
+Indeed, let $g_1:X_1(n) \rightarrow X_1(n')$ and $g_2:X_1(n') \rightarrow X_1(n'')$.
 Suppose for the sake of contradiction that  $\abedit{d}<\abedit{d'}\cdot\deg g_1$.
@@
 
-Now fix a vertex $(x,n,d)$ and consider its \textbf{descendants}, i.e.
+Now fix a vertex $(x,n,d)$ and consider \travis{the graph induced by $(x,n,d)$ and} its \textbf{descendants}, i.e.
 all vertices $(x',n',d')$ reachable by a path from $(x,n,d)$.
@@
 \abedit{In this section, we will show that this graph has a single sink as well.}    \abbey{Is there standard notation for this?
-I use $D(v)$ below.}
+I use $D(v)$ below.} \sachi{I think this is typically the out-neighborhood of a vertex, denoted $N^+(v)$.
+i.e.
+this is the set of vertices $w$ such that there is an edge from $v$ to $w$.
+By the way, what we have defined as $D(v)$ (and also $N^+(v)$) is technically not directed acyclic graph, it's just a set -- but we can consider the induced subgraph on $N^+(v)$, i.e.
+the set of these vertices and along with all of the edges going between them that were in the original graph.} \travis{added that we consider the induced graph, making it a graph instead of a set}\travis{I think out-neighborhood happens to work for our DAG, since $(x,n,d)$ is adjacent to any vertex it has a path to.
+It wouldn't in general be the same thing.}
 
 \begin{proposition}\label{Prop:single_sink}
-    Let $m\geq 1$ be an integer and let $E/\Q$ be an elliptic curve. Fix $v=(x,m,d)$ in $G(E,m)$, and consider the subgraph $D(v)$ of all its descendants. Then $D(v)$ has a single sink.
+    Let $m\geq 1$ be an integer and let $E/\Q$ be an elliptic curve.
+Fix $v=(x,n,d)$ in $G(E,m)$, and consider the \sedit{induced} subgraph \sedit{on the set} $D(v)$ of all its descendants.
+Then \sedit{this subgraph} has a single sink.
+\abbey{Is there a reason why we can't let $D(v)$ -- or some other, better notation -- denote the induced subgraph, not just the set of descendants?
+It seems better to emphasize the subgraph for the purposes of this statement.
+We could also just say, ``For any fixed vertex $v$ in $G(E,m)$, the induced subgraph on its descendants has a single sink." Is this better?} \sachi{There is no reason why -- we should just define it this way in the beginning :) Right now we are saying it's a set, so I found it a bit confusing, since it's not entirely clear which edges we are taking on the set of vertices.
+I think either phrasing is OK -- as you suggest, we can also define $D(v)$ to be the induced subgraph on the set of descendents (instead of the set of descendents itself), or remark that we abuse notation and denote the induced subgraph and the set of vertices by the same notation.}
 \end{proposition}
@@
 \begin{lemma}\label{lem:LCM}
-Let $n_1,n_2 \in \Z^+$ and define $n \coloneqq \lcm(n_1,n_2)$.
-If $g=\gcd(n_1,n_2)$, we let $n_1=g\cdot n_1'$ and $n_2=g\cdot n_2'$.
-Suppose $E/F$ is an elliptic curve, and $P \in E(\overline{F})$ is a point of order $n$.
-If $n_2'P\in E(F)$ and $n_1'P \in E(F)$, then $P \in E(F)$.
+Let $n_1,n_2 \in \Z^+$ and $n \coloneqq \lcm(n_1,n_2)$. For $g=\gcd(n_1,n_2)$, we define $n_1'\coloneqq n_1/g$ and $n_2'\coloneqq n_2/g$. 
+Suppose $E/F$ is an elliptic curve, and $P \in E(\overline{F})$ is a point of order $n$. If $n_2'P\in E(F)$ and $n_1'P \in E(F)$, then $P \in E(F)$.
 \end{lemma}
@@
 \begin{lemma} \label{lem:compositum_res_fields}
-Let $n_1,n_2 \in \Z^+$ and define $n \coloneqq \lcm(n_1,n_2)$.
-If $g=\gcd(n_1,n_2)$, we let $n_1=g\cdot n_1'$ and $n_2=g\cdot n_2'$.
+Let $n_1,n_2 \in \Z^+$ and $n \coloneqq \lcm(n_1,n_2)$.
+For $g=\gcd(n_1,n_2)$, we define $n_1'\coloneqq n_1/g$ and $n_2'\coloneqq n_2/g$.
 Let $x=[E,P] \in X_1(n)$ for an elliptic curve $E$ with $j(E) \neq 0,1728$, and define $x_1=[E,n_2'P] \in X_1(n_1)$ and $x_2=[E,n_1'P] \in X_1(n_2)$.
@@
 \subsection{Proof of Proposition \ref{Prop:single_sink}}
-The proof of Proposition \ref{Prop:single_sink} will appear as a corollary to the following more general result.
+The proof of Proposition \ref{Prop:single_sink} will appear as a corollary to the following result.
 
 \begin{proposition}\label{Prop:gcd}
-Let $m\geq 1$ be an integer and let $E/\Q$ be an elliptic curve. In $G(E,m)$,
+Let $m\geq 1$ be an integer and let $E/\Q$ be an elliptic curve. In the graph $G(E,m)$,
 suppose $(x,n,d)$ is connected by a path to both $(x_1,n_1,d_1)$ and $(x_2,n_2,d_2)$, where $n=\lcm(n_1,n_2)$.
@@
     \begin{proof}  By assumption, the integer $g=\gcd(n_1,n_2)$ is a proper divisor of both $n_1=gn_1'$ and $n_2=gn_2'$.
-
-    Let $f_1: X_1(n) \rightarrow X_1(n_1)$ and let $f_2: X_1(n) \rightarrow X_1(n_2)$. We consider two cases.
+Let $f_1: X_1(n) \rightarrow X_1(n_1)$ and let $f_2: X_1(n) \rightarrow X_1(n_2)$.
+We consider two cases.
     \begin{enumerate}
-    \item Suppose $ g>2$, or if $g=1$, that exactly one of $n_1$ or $n_2$ is greater than 2.
-In the latter case, without loss of generality we may assume $n_1>2$, and $n_2=2$.
+    \item Suppose $ g>2$, \abedit{or if $g=1$, that there exists $n_i \leq 2$.
+In the latter case, our assumptions imply that exactly one of $n_1$ or $n_2$ is equal to 2 and the other is greater than 2.
+So if $g=1$,} without loss of generality we may assume $n_1>2$ and $n_2=2$.
 Then $\Q(x_1)\Q(x_2)=\Q(x)$ by Lemma \ref{lem:compositum_res_fields}, and so by assumption
@@
 Similarly, for a prime $p \mid n_2'$, we have $p \nmid g$ if and only if $p \nmid n_1$.
-Thus
+Thus by Corollary \ref{Cor:DegreeFormula}, we have
     \begin{align*}
@@
 \begin{corollary}
-Let $m\geq 1$ be an integer and let $E/\Q$ be an elliptic curve. Fix $v=(x,m,d)\in G(E,m)$, and consider the subgraph $D(v)$ of all its descendants. Then $D(v)$ has a single sink.
+Let $m\geq 1$ be an integer and let $E/\Q$ be an elliptic curve.
+Fix $v=(x,n,d)\in G(E,m)$, and consider the \sedit{induced} subgraph \sedit{on} $D(v)$ \sedit{the set} of all its descendants.
+Then $D(v)$ has a single sink.
 \end{corollary}
@@
 \begin{proof}
-Suppose for the sake of contradiction that $D(v)$ has two distinct sinks, $v_1=(x_1,n_1,d_1)$ and $v_2=(x_2,n_2,d_2)$.
-But having a path from $(x,n,d)$ to each of $v_1,v_2$ implies there is a path from $(x',\text{lcm}(n_1,n_2),d')$ to each of $v_1,v_2$.
+Suppose for the sake of contradiction that \sedit{the subgraph induced by} $D(v)$ has two distinct sinks, $v_1=(x_1,n_1,d_1)$ and $v_2=(x_2,n_2,d_2)$.
+\abedit{If $n_1 \mid n_2$, then the arrows from $v$ to $v_1$ and $v$ to $v_2$ force there to be an arrow from $v_2$ to $v_1$.
+This contradicts the fact that $v_2$ is a sink, so it must be that $n_1 \nmid n_2$.
+Similarly, it must be that $n_2 \nmid n_1$.
+Note} having a path from $v$ to each of $v_1,v_2$ implies there is a path from $(x',\text{lcm}(n_1,n_2),d')$ to each of $v_1,v_2$; see Remark \ref{Remark:Transitivity}.
 But then both $v_1,v_2$ map to $(x_3,\text{gcd}(n_1,n_2),d_3)$ by Proposition \ref{Prop:gcd}, contradicting the fact that they were both sinks.
-
-\abbey{need to rule out case where $\gcd=n_1$ or $n_2$ since removed from proposition}
 %If $n_1 \mid n_2$, then the claim holds since the natural map $X_1(n) \rightarrow X_1(n_1)$ factors through $X_1(n_2)$ in this case \abbey{Add more details.
@@
 \label{sec:mainalg}
-\abbey{Section updated to match revised algorithm; added examples.} The following algorithm is the main procedure for determining whether a given non-CM $j$-invariant in $\Q$ is the image of a $\PP^1$-isolated point on $X_1(N)$ for some $N$ based on results in \cite{BELOV,ZywinaAlgorithm}.
+The following algorithm is the main procedure for determining whether a given non-CM $j$-invariant in $\Q$ is the image of a $\PP^1$-isolated point on $X_1(N)$ for some $N$ based on results in \cite{BELOV,ZywinaAlgorithm}.
 We note that for any CM $j$-invariant $j$, there exists infinitely many $N\in\Z^+$ for which there is a sporadic point $x\in X_1(N)$ with $j(x)=j$ by \cite[Theorem 7.1]{BELOV}, so it is not necessary to consider them in this algorithm.
@@
 Apply Algorithm \ref{alg:reduce_level} to $G(N)$ to obtain the level $m_0$ of the $m$-adic Galois representation associated to $E$, where $m$ is the product of 2, 3, and all non-surjective primes.\\
-Using Algorithm \ref{alg:compute_prim_degree}, return a multiset $D$ with entries $\langle n, \{\langle a_1, d_1\rangle ,  \dots,  \langle a_r, d_r\rangle \} \rangle$
+Using Algorithm \ref{alg:compute_prim_degree}, return a multiset $D$ \abbey{updated to match new definitions} with entries $\langle n, \{\langle a_1, d_1\rangle ,  \dots,  \langle a_r, d_r\rangle \} \rangle$
     for all positive divisors $n$ of $m_0$ such that the degree of the corresponding 
@@
 \label{sec:madicrep}
-\abbey{Updated the algorithm description to be less technical; added math proposition to justify; added examples.}
+
 Let $E/\Q$ be a non-CM elliptic curve, and define the set 
@@
 
+  \begin{example}
+Suppose $E/\Q$ is a non-CM elliptic curve such that $\rho_{E}$ has level $N$.
+As above, define $n=\prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$ and let $m_0$ be the level of $\rho_{E,m^{\infty}}$ for $m= \prod_{\ell \in S_E} \ell$.
+It follows that $m_0| n$ and $n | N$.
+Each of these divisibilities can be proper \abbey{emphasize at start -- or start of secction}.
+For example, if $E=75072.bc2$, we see that $\rho_E$ has level $N=4682=2^2 \cdot 3 \cdot 17 \cdot 23$.
+Since 2 is the only non-surjective prime, $n=2^2$.
+However, the level of the $m$-adic Galois representation associated to $E$ is 2.
+On the other hand, it can also happen that $N=m_0$.
+For example, if $E=54.b2$, we see that $\rho_E$ has level 72, and this is also the level of the $m$-adic Galois representation associated to $E$.
+\end{example}
   \begin{proposition}
@@
   \end{corollary}
-
-  \begin{example}
-Suppose $E/\Q$ is a non-CM elliptic curve such that $\rho_{E}$ has level $N$.
-As above, define $n=\prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$ and let $m_0$ be the level of $\rho_{E,m^{\infty}}$ for $m= \prod_{\ell \in S_E} \ell$.
-It follows that $m_0| n$ and $n | N$.
-Each of these divisibilities can be proper.
-For example, if $E=75072.bc2$, we see that $\rho_E$ has level $N=4682=2^2 \cdot 3 \cdot 17 \cdot 23$.
-Since 2 is the only non-surjective prime, $n=2^2$.
-However, the level of the $m$-adic Galois representation associated to $E$ is 2.
-On the other hand, it can also happen that $N=m_0$.
-For example, if $E=54.b2$, we see that $\rho_E$ has level 72, and this is also the level of the $m$-adic Galois representation associated to $E$.
-\end{example}
 
@@
 Proposition~\ref{prop:compute_degrees} below allows us to compute $\deg x$ and $\deg y$ from $n,n/a,\#vH$, and $\#avH$.
-If  $\deg(x)/\deg(y)=\deg(f)$ then we include $( \frac{n}{a},\deg y)$  in the list $L$.
+If  $\deg(x)/\deg(y)=\deg(f)$, then we include $(\frac{n}{a},\deg y)$  in the list $L$.
 % ($\deg y$ is computed as $c\#dvH$ where $c=\frac{1}{2}$ if $ed\leq 2$ and $c=1$ otherwise). 
@@
 Assume that $n>2$.
-When $-I\in G$, the points $P$ and $-P$ are distinct and in the same Galois orbit so $[\Q(x(P)):\Q]=[\Q(P):\Q]/2$ and $\#vH=\#vG$.
+When $-I\in G$, the points $P$ and $-P$ are distinct and in the same Galois orbit so $[\Q(x(P)):\Q]=\frac{1}{2}[\Q(P):\Q]$ and $\#vH=\#vG$.
 We conclude that
     \[
-    \deg x = [\Q(x(P)):\Q] = [\Q(P):\Q]/2 = \frac{1}{2}\#vG = \frac{1}{2}\#vH. 
+    \deg x = [\Q(x(P)):\Q] = \frac{1}{2}[\Q(P):\Q] = \frac{1}{2}\#vG = \frac{1}{2}\#vH. 
     \]
@@
     \]
-    so we again have that the degree of the point represented by $(E,P)$ is $\#vH/2$.
+    so we again have that the degree of the point represented by $(E,P)$ is $\frac{1}{2}\#vH$.
 
@@
 
-\abbey{New section.} In this section, we will prove results on the validity of our Main Algorithm as stated in Section \ref{sec:mainalg}.
+In this section, we will prove results on the validity of our Main Algorithm as stated in Section \ref{sec:mainalg}.
 After recording preliminary results in Section \ref{sec:prelimresult}, we will give the proof in Section \ref{sec:proofvalidity}.
@@
 
-\sachi{Swap this section with the next section?} \abbey{I moved the last section way earlier -- what do you think?}
-
 \abedit{Suppose $E/\Q$ is non-CM elliptic curve such that one of the following holds:
@@
     \item $N_E=p \leq 200{,}000{,}000$ for some prime number $p$.
-\end{itemize} Then running Algorithm 1 on $E$ results in the empty set, aside from the output for those $j$-invariants given in the Appendix.}
-In this section we describe additional criteria which can prove that there are no isolated points on $X_1(N)$ for a fixed $N$ corresponding to a given $j$-invariant \abedit{$j \notin \{-140625/8,-9317,351/4, -162677523113838677\}$, proving Theorem \ref{LMFDBoutputThm}}.
-
+\end{itemize} Then running Algorithm 1 on $E$ results in the empty set, aside from the output for those $95$ $j$-invariants given in the Appendix.}
+Additionally, the only $j$-invariants corresponding to points of degree $d$ on $X_1(N)$ whose mod $N$ image is genus $>0$ are listed in Table~\ref{table:imagegt0}, along with the output of the algorithm and the genus of the mod $N$ image.
+\abbey{I'm so interested in this genus 5 curve with an exceptional non-CM rational point which gives rise to the degree 9 point on $X_1(28)$.
+Is there any explanation for the rational point on this genus 5 curve?
+We kind of understand why the other isolated $j$-invariants arise, but not this one.}
+	\begin{table}[h]
+	\begin{center}
+		\begin{tabularx}{242pt}{l l c} \toprule
+		$j$ & $<N, d>$ & genus  \\\midrule
+$-140625/8$ &  $\{ <21, 3>^2 \} $ & $1$\\
+ $-162677523113838677$& $\{ <37, 18> \}$ & $4$\\
+ $-882216989/131072$ & $\{ <17, 4>^2\}$ & $1$ \\
+ $-9317$ & $\{ <37, 6>^3 \} $ & $4$\\
+ $16778985534208729/81000$ & $\{ <24, 4>^2 \}$ & $1$\\
+ $351/4$ & $\{ <28, 9>^2 \}$ & $5$\\ \bottomrule
+		\end{tabularx}
+		\caption{Output of main algorithm with mod $N$ genus $>0$}\label{table:imagegt0}
+	\end{center}
+\end{table}
+
+In this section we describe additional computations that prove that the only $\PP^1$-isolated points on $X_1(N)$ for a fixed $N$ correspond to the four $j$-invariants $j=-140625/8,-9317,351/4, -16267752311383867$, proving Theorem \ref{LMFDBoutputThm}.
+\if{false}
 \begin{proposition} \abbey{New plan is to use result about genus 0 mod $N$ images in place of this Proposition (instead of working to correct it).}
@@
 
-\subsection{Special cases}
-We now explain how we dealt with cases that passed all the filters.
+\fi
+
+\subsubsection{Degree $18$ point on $X_1(37)$ corresponding to $j=-162677523113838677$}
+
+We show that the point $x\in X_1(37)(K)$, where $K$ is a degree 18 number field, and $j(x)=-162677523113838677$ is $\PP^1$-isolated.
+We explicitly compute the coordinates of $x$ on a model of $X_1(37)$ and define  $\sigma_i$, for $i=1,\ldots, 18$ to be the automorphisms of $K$ and $D=\sum_{i=1}^{18}\sigma_i(x)$.
+Reducing everything modulo $3$ and denoting the reduction of $D$ modulo $3$ by $\overline{D}$, we obtain $\ell(\overline{D})=1$, which shows that the reduction
+$\overline{x}$ of $x$ modulo 3 is $\PP^1$-isolated, and hence it follows that $x$ is $\PP^1$-isolated.  %\abbey{I believe we mean that it \emph{is} $\PP^1$-isolated.} \filip{Yes, fixed.}
+\sachi{Do we need to prove this is isolated or was it already done in van Hoeij and Derickx?
+It seems asymmetric that this is the only isolated point we talk about, of the four.} \abbey{I don't think they proved (or, at least, published a proof) that it was $\PP^1$-isolated -- it's not sporadic, and it looks like they stopped looking for points on $X_1(37)$ after degree 17.
+See here: https://www.math.fsu.edu/~hoeij/files/X1N/LowDegreePlaces.
+The other three $j$-invariants were known to be isolated before and are described in the introduction.
+However, $j(x)=-162677523113838677$ was known to give a degree 18 point prior to our computation, since it gives a rational point on $X_0(37)$ and $\deg(X_1(37) \rightarrow X_0(37))=18$.
+So it's not so much that this is ``discovering" a new $\PP^1$-isolated point, as just making the official observation that this known point is actually $\PP^1$-isolated.}
 
@@
 
-\subsubsection{Degree $18$ point on $X_1(37)$ corresponding to $j=-162677523113838677$}
-
-We show that the points $x\in X_1(37)(K)$, where $K$ is a degree 18 number field, and $j(x)=-162677523113838677$ is $\PP^1$-isolated.
-We explicitly compute the coordinates of $x$ on a model of $X_1(37)$ and define  $\sigma_i$, for $i=1,\ldots, 18$ to be the automorphisms of $K$ and $D=\sum_{i=1}^{18}\sigma_i(x)$.
-Reducing everything modulo $3$ and denoting the reduction of $D$ modulo $3$ by $\overline{D}$, we obtain $\ell(\overline{D})=1$, which shows that the reduction
-$\overline{x}$ of $x$ modulo 3 is $\PP^1$-isolated, and hence it follows that $x$ is $\PP^1$-isolated.  %\abbey{I believe we mean that it \emph{is} $\PP^1$-isolated.} \filip{Yes, fixed.}
-
 \filip{I did not go into much details here, as I think more details would entail just writing a bunch of equations, and the code where all the computations are dove, will be supplied.}
+
+\subsubsection{Degree $4$ point on $X_1(24)$ corresponding to $j=16778985534208729/81000$}
+\sachi{can/should we combine this with the previous subsection?}
+To show that this point is not isolated we compute the coordinates of a degree $4$ point $x$ corresponding to our curve on a model of $X_1(24)$.
+The point $x$ is defined over a quartic field.
+Let $\sigma_i$, for $i=1,\ldots, 4$ be the automorphisms of $K$ and $D=\sum_{i=1}^4\sigma_i(x)$.
+\sachi{is this how you did this Filip?}
+We compute $\ell(D)=2$, which implies that $x$ is not $\PP^1$-isolated.
 
@@
 \label{appendix}
-\abbey{Added output of Algorithm 1.}
+
 Suppose $E/\Q$ is non-CM elliptic curve such that one of the following holds:

### 2023-07-27 TeX/draft.tex
Small edits

@@
 \newcommand{\travis}[1]{\textcolor{orange}{Travis: #1}}
+\newcommand{\dldedit}[1]{{\color{Plum} #1}}
 \newcommand{\abedit}[1]{{\color{blue} #1}}
@@
 \begin{document}
+
 \begin{abstract}
@@
 \end{abstract}
+
 \maketitle
@@
 We are interested in studying isolated points on $X_1(N)$.
-Roughly speaking these are points of degree $d$ not belonging to an infinite family of degree $d$ points parametrized by a geometric object.
+Roughly speaking, these are points of degree $d$ not belonging to an infinite family of degree $d$ points parametrized by a geometric object.
 For example, if $f: X_1(N) \rightarrow \PP^1$ is a rational map of degree $d$, then $f^{-1}(\PP^1(\Q))$ contains infinitely many closed points of degree $d$ by Hilbert's irreducibility theorem \cite[Chapter~9]{serre97}.
@@
 If a closed point $x\in X_1(N)$ is both $\PP^1$- and AV-isolated, then we say $x$ is \textbf{isolated}.
+
 Isolated points can be thought of as those points whose existence is not explained by a geometric construction.
@@
 
-One special class of isolated points is \textbf{sporadic} points, which are $x \in X_1(N)$ such that there are only finitely many points on $X_1(N)$ of degree at most $\deg(x)$.
-Hence a non-cuspidal sporadic point corresponds to an elliptic curve with a point of order $N$ in ``usually low degree." Elliptic curves with complex multiplication (CM) provide many natural examples of sporadic points, since the extra endomorphisms of a CM elliptic curve constrain the size of the image of the associated Galois representation.
-Indeed, as shown in \cite[Theorem~8.2]{CGPS2022}, there exist sporadic CM points on $X_1(N)$ for all $N\geq 721$.
+One special class of isolated points is \textbf{sporadic} points, which are
+points $x \in X_1(N)$ such that there are only finitely many points on $X_1(N)$
+of degree at most $\deg(x)$. Hence a non-cuspidal sporadic point corresponds to
+an elliptic curve with a point of order $N$ \dldedit{with ``unusually low degree.''}
+Elliptic curves with complex multiplication (CM) provide many natural examples
+of sporadic points, since the extra endomorphisms of a CM elliptic curve
+constrain the size of the image of the associated Galois representation.
+Indeed, as shown in \cite[Theorem~8.2]{CGPS2022}, there exist sporadic CM
+points on $X_1(N)$ for all $N\geq 721$.
 
@@
 \noindent Since the image of the adelic Galois representation of a non-CM elliptic curve $E/\Q$ has finite level, this theorem reduces the problem of determining whether $j(E)$ is isolated to the problem of determining whether $E$ gives rise to an isolated point on a finite number of modular curves.
-While a sufficient finite list can be deduced directly from the adelic level as found by Zywina \cite{ZywinaAlgorithm}, our output works to reduce this list to its minimal size.
+While a sufficient finite list can be deduced directly from the adelic level as found by Zywina's Algorithm~\cite{ZywinaAlgorithm}, our \dldedit{approach attempts to reduce the size of this list as much as possible}.
 This inspires the notion of \textbf{primitive points} on modular curves, as studied in Section \ref{sec:PrimitivePoints}.
@@
 We thank Pete Clark, Maarten Derickx, Jeremy Rouse, and David Zureick-Brown for helpful conversations.
+\dld{Perhaps we also give an explicit shoutout to Zywina for making his code public too?}
 

### 2023-09-21 dolinesteinwatkins.m
add check for genus 0, add a parallelize for stein-watkins database

@@ -1,0 +1,25 @@
+AttachSpec("../OpenImage.spec");                                                      
+path := OpenImageContext("../OpenImage/data-files");                                                               
+AttachSpec("isolated.spec");
+
+
+if assigned seq then
+    SetColumns(0);
+    SetAutoColumns(false);
+    n := #seq;
+    if n lt 4 then 
+    	for i in [1 .. 4-n] do
+    		seq := "0" cat seq;
+    	end for;
+    end if;
+    seq := "x" cat seq;
+    inputs := Split(Read(seq), "\n");
+    for i in [1..#inputs] do
+        jinv := inputs[i];
+        jinv := eval jinv;
+        jinv := Rationals()!jinv;
+        output := NotIsolated(jinv, path);
+        print Join([Sprint(elt) : elt in output], ":");
+	end for;
+    exit;
+end if;

### 2023-09-21 isolatedpoints.m

@@ -183,6 +183,11 @@ intrinsic NotIsolated(j::FldRatElt, path::Assoc : ainvs :=[]) -> List
     end if;
 
     G0 := ChangeRing(G,Integers(m0));
+
+    if GL2Genus(G0) eq 0 then
+        return [* j, {* *} *];
+    end if;
+
     primitivepts := PrimitiveDegreesOfPoints(G0); 
     potisolated := FilterByRiemannRoch(primitivepts);
 

### 2023-09-21 dolinesteinwatkins.m
fix doline

@@ -1,5 +1,6 @@
-AttachSpec("../OpenImage.spec");                                                      
-path := OpenImageContext("../OpenImage/data-files");                                                               
+AttachSpec("../OpenImage/OpenImage.spec");                                                      
+path := OpenImageContext("../OpenImage/data-files");  
+Attach("../ell-adic-galois-images/groups/gl2.m");                                                             
 AttachSpec("isolated.spec");
 
 

### 2023-09-21 TeX/author_info.tex
Updates from Overleaf

@@
 \email{\url{bourdoam@wfu.edu}}
-\thanks{AB is supported by NSF Grant DMS-2145270.}
+\thanks{AB was supported by NSF Grants DMS-2145270 and DMS-1928930.
+Part of the work was completed while the author was in residence at the Simons Laufer Mathematical Science Institute in Berkeley, CA, during the semester of Diophantine Geometry.}
 
 \author[Hashimoto]{Sachi Hashimoto}
-\address{%
-  Sachi Hashimoto,
-  Max Planck Institut für Mathematik in den Naturwissenschaften,
-  Inselstraße 22,
-  04103 Leipzig
+\address{  Sachi Hashimoto, Department of Mathematics,
+  Brown University,
+  Box 1917,
+  151 Thayer Street,
+  Providence, RI, 02912
 }
-\email{\url{sachi.hashimoto@mis.mpi.de}}
+\email{\url{sachi_hashimoto@brown.edu}}
 \urladdr{\url{https://sachihashimoto.github.io/}}
@@
 \author[Keller]{Timo Keller}
-\address{Timo Keller, Leibniz Universität Hannover, Institut für Algebra, Zahlentheorie und Diskrete Mathematik, Welfengarten 1, 30167 Hannover, Germany}
-\email{keller@math.uni-hannover.de}
+\address{Timo Keller, Rijksuniveriteit Groningen, Bernoulli Institute, Bernoulliborg, Nijenborgh 9, 9747 AG Groningen, The Netherlands (previously: Leibniz Universität Hannover, Institut für Algebra, Zahlentheorie und Diskrete Mathematik, Welfengarten 1, 30167 Hannover, Germany)}
+\email{t.keller@rug.nl}
 \urladdr{\url{https://www.timo-keller.de}}
+\thanks{%
+  TK was partially supported by the 2021 MSCA Postdoctoral Fellowship 01064790 -- ExplicitRatPoints.
+}
 
@@
 \urladdr{\url{https://travismo.github.io/}}
+\thanks{TM was partially supported by the Commonwealth Cyber Initiative.}
 
@@
 \urladdr{\url{https://web.math.pmf.unizg.hr/~fnajman/}}
+\thanks{FN is supported by the QuantiXLie Centre of Excellence, a
+  project co-financed by the Croatian Government and European Union
+  through the European Regional Development Fund - the Competitiveness
+  and Cohesion Operational Programme (Grant KK.01.1.1.01.0004).}
 

### 2023-09-21 TeX/draft.tex
Updates from Overleaf

--- 2023-07-20 TeX/draft.tex
@@
 
+%for tables
+\usepackage{tabularx}
+\usepackage{booktabs}
+
 % Presented to you by Technicolor, and the number 3
@@
 %\usepackage{ulem}
-\usepackage{hyperref}
+\usepackage[pagebackref=true, colorlinks, allcolors=blue]{hyperref}
+\renewcommand*{\backreflastsep}{, }
+\renewcommand*{\backreftwosep}{, }
+\renewcommand*{\backref}[1]{}
+\renewcommand*{\backrefalt}[4]{%
+  \ifcase #1 %
+    \relax
+  \or
+    $\uparrow$#2.%
+  \else
+    $\uparrow$#2.%
+  \fi%
+}
 \usepackage{cleveref}
@@
 \usepackage{tikz}
-
+\usetikzlibrary{cd}
 % For full page usage, shockingly
@@
 \newcommand{\proj}{\operatorname{proj}}
-
-\newcommand{\davidnote}[1]{\textcolor{Plum}{David: #1}}
+\newcommand{\iso}{\simeq}
+\newcommand{\isom}{\cong}
+
+\newcommand{\davidnote}[1]{\textcolor{VioletRed}{David: #1}}
 \newcommand{\filip}[1]{{\textcolor{cyan}{Filip: [#1]}}}
 \newcommand{\abbey}[1]{\textcolor{blue}{Abbey: #1}}
-\newcommand{\dld}[1]{\textcolor{Plum}{dld: #1}}
+\newcommand{\dld}[1]{\textcolor{VioletRed}{dld: #1}}
 \newcommand{\sachi}[1]{\textcolor{purple}{Sachi: #1}}
@@
 \newcommand{\travis}[1]{\textcolor{orange}{Travis: #1}}
+\newcommand{\tmedit}[1]{{\color{orange} #1}}
+\newcommand{\dldedit}[1]{{\color{VioletRed} #1}}
 \newcommand{\abedit}[1]{{\color{blue} #1}}
 \newcommand{\fedit}[1]{{\color{cyan} #1}}
+\newcommand{\sedit}[1]{{\color{purple} #1}}
+\newcommand{\hs}[1]{{\color{brown}{Himanshu: [#1]}}}
+
 % Don't have subsections appear in TOC
@@
 \input{author_info.tex}
-\date{\today}
+%\date{\today}
 
 \begin{document}
+
 \begin{abstract}
@@
 \label{sec:intro}
-\abbey{Updated to account for isolated points.}
+
 The modular curve $X_1(N)$ is an algebraic curve over $\Q$ whose non-cuspidal points parametrize elliptic curves with a distinguished point of order $N$.
-We are interested in studying isolated points on $X_1(N)$.
-Roughly speaking these are points of degree $d$ not belonging to an infinite family of degree $d$ points parametrized by a geometric object.
-For example, if $f: X_1(N) \rightarrow \PP^1$ is a rational map of degree $d$, then $f^{-1}(\PP^1(\Q))$ contains infinitely many closed points of degree $d$ by Hilbert's irreducibility theorem \cite[Chapter 9]{serre97}.
+We are interested in studying isolated points on $X_1(N)$, which are roughly those not belonging to an infinite family of points parametrized by a geometric object.
+For example, if $f\colon X_1(N) \rightarrow \PP^1$ is a rational map of degree $d$, then $f^{-1}(\PP^1(\Q))$ contains infinitely many closed points of degree $d$ by Hilbert's irreducibility theorem \cite[Chapter~9]{serre97}.
 We say a degree $d$ point \emph{not} arising from such a map is \textbf{$\PP^1$-isolated}.
@@
 If a closed point $x\in X_1(N)$ is both $\PP^1$- and AV-isolated, then we say $x$ is \textbf{isolated}.
-Isolated points can be thought of as those points whose existence is not explained by a geometric construction.
-The lack of control of isolated points in infinite families of modular curves lies at the heart of several important open problems.
-See, for example, \cite[Question 1]{MazurNote} and \cite[Theorem 1.3]{BourdonNajman2021}.
-
-One special class of isolated points is \textbf{sporadic} points, which are $x \in X_1(N)$ such that there are only finitely many points on $X_1(N)$ of degree at most $\deg(x)$.
-Hence a non-cuspidal sporadic point corresponds to an elliptic curve with a point of order $N$ in ``usually low degree." Elliptic curves with complex multiplication (CM) provide many natural examples of sporadic points, since the extra endomorphisms of a CM elliptic curve constrain the size of the image of the associated Galois representation.
-Indeed, as shown in \cite[Theorem 8.2]{CGPS2022}, there exist sporadic CM points on $X_1(N)$ for all $N\geq 721$.
-
-Non-CM isolated points on $X_1(N)$ remain much more mysterious.
+One special class of isolated points is \textbf{sporadic} points, which are points $x \in X_1(N)$ such that there are only finitely many points on $X_1(N)$ of degree at most $\deg(x)$.
+While every sporadic point is isolated \cite[Theorem 4.2]{BELOV}, the converse need not hold.
+
+Elliptic curves with complex multiplication (CM) provide many natural examples
+of isolated points, since the extra endomorphisms of a CM elliptic curve
+constrain the size of the image of the associated Galois representation.
+Indeed, as shown in \cite[Theorem~8.2]{CGPS2022}, there exist sporadic CM
+points on $X_1(N)$ for all $N\geq 721$.
+Non-CM isolated points on $X_1(N)$ remain much more mysterious, and are tied to open uniformity problems of Balakrishnan and Mazur \cite[Conjecture 17]{BalakrishnanMazur23} and Serre \cite[$\S4.3$]{serre72}; see Section \ref{sec:UniformityConnections} for details.
 One recent line of investigation has focused on the class of isolated points associated to non-CM elliptic curves with $j$-invariant in $\Q$.
-To date, there are only three known examples of such curves, up to isomorphism over $\overline{\Q}$:
+To date, there are only three known examples of such elliptic curves, up to isomorphism over $\overline{\Q}$:
 \begin{itemize}
-\item The elliptic curve with $j$-invariant $-140625/8$ corresponds to two points of degree 3 on $X_1(21)$.
-Since there are only finitely many points of degree at most 3 on this modular curve, these are sporadic (and hence isolated) points.
+    \item The elliptic curve with $j$-invariant $-140625/8$ corresponds to two sporadic points of degree 3 on $X_1(21)$.
 This example was first discovered by Najman \cite{najman16}.
-In fact, this is the unique elliptic curve giving a sporadic point of degree at most 3 on \emph{any} modular curve of the form $X_1(N)$, as shown in recent work of Derickx, Etropolski, van Hoeij, Morrow, and Zureick-Brown \cite{DEvHMZB2021}.
-\item The elliptic curve with $j$-invariant $-9317$ gives three degree 6 points on $X_1(37)$, as in work of van Hoeij \cite{vanHoeij}.
-Since 6 is less than half the $\Q$-gonality of $X_1(37)$, as computed in \cite{DerickxVanHoeij2014}, the point is necessarily sporadic by work of Frey \cite{frey}.
+In fact, this is the unique elliptic curve giving a sporadic point of degree at most 3 on \emph{any} modular curve $X_1(N)$, as shown in \cite{DEvHMZB2021}.
+
+    \item The elliptic curve with $j$-invariant $-9317$ gives three points of degree 6 on $X_1(37)$, as in work of van Hoeij \cite{vanHoeij}.
+Since 6 is less than half the $\Q$-gonality of $X_1(37)$, as computed in \cite{DerickxVanHoeij2014}, the points are necessarily sporadic by work of Frey \cite{frey}.
+
     \item The elliptic curve with $j$-invariant $351/4$ gives an isolated point of degree 9 on $X_1(28)$; see \cite[Theorem 2]{OddDeg}.
-There are infinitely many points on $X_1(28)$ of degree 6, as shown in \cite{DerickxVanHoeij2014}, so this point is isolated but not sporadic.
+There are infinitely many points on $X_1(28)$ of degree 9, as shown in \cite{DerickxVanHoeij2014}, so this point is isolated but not sporadic.
 \end{itemize}
 
-If $x \in X_1(N)$ is a sporadic (resp.
-isolated) point, we say $j(x) \in X_1(1) \cong \mathbf{P}^1$ is a \textbf{sporadic} (resp.
-\textbf{isolated}) \textbf{$j$-invariant}.
-Thus the three $j$-invariants listed above are isolated $j$-invariants, while $-140625/8$  and $-9317$ are also sporadic $j$-invariants.
+If $x \in X_1(N)$ is an isolated (resp.
+sporadic) point, we say $j(x) \in X_1(1) \cong \mathbf{P}^1$ is an \textbf{isolated} (resp.
+\textbf{sporadic}) \textbf{$j$-invariant}.
+Thus the three $j$-invariants listed above are isolated $j$-invariants, while only the first two, $-140625/8$ and $-9317$, are sporadic $j$-invariants.
 We have good reason to believe that the set of all isolated $j$-invariants in $\Q$ is finite.
-\begin{theorem}[Bourdon, Ejder, Liu, Odumodu, Viray \cite{BELOV}]
-\label{BELOVfiniteness}
-Suppose there exists a constant $C$ such that the mod $\ell$ Galois representation of any non-CM elliptic curve over $\Q$ is surjective for primes $\ell>C$.
+Indeed, in \cite[Corollary 1.7]{BELOV} the authors show that this would follow from an affirmative answer to Serre’s Uniformity Question \cite{serre72}, which is now a conjecture of Sutherland \cite{sutherland} and Zywina \cite{ZywinaImages}.
+Moreover, in \cite[$\S1.2$]{BELOV}, the authors pose the following question:
+
+\begin{question}[Bourdon, Ejder, Liu, Odumodu, Viray]
+    Can one explicitly identify the (likely finite) set of isolated $j$-invariants in $\Q$?
+\end{question}
+
+%\begin{theorem}[Bourdon, Ejder, Liu, Odumodu, Viray \cite{BELOV}]
+%\label{BELOVfiniteness}
+%Suppose there exists a constant $C$ such that the mod $\ell$ Galois representation of any non-CM elliptic curve over $\Q$ is surjective for primes $\ell>C$.
 Then there are only finitely many isolated $j$-invariants in $\Q$.
-\end{theorem}
-
-\noindent The assumption about Galois representations stated in Theorem \ref{BELOVfiniteness} was originally asked as a question by Serre \cite{serre72}, and it has now been formally conjectured by both Sutherland \cite{sutherland} and Zywina \cite{ZywinaImages}.
+%\end{theorem}
+
+%\noindent The assumption about Galois representations stated in Theorem \ref{BELOVfiniteness} was originally asked as a question by Serre \cite{serre72}, and it has now been formally conjectured by both Sutherland \cite{sutherland} and Zywina \cite{ZywinaImages}.
 It is even suspected that $C=37$.
-Theorem \ref{BELOVfiniteness} is known unconditionally for points of odd degree \cite{OddDeg}: indeed, $j=-140625/8$ and $j=351/4$ are the only non-CM $j$-invariants in $\Q$ giving an isolated point of odd degree on $X_1(N)$, even as $N$ ranges over all positive integers.
-
-In \cite{BELOV}, they ask whether one can explicitly determine the set of isolated $j$-invariants in $\Q$.
-This is the motivation for the present work.
-We develop an algorithm which can be used to determine whether a given non-CM $j$-invariant $j\in \Q$ is isolated.
-Starting with the adelic image of the adelic Galois representation associated $E/\Q$ with $j(E)=j(x)$, as computed by Zywina \cite{ZywinaAlgorithm}, we apply various filters inspired by \cite{BELOV} to determine whether there exists an isolated point on $x \in X_1(N)$ with $j(x)=j$.
+
+This question serves as motivation for the present work.
+To this end, we develop an algorithm which can be used to determine whether a given non-CM $j$-invariant in $\Q$ is isolated.
+Starting with the image of the adelic Galois representation associated to $E/\Q$ with $j(E)=j$, as computed by Zywina \cite{ZywinaAlgorithm}, we apply various filters to determine whether there exists an isolated point $x \in X_1(N)$ with $j(x)=j$ for some $N$.
+% DLD TODO - words on what algorithm is
 
@@
     \KwIn{A non-CM $j$-invariant $j \in \Q$.}
-\KwOut{A list $[j,\{\langle a_1,d_1\rangle, \dots, \langle a_k,d_k\rangle \}]$ such that any isolated point $x \in X_1(N)$ with $j(x)=j$ maps down under the natural projection map to an isolated point of degree $d_i$ on $X_1(a_i)$ for some $1 \leq i \leq k$.}
+    \KwOut{A finite list $\{(a_1, d_1), \ldots, (a_k, d_k)\}$ of (level, degree) pairs such that $j$ is isolated if and only if there exists an isolated point $x \in X_1(a_i)$ of degree $d_i$ with $j(x) = j$ for some $(a_i, d_i)$ in the list.}
 \end{algorithm}
 
-\noindent In particular, if the output of Algorithm \ref{alg:mainalgorithm} is the empty set, then $j$ is not an isolated $j$-invariant.
-We give an overview of the main algorithm in Section \ref{alg:mainalgorithm}, with key sub-algorithms described in detail in Sections \ref{sec:madicrep} and \ref{sec:primitivedeg}.
-We address the validity of Algorithm \ref{alg:mainalgorithm} in Section \ref{sec:validity}.
-
-Running Algorithm \ref{alg:mainalgorithm} on all elliptic curves currently in the $L$-functions and Modular Forms Database (LMFDB) \cite{LMFDB} gives a list of 95 $j$-invariants which require further consideration; see the Appendix.
-After applying certain additional filters to address special cases, as discussed in Section~\ref{sec:remainingfilters}, we arrive at the following result.
+\noindent
+In particular, if the output of Algorithm \ref{alg:mainalgorithm} is the empty set, then $j$ is not an isolated $j$-invariant.
+If the output is nonempty,
+%In some cases,
+one can try to use other techniques to determine whether each point of degree $d_i$ on $X_1(a_i)$ associated to $E$ is isolated, from which we can definitively say whether $j(E)$ is an isolated $j$-invariant.
+
+Running Algorithm \ref{alg:mainalgorithm} on all elliptic curves currently in the $L$-functions and Modular Forms Database (LMFDB) \cite{LMFDB} shows that all but 6 of the non-CM $j$-invariants in $\Q$ from the LMFDB
+are \emph{not} isolated.
+As noted above, three of these $6$ $j$-invariants are known to be isolated; in Section~\ref{sec:remainingfilters} we perform a case-by-case analysis to study the remaining $3$ candidates.
+This gives the following result.
 
@@
 \begin{itemize}
-    \item$N_E \leq 500{,}000$,
+    \item $N_E \leq 500{,}000$,
     \item $N_E$ is only divisible by primes $p \leq 7$, or
-    \item $N_E=p \leq 200{,}000{,}000$ for some prime number $p$.
+    \item $N_E=p \leq 300{,}000{,}000$ for some prime number $p$.
 \end{itemize}
 Then $j(E) \in \{-140625/8,-9317,351/4, -162677523113838677\}$.
-Moreover, each of these $j$-invariants corresponds to a $\PP^1$-isolated point on $X_1(21)$, $X_1(37)$, $X_1(28)$, and $X_1(37)$, respectively.
+Moreover, each one of these $j$-invariants corresponds to a $\PP^1$-isolated point on $X_1(21)$, $X_1(37)$, $X_1(28)$, or $X_1(37)$, respectively.
 \end{theorem}
 
-Based on these results, we conjecture that the four non-CM isolated $j$-invariants identified above are in fact the \emph{only} $j$-invariants in $\Q$ associated to non-CM elliptic curves which give rise to $\PP^1$-isolated points.
-
-\begin{conjecture}
-If $x\in X_1(N)$ is a $\PP^1$-isolated point with $j(x) \in \Q$, then $j(x)=-140625/8$,$-9317$, $351/4$, $-162677523113838677$, or one of the 13 CM $j$-invariants in $\Q$.
+\begin{remark}
+Though we did not find a result in the literature showing the degree 18 point on $X_1(37)$ associated to $j=-162677523113838677$ is $\PP^1$-isolated, the point itself was well-known prior to this work.
+Indeed, this $j$-invariant corresponds to one of two non-CM elliptic curves over $\Q$ with a rational cyclic 37-isogeny (see, e.g., \cite[Table 4]{LRAnn}), and any elliptic curve with a $\Q$-rational cyclic $N$-isogeny will give a point on $X_1(N)$ in degree at most $\varphi(N)/2$.
+\end{remark}
+We conjecture that the four non-CM isolated $j$-invariants identified above are in fact the \emph{only} $j$-invariants in $\Q$ associated to non-CM elliptic curves which give rise to $\PP^1$-isolated points on $X_1(N)$.
+Such a result has already been established for points of odd degree: by \cite{OddDeg} we know that $j=-140625/8$ and $j=351/4$ are the only non-CM $j$-invariants in $\Q$ giving an isolated point of odd degree on $X_1(N)$, even as $N$ ranges over all positive integers.
+
+\begin{conjecture}\label{conj}
+If $x\in X_1(N)$ is a $\PP^1$-isolated point with $j(x) \in \Q$, then $j(x)=-140625/8$, $-9317$, $351/4$, $-162677523113838677$, or one of the 13 CM $j$-invariants in $\Q$.
 \end{conjecture}
 
-\noindent Since any CM elliptic curve is known to produce sporadic points on infinitely many modular curves of the form $X_1(N)$ by \cite[Theorem 7.1]{BELOV}, it follows conversely that every $j$-invariant in this set is isolated.
-
+\noindent Since any CM elliptic curve is known to produce sporadic points on infinitely many modular curves of the form $X_1(N)$ by \cite[Theorem 7.1]{BELOV}, it follows conversely that every $j$-invariant in this set is $\PP^1$-isolated.
+
+\begin{remark}
+Let $x\in X_1(N)$ be a $\PP^1$-isolated point with $j(x) \in \Q$.
+One expects that the square-free part of the conductor of any $E$ with $j(E) = j(x)$ will be very small.
+The reason for this is that any such isolated point will generally have small mod $\ell$ image for some $\ell$ dividing $N$.
+Unless $\ell$ is small, we expect this to force potentially good reduction on $E$ at all odd primes; see~\cite[Corollary 4.4]{Mazur1978} and \cite[Theorem 5.1]{BiluParent11} for examples of this phenomenon.
+Indeed this happens for all the curves appearing in~\Cref{conj}: their conductors are either a square, or twice a square.
+
+Heuristically one might except to find most or all of the $\PP^1$-isolated points among elliptic curves with relatively small conductor (and hence in the LMFDB).
+One can also numerically observe that elliptic curves with small Galois representations are over-represented among curves with small conductor.
+Only 4 of the first 50 curves ordered by conductor have trivial torsion groups and all of them have non-trivial isogenies, while one expects asymptotically almost all curves to have surjective Galois representations when ordered by height, see \cite[Theorem 1]{Duke97}.
+
+These observations bolster the computational evidence supporting \Cref{conj}.
+\end{remark}
+
+It is natural to suspect a connection between isolated points on $X_1(N)$ and isolated points on $X_0(N)$, the modular curve parametrizing elliptic curves with a rational cyclic $N$-isogeny.
+We say a point $x \in X_0(N)(\Q)$ is \textbf{exceptional} if $X_0(N)(\Q)$ is finite and $x$ corresponds to a non-CM elliptic curve over $\Q$.
 It is worth noting that the sporadic points on $X_1(21)$ associated to $j=-140625/8$ and the sporadic points on $X_1(37)$ associated to $j=-9317$ lie above exceptional rational points on $X_0(21)$ and $X_0(37)$, respectively.
-We say a point $x \in X_0(N)(\Q)$ is \textbf{exceptional} if $X_0(N)(\Q)$ is finite and $x$ corresponds to a non-CM elliptic curve over $\Q$.
-Thus it is natural to ask whether there exist other sporadic points on $X_1(N')$ lying above such exceptional rational points.
-Running Algorithm~\ref{alg:mainalgorithm} on the 14 $j$-invariants corresponding to exceptional rational points on $X_0(N)$ (see, for example, \cite[Table 4]{LRAnn}) shows that there are no additional sporadic $j$-invariants in this set.
+One might wonder whether other sporadic $j$-invariants can be obtained by a similar construction.
+Running Algorithm~\ref{alg:mainalgorithm} on all 14 $j$-invariants corresponding to exceptional rational points on $X_0(N)$ for any $N$ (described, for example, in~\cite[Table 4]{LRAnn}) shows that there are no additional sporadic $j$-invariants.
+
 \begin{theorem}
-Let $E$ be an elliptic curve corresponding to an exceptional rational point on $X_0(N)$. If there exists a sporadic point $x \in X_1(N')$ with $j(x)=j(E)$, then $j(E) =-140625/8$ or $-9317$.
+Let $E$ be an elliptic curve corresponding to an exceptional rational point on $X_0(N)$ for some positive integer $N$. If $j(E)$ is sporadic, then $j(E)=-140625/8$ or $-9317$.
 \end{theorem}
@@
 It is still an open problem to determine all sporadic points $x \in \cup_{N \in \Z^+} X_1(N)$ with $j(x) =-140625/8$ or $-9317$.
+
+\subsection{Key Components of Algorithm.} The first step of our algorithm applies results of \cite{BELOV} and \cite{ZywinaAlgorithm} to compute the finite set of \textbf{primitive points} associated to a non-CM elliptic curve $E/\Q$.
+The primitive points are characterized by the following theorem.
+\begin{theorem}\label{Thm:PrimPtsIntro}
+Let $E/\Q$ be a non-CM elliptic curve.
+There exists a finite set $\mathcal{P}=\mathcal{P}(E)$ of primitive points in $\cup_{n \in \Z^+} X_1(n)$ associated to $E$ which are characterized by the following properties:
+\begin{enumerate}
+\item For each $N\in \Z^+$, a point $x \in X_1(N)$ with $j(x)=j(E)$ corresponds to a unique element $x' \in \mathcal{P}$ under the natural projection map.
+Moreover, if $x' \in X_1(a)$, then $a \mid N$ and $\deg(x)=\deg(f)\cdot \deg(x')$, where $f\colon X_1(N) \rightarrow X_1(a)$ is the natural map.
+\item The rational number $j(E)$ is isolated if and only if there exists an isolated point in $\mathcal{P}$.
+\end{enumerate}
+Moreover, the set $\mathcal{P}$ is minimal with respect to condition (i).
+\end{theorem}
+
+\noindent By Theorem~\ref{Thm:PrimPtsIntro}\,(i), one can think of $\mathcal{P}(E)$ as the minimal set needed to reproduce the degrees of all points $x \in \cup_{n \in \Z^+} X_1(n)$ with $j(x) = j(E)$.
+Moreover, any isolated point $x \in X_1(n)$ with $j(x)=j(E)$ will correspond to a unique primitive point of minimal level.
+See Section \ref{sec:PrimitivePoints} for details.
+
+The second part of Algorithm \ref{alg:mainalgorithm} works to show the primitive points corresponding to $E$ are \emph{not} isolated.
+For example, if the Riemann--Roch space associated to $x \in X_1(N)$ has dimension at least 2, then $x$ is not $\PP^1$-isolated (and therefore not isolated).
+In other cases, we can show $x \in X_1(N)$ is not isolated by applying the following result.
+
+\begin{theorem}\label{Prop:Genus0Intro}
+Let $E/\Q$ be an elliptic curve, and let $H \leq \GL_2(\Z/N\Z)$ be the image of the mod $N$ Galois representation of $E$, after some choice of basis.
+If the modular curve $X_H$ has genus $0$, then there are no isolated points on $X_1(N)$ associated to $E$.
+\end{theorem}
+
+\noindent In particular, any elliptic curve with adelic image of genus 0 does not give rise to any isolated points on $X_1(N)$, even as $N$ ranges over all positive integers.
+However, Theorem \ref{Prop:Genus0Intro} is more broadly applicable.
+Even when the adelic image of $E$ has positive genus, it can still be that for all \emph{primitive} points $x \in X_1(a)$ associated to $E$, the mod $a$ Galois representation of $E$ gives a genus 0 modular curve.
+This occurs more often than one might expect: our preliminary computations identified at least 89 distinct such non-CM elliptic curves (up to $\overline{\Q}$-isomorphism) just within those currently in the LMFDB.
+See Example \ref{eg:modngenus0} for one such curve.
+
+\subsection{Connection to Open Uniformity Problems}\label{sec:UniformityConnections} Several well-known uniformity problems can be tied to isolated points on $X_1(N)$.
+One of the most longstanding examples is Serre's Uniformity Problem \cite[\S\,4.3]{serre72}, which in modern formulations \cite{sutherland,ZywinaImages} asks whether the mod $\ell$ Galois representation for any non-CM elliptic curve over $\Q$ is surjective for all $\ell>37$.
+In the proof of \cite[Theorem~1.3]{BourdonNajman2021}, the authors show that a non-CM elliptic curve $E/\Q$ with non-surjective mod $\ell$ Galois representation can be used to construct sporadic points on $X_1(\ell^2)$ for all $\ell$ sufficiently large.
+This approach allows one to phrase Serre's Uniformity Problem to be about controlling isolated points on $X_1(\ell^2)$ within certain families of non-CM $\Q$-curves.
+
+A more recent example is \cite[Conjecture 17]{BalakrishnanMazur23}, where Balakrishnan and Mazur conjecture that for sufficiently large $N$, any elliptic curve giving a quadratic point on $X_0(N)$ must have complex multiplication.
+Since a quadratic point on $X_0(N)$ will give a sporadic point on $X_1(N)$ for $N$ sufficiently large, we can connect this conjecture to one about non-CM isolated points $x \in X_1(N)$ with $j(x)$ generating at most a quadratic extension.
+
+\subsection{Outline}
+After providing relevant background material in Section \ref{sec:background}, we give an overview of the main algorithm in Section \ref{sec:mainalg}.
+The sub-algorithms used to compute primitive points and related mathematical results are discussed in Sections \ref{sec:madicrep}--\ref{sec:primitivedeg}, with the proof of Theorem \ref{Thm:PrimPtsIntro} appearing in Section \ref{sec:PrimitivePoints}.
+Results on genus 0 adelic images, including the proof of Theorem \ref{Prop:Genus0Intro}, are in Section \ref{sec:genus0}.
+We address the validity of Algorithm \ref{alg:mainalgorithm} in Section \ref{sec:validity}.
+The output the main algorithm obtained after running it on all elliptic curves in the LMFDB and its final analysis is discussed in Section \ref{sec:remainingfilters}.
+
+\subsection{Code} We have implemented our algorithm in Magma \cite{Magma}. Code is available in the GitHub repository at \url{https://github.com/davidlowryduda/isolated_points}.
 
@@
 We thank Pete Clark, Maarten Derickx, Jeremy Rouse, and David Zureick-Brown for helpful conversations.
+We also thank David Zywina for making his code to compute Galois images available, and David Roe for further making Zywina's code and implementation more readily available for other mathematicians to use; this project would not have been possible without their work.
+This project began at the \emph{COmputations and their Uses in Number Theory} conference at CIRM in March 2023; we thank the organizers as well as CIRM for providing the opportunity for collaboration.
 
@@
 \subsection{Isolated Points on Curves}
-Let $C$ be a curve, by which we will mean a nonsingular projective geometrically integral 1-dimensional scheme defined over a number field $k$; we suppose all curves satisfy these assumptions throughout the paper.
+Let $C$ be a curve, by which we will mean a smooth projective geometrically integral $1$-dimensional scheme defined over a number field $k$; we suppose all curves satisfy these assumptions throughout the paper.
 To streamline our exposition, we assume there exists a point $P_0 \in C(k)$, but this is not required; see \cite[$\S4$]{BELOV}.
@@
 \[
- x=P_1+ \cdots +P_{d},
+P_1+ \cdots +P_{d}, 
 \] 
@@
 \label{eqn:phid}
-\Phi_d: C^{(d)} \rightarrow \Jac(C)
+\Phi_d\colon C^{(d)} \rightarrow \Jac(C)
 \end{align}
-which sends the effective divisor $D$ of degree $d$ to the class $[D - dP_0]$, where $P_0 \in C(k)$.
+which sends an effective divisor $D$ of degree $d$ to the class $[D - dP_0]$.
 If $\Phi_d(x)=\Phi_d(y)$ for some other point $y \in C^{(d)}(k)$, then there exists a non-constant function $f \in k(C)^{\times}$ with $\text{div}(f)=x-y$.
-Since $x$ is a degree $d$ point and $x\not=y$, $x$ and $y$ have distinct support so $f: C \rightarrow \mathbf{P}^1_{k}$ is a dominant morphism of degree $d$.\footnote{In particular, this shows $\Phi_d$ is injective if $d$ is less than the $k$-gonality of $C$, which is the least degree of a non-constant rational map to $\mathbf{P}^1$.} By Hilbert's irreducibility theorem \cite[Chapter 9]{serre97}, $f^{-1}(\mathbf{P}^{1}(k))$ will contain infinitely many closed points of degree $d$.
-On the other hand, if $\Phi_d$ is injective on closed points of degree $d$, then by Faltings' Theorem \cite{faltings} there can exist infinitely many such points only if all but finitely many are parametrized by translates of positive rank abelian subvarieties of $\Jac(C)$.
-\sachi{or maybe: Suppose $\Phi_d$ is injective on closed points of degree $d$.
-Then Faltings' theorem \cite{faltings} implies all but finitely many such points are parametrized by translates of positive rank abelian subvarieties of $\Jac(C)$.}
+Since $x$ is a degree $d$ point and $x\not=y$, the divisors associated to $x$ and $y$ have distinct support so $f\colon C \rightarrow \mathbf{P}^1_{k}$ is a dominant morphism of degree $d$.\footnote{In particular, this shows $\Phi_d$ is injective if $d$ is less than the $k$-gonality of $C$, which is the least degree of a non-constant rational map to $\mathbf{P}^1$.} By Hilbert's irreducibility theorem \cite[Chapter 9]{serre97}, $f^{-1}(\mathbf{P}^{1}(k))$ will contain infinitely many closed points of degree $d$.
+On the other hand, if $\Phi_d$ is injective on closed points of degree $d$, then Faltings's Theorem \cite{faltings} implies that all but finitely many such points are parametrized by translates of positive rank abelian subvarieties of $\Jac(C)$.
 This inspires the following:
-
 \begin{definition} Let $C$ be a curve defined over a number field $k$. Let $\Phi_d$ be the map in \eqref{eqn:phid}.
 \begin{enumerate}
-\item []
-\item A closed point $x \in C$ of degree $d$ is $\PP^1$\textbf{-parametrized} if there exists a point $x' \in C^{(d)}(k)$ such that $\Phi_d(x)=\Phi_d(x')$.
+\item A closed point $x \in C$ of degree $d$ is $\PP^1$\textbf{-parametrized} if there exists a point $x' \in C^{(d)}(k)$ with $x' \neq x$ such that $\Phi_d(x)=\Phi_d(x')$.
 Otherwise, we say $x$ is $\PP^1$\textbf{-isolated}.
@@
 For any subgroup $H \leq \GL_2(\Z/N\Z)$, we define the modular curve $X_H$ to be the coarse space of the stack $\mathcal{M}_H$, as defined in Deligne--Rapoport \cite{DR}.
-The curve $X_H$ is a scheme over $\text{Spec }\Z[1/N]$ and parametrises generalized elliptic curves with $H$-level structure.
-\abedit{In particular, its $k$-rational points roughly classify elliptic curves over $k$ whose mod $N$ image is contained in $H$}; see, for example, \cite[$\S2.3$]{RSZB2022} for details.
+The curve $X_H$ is a scheme over $\text{Spec }\Z[1/N]$ and parametrizes generalized elliptic curves with $H$-level structure.
+In particular, its $k$-rational points roughly classify elliptic curves over $k$ whose mod $N$ image is contained in $H$; see, for example, \cite[$\S2.3$]{RSZB2022} for details.
 If we take
@@
 then $X_{B_1(N)}=X_1(N)$, the modular curve whose noncuspidal points parametrize elliptic curves with a distinguished point of order $N$.
-There is an analytic isomorphism between $X_1(N)(\mathbb{C})$ and the Riemann surface constructed as a quotient of the extended upper-half plane by the congruence subgroup
+There is an analytic isomorphism between $X_1(N)(\mathbf{C})$ and the Riemann surface constructed as a quotient of the extended upper-half plane by the congruence subgroup
 \[
@@
 
-\abedit{We may also define a modular curve associated to an open subgroup $G$ of $\GL_2(\widehat{\Z})$.
-For any $N \in \Z^+$, let $\pi:\GL_2(\widehat{\Z}) \rightarrow \GL_2(\Z/N\Z)$ be the natural projection map, and define $G(N) \coloneqq \pi(G)$.
-We say $G$ has \textbf{level} $N$ if $G=\pi^{-1}(G(N))$ and $N$ is minimal with respect to this property.} If $\det(G)=\widehat{\Z}^{\times}$, we define the modular curve $X_G \coloneqq X_{G(N)}$.
+We may also define a modular curve associated to an open subgroup $G$ of $\GL_2(\widehat{\Z})$.
+For any $N \in \Z^+$, let $\pi\colon\GL_2(\widehat{\Z}) \rightarrow \GL_2(\Z/N\Z)$ be the natural projection map, and define $G(N) \coloneqq \pi(G)$.
+We say $G$ has \textbf{level} $N$ if $G=\pi^{-1}(G(N))$ and $N$ is minimal with respect to this property.
+If $\det(G)=\widehat{\Z}^{\times}$, we define the modular curve $X_G \coloneqq X_{G(N)}$ where $N$ is the level of $G$.
 If $G=\GL_2(\widehat{\Z})$, then we identify $X_G \cong \PP^1$ with the $j$-line.
 
-\subsection{Closed Points on Modular Curves}\abbey{I updated the first 2 paragraphs of this section.} To discuss isolated points on modular curves, we must consider closed points on $X_1(N)$, viewed always as a scheme over $\Q$.
+\subsection{Closed Points on Modular Curves} \label{sec:ClosedPts} To discuss isolated points on modular curves, we must consider closed points on $X_1(N)$, viewed always as a scheme over $\Q$.
 Let $k$ be a field with an embedding of $k$ into $\overline \Q$.
 Given an elliptic curve $E/k$ with $P \in E(k)$ of order $N$, the pair $(E,P)$ induces a $k$-valued point on $X_1(N)$ via the moduli interpretation described above.
-We denote this $k$-valued point by $(E,P)_k$, and by definition it corresponds to a morphism of $\Q$-schemes $f:\text{Spec } k \rightarrow X_1(N)$.
-The map $f$ sends the unique point of $\text{Spec } k$ to a point $x \in X$, and we call $x$ the \textbf{closed point} associated to $(E,P)$.\footnote{Note $x$ is indeed closed since $\Q(x)/\Q$ is finite; see, for example, \cite[Exercise 5.9, p.76] {Liu2002}.} We define the \textbf{degree} of $x$ to be the degree of the residue field $\Q(x)$ over $\Q$.
+We denote this $k$-valued point by $(E,P)_k$, and by definition it corresponds to a morphism of $\Q$-schemes $f\colon\text{Spec } k \rightarrow X_1(N)$.
+The map $f$ sends the unique point of $\text{Spec } k$ to a point $x \in X_1(N)$, and we call $x$ the \textbf{closed point} associated to $(E,P)$.\footnote{Note $x$ is indeed closed since $\Q(x)/\Q$ is finite; see, for example, \cite[Exercise~5.9, p.~76]{Liu2002}.} We define the \textbf{degree} of $x$ to be the degree of the residue field $\Q(x)$ over $\Q$.
 Since there are many scheme-valued points which induce the same closed point, it is sometimes preferable to consider Galois orbits of points in $X_1(N)(\overline{\Q})$, which are in bijection with the set of closed points.
 Thus one could alternatively define the closed point associated to $(E,P)$ as the $\Gal_\Q$-orbit of $(E,P)_{\overline{\Q}}$.
-\sachi{I think the difference between $k$-valued points and $k$-rational points is confusing, since the names are so similar.
-It would be nice to explicitly point out what is meant by $k$-rationality somewhere (in constrast to $k$-valued).} \abbey{They are all the same thing for a scheme over a field.
-I used the term $k$-valued b/c it's the term used in Qing Liu's book \cite{Liu2002}, but it matches what Poonen calls a $k$-rational point or a $k$-point of a scheme over a field in \emph{Rational points on varieties}, for example.
-The definition is actually already above --- it's a morphism of $\Q$-schemes $f:\text{Spec} k \rightarrow X_1(N)$.
-If you say $k$-rational point, I imagine most people just think of points with coordinates in $k$, rather than this scheme-theoretic definition.
-These two notions coincide, but it's something to prove, for example, as in Prop.
-2.18 in Section 3.2.3 of \cite{Liu2002}.}
 
 \begin{remark} Given a $k$-valued point $(E,P)_k$, we note that the degree of the associated closed point $x$ may be strictly less than the degree of $k$.
-However, there always exists $E'/\Q(x)$ with $j(E')=j(E)$ and $P' \in E'(\Q(x))$, where the point $P' \in E'$ maps to $P \in E$ under a $\overline \Q$-isomorphism sending $E$ to $E'$.
-See \cite[p.
-274, Proposition VI.3.2]{DR}.
+However, there always exists $E'/\Q(x)$ with $j(E')=j(E)$ and $P' \in E'(\Q(x))$, where the point $P' \in E'$ maps to $P \in E$ under a $\overline \Q$-isomorphism sending $E'$ to $E$.
+See \cite[p.~274, Proposition~VI.3.2]{DR}.
 The pair $(E',P')$ gives a $\Q(x)$-valued point, and it is the unique $\Q(x)$-valued point such that $(E,P)_{k}=(E',P')_{k}.$
@@
 
-Let $E/k$ be an elliptic curve and $P \in E(k)$ a point of order $N$.
-Note that for any $\xi \in \Aut(E)$, the pair $(E,\xi P)$ induces the same closed point $x \in X_1(N)$, since $\xi$ provides the necessary isomorphism.
+Let $E/k$ be an elliptic curve and let $P \in E(k)$ a point of order $N$.
+For any $\xi \in \Aut(E)$, the pair $(E,\xi P)$ induces the same closed point $x \in X_1(N)$, since $\xi$ provides the necessary isomorphism.
 This can be used to obtain a more explicit description of the residue field $\Q(x)$.
@@
 
-\abbey{Add Shimura definition of $\mathfrak{h}$.}
-
-\begin{remark}\label{ResidueFieldRmk} In particular, if $E/\Q(j(E))$ does not have complex multiplication and $P=(x_0,y_0)$, then one can take $\Q(x)\cong\Q(j(E),x_0)$. See \cite[p. 107]{shimura}.
+ \begin{remark}\label{ResidueFieldRmk}At times, it can be useful to work with an explicit model-independent formulation of a Weber function.
+For example, if $E:y^2=4x^3-c_2x-c_3$ and $j(E)\neq 0,1728$, we can define
+\[
+\mathfrak{h}((x,y))=\frac{c_2c_3}{\Delta}x,
+\]
+where $\Delta=c_2^3-27c_3^2$. One can verify:
+\begin{enumerate}
+    \item We have $\mathfrak{h}(P)=\mathfrak{h}(P')$ if and only if $P=\xi P'$ for some $\xi \in \Aut(E)$.
+    \item If $\eta \colon E \rightarrow E'$ is an isomorphism, then $\mathfrak{h}_E=\mathfrak{h}_{E'}\circ \eta$.
+\end{enumerate}
+See \cite[p. 107]{shimura}. In particular, if $E/\Q(j(E))$ does not have complex multiplication and $P=(x_0,y_0)$, then one can take $\Q(x)\cong\Q(j(E),x_0)$. 
 \end{remark}
-\begin{example}
-Let $E_1:y^2+xy+y=x^3-x^2-3x+3$ and $P_1=(-1,2)$ a point of order 7.
+
+\begin{example}[Closed points versus geometric points I]
+Let $E_1\colon y^2+xy+y=x^3-x^2-3x+3$ and $P_1=(-1,-2)$ a point of order 7.
 Then $(E_1,P_1)$ gives a $\Q$-valued point on $X_1(7)/\Q$ and also a closed point $x\in X_1(7)$ of degree 1.
-On the other hand, let $E_2:y^2=x^3-43x-166$ and $P_2=(5,i\sqrt{256})$ a point of order 7.
-Then $(E_2,P_2)$ gives a $\Q(i)$-valued point on $X_1(7)/\Q$ and also a closed point $x\in X_1(7)$ of degree 1 by \abedit{Remark \ref{ResidueFieldRmk}} \sachi{(and therefore a $\Q$-rational point)} \abbey{We want to think of it as \emph{inducing} a $\Q$-rational point---as explained in the paragraph below, or in Remark 7 above---rather than $(E_2,P_2)$ itself being $\Q$-rational.
-The non-cuspidal $\Q$-rational points of $X_1(7)(\Q)$ correspond to $\Q$-isomorphism classes of elliptic curves $E/\Q$ with a point $P\in E(\Q)$ of order 7, where this comes from the curve being a fine moduli space.
-So the representative $E_2,P_2$ does not show up here, since $P_2$ is not in $\Q$.}.
+On the other hand, let $E_2\colon y^2=x^3-43x-166$ and $P_2=(5,\sqrt{-256})$ a point of order 7.
+Then $(E_2,P_2)$ gives a $\Q(\sqrt{-256})$-valued point on $X_1(7)/\Q$ and also a closed point $x\in X_1(7)$ of degree 1 by Remark \ref{ResidueFieldRmk}.
 In fact, both $(E_1,P_1)$ and $(E_2,P_2)$ induce the same geometric point on $X_1(7)$ since $(E_1,P_1)_{\overline{\Q}}=(E_2,P_2)_{\overline{\Q}}$.
 
-One could alternatively compute the Kubert--Tate normal form associated to $E_2/\Q(i)$, with $P_2=(5,i\sqrt{256})$:
-\[E_3: y^2-xy-4y=x^3-4x^2,\, \, P_3=(0,0).
-\]
-We can check that $(E_1,P_1)_{\Q}=(E_3,P_3)_{\Q}$ and $(E_2,P_2)_{\Q(i)} =(E_3,P_3)_{\Q(i)}$.
+One could alternatively compute the Kubert--Tate normal form associated to $E_2/\Q(\sqrt{-256})$, with $P_2=(5,\sqrt{-256})$:
+\[
+    E_3\colon y^2-xy-4y=x^3-4x^2,\, \, P_3=(0,0).
+\]
+We can check that $(E_1,P_1)_{\Q}=(E_3,P_3)_{\Q}$ and $(E_2,P_2)_{{\Q(\sqrt{-256})}} =(E_3,P_3)_{{\Q(\sqrt{-256})}}$.
 Thus it is fair to say that $(E_2,P_2)$ induces a $\Q$-valued point, even though it is not itself a $\Q$-valued point.
@@
 
-\begin{example}
+\begin{example}[Closed points versus geometric points II]
 The distinction between closed points and geometric points can be seen when counting the number of points of a particular degree.
@@
 For each $a \in (\Z/21\Z)^{\times}$, we consider the geometric point on $X_1(21)$ associated to $(E,aP)$.
-Since $(E,aP)_{\overline{\Q}}=(E,-aP)_{\overline{\Q}}$, we find there are six distinct geometric points corresponding to $(E,aP)$ for $a \in (\Z/21\Z)^{\times}$.
+Since $(E,aP)_{\overline{\Q}}=(E,-aP)_{\overline{\Q}}$, we find that there are six distinct geometric points corresponding to $(E,aP)$ for $a \in (\Z/21\Z)^{\times}$.
 However, these six $\overline{\Q}$-points lie in two Galois orbits, each of size 3.
-Thus we would say there are two closed points of degree 3, and the cardinality of the Galois orbit equals the degree.
+Thus there are two closed points of degree 3, and the cardinality of the Galois orbit equals the degree.
 \end{example}
@@
 Let $N$ be the level of $G$.
-For any subgroup $H$ of $\GL_2(\Z /N\Z)$, we have $\Q(X_H)=\Q(X(N))^H$.
-Now by Galois theory it follows that $\Q(X_G) \supseteq \Q(X_{G'})$, so we conclude that there exists a $\Q$-rational morphism $f:X_G \rightarrow X_{G'}$.
+For any subgroup $H$ of $\GL_2(\Z/N\Z)$, we have $\Q(X_H)=\Q(X(N))^H$.
+Now by Galois theory it follows that $\Q(X_G) \supseteq \Q(X_{G'})$, so we conclude that there exists a $\Q$-rational morphism $f\colon X_G \rightarrow X_{G'}$.
 
 To determine its degree, let $\Gamma$ and $\Gamma'$ be the intersection with $\SL_2(\Z)$ of the inverse image of $G$ and $G'$ in $\GL_2(\Z)$.
-Over $\bC$, the morphism $f$ is the quotient map $\Gamma \backslash \mathcal{H} \rightarrow \Gamma' \backslash \mathcal{H}$.
+Over $\bC$, the morphism $f$ is the quotient map $\Gamma \backslash \mathcal{H}^* \rightarrow \Gamma' \backslash \mathcal{H}^*$.
+Here, $\mathcal{H}^*$ is the extended complex upper half plane.
 Since the kernel of the action of $\SL_2(\Z)$ on $\mathcal H$ is $\pm I$, the degree of $f$ is as claimed.
 \end{proof}
+
 Let $a$ and $b$ be positive integers.
 Taking $G=\pi^{-1}(B_1(ab))$ and $G'=\pi^{-1}(B_1(a))$ gives the following corollary, which under the moduli interpretation corresponds to sending $(E,P)$ to $(E,bP)$.
-\begin{corollary}
+
+\begin{corollary}\label{Cor:DegreeFormula}
                 For positive integers $a$ and $b$, the natural $\Q$-rational map $f\colon X_1(ab) \rightarrow X_1(a)$ has
@@
                 \]
-                where $c_{f}=1/2$ if $a \leq 2$ and $ab>2$ and $c_{f}=1$ otherwise. 
+                where $c_{f}=\frac{1}{2}$ if $a \leq 2$ and $ab>2$ and $c_{f}=1$ otherwise.
 \end{corollary}
 
-\subsection{Galois Representations}\abbey{Recently added section.} If $E$ is an elliptic curve defined over a number field $k$, then $\Gal_k$ acts naturally on the points of $E$.
+\subsection{Galois Representations} If $E$ is an elliptic curve defined over a number field $k$, then $\Gal_k$ acts naturally on the $\overline{k}$-points of $E$.
 On torsion points, this action is described by the \textbf{adelic Galois representation} associated to $E/k$,
 \[
-\rho_{E}: \Gal_k \rightarrow \Aut(E(\overline{k})_{\text{tors}}) \cong \GL_2(\widehat{\Z}). 
+\rho_{E}\colon \Gal_k \rightarrow \Aut(E(\overline{k})_{\text{tors}}) \cong \GL_2(\widehat{\Z}).
 \]
 From this we can obtain two other Galois representations.
-On the one hand, fixing a positive integer $m$, we can choose to record the action of $\Gal_k$ on points \abedit{whose order is divisible only by those primes dividing $m$}.
+On the one hand, fixing a positive integer $m$, we can choose to record the action of $\Gal_k$ on points whose order is divisible only by those primes dividing $m$.
 This is the \textbf{$m$-adic Galois representation} associated to $E$:
@@
 In particular, if $m=\ell$ is a prime number, we recover the standard $\ell$-adic representation associated to $E$.
-Alternatively, we may wish to record Galois action only on points of order dividing $m$; we use $E[m]$ to denote the finite subgroup of such points.
+Alternatively, we may wish to record the Galois action only on points of order dividing $m$.
+We use $E[m]$ to denote the finite subgroup of such points.
 This gives the \textbf{mod $m$ Galois representation} associated to $E$,
@@
 
-If $E/k$ is a non-CM elliptic curve, we define the \textbf{level} of $\rho_E$ to be the smallest positive integer $N$ such that $\im \rho_E=\pi^{-1}(\im \rho_{E,N})$, where $\pi:\GL_2(\widehat{\Z}) \rightarrow \GL_2(\Z/N\Z)$ is the natural reduction map; that such an $N$ exists is a consequence of Serre's Open Image Theorem \cite{serre72}.
+If $E/k$ is a non-CM elliptic curve, we define the \textbf{level} of $\rho_E$ to be the smallest positive integer $N$ such that $\im \rho_E=\pi^{-1}(\im \rho_{E,N})$, where $\pi\colon\GL_2(\widehat{\Z}) \rightarrow \GL_2(\Z/N\Z)$ is the natural reduction map; that such an $N$ exists is a consequence of Serre's Open Image Theorem \cite{serre72}.
 The level of $\rho_{E,m^{\infty}}$ may be defined in an analogous way.
@@
 Though $\rho_E$ is never surjective when $k=\Q$, this can occur for elliptic curves defined over number fields of higher degree \cite[Theorem 1.2]{Greicius2010}.
+
+\section{Overview of the Main Algorithm}
+\label{sec:mainalg}
+The following algorithm is the main procedure for determining whether a given non-CM $j$-invariant in $\Q$ is the image of an isolated point on $X_1(N)$ under the map to the $j$-line, based on results in \cite{BELOV,ZywinaAlgorithm}.
+We note that for any CM $j$-invariant $j$, there exists infinitely many $N\in\Z^+$ for which there is a sporadic point $x\in X_1(N)$ with $j(x)=j$ by \cite[Theorem 7.1]{BELOV}, so it is not necessary to consider them in this algorithm.
+The outline below gives an overview of the structure, while the algorithms to perform particular steps are described in detail in Sections \ref{sec:madicrep}, \ref{sec:primitivedeg}, and \ref{sec:genus0images}.
+We will prove a theorem on the validity of Algorithm \ref{alg:mainalgorithm} in Section \ref{sec:validity}.
+
+\setcounter{algocf}{0}
+\begin{algorithm}[h!]
+\caption{Main Algorithm}\label{alg:mainalgorithm}
+\KwIn{A non-CM $j$-invariant $j \in \Q$.}
+\KwOut{A finite list $\{(a_1, d_1), \ldots, (a_k, d_k)\}$ of (level, degree) pairs such that $j$ is isolated if and only if there exists an isolated point $x \in X_1(a_i)$ of degree $d_i$ with $j(x) = j$ for some $(a_i, d_i)$ in the list.}
+Construct an elliptic curve $E/\Q$ with $j(E)=j$.\\
+Compute the adelic image $G$ of $E/\Q$ as a subgroup of $\GL_2(\hat{\Z})$ using Zywina's algorithm \cite{ZywinaAlgorithm}.
+Represent the output as the level $N$ and the subgroup $G(N)$ of $\GL_2(\Z/N\Z)$.\\
+Apply Algorithm \ref{alg:reduce_level} to $G(N)$ to obtain the level $m_0$ of the $m$-adic Galois representation associated to $E$, where $m$ is the product of 2, 3, and all non-surjective primes.\\
+Apply Algorithm \ref{alg:compute_prim_degree} to $\im \rho_{E,m_0}$.
+For each positive divisor $n$ of $m_0$ and each closed point $x \in X_1(n)$ with $j(x)=j$, this gives the primitive point associated to $x$, say $x' \in X_1(a)$ of degree $d$.
+Return a multiset $D$ with entries $\langle n, (a, d) \rangle$.\\
+Construct the multiset $D' \subseteq D$ containing only those elements $\langle n, (a, d)\rangle$ for which $d\leq \text{genus}(X_1(a))$.\\
+Create the multiset $M$ consisting of all pairs $(a,d)$ with $\langle n, (a,d) \rangle$ appearing in $D'$.
+We include $(a,d) $ with multiplicity $\mu$ if and only if $X_1(a)$ has $\mu$ distinct closed points of degree $d$ associated to $E$.\\
+Remove from $M$ any pair $(a_i,d_i)$ where the mod $a_i$ Galois representation of $E/\Q$ corresponds to a modular curve of genus 0.\\
+\Return{$M$}
+
+\end{algorithm}
+
+In particular, note that if Algorithm \ref{alg:mainalgorithm} outputs $\{\}$, then $j$ is not the image of any isolated point on $X_1(N)$, even as $N$ ranges over all positive integers.
+See Corollary \ref{cor:P1_isolated}.
+
+\begin{example}
+If $j=-9317$, then Algorithm \ref{alg:mainalgorithm} returns $ \{(37,6) ^3\}$.
+This means that any isolated point $x\in X_1(N)$ with $j(x)=j$ and $N \in \Z^+$ maps down under the natural projection map to one of the 3 closed points of degree 6 on $X_1(37)$.
+In fact, these points are all sporadic by \cite[Proposition 2]{frey}, since $6 < \frac{1}{2} \gon_{\Q}(X_1(37)) = 18$.
+Here, the gonality computation is a result of \cite{DerickxVanHoeij2014}.
+Thus $j$ is a sporadic --- and hence isolated --- $j$-invariant.
+\end{example}
+
+\begin{example}
+If $j=-121$, then Algorithm \ref{alg:mainalgorithm} returns $\{\}$. This means that there are no isolated points on $X_1(N)$ associated to this $j$-invariant.
+\end{example}
+
+\begin{example}
+If $j=-882216989/131072$, then Algorithm \ref{alg:mainalgorithm} returns  $\{( 17,4) ^2\}$.
+This means that $j$ is associated to an isolated point on a modular curve of the form $X_1(N)$ if and only if there exists a degree 4 isolated point $x \in X_1(17)$ with $j(x)=j$.
+In Section \ref{sec:remainingfilters}, we will see that no such isolated point exists, from which we can conclude that $j$ is not an isolated $j$-invariant.
+\end{example}
 
@@
 
-\section{Genus 0 adelic images do not produce isolated points}
-
-\abbey{I moved this from the end.}
-\label{sec:genus0}
-Let $E/\Q$ be an elliptic curve and $G\in \GL_2(\hat \Z)$ its adelic image.
-By $G(N)$ denote the image of its mod $N$ representation.
-Denote by $B_1(N)$ the subgroup of $\GL_2(\Z/N\Z)$ consisting of the upper triangular matrices with a $1$ in the upper left entry.
-Note that $X_{B_1(N)}=X_1(N)$.
-We say that a congruence group $\Gamma$ is of genus $g$ if $X_\Gamma$ is of genus $g$.
-We say that a point $P$ corresponds to an elliptic curve $E$ if $j(P)=j(E)$.
-
-\begin{lemma} \label{lem:map to Symd}
-Let $f\colon X \to Y$ be a finite morphism of curves of degree $d$. Then $f$ induces a non-constant morphism $f^*\colon Y \to X^{(d)}$.
-\end{lemma}
-\begin{proof}
-    See~\cite[Theorem~3.13]{MilneJV}. The morphism is non-constant since fibers above different points are mapped to different points.
-\end{proof}
-
-Note that a rational map from $\PP^1$ to a smooth variety of degree $1$ extends uniquely to a morphism (by the valuative criterion of properness) and is an isomorphism onto its image since a genus $0$ curve cannot have singularities.
-The symmetric powers of a smooth projective curve are smooth~\cite[Proposition~3.2]{MilneJV}.
-
-\begin{lemma} \label{lem:iso1}
-Let $X$ be a curve with a copy of $\bP^1$ inside $X^{(d)}$ and let $x\in X^{(d)}(\Q)$ be irreducible and lying on the image of $\PP^1$ inside of $X^{(d)}$. Then $x$ is not $\PP^1$-isolated.
-\end{lemma}
-\begin{proof}
-The restriction of the map $\Phi_d:X^{(d)}\rightarrow \Jac (X)$ to the image of $\PP^1$ inside $X^{(d)}$ factors through $\Jac(\PP^1)=\{0 \}$ by the Albanese property of the Jacobian, so it contracts the $\PP^1$ to a point on $\Jac(X)$.\footnote{Or because abelian varieties contain no positive dimensional rational varieties~\cite[Corollary~3.9]{MilneAV}.} Hence $\Phi_d(y) = \Phi_d(x)$ for any $y$ lying on this image of $\PP^1$.
-\end{proof}
-
-\begin{lemma} \label{lem:iso2}
-Let $f: X\rightarrow Y$ be a finite morphism of curves and $x$ a point on $X$, and assume  $\deg x = \deg f(x)$. If $x$ is not $\PP^1$-isolated, then neither is $f(x)$.
-\end{lemma}
-\begin{proof}
-If $x$ is not $\bP^1$-isolated (i.e., $x$ is $\bP^1$-parametrized), then 
-by Lemmas \ref{lem:iso1} and \ref{lem:iso2} $x$ lies on a $\PP^1$ inside of $X^{(d)}$ and $f(x)$ lies on the image of this $\PP^1$ (which is again a $\PP^1$ by \Cref{lem:map to Symd} or because the induced morphism on the $d$-th symmetric power is again finite) inside of $Y^{(d)}$.
-Now the conclusion follows by \Cref{lem:iso1}.
-\end{proof}
-
-\begin{proposition} \label{Genus0Prop}
-Let $E/\Q$ be an elliptic curve with mod $N$ image $G(N)$ of genus $0$ and $N$ a positive integer. Then there does not exist a point corresponding to $E$ on $X_1(N)$ that is $\PP^1$-isolated.
+\section{\texorpdfstring{Computing the level of the $m$-adic representation}{Computing the level of the m-adic representation}}
+\label{sec:madicrep}
+
+Given a non-CM elliptic curve $E/\Q$, we define the set
+\[
+S_E\coloneqq \{2,3\} \cup \{ \ell: \rho_{E,\ell^{\infty}}(\Gal_{\Q}) \neq \GL_2(\Z_{\ell}) \}.
+\] Here, we include 2 and 3 in $S_E$ to allow us to apply results of \cite{BELOV} in later steps of the algorithm; see Section \ref{ssec:finiteness of PE} for details.
+For $m \coloneqq \prod_{\ell \in S_E} \ell$, we want an algorithm to obtain the level of the $m$-adic Galois representation associated to $E$ from the image of the adelic representation of $E$, where the latter can be computed by Zywina's algorithm \cite{ZywinaAlgorithm}.
+If $\im \rho_E$ has level $N$, define $n=\prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$ and let $m_0$ denote the level of $\rho_{E,m^{\infty}}$.
+We will show in Proposition \ref{Prop:Level} that $m_0| n$ and $n | N$.
+Each of these divisibilities can be proper, as the following examples illustrates.
+
+\begin{example}
+ If $E=75072.bc2$, we see that $\rho_E$ has level $N=4682=2^2 \cdot 3 \cdot 17 \cdot 23$.
+Since 2 is the only non-surjective prime, $n=2^2\cdot 3$.
+However, the level of the $m$-adic Galois representation associated to $E$ is 2.
+On the other hand, it can also happen that $N=m_0$.
+For example, if $E=54.b2$, we see that $\rho_E$ has level 72, and this is also the level of the $m$-adic Galois representation associated to $E$.
+\end{example}
+
+\begin{algorithm}[H]
+  \KwIn{$G(N)\leq \GL_2(\Z/N\Z)$ where $\im\rho_E=G$ and $N$ is the level.}
+  \KwOut{$m_0 \in \Z^+$, the level of $\rho_{E,m^{\infty}}$ for $m= \prod_{\ell \in S_E} \ell$.}
+  \caption{Compute Reduced level}%
+  \label{alg:reduce_level}
+  Let $n = \prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$.\\
+Compute the smallest $m_0$ dividing $n$ such that \[\#G(n)=\#G(m_0) \cdot \#\ker(\GL_2(\Z/n\Z) \rightarrow \GL_2(\Z/m_0\Z)).\]\\
+  \Return{$m_0$}
+\end{algorithm}
+
+The validity of this algorithm is a consequence of the following proposition.
+  \begin{proposition}\label{Prop:Level}
+  Let $E/\Q$ be a non-CM elliptic curve, and let $\im \rho_E=G \leq \GL_2(\widehat{\Z})$ be a subgroup of level $N$.
+Define $n \coloneqq \prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$ and $m\coloneqq \prod_{\ell \in S_E} \ell$.
+If $m_0$ is the smallest positive integer dividing $n$ such that \[\#G(n)=\#G(m_0) \cdot \#\ker(\GL_2(\Z/n\Z) \rightarrow \GL_2(\Z/m_0\Z)),\] then $m_0$ is the level of the $m$-adic Galois representation associated to $E$.
   \end{proposition}
   \begin{proof}
-Let $x$ be a $\Q$-rational point on $X_{G(N)}$ corresponding to $E$.
-
-%Let $B$ be the group generated by $G(n)$ and a conjugate of $B_1(n)$ in $\GL_2(\Z/n\Z)$; this is again a group of genus $0$ on which the image $P'$ of $P$ under the map $X_{G(n)}\rightarro X_B$ is $\Q$-rational.
-The inclusion of subgroups $B\subset B_1(n)$ induces a map $X_1(n)\rightarrow  X_B$.
-
-Let $(E,P)=\abedit{y} \in X_1(N)$ correspond to $E$.
-Let $B \colonequals B_1(N) \cap c(G(N))$ in $c(G(N))$, where $c$ denotes the appropriate choice of conjugation in $\GL_2(\Z/N\Z)$ such that $P$ is an element of the basis inducing the mod $N$ representation.
-Let $d \colonequals [\pm c(G(N)) : \pm B]$.
-%\abbey{Seems like we'd want to take the conjugate of $G(N)$ such that $P$ is the first basis element, but keep $B_1(N)$ as is.
-Also, we want the index of $\pm B$ in $\pm G(N)$.} \filip{Yes, fixed.}
-
-Let $f\colon X_{B}\rightarrow X_{G(N)} \simeq \PP^1$ be the corresponding degree $d$ map of modular curves.
-%\timo{One has $\deg(x) = \deg(f(x))$ [yes, but this is not what we need]: $B$ is the exact stabilizer of $x$ in $G(N)$, so the fiber above $f(x)$ is completely split, working with quotients $f\colon X/H \to X/G$ by finite groups $H \leq G$ such that $H = G_x$ because $f(x) = Gx = G/Hx$ has $\#G/H = \deg(f)$ preimages.}
-\Cref{lem:map to Symd} yields a non-constant morphism $f^*\colon X_{G(N)} \to X_{B}^{(d)}$ such that $f^*(x)$ lies on a $\PP^1 \simeq X_{G(N)}$.
-Hence $x \in X_B$ is not $\PP^1$-isolated by \Cref{lem:iso1} [irreducible].
-Consider the morphism $g\colon X_B \to X_1(N)$ corresponding to $B \leq B_1(N)$.
-It is totally ramified above $g(x)$ because $B_1(N)$ stabilizes $g(x) = y$ and so does $B$, so the decomposition group of $x$ equals its inertia subgroup.
-Hence it satisfies $\deg(g(x)) = \deg(x)$, so $g(x)$ is not $\PP^1$-isolated by \Cref{lem:iso2}.
-%\abbey{How do we know $f^{-1}(x)$ is irreducible, in order to apply \Cref{lem:iso1}?} \filip{Well because the mod $N$ image is equal to $G(N)$ (and not a subgroup).
-So to get the image to reduce to $B$, we need to go to an extension of the index of $B$ in $G(N)$.
-This is a more general result: if $G\geq H$ are congruence groups of level $N$ and $f:X_H\rightarrow X_G$ and $x$ corresponds to an elliptic curve whose mod $N$ image is $G$ over $\Q$, then the degree of $f^{-1}(x)$ is $\deg f$.} \abbey{Oh, right -- that makes sense.
-Thanks.}
+  First we will show that $\im \rho_{E,m^{\infty}}=\pi_1^{-1}(G(n))$, where $\pi_1\colon \prod_{\ell \in S_E} \GL_2(\Z_{\ell}) \rightarrow \GL_2(\Z/n\Z)$ is the natural reduction map.
+It suffices to show that $\ker \pi_1 \subseteq \im \rho_{E,m^{\infty}}$.
+We write $N=n\cdot n'$ with $\gcd(n,n')=1$, and so we may identify $G(N)$ as a subgroup of $\GL_2(\Z/n\Z) \times \GL_2(\Z/n'\Z)$.
+Under this identification, let $H$  be the intersection of $G(N)$ with the subgroup $\{I\} \times \GL_2(\Z/n'\Z)$.
+Then since $G$ has level $N$,
+  \[
+  \pi^{-1}(H) \subseteq \im \rho_E,
+  \]
+  where $\pi\colon \GL_2(\widehat{\Z}) \rightarrow \GL_2(\Z/N\Z)$ is the natural reduction map.
+The image of this subset relation under the natural projection map  $\GL_2(\widehat{\Z}) \cong \prod_{\ell} \GL_2(\Z_{\ell}) \rightarrow  \prod_{\ell \in S_E} \GL_2(\Z_{\ell}) $ gives
+  \[
+  \ker(\pi_1) \subseteq \im \rho_{E,m^{\infty}},
+  \]
+  as desired.
+
+Let $\pi_2\colon \GL_2(\Z/n\Z) \rightarrow \GL_2(\Z/m_0\Z)$ be the natural reduction map.
+The assumption on $m_0$ implies that $\ker(\pi_2) \subseteq G(n)$, so it follows that $G(n) = \pi_2^{-1}(G(m_0))$.
+Thus if $\pi_3\colon \prod_{\ell \in S_E} \GL_2(\Z_{\ell}) \rightarrow \GL_2(\Z/m_0\Z)$ denotes the reduction map, we have
+  \begin{align*}
+  \pi_3^{-1}(G(m_0))&=\pi_1^{-1}(\pi_2^{-1}(G(m_0)))\\
+  &=\pi_1^{-1}(G(n))\\
+  &=\im \rho_{E,m^{\infty}}.
+  \end{align*}
+By construction $m_0$ is the smallest positive integer with this property.
   \end{proof}
@@
 \begin{corollary}
-Let $E/\Q$ be an elliptic curve with adelic image $G$ of genus $0$ and $n$ a positive integer. Then there does not exist an $n$ such that a point corresponding to $E$ on $X_1(n)$ is $\PP^1$-isolated.
+  Algorithm \ref{alg:reduce_level} is correct.
 \end{corollary}
-\begin{proof}
-Since $G$ is by assumption of genus $0$, it follows that so is $G(n)$. The result then follows from Proposition \ref{Genus0Prop}.
-\end{proof}
-
-\begin{comment}
-are of degree $d$. 
-Let $x'\in f^{-1}(x) \subseteq X_{B}$ be a point corresponding to $E$, and let $g\colon X_{B}\rightarrow X_1(n)$ be the map induced by the inclusion $B_1(N) \supseteq B$.
-The point $x'$ lies on a $\PP^1$ inside $X_B^{(d)}$ and hence $g(x')$ lies on a $\PP^1$ inside $X_1(n)^{(d)}$.
-Since no Abelian variety has $\PP^1$ as a subvariety, $\Phi_d$ contracts this $\PP^1$ inside $X_1(n)^{(d)}$ to a single point; it follows that $g(x')$ is not $\PP^1$-isolated.
-
-We have the following commutative diagram:
-
-$$
-\xymatrix{
-& X_B \ar[r]^{g} \ar[d]^{f} & X_1(N) \ar[d]^{q} \\
-&X_{G(N)} \ar[r]^{h} & X_{G'},
-}
-$$
-where $G'$ is defined to be the subgroup of $\GL_2(\Z/N\Z)$ generated by the union of $B_1(N)$ and $G(N)$, and the maps $q:X_1(N) \rightarrow X_{G'}$ and $h:X_G(N) \rightarrow X_{G'}$ are induced by the inclusion of the corresponding subgroups.
-The curve $X_{G'}$ is obviously of genus $0$ as it is covered by $X_{G(N)}$ of genus 0.
-
-As $g(x')$ is of degree $d$ and $q(g(x'))=h(x)\in X_{G'}(\Q)$, it follows $\deg q\geq d$. Alternatively, the same conclusion follows from $\deg q=[\pm G':\pm B_1(N)]\geq [\pm G':\pm B]=d. $
-
-\filip{Work in progress.
-If we prove $\deg q=d$, we are done.
-There's a more general question here, which I think is interesting: given a morphism $f:X\rightarrow \PP^1$ over $\Q$, with genus of $X$ at least 2, is it possible that there's infinitely many points of degree $<d$ in $f^{-1}(\PP^1(\Q))$.
-For $d=2$, the answer is no, and I think this might be the case in general.
-If anyone knows of a reference (or proof) of this, let me know; this would complete the proof of this lemma.
-} \abbey{Seems like you'd want some sort of strong form of Hilbert's irreducibility for this?
-I hadn't thought of this before...
-I believe there are infinitely many $c\in\Q$ such that $f-c$ is irreducible, which gives infinitely many degree $d$ points.
-So you want to know whether there are only finitely many $c$ such that $f-c$ is reducible?
-It looks like in some cases something like this is true (e.g., ``Finiteness results for Hilbert's irreducibility theorem" by M\"{u}ller), but not in general.}
-\filip{Yes, this would be some strong form of Hilbert's irreducibility.
-Is there a single example, of an $X$ of genus $\geq 2$ and $f$, where $f$ does not factor as $f=f_1\circ f_2$  with $\deg f_i>1$ (otherwise there can be many counterexamples), where this is not true?}
-\end{comment}
-
-%\filip{I remember what the issue was: we construct maps $X_B\rightarrow X_{G(n)}$ and $f:X_B\rightarrow X_1(n)$, and show that the point associated to $E$ on $X_B$ is not $\PP^1$-isolated.
-But I don't know how to show that this would imply that the image of this point under $f$ is not $\PP^1$-isolated.
-}\\
-%\filip{This is I think a more general group theoretic problem: we have a subgroup $A$ of $G(n)$ of index $d$, i.e.
-$[G(n):A]=d$, where $A\leq B_1(N)$ (or some conjugate of $B_1(n)$).
-Then we ask what is the index of $B_1(N)$ in the group generated by $G(n)$ and $B_1(n)$.
-If the answer is again necessarily $d$ (or we can always choose a conjugate of $B_1(n)$) such that the index is $d$, then we are good.}
 
 \section{Primitive Points on Modular Curves}
-\abbey{New section which answers Zev's question about the PrimitiveDegreesOfPoints algorithm in the affirmative.}
-At a high level, our algorithm to decide whether a given $E$ defined over $\Q$ is \abedit{gives rise to} an isolated point on $X_1(N)$ for some $N\geq 1$ proceeds in two steps.
-First, we reduce this to a finite computation by computing a level $n$ associated to the adelic image of $E$ so that we need only consider levels $m|n$.
+\label{sec:PrimitivePoints}
+
+Let $E$ be a non-CM elliptic curve.
+In this section, we will reduce the question of determining whether $j(E)$ is isolated to the analysis of an associated finite set of \emph{primitive points} on modular curves.
+The primitive points are characterized by the following theorem.
+
+\begin{theorem}\label{Thm:PrimPts}
+Let $E/\Q$ be a non-CM elliptic curve.
+There exists a finite set $\mathcal{P}=\mathcal{P}(E)$ of primitive points in $\cup_{n \in \Z^+} X_1(n)$ associated to $E$ which are characterized by the following properties:
+\begin{enumerate}
+\item For each $N\in \Z^+$, a point $x \in X_1(N)$ with $j(x)=j(E)$ corresponds to a unique element $x' \in \mathcal{P}$ under the natural projection map.
+Moreover, if $x' \in X_1(a)$, then $a \mid N$ and $\deg(x)=\deg(f)\cdot \deg(x')$, where $f\colon X_1(N) \rightarrow X_1(a)$ is the natural map.
+\item The rational number $j(E)$ is isolated if and only if there exists an isolated point in $\mathcal{P}$.
+\end{enumerate}
+Moreover, the set $\mathcal{P}$ is minimal with respect to conditions (i) and (ii).
+\end{theorem}
+
+\noindent Though in many ways this can be viewed as a refinement of results in \cite{BELOV}, the uniqueness of Theorem~\ref{Thm:PrimPts}\,(i) is new.
+In Section~\ref{sec:primitivedeg}, we give an algorithm for enumerating $\mathcal{P}(E)$ given a non-CM elliptic curve $E/\Q$.
+
+%\abbey{New section which answers Zev's question about the PrimitiveDegreesOfPoints algorithm in the affirmative.}
+%At a high level, our algorithm to decide whether a given $E/\Q$ gives rise to an isolated point on $X_1(N)$ for some $N\geq 1$ proceeds in two steps.
+First, we reduce this to a finite computation by computing a level $n$ associated to the adelic image of $E$, so that we need only consider levels $m|n$.
 Next, we try to reduce the  levels $m|n$ which we need to check: our filters for non-isolated points work better for points of lower level, in general.
 In this section, we introduce a notion of a primitive point on a modular curve.
-For a computable integer $m$ \abbey{We don't need any restrictions here -- $m$ doesn't have to correspond to the level.
+%For a computable integer $m$ \abbey{We don't need any restrictions here -- $m$ doesn't have to correspond to the level.
 The point is that any isolated point on $X_1(n)$ for $n \mid m$ will map down under the natural projection map to a primitive point which is isolated by \cite[Theorem 4.3]{BELOV}.
@@
 
-Let $m\geq 1$ be an integer.
-We now define the $m$-primitive points above a given elliptic curve $E$ defined over $\Q$.
-We begin by defining a directed graph $G=G(E,m)$ on the points of $X_1(n)$ \abedit{corresponding to $E$} for $n|m$.
-The vertices of $G(E,m)$ are tuples $(x,n,d)$ where:
+\subsection{\texorpdfstring{Construction of $\mathcal{P}(E)$ and minimality.}{Construction of P(E) and minimality}} Let $E/\Q$ be a non-CM elliptic curve, and let $m\geq 1$ be an integer.
+We begin by defining a directed graph $G(E,m)$ on the points of $X_1(n)$ corresponding to $E$ for all $n|m$. The vertices of $G(E,m)$ are tuples $(x,n,d)$ where:
 \begin{enumerate}
     \item $n|m$,
-    \item $x$ is a degree $d$ point on $X_1(n)$, and 
+    \item $x$ is a closed point on $X_1(n)$ of degree $d$, and
     \item $j(x)=j(E)$.
 \end{enumerate}
-We connect $(x,n,d)$ with an arrow to $(x',n',d')$ if: 
+We connect $(x,n,d)$ with a directed edge to $(x',n',d')$ if:
 \begin{enumerate}
@@
 \begin{definition}\label{def:mprimitive}
-    Let $E$ be an elliptic curve over $\Q$ and let $m\geq 1$ be an integer.
-The \textbf{$m$-primitive points} above $E$ are the sinks \abedit{of} $G(E,m)$.
+    Let $E$ be a non-CM elliptic curve over $\Q$ and let $m\geq 1$ be an integer.
+The \textbf{$m$-primitive points} of $E$ are the sinks of $G(E,m)$.
 The \textbf{$m$-primitive degrees} are the tuples $(n,d)$, where $(x,n,d)$ is $m$-primitive for $E$.
-\travis{multiplicity?}
+The union of all $m$-primitive points as $m$ ranges over all positive integers is the set of \textbf{primitive points} associated to $E$, denoted $\mathcal{P}(E)$.
+The union of all $m$-primitive degrees is the set of \textbf{primitive degrees} associated to $E$.
 \end{definition}
-In Section~\ref{sec:primitivedeg}, we give an algorithm for enumerating the sinks of $G(E,m)$. 
-\begin{remark}
-Suppose $n'' | n' | n | m$ and that $(x,n,d), (x',n',d'), (x'',n'',d'')$ are vertices.
-This graph is \textbf{transitive}, meaning that if there is an arrow from $(x,n,d)$ $(x',n',d')$ and from $(x',n',d')$ to $(x'',n'',d''),$ then
-there is also an arrow from $(x,n,d)$ to $(x'',n'',d'')$.
-\travis{Moreover, if there is an arrow from $(x,n,d)$ to $(x'',n'',d''),$ then we  claim there \abedit{is} an arrow from $(x,n,d)$ to $(x',n',d')$, \abedit{where $x'$ is the image of $x$ on $X_1(n')$ and $n'$ properly divides $n$}.
+
+By construction, for any $(x,n,d) \in \mathcal{P}(E)$, there does \emph{not} exist a proper divisor $n' \mid n$ with $d=\deg(f) \cdot \deg(f(x))$, where $f\colon X_1(n) \rightarrow X_1(n')$ is the natural map.
+Thus $\mathcal{P}(E)$ is the minimal set which can satisfy Theorem \ref{Thm:PrimPts}(i).
+
+\begin{remark}\label{Remark:Transitivity}
+Suppose $n'' | n' | n | m$ and that $(x,n,d), (x',n',d'), (x'',n'',d'')$ are vertices in $G(E,m)$.
+This graph is \textbf{transitive}, meaning that if there is an edge from $(x,n,d)$ to $(x',n',d')$ and from $(x',n',d')$ to $(x'',n'',d''),$ then
+there is also an edge from $(x,n,d)$ to $(x'',n'',d'')$.
+Moreover, if there is an edge from $(x,n,d)$ to $(x'',n'',d''),$ then we  claim there is an edge from $(x,n,d)$ to $(x',n',d')$, where $x'$ is the image of $x$ on $X_1(n')$ and $n'$ is any multiple of $n''$ which properly divides $n$.
 Intuitively, if the degree grows as much as possible from level $n''$ to level $n$ then it also grows as much as possible from level $n'$ to level $n$.
-Indeed: let $g_1:X_1(n) \rightarrow X_1(n')$ and $g_2:X_1(n') \rightarrow X_1(n'')$.
-Suppose for the sake of contradiction that  $\abedit{d}<\abedit{d'}\cdot\deg g_1$.
-But since $\abedit{d'} \leq \abedit{d''} \cdot \deg g_2$, this would imply $\abedit{d}<\abedit{d''} \cdot\deg g_1\cdot \deg g_2 $.
-This contradicts our assumption that there is an arrow from $(x,n,d)$ to $(x'',n'',d'')$.}
+Indeed, let $f_1\colon X_1(n) \rightarrow X_1(n')$ and $f_2\colon X_1(n') \rightarrow X_1(n'')$.
+Suppose for the sake of contradiction that  $d<d'\cdot\deg f_1$.
+Since $d' \leq d'' \cdot \deg f_2$, this would imply $d<d'' \cdot\deg f_1\cdot \deg f_2$.
+This contradicts our assumption that there is an edge from $(x,n,d)$ to $(x'',n'',d'')$.
 \end{remark}
 
-Now fix a vertex $(x,n,d)$ and consider its \textbf{descendants}, i.e.
-all vertices $(x',n',d')$ reachable by a path from $(x,n,d)$.
+\begin{definition}
+Let $E/\Q$ be a non-CM elliptic curve and $m \in \Z^+$.
+For a fixed vertex $(x,n,d)$ in $G(E,m)$, consider the directed graph induced by $(x,n,d)$ and its \textbf{descendants}, i.e., all vertices $(x',n',d')$ reachable by a path from $(x,n,d)$.
 This is a directed acyclic graph with a single source, $(x,n,d)$.
-\abedit{In this section, we will show that this graph has a single sink as well.}    \abbey{Is there standard notation for this?
-I use $D(v)$ below.}
-
-\begin{proposition}\label{Prop:single_sink}
-    Let $m\geq 1$ be an integer and let $E/\Q$ be an elliptic curve. Fix $v=(x,m,d)$ in $G(E,m)$, and consider the subgraph $D(v)$ of all its descendants. Then $D(v)$ has a single sink.
+\end{definition}
+
+In Corollary \ref{Cor:SingleSink} below, we will show the induced graph on the descendants of $(x,n,d)$ has a single sink as well; this is $x' \in \mathcal{P(E)}$ associated to $x$, as in Theorem \ref{Thm:PrimPts}\,(i).
+
+\subsection{\texorpdfstring{Finiteness of $\mathcal{P}(E)$}{Finiteness of P(E)}} \label{ssec:finiteness of PE} Let $E/\Q$ be a non-CM elliptic curve, and let $m$ be the product of 2, 3, and any primes $\ell$ such that the mod $\ell$ Galois representation of $E$ is non-surjective.
+It is a consequence of Serre's Open Image Theorem \cite{serre72} that $m \in \Z^+$, and there exists $m_0 \in \Z^+$ which is the level of the $m$-adic Galois representation of $E$.
+Suppose $v=(x,n,d) \in \mathcal{P}(E)$.
+Then $v$ is a sink of $G(E,N)$ for some $N \in \Z^+$.
+By \cite[Theorem~5.1]{BELOV}, we have
+\[
+\deg(x)=\deg(f) \cdot \deg(f(x)),
+\]
+where $f\colon X_1(n) \rightarrow X_1(\gcd(n,m_0))$ is the natural map. 
+In particular, we are using the fact that $\{2,3\} \subseteq S_E$ here.
+If $\gcd(n,m_0)$ properly divides $n$, this contradicts the fact that $v$ is a sink.
+Thus $\gcd(n,m_0)=n$ and $n \mid m_0$.
+In particular, $v$ is a sink of $G(E,m_0)$.
+It follows that $\mathcal{P}(E)$ is the set of sinks of $G(E,m_0)$, and $\mathcal{P}(E)$ is finite since $m_0$ is a fixed positive integer depending only on $E$.
+We note in particular that the level of any primitive point will divide $m_0$, which in turn divides the level of the adelic Galois representation associated to $E$ (see $\S \ref{sec:madicrep}$).
+We record this observation in the following proposition.
+
+\begin{proposition}\label{Rmk:Level}
+  Let $E/\Q$ be a non-CM elliptic curve, and let $\mathcal{P}(E)$ denote the set of associated primitive points in $\cup_{n \in \Z^+} X_1(n)$.
+If $x\in X_1(a)$ is in $\mathcal{P}(E)$, then $a$ divides $m_0$.
 \end{proposition}
 
-\subsection{Preliminary Results}
+\subsection{Preliminary Results} In this section, we establish two results concerning the residue fields of points on modular curves.
 
 \begin{lemma}\label{lem:LCM}
-Let $n_1,n_2 \in \Z^+$ and define $n \coloneqq \lcm(n_1,n_2)$.
-If $g=\gcd(n_1,n_2)$, we let $n_1=g\cdot n_1'$ and $n_2=g\cdot n_2'$.
-Suppose $E/F$ is an elliptic curve, and $P \in E(\overline{F})$ is a point of order $n$.
-If $n_2'P\in E(F)$ and $n_1'P \in E(F)$, then $P \in E(F)$.
+Let $n_1,n_2 \in \Z^+$ and $n = \lcm(n_1,n_2)$. For $g=\gcd(n_1,n_2)$, we define $n_1'\coloneqq n_1/g$ and $n_2'\coloneqq n_2/g$.
+Suppose $E/F$ is an elliptic curve, and $P \in E(\overline{F})$ is a point of order $n$. If $n_2'P\in E(F)$ and $n_1'P \in E(F)$, then $P \in E(F)$.
 \end{lemma}
@@
 \begin{lemma} \label{lem:compositum_res_fields}
-Let $n_1,n_2 \in \Z^+$ and define $n \coloneqq \lcm(n_1,n_2)$.
-If $g=\gcd(n_1,n_2)$, we let $n_1=g\cdot n_1'$ and $n_2=g\cdot n_2'$.
+Let $n_1,n_2 \in \Z^+$ and $n = \lcm(n_1,n_2)$.
+For $g=\gcd(n_1,n_2)$, we define $n_1'\coloneqq n_1/g$ and $n_2'\coloneqq n_2/g$.
 Let $x=[E,P] \in X_1(n)$ for an elliptic curve $E$ with $j(E) \neq 0,1728$, and define $x_1=[E,n_2'P] \in X_1(n_1)$ and $x_2=[E,n_1'P] \in X_1(n_2)$.
@@
 If $n_1=2$ or $n_2=2$, we may assume without loss of generality that $n_2=2$.
-Fix a Weierstrass equation for $E/\Q(j(E))$ so we may take $F_1=\Q(j(E),\mathfrak{h}(n_2'P))$, $F_2=\Q(j(E),\mathfrak{h}(n_1'P))$, and $F=\Q(j(E),\mathfrak{h}(P))$ by Lemma \ref{ResidueFieldLemma}.
-
-There exists $E'/F_1$ such that $\varphi:E \rightarrow E'$ is an isomorphism and $\varphi(n_2'P) \in E'(F_1)$; see, for example, \cite[p.
-274, Proposition VI.3.2]{DR}.
-Moreover, we have $F_2= \Q(j(E),\mathfrak{h}(n_1'P))=\Q(j(E),\mathfrak{h}(\varphi(n_1'P)))$ by \cite[p.
-107]{shimura}.
-In particular, the explicit formulas for $\mathfrak{h}$ as in \cite[p.
-107]{shimura} show that the $x$-coordinate of $\varphi(n_1'P)$ is rational over $F_1F_2$.
+Fix a Weierstrass equation for $E/\Q(j(E))$ so we may identify $F_1=\Q(j(E),\mathfrak{h}(n_2'P))$, $F_2=\Q(j(E),\mathfrak{h}(n_1'P))$, and $F=\Q(j(E),\mathfrak{h}(P))$ by Lemma \ref{ResidueFieldLemma}.
+
+There exists $E'/F_1$ such that $\varphi \colon E \rightarrow E'$ is an isomorphism and $\varphi(n_2'P) \in E'(F_1)$; see, for example, \cite[p.~274, Proposition~VI.3.2]{DR}. Moreover, we have 
+\[F_2= \Q(j(E),\mathfrak{h}(n_1'P))=\Q(j(E),\mathfrak{h}(\varphi(n_1'P)))\] by Remark \ref{ResidueFieldRmk}, and the same remark shows that the $x$-coordinate of $\varphi(n_1'P)$ is rational over $F_1F_2$.
 The $y$-coordinate of $\varphi(n_1'P)$ is defined over at worst a quadratic extension $L/F_1F_2$, and $L=F_1F_2$ if $n_2=2$.
@@
 Suppose that $F/F_1F_2$ is a quadratic extension.
+In particular, this means $n_1 \neq 2$ and $n_2 \neq 2$.
 Then consider $E'/F_1F_2$, and let $\{\varphi(P),Q\}$ be a basis for $E'[n]$.
@@
 Similarly, $M\pmod{n_2}$ gives $\rho_{E',n_2}(\sigma)$ with respect to the basis $\{n_1'\varphi(P),n_1'Q\}$.
-Since $n_2'(\varphi(P))$ is $F_1F_2$-rational and only the $x$-coordinate of $n_1'\varphi(P)$ is defined over $F_1F_2$, there is $\sigma\in \Gal_{F_1F_2}$ such that $\sigma(n'\varphi(P))=-n_1\varphi(P)$ and $\sigma(n_2'(\varphi(P))=n_2'\varphi(P)$.
+Since $n_2'(\varphi(P))$ is $F_1F_2$-rational and only the $x$-coordinate of $n_1'\varphi(P)$ is defined over $F_1F_2$, there is $\sigma\in \Gal_{F_1F_2}$ such that $\sigma({n_1'}\varphi(P))={-n_1'}\varphi(P)$ and $\sigma(n_2'(\varphi(P))=n_2'\varphi(P)$.
 Thus $\sigma(\varphi(P))=\alpha \varphi(P)+\beta Q$ where $\alpha \equiv 1 \pmod{n_1}$ and $\alpha \equiv -1 \pmod{n_2}$.
-If $g>2$, then $1 \equiv -1 \pmod{g}$, and we have a contradiction.
-\end{proof}
-
-\subsection{Proof of Proposition \ref{Prop:single_sink}}
-The proof of Proposition \ref{Prop:single_sink} will appear as a corollary to the following more general result.
+Therefore $g$ divides $2=(\alpha+1)-(\alpha-1)$, so $g\leq 2$.
+\end{proof}
+
+\subsection{Proof of Theorem \ref{Thm:PrimPts}\,(i)}
+Theorem \ref{Thm:PrimPts}\,(i) is a consequence of a corollary to the following result.
 
 \begin{proposition}\label{Prop:gcd}
-Let $m\geq 1$ be an integer and let $E/\Q$ be an elliptic curve. In $G(E,m)$,
+Let $m\geq 1$ be an integer and let $E/\Q$ be a non-CM elliptic curve. In the graph $G(E,m)$,
 suppose $(x,n,d)$ is connected by a path to both $(x_1,n_1,d_1)$ and $(x_2,n_2,d_2)$, where $n=\lcm(n_1,n_2)$.
-Then \abedit{if $\gcd(n_1,n_2) \neq n_1,n_2$}, it follows that both $(x_1,n_1,d_1)$ and $(x_2,n_2,d_2)$ connect to $(x_3, \gcd(n_1,n_2),d_3)$.
+Then if $\gcd(n_1,n_2) \neq n_1,n_2$, it follows that both $(x_1,n_1,d_1)$ and $(x_2,n_2,d_2)$ connect to $(x_3, \gcd(n_1,n_2),d_3)$, where $x_3$ is the image of $x$ on $X_1(\gcd(n_1,n_2))$ under the natural projection map.
 
 \end{proposition}
-
-%    \begin{figure}[h] 
-%        \begin{center}
-%        \begin{tikzpicture}[node distance=2cm]
-%        
-%        \node (n){$X_1(n)$};
-%        \node (n1)[below left of=n, node distance=3cm]{$X_1(n_1)$};
-%        \node (n2)[below right of=n, node distance=3cm]{$X_1(n_2)$};
-%        \node (gcd)[below of=n, node distance=4.5cm]{$X_1(\gcd(n_1,n_2))$};
-%        \draw[-] (n) edge node [left]{$f_1$}(n1);
-%        \draw[-] (n) edge node [right]{$f_2$}(n2);
-%        \draw[-] (n1) edge node [left]{}(gcd);
-%        \draw[-] (n2) edge node [left]{}(gcd);
-%
-%        \end{tikzpicture}
-%        \end{center}
-%        \caption{Maps of Modular Curves}
-%    \end{figure}
 
@@
     \begin{proof}  By assumption, the integer $g=\gcd(n_1,n_2)$ is a proper divisor of both $n_1=gn_1'$ and $n_2=gn_2'$.
-
-    Let $f_1: X_1(n) \rightarrow X_1(n_1)$ and let $f_2: X_1(n) \rightarrow X_1(n_2)$. We consider two cases.
+Let $f_1 \colon X_1(n) \rightarrow X_1(n_1)$ and let $f_2 \colon X_1(n) \rightarrow X_1(n_2)$.
+We consider two cases.
     \begin{enumerate}
-    \item Suppose $ g>2$, or if $g=1$, that exactly one of $n_1$ or $n_2$ is greater than 2.
-In the latter case, without loss of generality we may assume $n_1>2$, and $n_2=2$.
-Then $\Q(x_1)\Q(x_2)=\Q(x)$ by Lemma \ref{lem:compositum_res_fields}, and so by assumption
+    \item Suppose $ g>2$, or if $g=1$, that there exists $n_i \leq 2$.
+In the latter case, our assumptions imply that exactly one of $n_1$ or $n_2$ is equal to 2 and the other is greater than 2.
+So if $g=1$, without loss of generality we may assume $n_1>2$ and $n_2=2$.
+In either case, we have $\Q(x_1)\Q(x_2)=\Q(x)$ by Lemma \ref{lem:compositum_res_fields}, and so by assumption
     \begin{align*}
@@
     \end{align*}
-    Putting this together, we find that $\frac{d_1}{d_3}=\deg(f_2)$ and $\frac{d_2}{d_3}=\deg(f_1)$, and the conclusion holds.
+    Thus  $d_1=d_3\cdot \deg(X_1(n_1) \rightarrow X_1(g))$ and $d_2=d_3 \cdot \deg(X_1(n_2) \rightarrow X_1(g))$, so the conclusion holds.
     \item Suppose $g=2$ or, if $g=1$, that $n_1,n_2>2$.
-It follows from Lemma \ref{lem:compositum_res_fields} and the same argument as above that $\frac{\deg(f_2)}{2} \leq \frac{d_1}{d_3}$ and $\frac{\deg(f_1)}{2} \leq \frac{d_2}{d_3}$.
+It follows from Lemma \ref{lem:compositum_res_fields} and the same argument as above that $\frac{\deg(f_2)}{2} \leq \frac{d_1}{d_3}$ and $\frac{\deg(f_1)}{2} \leq \frac{d_2}{d_3}$; see Figure 1.
 However, since $n_1,n_2>2$ by assumption, we have
@@
     \end{align*}
-   Thus $\frac{d_1}{d_3}=\frac{\deg(f_2)}{2}$ and $\frac{d_2}{d_3}=\frac{\deg(f_1)}{2}$, and the conclusion follows. \qedhere
+   Thus $d_1=d_3 \cdot \deg(X_1(n_1) \rightarrow X_1(g))$ and $d_2=d_3 \cdot \deg(X_1(n_2) \rightarrow X_1(g))$, so the conclusion follows. \qedhere
       \end{enumerate}
@@
 
-\begin{corollary}
-Let $m\geq 1$ be an integer and let $E/\Q$ be an elliptic curve. Fix $v=(x,m,d)\in G(E,m)$, and consider the subgraph $D(v)$ of all its descendants. Then $D(v)$ has a single sink.
+\begin{corollary}\label{Cor:SingleSink}
+   Let $m\geq 1$ be an integer and let $E/\Q$ be a non-CM elliptic curve. For any fixed vertex $v=(x,n,d)$ in $G(E,m)$, the induced subgraph on its descendants has a single sink.
 \end{corollary}
@@
 \begin{proof}
-Suppose for the sake of contradiction that $D(v)$ has two distinct sinks, $v_1=(x_1,n_1,d_1)$ and $v_2=(x_2,n_2,d_2)$.
-But having a path from $(x,n,d)$ to each of $v_1,v_2$ implies there is a path from $(x',\text{lcm}(n_1,n_2),d')$ to each of $v_1,v_2$.
-But then both $v_1,v_2$ map to $(x_3,\text{gcd}(n_1,n_2),d_3)$ by Proposition \ref{Prop:gcd}, contradicting the fact that they were both sinks.
-
-\abbey{need to rule out case where $\gcd=n_1$ or $n_2$ since removed from proposition}
-%If $n_1 \mid n_2$, then the claim holds since the natural map $X_1(n) \rightarrow X_1(n_1)$ factors through $X_1(n_2)$ in this case \abbey{Add more details.
-Also, this is allowing for a vertex to (trivially) connect to itself...
-modify definition to allow?}; similarly, the claim holds if $n_2 \mid n_1$.
-\end{proof}
-
-\section{Overview of the Main Algorithm}
-\label{sec:mainalg}
-\abbey{Section updated to match revised algorithm; added examples.} The following algorithm is the main procedure for determining whether a given non-CM $j$-invariant in $\Q$ is the image of a $\PP^1$-isolated point on $X_1(N)$ for some $N$ based on results in \cite{BELOV,ZywinaAlgorithm}.
-We note that for any CM $j$-invariant $j$, there exists infinitely many $N\in\Z^+$ for which there is a sporadic point $x\in X_1(N)$ with $j(x)=j$ by \cite[Theorem 7.1]{BELOV}, so it is not necessary to consider them in this algorithm.
-The outline below gives an overview of the structure, while the algorithms to perform particular steps are described in detail in Sections \ref{sec:madicrep} and \ref{sec:primitivedeg}.
-We will prove a theorem on the validity of Algorithm \ref{alg:mainalgorithm} in Section \ref{sec:validity}.
-
-\setcounter{algocf}{0}
-\begin{algorithm}[h!]
-\caption{Main Algorithm}\label{alg:mainalgorithm}
-\KwIn{A non-CM $j$-invariant $j \in \Q$.}
-\KwOut{A list $[j,\{\langle a_1,d_1\rangle, \dots, \langle a_k,d_k\rangle \}]$ such that any isolated point $x \in X_1(N)$ with $j(x)=j$ maps down under the natural projection map to an isolated point of degree $d_i$ on $X_1(a_i)$ for some $1 \leq i \leq k$.}
-Construct an elliptic curve $E/\Q$ with $j(E)=j$.\\
-Compute the adelic image $G$ of $E/\Q$ as a subgroup of $\GL_2(\hat{\Z})$ using Zywina's algorithm \cite{ZywinaAlgorithm}.
-Represent the output as the level $N$ and the subgroup $G(N)$ of $\GL_2(\Z/N\Z)$.\\
-Apply Algorithm \ref{alg:reduce_level} to $G(N)$ to obtain the level $m_0$ of the $m$-adic Galois representation associated to $E$, where $m$ is the product of 2, 3, and all non-surjective primes.\\
-Using Algorithm \ref{alg:compute_prim_degree}, return a multiset $D$ with entries $\langle n, \{\langle a_1, d_1\rangle ,  \dots,  \langle a_r, d_r\rangle \} \rangle$
-    for all positive divisors $n$ of $m_0$ such that the degree of the corresponding 
-    closed point on $X_1(n)$ is as large as possible given that its image on $X_1(a_i) $
-    has degree $d_i$.\\
-Construct the multiset $D' \subseteq D$ containing only those elements $\langle n, \{\langle a_1, d_1\rangle ,  \dots,  \langle a_r, d_r\rangle \} \rangle$ for which $d_i \leq \text{genus}(X_1(a_i))+1$ for all $1 \leq i \leq r$.\\
-Create the multiset $M$ consisting of all pairs $\langle a_i,d_i\rangle $ appearing in $D'$, where $\langle a_i,d_i\rangle $ has multiplicity $\mu$ if and only if $X_1(a_i)$ has $\mu$ distinct closed points of degree $d_i$.\\
-\Return{$[j,M]$}
-
-\end{algorithm}
-
-In particular, note that if Algorithm \ref{alg:mainalgorithm} outputs $[j,\{\}]$, then $j$ is not the image of any $\mathbf{P}^1$-isolated point on $X_1(N)$, even as $N$ ranges over all positive integers.
-See Corollary \ref{cor:P1_isolated}.
-
-\begin{example}
-If $j=-9317$, then Algorithm \ref{alg:mainalgorithm} returns $[j, \{\langle 37,6\rangle ^3\}]$.
-This means that any isolated point $x\in X_1(N)$ with $j(x)=j$ and $N \in \Z^+$ maps down under the natural projection map to one of the 3 closed points of degree 6 on $X_1(37)$.
-In fact, these points are all sporadic by \cite[Proposition 2]{frey}, since $6 < \frac{1}{2} \gon_{\Q}(X_1(37)) = 18$.
-Here, the gonality computation is a result of \cite{DerickxVanHoeij2014}.
-Thus $j$ is a sporadic --- and hence isolated --- $j$-invariant.
-\end{example}
-
-\begin{example}
-If $j=-121$, then Algorithm \ref{alg:mainalgorithm} returns $[j, \{\}]$. This means that there are no isolated points on $X_1(N)$ associated to this $j$-invariant. 
-\end{example}
-
-\begin{example}
-If $j=-882216989/131072$, then Algorithm \ref{alg:mainalgorithm} returns  $[j,\{\langle 17,4\rangle ^2\}]$.
-This means that $j$ is associated to an isolated point on a modular curve of the form $X_1(N)$ if and only if there exists a degree 4 isolated point $x \in X_1(17)$ with $j(x)=j$.
-In Section \ref{sec:remainingfilters}, we will show that no such isolated point exists, from which we can conclude that $j$ is not an isolated $j$-invariant.
-\end{example}
-
-\section{\texorpdfstring{Computing the level of the $m$-adic representation}{Computing the level of the m-adic representation}}
-\label{sec:madicrep}
-\abbey{Updated the algorithm description to be less technical; added math proposition to justify; added examples.}
-Let $E/\Q$ be a non-CM elliptic curve, and define the set 
-\[
-S_E\coloneqq \{2,3\} \cup \{ \ell: \rho_{E,\ell^{\infty}}(\Gal_{\Q}) \neq \GL_2(\Z_{\ell}) \}.
-\] For $m \coloneqq \prod_{\ell \in S_E} \ell$, we give an algorithm to obtain the level of the $m$-adic Galois representation associated to $E$ from the image of the adelic representation of $E$.
-In practice, we can obtain $\im \rho_E$ from Zywina's algorithm \cite{ZywinaAlgorithm}.\\
-
-\begin{algorithm}[H]
-  \KwIn{$G(N)\leq \GL_2(\Z/N\Z)$ where $\im\rho_E=G$ and $N$ is the level.} 
-  \KwOut{$m_0 \in \Z^+$ the level of $\rho_{E,m^{\infty}}$ for $m= \prod_{\ell \in S_E} \ell$.}
-  \caption{Reduced level}%
-  \label{alg:reduce_level}
-  Let $n = \prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$.\\
-Compute smallest $m_0$ dividing $n$ such that \[\#G(n)=\#G(m_0) \cdot \#\ker(\GL_2(\Z/n\Z) \rightarrow \GL_2(\Z/m_0\Z)).\]\\
-  \Return{$m_0$}
-\end{algorithm}
-
-  \begin{proposition}
-  Let $E/\Q$ be a non-CM elliptic curve, and let $\im \rho_E=G \leq \GL_2(\widehat{\Z})$ be a subgroup of level $N$.
-Define $n \coloneqq \prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$.
-If $m_0$ is the smallest positive integer dividing $n$ such that \[\#G(n)=\#G(m_0) \cdot \#\ker(\GL_2(\Z/n\Z) \rightarrow \GL_2(\Z/m_0\Z)),\] then $m_0$ is the level of the $m$-adic Galois representation associated to $E$ for $m= \prod_{\ell \in S_E} \ell$.
-  \end{proposition}
-  \begin{proof}
-  First we will show that $\im \rho_{E,m^{\infty}}=\pi_1^{-1}(G(n))$, where $\pi_1:\prod_{\ell \in S_E} \GL_2(\Z_{\ell}) \rightarrow \GL_2(\Z/n\Z)$ is the natural reduction map.
-It suffices to show that $\ker \pi_1 \subseteq \im \rho_{E,m^{\infty}}$.
-We have $N=n\cdot n'$ with $(n,n')=1$, and so we may identify $G(N)$ as a subgroup of $\GL_2(\Z/n\Z) \times \GL_2(\Z/n'\Z)$.
-Under this identification, let $H$  be the intersection of $G(N)$ with the subgroup $\{I\} \times \GL_2(\Z/n'\Z)$.
-Then since $G$ has level $N$,
-  \[
-  \pi^{-1}(H) \subseteq \im \rho_E,
-  \]
-  where $\pi: \GL_2(\widehat{\Z}) \rightarrow \GL_2(\Z/N\Z)$ is the natural reduction map.
-The image of this subset relation under the natural projection map  $\GL_2(\widehat{\Z}) \cong \prod_{\ell} \GL_2(\Z_{\ell}) \rightarrow  \prod_{\ell \in S_E} \GL_2(\Z_{\ell}) $ gives
-  \[
-  \ker(\pi_1) \subseteq \im \rho_{E,m^{\infty}},
-  \]
-  as desired.
-
-Let $\pi_2: \GL_2(\Z/n\Z) \rightarrow \GL_2(\Z/m_0\Z)$ be the natural reduction map.
-The assumption on $m_0$ implies that $\ker(\pi_2) \subseteq G(n)$, so it follows that $G(n) = \pi_2^{-1}(G(m_0))$.
-Thus if $\pi_3: \prod_{\ell \in S_E} \GL_2(\Z_{\ell}) \rightarrow \GL_2(\Z/m_0\Z)$ denotes the reduction map, we have
-  \begin{align*}
-  \pi_3^{-1}(G(m_0))&=\pi_1^{-1}(\pi_2^{-1}(G(m_0))\\
-  &=\pi_1^{-1}(G(n))\\
-  &=\im \rho_{E,m^{\infty}}.
-  \end{align*}
-By construction $m_0$ is the smallest positive integer with this property.
-  \end{proof}
-
-  \begin{corollary}
-  Algorithm \ref{alg:reduce_level} is correct.
-  \end{corollary}
-
-  \begin{example}
-Suppose $E/\Q$ is a non-CM elliptic curve such that $\rho_{E}$ has level $N$.
-As above, define $n=\prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$ and let $m_0$ be the level of $\rho_{E,m^{\infty}}$ for $m= \prod_{\ell \in S_E} \ell$.
-It follows that $m_0| n$ and $n | N$.
-Each of these divisibilities can be proper.
-For example, if $E=75072.bc2$, we see that $\rho_E$ has level $N=4682=2^2 \cdot 3 \cdot 17 \cdot 23$.
-Since 2 is the only non-surjective prime, $n=2^2$.
-However, the level of the $m$-adic Galois representation associated to $E$ is 2.
-On the other hand, it can also happen that $N=m_0$.
-For example, if $E=54.b2$, we see that $\rho_E$ has level 72, and this is also the level of the $m$-adic Galois representation associated to $E$.
-\end{example}
-
-\section{Compute Primitive Degrees}
+Suppose the induced subgraph has two sinks, $v_1=(x_1,n_1,d_1)$ and $v_2=(x_2,n_2,d_2)$.
+We will show that $n_1=n_2$, which implies $v_1=v_2$ since both $v_1$ and $v_2$ are descendants of the same vertex $(x,n,d)$.
+Let $g=\gcd(n_1,n_2)$.
+Since $v_1,v_2$ are sinks, we must have $g=n_1$ or $g=n_2$, by Proposition~\ref{Prop:gcd}, so let $g=n_1|n_2$.
+Remark~\ref{Remark:Transitivity} implies $n_1$ does not properly divide $n_2$ since $v_2$ is a sink.
+Therefore $n_1=n_2$ and $v_1=v_2$.
+\end{proof}
+
+\subsection{Proof of Theorem \ref{Thm:PrimPts}\,(ii)} Let $E/\Q$ be a non-CM elliptic curve.
+If there exists an isolated point in $\mathcal{P}(E)$, then $j(E)$ is isolated by definition.
+To establish the other direction, suppose $j(E)$ is isolated.
+Then there exists an isolated point $x \in X_1(n)$ with $j(x)=j(E)$.
+By Theorem \ref{Thm:PrimPts}\,(i), we see that $x$ corresponds to a unique element $(x',n',d') \in \mathcal{P}(E)$ under the natural projection map.
+By the definition of $\mathcal{P}(E)$,
+\[
+\deg(x)=\deg(f)\cdot d',
+\]
+where $f\colon X_1(n) \rightarrow X_1(n')$ is the natural projection map. By \cite[Theorem 4.3]{BELOV}, the point $x'$ is isolated.
+
+\section{Computing Primitive Degrees}
 \label{sec:primitivedeg}
-% \abbey{Travis is working to update this section; I updated input/output description to match that in our isolatedpoints.m file}
 % (In the \texttt{Magma} implementation, we have to be careful that \texttt{Magma} uses right actions, but in our mathematics, we use left action.
@@
 
-Let $E$ be an elliptic curve over $\Q$ and let $m\geq1$ be an integer.
+Let $E$ be a non-CM elliptic curve over $\Q$ and let $m\geq1$ be an integer.
 In this section, we discuss an algorithm for computing the list  of $m$-primitive degrees.
@@
 The sinks are the $m$-primitive points, and we record the associated $m$-primitive degree.
-We only retain the level $n$ and degree $d$ of a $m$-primitive point $(x,n,d)$ since, in our main algorithm, we will often try show that $X_1(n)$ has no isolated points of degree $d$ at all.
+We only retain the level $n$ and degree $d$ of a $m$-primitive point $(x,n,d)$ since, in our main algorithm, we will often try to show that $X_1(n)$ has no isolated points of degree $d$ at all.
 The input to the algorithm is $G=\im \rho_{E,m}\leq \GL_2(\Z/m\Z)$.
@@
 
-\begin{algorithm}[H] \caption{Compute Primitive Degrees}\label{alg:compute_prim_degree}
-  \KwIn{$G\leq \GL_2(\Z/m\Z)$ such that $\im\rho_{E,m}=G$}
-  \KwOut{The multiset of $m$-primitive degrees for $E$}
-  % multiset with entries $\langle n, \{\langle a_1, d_1\rangle,  ...
+% \begin{algorithm}[H] \caption{Compute Primitive Degrees}\label{alg:compute_prim_degree}
+%   \KwIn{$G\leq \GL_2(\Z/m\Z)$ such that $\im\rho_{E,m}=G$}
+%   \KwOut{The multiset of $m$-primitive degrees for $E$}
+%   % multiset with entries $\langle n, \{\langle a_1, d_1\rangle,  ...
 \}\rangle$ for all positive divisors $n$ of $m$ such that the degree of the corresponding closed point on $X_1(n)$ is as large as possible given that its image on $X_1(a_i)$ has degree $d_i$ \abedit{and no $a_i \mid a_j$ for $i \neq j$}}
-  % \travis{I think this should say something like: A multiset with entries $\langle n, \{\langle a_1, d_1\rangle,  ... \}\rangle$ 
-  % in bijection with the closed points $(E,P)$ in $X_1(n)$ above $E$, where $n$ divides $m$ and $(E,P)$ maps down to a point $(E,\frac{m}{n}P)$ on $X_1(n)$ of degree }\abbey{But it's not returning all divisors $a_i$ of $n$.}\travis{right the code appends
-  % one element to the output per orbit, i.e.
+%   % \travis{I think this should say something like: A multiset with entries $\langle n, \{\langle a_1, d_1\rangle,  ... \}\rangle$
+%   % in bijection with the closed points $(E,P)$ in $X_1(n)$ above $E$, where $n$ divides $m$ and $(E,P)$ maps down to a point $(E,\frac{m}{n}P)$ on $X_1(n)$ of degree }\abbey{But it's not returning all divisors $a_i$ of $n$.}\travis{right the code appends
+%   % one element to the output per orbit, i.e.
 per point in X1m above E, i think?}\abbey{I think in theory it could return $a_1,a_2$ if a certain divisibility condition is not satisfied (the ``b mod a ne 0" part of the code).
 I don't think there are any examples of this, but this is interesting in its own right.}
-  Let $H \colonequals \langle G, -I_2\rangle \leq \GL_2(\Z/m\Z)$\;
-  Compute the orbits $O$ of $H$ acting on $(\Z/m\Z)^2$\label{Inc-1}\;
-  Let $D= \{\}$\;
-  \For{each orbit $vH\in O$}{ \label{alg:compute_primitive_degrees:minimal_levels}
-  Let $n$ be the order of $v$ in $(\Z/m\Z)^2$\;
-  Let $L= \{\}$\;
-  \For{$a|n$}{
-  \If{$\deg x = \deg y \cdot \deg f$, where $x$ corresponds to $vG$, 
-  $f\colon X_1(n)\to X_1(n/a)$ is the natural map, and $y=f(x)$}{
-  Append $(n/a,\deg y)$ to $L$\;
-  }
-  }
-  Remove all $( a,d)\in L$ such that there exists $(a',d')\in L$ with $a'$ properly dividing $a$\; 
-  Append $L$ to $D$\;
-  } 
-  % compute all tuples $\langle a,d\rangle$ such that $a|n$, the point $x=(E,P)\in X_1(n)$ corresponding to $vH$ maps to $y=(E,\frac{n}{a}P)\in X_1(a)$ with $\deg y = d$, $\deg x = (\deg f)(\deg y)$, and $a$ is minimal with respect to the divisibility ordering\;
-
-  % Filter the orbit representatives $R$ for orbits $O$ \travis{representatives?} that have order equal to $N$ in $(\Z/N)^2$\;
-  % For each element of $R$, compute the orbit sizes $s$ and their ``degrees'' as $s/2$; store the degees in $D$\label{DivBy2}\;
-  % Remove duplicates in $D$\label{RemDup}\;
+%   Let $H \colonequals \langle G, -I_2\rangle \leq \GL_2(\Z/m\Z)$\;
+%   Compute the orbits $O$ of $H$ acting on $(\Z/m\Z)^2$\label{Inc-1}\;
+%   Let $D= \{\}$\;
+%   \For{each orbit $vH\in O$}{ \label{alg:compute_primitive_degrees:minimal_levels}
+%   Let $n$ be the order of $v$ in $(\Z/m\Z)^2$\;
+%   Let $L= \{\}$\;
+%   \For{$a|n$}{
+%   \If{$\deg x = \deg y \cdot \deg f$, where $x$ corresponds to $vG$,
+%   $f\colon X_1(n)\to X_1(n/a)$ is the natural map, and $y=f(x)$}{
+%   Append $(n/a,\deg y)$ to $L$\;
+%   }
+%   }
+%   Remove all $( a,d)\in L$ such that there exists $(a',d')\in L$ with $a'$ properly dividing $a$\;
+%   Append $L$ to $D$\;
+%   }
+%   % compute all tuples $\langle a,d\rangle$ such that $a|n$, the point $x=(E,P)\in X_1(n)$ corresponding to $vH$ maps to $y=(E,\frac{n}{a}P)\in X_1(a)$ with $\deg y = d$, $\deg x = (\deg f)(\deg y)$, and $a$ is minimal with respect to the divisibility ordering\;
+
+%   % Filter the orbit representatives $R$ for orbits $O$ \travis{representatives?} that have order equal to $N$ in $(\Z/N)^2$\;
+%   % For each element of $R$, compute the orbit sizes $s$ and their ``degrees'' as $s/2$; store the degees in $D$\label{DivBy2}\;
+%   % Remove duplicates in $D$\label{RemDup}\;
+%   \Return{$D$}
+% \end{algorithm}
+
+\begin{algorithm}[H] \caption{Compute Primitive Degrees}\label{alg:compute_prim_degree}
+  \KwIn{$G\leq \GL_2(\Z/m\Z)$ such that $\im\rho_{E,m}=G$.}
+  \KwOut{The multiset of $m$-primitive degrees for $E$.}
+  Let $H \colonequals \langle G, -I_2\rangle \leq \GL_2(\Z/m\Z)$.\\
+  Compute the orbits $O$ of $H$ acting on $(\Z/m\Z)^2$\label{Inc-1}.
+If $v\in (\Z/m\Z)^2 \cong E[m]$ has order $n$, then $v$ corresponds to $x\in X_1(n)$ with $j(x)=j(E)$.
+If $n>2$, then $\deg(x)=\#(Hv)/2$, and $\deg(x)=\#(Hv)$ otherwise.\\
+   Let $D= \{\}$.\\
+  For each orbit $Hv \in O$ with $v$ of order $n$, let $x \in X_1(n)$ be the associated point.
+Find the largest divisor $d\mid n$ such that $H(dv)$ associated to $x' \in X_1(n/d)$ satisfies $\deg(x)=\deg(x') \cdot \deg(X_1(n) \rightarrow X_1(n/d))$.
+Append $\langle n, (n/d, \deg(x'))\rangle$ to $D$.\label{alg:compute_primitive_degrees:minimal_levels}\\
   \Return{$D$}
@@
 
-\abbey{In practice, it appeared that for an element $\langle n, \{\langle a_1, d_1\rangle,  \ldots \}\rangle$ in the output of this algorithm, the set $\#\{\langle a_1, d_1\rangle,  \ldots \}$ contains only 1 element.
-(Zev's observation) See section 4 for a proof of this.}
-
-We briefly discuss how we execute the loop in Step~\ref{alg:compute_primitive_degrees:minimal_levels} in Algorithm~\ref{alg:compute_prim_degree}.
-The orbits of $H$ acting on $(\Z/m\Z)^2$ are in bijection with the elements in the multiset output by Algorithm~\ref{alg:compute_prim_degree}.
-We discuss how we build the list in $L$ corresponding to an orbit orbit $x=vH$, where $v\in (\Z/m\Z)^2$ is a representative $x$.
-We initialize $L$ to the empty list.
-Let $n$ be the order of $v$ in $(\Z/m\Z)^2$.
-For a divisor $a$ of $n$, we compute the orbit $y=avH$ of $av$ under the action of $H$.
-These orbits $x$ and $y$ correspond to points $(E,P)$ and $(E,aP)$ on $X_1(n)$ and $X_1(\frac{n}{a})$.
-Proposition~\ref{prop:compute_degrees} below allows us to compute $\deg x$ and $\deg y$ from $n,n/a,\#vH$, and $\#avH$.
-If  $\deg(x)/\deg(y)=\deg(f)$ then we include $( \frac{n}{a},\deg y)$  in the list $L$.
-% ($\deg y$ is computed as $c\#dvH$ where $c=\frac{1}{2}$ if $ed\leq 2$ and $c=1$ otherwise). 
-After repeating this procedure for each divisor of $n$,  we remove every element $( a,d)$ of $L$ such that there exists $( a',d') $ with $a'|a$ and $a'\not=a$. This corresponds to identifying the 
-sinks in the subgraph $G(E,m)$ consisting of vertices reachable by a path from the point $(x,n,\deg x)$: we simply enumerate every vertex reachable from $(x,n,d)$, and remove every vertex which is not a sink.
-
-The following proposition allows us to calculate the degrees of $x$ and $y$ from the data $n,n/a,\#vH$ and $\#avH$.
+\begin{example}
+Let $E/\Q$ be the non-CM elliptic curve \href{https://www.lmfdb.org/EllipticCurve/Q/147/b/1}{147.b1}, and let $m$ be the product of 2, 3, and all primes $\ell$ for which the mod $\ell$ Galois representation associated to $E$ is not surjective.
+Zywina's algorithm \cite{ZywinaAlgorithm} gives the image of the adelic Galois representation as the complete preimage of $G \leq \GL_2(\Z/546\Z)$, and applying Algorithm \ref{alg:reduce_level} to $G$ shows the $m$-adic Galois representation has level 78.
+By Proposition \ref{Rmk:Level}, the level of any primitive point in $\mathcal{P}(E)$ divides 78.
+Applying Algorithm \ref{alg:compute_prim_degree} to $\im \rho_{E,78}$ shows $\mathcal{P}(E)$ consists of 4 points: one point on $X_1(13)$ of degree 6, two points on $X_1(13)$ of degree 39, and one point on $X_1(1)$ of degree 1.
+The points on $X_1(13)$ are expected, since the mod 13 Galois representation of $E$ is not surjective.
+
+However, it is not necessarily the case that non-surjective primes must divide the level of some primitive point.
+For example, let $E/\Q$ be the non-CM elliptic curve \href{https://www.lmfdb.org/EllipticCurve/Q/232544/f/1}{232544.f1}.
+Then the adelic Galois representation of $E$ has level $1892$ and the $m$-adic level is 44.
+In particular, the mod 11 Galois representation associated to $E$ is non-surjective.
+However, in this case $\mathcal{P}(E)$ consists of a single point, namely, the degree one point on $X_1(1)$ associated to $E$.
+\end{example}
+
+We briefly discuss Algorithm~\ref{alg:compute_prim_degree}.
+Conceptually, to compute the $m$-primitive degrees of $E$, we compute for each closed point $x\in X_1(n)$ above $E$ with $n\mid m$ the unique (by Corollary~\ref{Cor:SingleSink}) $m$-primitive point induced by $x$ and record its level $a$ and degree $d$.
+In practice, instead of working with points on $X_1(m)$ above $E$, we compute with the matrix group $G=\im\rho_{E,m}$ and the orbits of points in $(\Z/m\Z)^2$ under the left-action of $G$.
+The following proposition allows us to calculate the degrees of points on modular curves from their associated orbit data.
 
 \begin{proposition}\label{prop:compute_degrees}
-Let $E/\Q$ be a non-CM elliptic curve and $m \in \Z_{>0}$.
+Let $E/\Q$ be a non-CM elliptic curve and $m \in \Z^+$.
 Let $\im \rho_{E,m} \cong G \leq \GL_2(\Z/m\Z)$ and let $H=\langle G,-I\rangle$.
-Let $v\in (\Z/m\Z)^2$ have order $n|m$ and let $(E,P)$ be a representative of the point $x$ of $X_1(n)$  corresponding to $vG$.
-If $n>2$, the degree of $x$ is $\#vH/2$.
+Let $v\in (\Z/m\Z)^2$ have order $n|m$ and let $(E,P)$ be a representative of the point $x$ of $X_1(n)$  corresponding to $Gv$.
+If $n>2$, the degree of $x$ is $\#Hv/2$.
 If $n\leq 2$, the degree of $x$ is
-$\#vH=\#vG$. 
+$\#Hv=\#Gv$.
 \end{proposition}
@@
     We begin by noting that $(E, P)$ and $(E, -P)$ induce the same closed point $x$ on $X_1(n)$. Therefore, since $E$ is defined over $\Q$, the degree of
-    $x$ depends only on $x(P)$ and is equal to $[\Q(x(P)):\Q]$. 
+    $x$ depends only on $x(P)$ and is equal to $[\Q(x(P)):\Q]$; see Remark \ref{ResidueFieldRmk}.
     % Indeed: assuming $E$ is given by $y^2=f(x)$, if $d=f(x(P))$ is not a square in $\Q(x(P))$, then the quadratic twist $E^{(d)}:dy^2=f(x)$ has the $\Q(x(P))$-rational point $P'=(x(P),1)$ of order $n$, and $(E^{(d)},P')$ represents the same point as $(E,P)$.
-    We next observe that $[\Q(P):\Q]=\#vG$.
+    We next observe that $[\Q(P):\Q]=\#Gv$.
 Assume that $n>2$.
-When $-I\in G$, the points $P$ and $-P$ are distinct and in the same Galois orbit so $[\Q(x(P)):\Q]=[\Q(P):\Q]/2$ and $\#vH=\#vG$.
+When $-I\in G$, the points $P$ and $-P$ are distinct and in the same Galois orbit so $[\Q(x(P)):\Q]=\frac{1}{2}[\Q(P):\Q]$ and $\#Hv=\#Gv$.
 We conclude that
     \[
-    \deg x = [\Q(x(P)):\Q] = [\Q(P):\Q]/2 = \frac{1}{2}\#vG = \frac{1}{2}\#vH. 
+    \deg x = [\Q(x(P)):\Q] = \frac{1}{2}[\Q(P):\Q] = \frac{1}{2}\#Gv = \frac{1}{2}\#Hv.
     \]
@@
     % \[
-    % \#vG = \#\Gal_{\Q} P = \#\Gal(L/\Q) P = \frac{\Gal(L/\Q)}{\#\{\sigma\in \Gal(L/\Q):\sigma(P)=P)\}} = \frac{[L:\Q]}{\#\Gal(L/\Q(P))}=\frac{[L:\Q]}{[\Q(P):\Q]}=[\Q(P):\Q].
+    % \#Gv = \#\Gal_{\Q} P = \#\Gal(L/\Q) P = \frac{\Gal(L/\Q)}{\#\{\sigma\in \Gal(L/\Q):\sigma(P)=P)\}} = \frac{[L:\Q]}{\#\Gal(L/\Q(P))}=\frac{[L:\Q]}{[\Q(P):\Q]}=[\Q(P):\Q].
     % \]
-    If $-I \notin G$, then $\#vH=2\#vG$.
-There exists a twist $E'$ of $E/\Q$ such that $\im \rho_{E',n}=\langle G, -I \rangle$ by \cite[Corollary 5.25]{sutherland}.
+    If $-I \notin G$, then there exists a twist $E'$ of $E/\Q$ such that $\im \rho_{E',n}=\langle G, -I \rangle$ by \cite[Corollary 5.25]{sutherland}.
 The point $(E,P)$ is also represented by $(E',P')$ for some $P'\in E'[n]$, and the same argument from above  implies
     \[
-    2\#vG=\#vH = [\Q(P'):\Q] = 2[\Q(x(P')):\Q] = 2[\Q(x(P)):\Q],
-    \]
-    so we again have that the degree of the point represented by $(E,P)$ is $\#vH/2$.
+    \#Hv = [\Q(P'):\Q] = 2[\Q(x(P')):\Q] = 2[\Q(x(P)):\Q],
+    \]
+    so we again have that the degree of the point represented by $(E,P)$ is $\frac{1}{2}\#Hv$.
 
@@
     \[
-    \deg x = [\Q(x(P)):\Q] = [\Q(P):\Q] = \#vG = \#vH. \qedhere
-    \]
-\end{proof}
-
-% Clearly the output of Algorithm~\ref{alg:compute_prim_degree} satisfies property (ii), since we simply remove entries $\langle a_i,d_i\rangle$ if there is some other entry $\langle a_j,d_j\rangle$ with $a_j|a_i$.
-The following proposition implies that the output is correct, i.e.
-the output satisfies property (i).
-% \begin{proposition}\label{prop:primitve_degrees}
-%     Let $E$ be a non-CM elliptic curve over $\Q$ with associated $m$-adic Galois representation $G=\im\rho_{E,m}\subseteq \GL_2(\Z/m_0\Z)$, where $m$ is the product of $2,3,$ and non-surjective primes and $m_0$ is the level of the representation.
-
-%     On input $G$, Algorithm~\ref{alg:compute_prim_degree} returns a list $L$ of lists of tuples $\langle a,d\rangle$ with the following property: if there exists some $N\geq 1$ and isolated point $x\in X_1(N)$ with $j(x)=j(E)$, then there exists a tuple $\langle a,d\rangle$ in $L$ such that $a|N$ and $f(x)\in X_1(a)$ is isolated, where $f\colon X_1(N)\to X_1(a)$ is the natural map.
-% \end{proposition}
-
-% \begin{proof}
-%     This follows from Theorems~\ref{thm:PushingForwardSporadicIsolated} and \ref{BELOVthm}.
-\travis{these appear in the next section.
-We can move them up before this section, mention that Proposition~\ref{prop:primitve_degrees} will be proven in the next section in the proof of Theorem~\ref{thm:validity_main_algorithm}, or just omit the proposition and mention that we will prove the correctness of Algorithm~\ref{alg:compute_prim_degree} while we prove correctness of Algorithm~\ref{alg:mainalgorithm}.}
-% \end{proof}
-% Note that only working with orbit(s) (representatives) significantly speeds up the implementation. The computation of the orbits of $G$ acting on $(\Z/N\Z)^2$ is efficiently implemented in Magma.
-
-% \begin{proposition}
-% Let $E/\Q$ be a non-CM elliptic curve and $N \in \Z_{>0}$.
-If $\im \rho_{E,N} \cong G \leq \GL_2(\Z/N\Z)$, then the Algorithm \ref{alg:compute_degree} outputs the sequence consisting of all possible degrees of $x(P)$, where $P\in E[N]$ is a point of order $N$.
-% \end{proposition}
-% \begin{proof}
-%     We begin by noting that $(E, P)$ and $(E, -P)$ \abedit{induce the same closed} point on $X_1(N)$, for $P \in E[N]$. Therefore, the degree of
-%     a point represented by $(E, P)$, when
-%     $E$ is defined over $\Q$ depends only on $x(P)$.
-%     If $E[N]$ is identified with $(\Z/N\Z)^2$, then $\deg(P)=\# (G. P)$, where $P$ on the left hand side is considered as an element of $(\Z/N\Z)^2$
-%     and on right hand side as an element of $E[N]$\travis{should this be right/left instead of left/right? what is the degree of a point in $(\Z/N)^2$?}.
-%     If $P$ and $-P$ are in the same Galois orbit, i.e., $-I_2\in G$, then $[\Q(x(P)):\Q]=[\Q(P):\Q]/2$. On the other hand, one has $[\Q(x(P)):\Q]=[\Q(P):\Q]$, when
-%     $-I_2\notin G$ \abbey{I don't think this last sentence is true.
-(Filip, didn't you orginally have a comment here?) Consider an elliptic curve with Galois image 7Ns.2.1, which does not contain $-I$.
-There is a $P$ such that $\Q(P)$ has degree 18 but $\Q(x(P))$ has degree 9.
-Alternatively, one can note that if $-I \notin G$, then there exists a twist $E'$ of $E/\Q$ such that $\im \rho_{E',N}=\langle G, -I \rangle$ by \cite[Corollary 5.25]{sutherland}, and we can divide by 2 b/c of your first argument.
-Degrees of (closed) points on $X_1(N)$ are not impacting by replacing a curve by its twist.} \filip{Yes, I had written that it should be the other way round, then got confused during the Zoom talk and deleted it.
-It should in fact be the other way round.}
-%     Therefore, computing the orbit sizes with respect to the
-%     group $H\coloneqq \langle G, -I_2 \rangle$ (step~\ref{Inc-1} in Algorithm \ref{alg:compute_degree}) and dividing
-%     by $2$ (step~\ref{DivBy2}) handles both the cases, because in the later case (i.e., when $-I_2\notin G$) the orbit sizes will be doubled.
-%     Finally, step~\ref{RemDup} makes sure that every degree occurs only once in the output sequence.
-% \end{proof}
+    \deg x = [\Q(x(P)):\Q] = [\Q(P):\Q] = \#Gv = \#Hv. \qedhere
+    \]
+\end{proof}
+
+\section{Genus 0 adelic images do not produce isolated points}
+\label{sec:genus0images}
+
+\label{sec:genus0}
+Let $E/\Q$ be an elliptic curve and $G\leq \GL_2(\hat \Z)$ its adelic image.
+Let $G(N)$ denote the image of its mod $N$ representation.
+Denote by $B_1(N)$ the subgroup of $\GL_2(\Z/N\Z)$ consisting of the upper triangular matrices with a $1$ in the upper left entry.
+Note that $X_{B_1(N)}=X_1(N)$.
+We say that a congruence group $\Gamma$ is of genus $g$ if $X_\Gamma$ is of genus $g$.
+We say that a point $x$ corresponds to an elliptic curve $E$ if $j(x) = j(E)$.
+In this section, we show that elliptic curves with genus $0$ mod $N$ image  do not correspond to $\PP^1$-isolated points on $X_1(N)$.
+
+\begin{lemma} \label{lem:map to Symd}
+Let $f\colon X \to Y$ be a finite morphism of curves of degree $d$. Then $f$ induces a non-constant morphism $f^*\colon Y \to X^{(d)}$.
+\end{lemma}
+\begin{proof}
+    The point is to show that the natural map $y \mapsto f^{-1}(y)$ is a morphism of schemes.
+Note that the composition of $\Gamma_f\colon X \to X \times Y$ sending $X$ to the graph of $f$ with $X \times Y \to Y$ is just $f$, which is flat as a finite morphism of irreducible curves~\cite[Proposition~4.3.9]{Liu2002}.
+So the graph of $f$ defines a relative effective Cartier divisor in the sense of~\cite[Definition~3.4]{MilneJV} on $X \times Y/Y$ of degree $d$.
+    Since all our schemes are regular, we can identify Cartier with Weil divisors. 
+    In the hypothesis of the statement of~\cite[Theorem~3.13]{MilneJV}, we can thus take the effective divisor to be the graph of $f$.
+This allows us to conclude that, as a map of sets, $f^*$ maps $y \in Y$ to the degree-$d$ divisor $f^{-1}(y) \colonequals [\{y\} \times_Y X]$ with the multiplicities of the reduced subscheme of the points in the fiber product equal to the ramification indices (see~\cite[\S\,1.5, \S\,1.7]{FultonIntersectionTheory}).
+
+    The morphism $f^*$ is non-constant since fibers above different points are mapped to different points by $f^*$.
+\end{proof}
+
+%Note that a rational map from $\PP^1$ to a smooth variety of degree $1$ extends uniquely to a morphism (by the valuative criterion of properness) and is an isomorphism onto its image since a genus $0$ curve cannot have singularities.
+The symmetric powers of a smooth projective curve are smooth~\cite[Proposition~3.2]{MilneJV}.
+\sachi{right now this reads like a random pair of facts, what are we trying to say with this pair of facts?} \filip{I agree, I'm not sure we need this.}
+
+The following lemma rephrases the definition of a point being $\PP^1$-parametrized of degree $d$. 
+\begin{lemma}[Characterization of $\bP^1$-parametrized points] \label{lem:iso1}
+Let $X/k$ be a curve. Let $x \in X^{(d)}(k)$ be an irreducible degree $d$ divisor. The following are equivalent:
+\begin{enumerate}
+    \item The point $x$ is $\bP^1$-parametrized.
+
+    \item There is a non-constant rational map $\bP^1 \dashrightarrow X^{(d)}$ containing $x$ in its image.
+\end{enumerate}
+\end{lemma}
+\begin{proof}
+(i)$\implies$(ii): If $x$ is $\PP^1$-parametrized, then there is an $x' \in X^{(d)}(k)$ different from $x$ such that 
+$x-x'=\mathrm{div}(f)$ for a non-constant function $f\in k(X)$.
+Here we treat $x$ and $x'$ as effective divisors of degree $d$ on $X$.
+This gives a degree $d$ map $f\colon X \to \PP^1$, which gives the copy of $\PP^1$ inside $X^{(d)}$ as the image under pullback of $f$ as in Lemma~\ref{lem:map to Symd}.
+
+(ii)$\implies$(i): 
+%The restriction of the map $\Phi_d\colon X^{(d)}\rightarrow \Jac(X)$ to the image of $\PP^1$ inside $X^{(d)}$ factors through a translate of $\Jac(\PP^1)=\{0\}$ by the Albanese property of the Jacobian,\footnote{For pointed varieties, this is~\cite[Proposition~6.1]{MilneJV}.
+For general morphisms, note that any scheme morphism between abelian varieties is the composition of a homomorphism with a translation~\cite[Corollary~3.6]{MilneAV}.} so it contracts the $\PP^1$ to a point on $\Jac(X)$.\footnote{Or because abelian varieties contain no positive dimensional rational varieties~\cite[Corollary~3.9]{MilneAV}.} Hence $\Phi_d(y) = \Phi_d(x)$ for any $y$ lying on this image of $\PP^1$.
+Since every rational map from a unirational variety to an abelian variety is constant~\cite[Corollary~3.9]{MilneAV}, the $\PP^1$ is contracted to a point under $\Phi_d\colon X^{(d)} \rightarrow \Jac(X)$.
+\end{proof}
+
+\begin{lemma} \label{lem:iso2}
+Let $f\colon X\rightarrow Y$ be a finite morphism of curves and $x$ a closed point on $X$, and assume  $\deg x = \deg f(x)$. If $x$ is $\PP^1$-parametrized, then so is $f(x)$.
+\end{lemma}
+\begin{proof}
+Let $d=\deg(x)$. The proof is diagram chasing using $\PP^1 \to X^{(d)}\stackrel{f^{(d)}}{\to} Y^{(d)}$, where $f^{(d)}$ is the natural map from $X^{(d)}$ to $Y^{(d)}$ induced by $f$.
+If $x\in X$ is not $\bP^1$-isolated (i.e., $x$ is $\bP^1$-parametrized), then
+by Lemma~\ref{lem:iso1}, $x$ can be viewed as a point on $X^{(d)}$ lying on the image of a non-constant map from $\PP^1$ to $X^{(d)}$.  
+Furthermore, $f(x)$ lies on the image of this $\PP^1$ (which is again a $\PP^1$ by \Cref{lem:map to Symd} or because the induced morphism on the $d$-th symmetric power is again finite) inside of $Y^{(d)}$.
+Now the conclusion follows by \Cref{lem:iso1}.
+\end{proof}
+
+\begin{theorem} \label{Genus0Prop}
+Let $E/\Q$ be an elliptic curve with mod $N$ image $G(N)$ of genus $0$ and $N$ a positive integer.
+%Then there does not exist a point corresponding to $E$ on $X_1(N)$ that is $\PP^1$-isolated.
+\abbey{Perhaps here and in corollary: Every $x\in X_1(N)$ with $j(x)=j(E)$ is $\PP^1$-parametrized.}
+Then every $x \in X_1(N)$ with $j(x) = j(E)$ is $\PP^1$-parametrized.
+\end{theorem}
+\begin{proof}
+Let $x=[E,P]\in X_1(N)$.
+Replacing $G(N)$ with an appropriate choice of conjugation if necessary, we may assume $G(N)$ is with respect to a basis having $P$ as its first element.
+Let $y$ be a $\Q$-rational point on $X_{G(N)}$ corresponding to $E$.
+Let $B \colonequals B_1(N) \cap G(N)$ in $G(N)$, and let $d \colonequals [\pm G(N) : \pm B]$.
+The proof is diagram chasing in the following two diagrams while keeping track of the degree of the point.
+The situation is as follows:
+\[
+\begin{tikzcd}
+     &X_B \arrow[rd, "f"] \arrow[dl,"g",swap] &  \\
+     X_1(N) & &X_{G(N)} \isom \PP^1
+\end{tikzcd}
+     \Longrightarrow
+\begin{tikzcd}
+      &X_B^{(d)} \arrow[dl,"g^{(d)}",swap] & \\
+     X_1(N)^{(d)} & &X_{G(N)} \isom \PP^1\arrow[ul, "f^*",swap]
+\end{tikzcd}
+\]
+Let $f\colon X_{B}\rightarrow X_{G(N)} \isom \PP^1$ be the corresponding degree $d$ map of modular curves.
+\Cref{lem:map to Symd} yields a non-constant morphism $f^*\colon X_{G(N)} \to X_{B}^{(d)}$ such that $f^*(y)$ lies on a $\PP^1 \isom X_{G(N)}$. 
+Hence any point in the support of the divisor represented by $f^*(y)$ in $X_B$ is $\PP^1$-parametrized by~\Cref{lem:iso1}.
+Consider the morphism $g\colon X_B \to X_1(N)$ corresponding to $B \leq B_1(N)$.
+Let $x'\in X_B$ be such that $g(x')=x$ and $f(x')=y$.
+We want to show that $g(x')$ has the same degree as $x'$.
+Note that $\deg(x')$ is $d$ and of $\deg(x)=[\pm G(N): \pm B]$ as $\pm B$ is the stabilizer of $x$.
+Hence it satisfies $\deg(g(x')) = \deg(x')$, so $x$ is $\PP^1$-parametrized by~\Cref{lem:iso2}.
+%\abbey{How do we know $f^{-1}(x)$ is irreducible, in order to apply \Cref{lem:iso1}?} \filip{Well because the mod $N$ image is equal to $G(N)$ (and not a subgroup).
+So to get the image to reduce to $B$, we need to go to an extension of the index of $B$ in $G(N)$.
+This is a more general result: if $G\geq H$ are congruence groups of level $N$ and $f:X_H\rightarrow X_G$ and $x$ corresponds to an elliptic curve whose mod $N$ image is $G$ over $\Q$, then the degree of $f^{-1}(x)$ is $\deg f$.} \abbey{Oh, right -- that makes sense.
+Thanks.}
+\end{proof}
+
+\begin{corollary}
+Let $E/\Q$ be an elliptic curve with adelic image $G$ of genus $0$ and $n$ a positive integer. %Then there does not exist an $n$ such that a point corresponding to $E$ on $X_1(n)$ is $\PP^1$-isolated.
+Then 
+%for all $n$ 
+every $x \in X_1(n)$ with $j(x) = j(E)$ is $\PP^1$-parametrized.
+\end{corollary}
+\begin{proof}
+Since $G$ is by assumption of genus $0$, it follows that so is $G(n)$. The result then follows from Proposition~\ref{Genus0Prop}.
+\end{proof}
+
+\begin{example}\label{eg:modngenus0}
+  Consider the elliptic curve $E$ with LMFDB label \href{https://www.lmfdb.org/EllipticCurve/Q/15/a/7}{15.a7}, which has adelic image of genus 13. We can show $E$ has the following primitive points:
+\begin{itemize}
+    \item $X_1(1)$ of degree 1,
+    \item $X_1(2)$ of degrees 1 and 2,
+    \item $X_1(4)$ of degree 1,
+    \item $X_1(8)$ of degree 2,
+    \item $X_1(16)$ of degree 4, and
+    \item $X_1(32)$ of degree 8.
+\end{itemize}
+By Theorem \ref{Thm:PrimPts}, it follows that $j(E)=-1/15$ is isolated if and only if one of these points is isolated.
+Any point $x \in X_1(n)$ with $\deg(x)>\text{genus}(X_1(n))$ has Riemann--Roch space of dimension at least 2 and thus is $\PP^1$-parametrized.
+It remains only to address the point on $X_1(32)$ of degree 8.
+However, the mod $32$ Galois representation of $E$ has genus $0$, so this point is $\PP^1$-parametrized by Theorem \ref{Genus0Prop}.
+We may conclude that $j(E)=-1/15$ is not an isolated $j$-invariant.
+\end{example}
+
+\begin{comment}
+are of degree $d$.
+Let $x'\in f^{-1}(x) \subseteq X_{B}$ be a point corresponding to $E$, and let $g\colon X_{B}\rightarrow X_1(n)$ be the map induced by the inclusion $B_1(N) \supseteq B$.
+The point $x'$ lies on a $\PP^1$ inside $X_B^{(d)}$ and hence $g(x')$ lies on a $\PP^1$ inside $X_1(n)^{(d)}$.
+Since no Abelian variety has $\PP^1$ as a subvariety, $\Phi_d$ contracts this $\PP^1$ inside $X_1(n)^{(d)}$ to a single point; it follows that $g(x')$ is not $\PP^1$-isolated.
+
+We have the following commutative diagram:
+
+$$
+\xymatrix{
+& X_B \ar[r]^{g} \ar[d]^{f} & X_1(N) \ar[d]^{q} \\
+&X_{G(N)} \ar[r]^{h} & X_{G'},
+}
+$$
+where $G'$ is defined to be the subgroup of $\GL_2(\Z/N\Z)$ generated by the union of $B_1(N)$ and $G(N)$, and the maps $q:X_1(N) \rightarrow X_{G'}$ and $h:X_G(N) \rightarrow X_{G'}$ are induced by the inclusion of the corresponding subgroups.
+The curve $X_{G'}$ is obviously of genus $0$ as it is covered by $X_{G(N)}$ of genus 0.
+
+As $g(x')$ is of degree $d$ and $q(g(x'))=h(x)\in X_{G'}(\Q)$, it follows $\deg q\geq d$. Alternatively, the same conclusion follows from $\deg q=[\pm G':\pm B_1(N)]\geq [\pm G':\pm B]=d. $
+
+\filip{Work in progress.
+If we prove $\deg q=d$, we are done.
+There's a more general question here, which I think is interesting: given a morphism $f:X\rightarrow \PP^1$ over $\Q$, with genus of $X$ at least 2, is it possible that there's infinitely many points of degree $<d$ in $f^{-1}(\PP^1(\Q))$.
+For $d=2$, the answer is no, and I think this might be the case in general.
+If anyone knows of a reference (or proof) of this, let me know; this would complete the proof of this lemma.
+} \abbey{Seems like you'd want some sort of strong form of Hilbert's irreducibility for this?
+I hadn't thought of this before...
+I believe there are infinitely many $c\in\Q$ such that $f-c$ is irreducible, which gives infinitely many degree $d$ points.
+So you want to know whether there are only finitely many $c$ such that $f-c$ is reducible?
+It looks like in some cases something like this is true (e.g., ``Finiteness results for Hilbert's irreducibility theorem" by M\"{u}ller), but not in general.}
+\filip{Yes, this would be some strong form of Hilbert's irreducibility.
+Is there a single example, of an $X$ of genus $\geq 2$ and $f$, where $f$ does not factor as $f=f_1\circ f_2$  with $\deg f_i>1$ (otherwise there can be many counterexamples), where this is not true?}
+\end{comment}
+
+%\filip{I remember what the issue was: we construct maps $X_B\rightarrow X_{G(n)}$ and $f:X_B\rightarrow X_1(n)$, and show that the point associated to $E$ on $X_B$ is not $\PP^1$-isolated.
+But I don't know how to show that this would imply that the image of this point under $f$ is not $\PP^1$-isolated.
+}\\
+%\filip{This is I think a more general group theoretic problem: we have a subgroup $A$ of $G(n)$ of index $d$, i.e.
+$[G(n):A]=d$, where $A\leq B_1(N)$ (or some conjugate of $B_1(n)$).
+Then we ask what is the index of $B_1(N)$ in the group generated by $G(n)$ and $B_1(n)$.
+If the answer is again necessarily $d$ (or we can always choose a conjugate of $B_1(n)$) such that the index is $d$, then we are good.}
 
@@
 
-\abbey{New section.} In this section, we will prove results on the validity of our Main Algorithm as stated in Section \ref{sec:mainalg}.
-After recording preliminary results in Section \ref{sec:prelimresult}, we will give the proof in Section \ref{sec:proofvalidity}.
-The section concludes with an additional example.
-
-\subsection{Preliminary Results}
-\label{sec:prelimresult}
-One of the key strategies of our algorithm is to exploit instances where the image of an isolated point is isolated. A prototypical result of this nature is the following.
-\begin{theorem}[\cite{BELOV}, Theorem 4.3]
-\label{thm:PushingForwardSporadicIsolated}
-    Let $f\colon C \to D$ be a finite map of curves, let $x\in C$ be a closed point, and let $y = f(x) \in D$.  Assume that $\deg(x) = \deg(y)\cdot\deg(f)$.
-    \begin{enumerate}
-        \item If $x$ is $\PP^1$-isolated, then $y$ is $\PP^1$-isolated.
-                \item If $x$ is $AV$-isolated, then $y$ is $AV$-isolated.
-        \item If $x$ is sporadic, then $y$ is sporadic.
-    \end{enumerate}
-\end{theorem}
-
-In the case where $C$ is a modular curve, this condition can be translated into one involving arithmetic properties of the corresponding elliptic curves.
-Though result stated below is formulated for more general elliptic curves in \cite{BELOV}, we record here the version for elliptic curves over $\Q$.
-
-\begin{theorem}[\cite{BELOV}, Theorem 1.1]\label{BELOVthm}
-Let $E/\Q$ be a non-CM elliptic curve, and let $m$ be the product of 2, 3, and all primes $\ell$ where the $\ell$-adic Galois representation of $E$ is not surjective.
-Let $m_0$ be the level of the $m$-adic Galois representation associated to $E$ and let $f\colon X_1(n) \rightarrow X_1(\gcd(n,m_0))$ denote the natural map.
-If $x\in X_1(n)$ is an isolated point with $j(x)=j(E)$, then $f(x)\in X_1(\gcd(n,m_0))$ is an isolated point.
-\end{theorem}
-
-\subsection{Validity of Main Algorithm}
-\label{sec:proofvalidity}
+In this section, we will prove that our Main Algorithm as stated in Section~\ref{sec:mainalg} is valid. The section concludes with an additional example.
+
 \begin{theorem}\label{thm:validity_main_algorithm}
 Let $j\in\Q$ be a non-CM $j$-invariant.
-If Algorithm \ref{alg:mainalgorithm} returns $[j,\{\langle n_1,d_1\rangle, \dots, \langle n_k,d_k\rangle \}]$, then any isolated point $x\in X_1(N)$ for $N \in \Z^+$ with $j(x)=j$ maps under the natural projection map to an isolated point of degree $d_i$ on $X_1(n_i)$ for some  $1 \leq i \leq k$.
+If Algorithm \ref{alg:mainalgorithm} returns $\{( a_1,d_1), \dots, ( a_k,d_k) \}$, then any isolated point $x\in X_1(N)$ for $N \in \Z^+$ with $j(x)=j$ maps under the natural projection map to an isolated point of degree $d_i$ on $X_1(a_i)$ for some  $1 \leq i \leq k$.
 \end{theorem}
@@
 \begin{remark}
-Since our algorithm builds on that of Zywina \cite{ZywinaAlgorithm}, it is possible that our algorithm give an error if the adelic image cannot be computed.
+Since our algorithm builds on that of Zywina \cite{ZywinaAlgorithm}, it is possible that our algorithm will give an error if the adelic image cannot be computed.
 See Zywina \cite{ZywinaImagesGit} for details.
@@
 Because we take preliminary steps to reduce the modulus of the matrix group (i.e., Section \ref{sec:madicrep}), this error did not occur when running our full algorithm on all elliptic curves currently in the LMFDB.
-\abbey{New remark; incorporates Timo's suggestion}
 \end{remark}
@@
 Let $E/\Q$ be a non-CM elliptic curve with $j(E)=j$.
+We note that the choice of $E$ will not impact our result; see Section \ref{sec:ClosedPts}.
 We may compute $\im \rho_E=G$ via Zywina's algorithm \cite{ZywinaAlgorithm}, and represent the output as $G(N) \leq \GL_2(\Z/N\Z)$ where $N$ is the level.
 By Algorithm \ref{alg:reduce_level}, we may use $G(N)$ to compute the level $m_0$ of the $m$-adic Galois representation associated to $E$, where $m$ is the product of 2, 3, and all non-surjective primes.
-Let $x\in X_1(N)$ be an isolated point with $j(x)=j$ and $N\in \Z^+$.
+By Proposition \ref{Rmk:Level}, the level of any primitive point in $\mathcal{P}(E)$ will divide $m_0$, so applying Algorithm \ref{alg:compute_prim_degree} to $\im \rho_{E,m_0}$ results in the complete set of primitive degrees for $E$.
+In particular, for each closed point $x \in X_1(n)$ with $j(x)=j$ and $n \mid m_0$, we have $x$ mapping to the primitive point $x' \in X_1(a)$ of degree $d$.
+We record the entry $\langle n, ( a, d) \rangle$ in the multiset $D$.
+By Theorem \ref{Thm:PrimPts}, we have $\deg(x)=\deg(x') \cdot \deg(X_1(n) \rightarrow X_1(a))$, and $j$ is isolated if and only if there is an isolated point on $X_1(a_i)$ of degree $d_i$ for some $\langle n_i, ( a_i, d_i) \rangle$ in $D$.
+
+%Let $x\in X_1(N)$ be an isolated point with $j(x)=j$ and $N\in \Z^+$.
 By Theorem \ref{BELOVthm}, it follows that $f(x)\in X_1(\gcd(N,m_0))$ is an isolated point, where $f\colon X_1(N) \rightarrow X_1(\gcd(N,m_0))$ is the natural map.
@@
 
-By Algorithm \ref{alg:compute_prim_degree}, we may compute the multiset $D$ with entries $\langle n, \{\langle a_1, d_1\rangle ,  \dots,  \langle a_r, d_r\rangle \} \rangle$ for all positive divisors $n$ of $m_0$ such that the degree of the corresponding closed point on $X_1(n)$ is as large as possible given that its image on $X_1(a_i) $ has degree $d_i$.
-Suppose $x \in X_1(n)$ is isolated.
-Then by Theorem \ref{thm:PushingForwardSporadicIsolated}, for all $1\leq i \leq r$ the point $f_i(x) \in X_1(a_i)$ is an isolated point of degree $d_i$, where $f_i: X_1(n) \rightarrow X_1(a_i)$ is the natural map.
-If there exists $i$ such that $\deg(f_i(x))>\text{genus}(X_1(a_i))+1$, then $f(x_i)$ is not $\PP^1$-isolated since its associated Riemann--Roch space has dimension at least 2 by the Riemann--Roch Theorem.
-This gives a contradiction.
-Thus we need only consider the multiset $D' \subseteq D$ containing only those elements $\langle n, \{\langle a_1, d_1\rangle ,  \dots,  \langle a_r, d_r\rangle \} \rangle$ for which $d_i \leq \text{genus}(X_1(a_i))+1$ for all $1 \leq i \leq r$.
-Moreover, since the image $f_i(x) \in X_1(a_i)$ is isolated and is the image of $x$ under the natural projection map, we may in fact record only the multiset $M$ containing of all pairs $\langle a_i,d_i\rangle $ appearing in $D'$.
-We include the element $\langle a_i,d_i\rangle $ in $M$ with multiplicity $\mu$ if and only if $X_1(a_i)$ has $\mu$ distinct closed points of degree $d_i$.
-Since Algorithm \ref{alg:mainalgorithm} returns $[j,M]$, we are done.
+Next, we will rule out pairs $(a,d)$ which cannot correspond to isolated points.
+If $d> \text{genus}(X_1(a))$, then the point is not $\mathbf{P}^1$-isolated since its associated Riemann--Roch space has dimension at least 2.
+Thus we need only consider the multiset $D' \subseteq D$ containing those elements $\langle n,( a, d) \rangle$ for which $d \leq \text{genus}(X_1(a))$.
+The integer $n$ is not relevant for our purposes, so we create a new multiset $M$ containing $(a,d)$ from $D'$.
+We record $(a,d)$ with multiplicity $\mu$ if and only if $X_1(a)$ has $\mu$ distinct closed points of degree $d$ which are associated to $E$.
+
+Finally, by Theorem \ref{Genus0Prop}, we may remove from $M$ any pair $(a,d)$ where $\im \rho_{E,a}$ corresponds to a modular curve of genus 0.
+Since Algorithm \ref{alg:mainalgorithm} returns $M$, we are done.
 \end{proof}
@@
 \begin{corollary}\label{cor:P1_isolated}
-If Algorithm \ref{alg:mainalgorithm} outputs an empty set on some $j$-invariant $j = j(E)$, then $j$ is not the image of an  isolated point on $X_1(N)$ for any positive integer $N$. 
+If Algorithm \ref{alg:mainalgorithm} outputs an empty set on some non-CM $j$-invariant $j \in \Q$, then $j$ is not the image of an  isolated point on $X_1(N)$ for any positive integer $N$.
 \end{corollary}
 
-\subsection{Additional Example}
-
+\begin{example}
 We end this section with an extended example to illustrate the impact of each step in Algorithm \ref{alg:mainalgorithm}.
@@
 \item We compute that $\text{genus}(X_1(37))=40$ and  $\text{genus}(X_1(1))=0$. Thus no point of degree 222 on $X_1(37)$ can be isolated, and neither is the rational point on $X_1(1)$.
-\item The algorithm returns $[j, \{\langle 37, 18 \rangle\}]$.
+\item Since the modular curve associated to $\im \rho_{E,37}$ has genus 4, the algorithm returns $ \{( 37, 18)\}$.
 \end{enumerate}
+\end{example}
 
@@
 
-\sachi{Swap this section with the next section?} \abbey{I moved the last section way earlier -- what do you think?}
-
-\abedit{Suppose $E/\Q$ is non-CM elliptic curve such that one of the following holds:
+Suppose $E/\Q$ is non-CM elliptic curve such that one of the following holds:
 \begin{itemize}
@@
     \item $N_E$ is only divisible by primes $p \leq 7$, or
-    \item $N_E=p \leq 200{,}000{,}000$ for some prime number $p$.
-\end{itemize} Then running Algorithm 1 on $E$ results in the empty set, aside from the output for those $j$-invariants given in the Appendix.}
-In this section we describe additional criteria which can prove that there are no isolated points on $X_1(N)$ for a fixed $N$ corresponding to a given $j$-invariant \abedit{$j \notin \{-140625/8,-9317,351/4, -162677523113838677\}$, proving Theorem \ref{LMFDBoutputThm}}.
-
+    \item $N_E=p \leq 300{,}000{,}000$ for some prime number $p$.
+\end{itemize} Then running Algorithm 1 on $E$ results in the empty set, aside from the $j$-invariants listed in Table~\ref{table:imagegt0}.
+The final step in the main algorithm filters out curves with mod $N$ genus $0$; we also list in the table the mod $N$ genus.
+This genus is computed using code associated to the paper \cite{RSZB2022}.
+	\begin{table}[h]
+	\begin{center}
+		\begin{tabularx}{266pt}{l l c} \toprule
+		$j$ & $( N, d )$ & genus mod $N$  \\\midrule
+$-140625/8$ &  $\{ ( 21, 3 )^2 \} $ & $1$\\
+ $-162677523113838677$& $\{ ( 37, 18 ) \}$ & $4$\\
+ $-882216989/131072$ & $\{ ( 17, 4 )^2\}$ & $1$ \\
+ $-9317$ & $\{ ( 37, 6 )^3 \} $ & $4$\\
+ $16778985534208729/81000$ & $\{ ( 24, 4 )^2 \}$ & $1$\\
+ $351/4$ & $\{ ( 28, 9 )^2 \}$ & $5$\\ \bottomrule
+		\end{tabularx}
+		\caption{Output of main algorithm}\label{table:imagegt0}
+	\end{center}
+\end{table}
+
+In this section we describe additional computations that prove that the only $\PP^1$-isolated points on $X_1(N)$ for a fixed $N$ correspond to the four $j$-invariants $j=-140625/8,-9317,351/4,$ and $ -16267752311383867$, proving Theorem \ref{LMFDBoutputThm}.
+Since $j=-140625/8,-9317$, and $351/4$ are known to be isolated (see Section \ref{sec:intro}), it suffices to consider only the remaining 3 $j$-invariants.
+\if{false}
 \begin{proposition} \abbey{New plan is to use result about genus 0 mod $N$ images in place of this Proposition (instead of working to correct it).}
@@
 
-\subsection{Special cases}
-We now explain how we dealt with cases that passed all the filters.
-
-\subsubsection{Degree $4$ point on $X_1(17)$ corresponding to $j=-882216989/131072$}
-To show that this point is not isolated we compute the coordinates of \fedit{a} degree $4$ point $x$ corresponding to our curve on a model of $X_1(17)$.
-\abbey{Does this construction depend on which closed point of degree 4 we choose?
-There are 2.} \filip{I didn't check, but it probably shouldn't.
-I changed "the" to "a" in the previous sentence.} The point $x$ is defined over a cyclic quartic field.
-Let $\sigma_i$, for $i=1,\ldots, 4$ be the automorphisms of $K$ and $D=\sum_{i=1}^4\sigma_i(x)$.
-We compute $\ell(D)=2$, which implies that $x$ is not $\PP^1$-isolated.
-
-The fact that this point is not $\PP^1$-isolated also follows from the results of \cite[Proposition 6.7]{DerickxMazurKamienny}, where it is shown that there are no $\PP^1$-isolated quartic points on $X_1(17)$.
+\fi
 
@@
 
-We show that the points $x\in X_1(37)(K)$, where $K$ is a degree 18 number field, and $j(x)=-162677523113838677$ is $\PP^1$-isolated.
+We show that the point $x\in X_1(37)(K)$, where $K$ is a degree 18 number field, and $j(x)=-162677523113838677$ is $\PP^1$-isolated.
 We explicitly compute the coordinates of $x$ on a model of $X_1(37)$ and define  $\sigma_i$, for $i=1,\ldots, 18$ to be the automorphisms of $K$ and $D=\sum_{i=1}^{18}\sigma_i(x)$.
 Reducing everything modulo $3$ and denoting the reduction of $D$ modulo $3$ by $\overline{D}$, we obtain $\ell(\overline{D})=1$, which shows that the reduction
-$\overline{x}$ of $x$ modulo 3 is $\PP^1$-isolated, and hence it follows that $x$ is $\PP^1$-isolated.  %\abbey{I believe we mean that it \emph{is} $\PP^1$-isolated.} \filip{Yes, fixed.}
-
-\filip{I did not go into much details here, as I think more details would entail just writing a bunch of equations, and the code where all the computations are dove, will be supplied.}
-
-\newpage
-\section*{Appendix}
-\label{appendix}
-\abbey{Added output of Algorithm 1.}
-Suppose $E/\Q$ is non-CM elliptic curve such that one of the following holds:
-\begin{itemize}
-    \item$N_E \leq 500{,}000$,
-    \item $N_E$ is only divisible by primes $p \leq 7$, or
-    \item $N_E=p \leq 200{,}000{,}000$ for some prime number $p$.
-\end{itemize}
-If the output of Algorithm 1 is non-empty, then $j(E)$ and the output appear in the list below.
-\scriptsize{
-\begin{align*}
-&-1/15:\{<32, 8>^2\}\\
-&-1139466686381936641/17587891077120:\{<32, 8>^2 \}\\
-&-13123858413236228917847770385659606286401/20767600023946451721766482684226058876:\{ <25, 10> \}\\
-&-1376562883316985524655287925404037121/1193272631368179777536:\{ <25, 5>^2 \}\\
-&-12757618324042173549858425461682176/1823806051450564693130128615083:\{ <25, 10> \}\\
-&-1415127831921321522248426938217281/3666855487972497940063476562500:\{ <32, 16>^2 \}\\
-&-140625/8:\{ <21, 3>^2 \}\\
-&-162677523113838677:\{ <37, 18> \}\\
-&-19328649688935739391016961/18446462598732840960:\{ <32, 16>^2 \}\\
-&-19465109/22:\{ <25, 10> \}\\
-&-18975420587737213095292649/255881160051786:\{<25, 10> \}\\
-&-225741686871429146260559062081/146211902909299839467520000:\{ <16, 2>^4 \}\\
-&-24680042791780949/369098752:\{ <25, 5>^2 \}\\
-&-2926956820564562516641/35459588343029760000:\{ <16, 2>^4 \}\\
-&-279328676638409/15200157696:\{ <25, 10> \}\\
-&-324503698618794407582644992737281/19342794667089993085747200:\{ <32, 8>^2 \}\\
-&-326573981641149886485204481/194520794324722008975:\{ <32, 8>^2 \}\\
-&-1638541430081273024/26265946892733:\{ <25, 10> \}\\
-&-353498371667659682101/113715890591105024:\{ <25, 10> \}\\
-&-3545733621855029067330337757367361/9094574488699436187744140625:\{ <32, 8>^2 \}\\
-&-3552277140342294754589991537894721/568432733416557312011718750:\{ <32, 16>^2 \}\\
-&-36703062611518813711084873444252734518401/397925291030084608863799302120300:\{ <32, 16>^2 \}\\
-&-4033422215926741/404:\{ <25, 10> \}\\
-&-4096/11:\{ <25, 5>^2 \}\\
-&-488162845931504468669161001/502:\{<25, 10> \}\\
-&-49019660417634625566551535616/52295500263431403:\{ <25, 5>^2 \}\\
-&-5107501047547200669121/186932676651373720080:\{ <32, 16>^2 \}\\
-&-52893159101157376/11:\{ <25, 10> \}\\
-&-56667352321/16711680:\{ <32, 16>^2 \}\\
-&-60627540058019895893705412918183361/10979320318525440000000000000000:\{ <16, 2>^4 \}\\
-&-60698457/40960:\{ <13, 2>^3 \}\\
-&-617298465273089376571121350031405627538001/165066:\{ <25, 10> \}\\
-&-70809965983288820433601/12128017136035299345:\{ <32, 8>^2 \}\\
-&-79184385609230668294081/759738277429254810:\{ <32, 16>^2 \}
-\end{align*}
-\begin{align*}
-&-882216989/131072: \{ <17, 4>^2\}\\
-&-460815199424/93:\{ <25, 10> \}\\
-&-9317:\{ <37, 6>^3 \}\\
-&1023887723039/928972800:\{ <16, 2>^4 \}\\
-&1139466686381936641/4080:\{ <32, 16>^2 \}\\
-&1144081181272479239133643526834383042983361/757051842880264964991840000:\{ <16, 2>^4 \}\\
-&115099000398621243971890559/78239096930039062500000000:\{ <16, 2>^4 \}\\
-&1259954716599707317761635279/782145653991396014555136:\{ <25, 5>^2 \}\\
-&128394017933147245660796166417119/493274390082338961058364010000:\{ <16, 2>^4 \}\\
-&13087181362848921857775657601/10116926999101440000:\{ <16, 2>^4 \}\\
-&13527956825588849127121/25701087819771000:\{ <24, 4>^2 \}\\
-&13619385906841/6048000:\{ <24, 4>^2 \}\\
-&13831657260716704136482954281709863361/17374959614531090376562500:\{ <32, 16>^2 \}\\
-&14551803469961881301880007324200000001/9536718750:\{ <32, 16>^2 \}\\
-&150336917982741967163778998756395764357350401/2077057800300:\{ <32, 16>^2 \}\\
-&1542085860252894509103949/6408896512:\{ <25, 10> \}\\
-&164711681450297281/8097103872000:\{ <24, 4>^2 \}\\
-&1663986362115498724215359/108912513076663261593600:\{ <32, 16>^2 \}\\
-&1663986362115498724215359/1169329859973065744640:\{ <32, 8>^2 \}\\
-&16778985534208729/81000:\{ <24, 4>^2 \}\\
-&178296503348692983836197044001/1342:\{ <25, 10> \}\\
-&1815401516599/8422162432:\{ <25, 10> \}\\
-&190705121216/71:\{ <25, 10> \}\\
-&19328649688935739391016961/1048320:\{ <32, 8>^2 \}\\
-&20250020461466473637047669654178374039681/501531896655344498219343780249600:\{ <32, 8>^2 \}\\
-&2119184381004022710620128465357091164489/26664780077208000:\{ <24, 4>^2 \}\\
-&2366200373628880151/2612420149248000:\{ <24, 4>^2 \}\\
-&236979190359324065638429091444161/447618521651352874905600:\{ <32, 16>^2 \}\\
-&291546910741641055583105024/382127162858793:\{ <25, 5>^2 \}\\
-&297106512928238351998640242081/3977028808593750000:\{ <16, 2>^4 \}\\
-&300872095888141441/22515023872:\{ <25, 5>^2 \}\\
-&324503698618794407582644992737281/268431360:\{ <32, 16>^2 \}\\
-&326573981641149886485204481/2690010:\{ <32, 16>^2 \}\\
-&3358085834636749/382:\{ <25, 10> \}\\
-&351/4:\{ <28, 9>^2 \}\\
-&3552277140342294754589991537894721/152581640625:\{ <32, 8>^2 \}\\
-&3634704740957616196378170215513091769/168224880645019054412841796875000:\{ <24, 4>^2 \}\\
-&364421318680576777174674911/450962301637624725000000:\{ <24, 4>^2 \}\\
-&36546944013036856482908761/14157275332658039712000:\{ <24, 4>^2 \}\\
-&378499465220294881/120530818800:\{ <16, 2>^4 \}\\
-&3922540634246430781376/71:\{ <25, 10> \}\\
-&44992447464066442427196092139811199/65124493101588450372219085693359375:\{ <32, 8>^2 \}\\
-&45960438227854760543785319/46920791622800342016000000:\{ <24, 4>^2 \}\\
-&5107501047547200669121/69461926257623040:\{ <32, 8>^2 \}\\
-&52300395461270777993673352489/30181158775846600704000000:\{ <24, 4>^2 \}\\
-&5345287166085790635663218704920974401/226978257155929261920000:\{ <16, 2>^4 \}
-\end{align*}
-\begin{align*}
-&5444502293860223539938743709179943321601/68719411200:\{ <32, 8>^2 \}\\
-&546397111960658404325211701139833360188801/209323126216982833463548776182030859375:\{<32, 8>^2 \}\\
-&5481351580593489628916345933548801/688740975:\{ <32, 8>^2 \}\\
-&56667352321/15:\{ <32, 8>^2 \}\\
-&56868272654707881404486749117441/10748658652923870314496000:\{ <24, 4>^2 \}\\
-&573007087724441463649920782881/67058993610000000000000000:\{ <16, 2>^4 \}\\
-&591720065532918583239955136329/116891407012939453125000000:\{ <24, 4>^2 \}\\
-&628284678908027418152998936285681/19884708881378173828125000:\{ <24, 4>^2 \}\\
-&6271688643866537984/1353:\{ <25, 10> \}\\
-&68699533290471196810719174361/268409217024000:\{ <24, 4>^2 \}\\
-&70809965983288820433601/2711034593280:\{ <32, 16>^2 \}\\
-&79184385609230668294081/42941745:\{ <32, 8>^2 \}\\
-&818546927584539194367471866449/14273634375000:\{ <24, 4>^2 \}\\
-&8827236347661221188886967161105287201/46539238473000000:\{ <24, 4>^2 \}\\
-&96653256179049031824319796125471784879999/341359290480134366830343600487545241600:\{ <32, 8>^2 \}
-\end{align*}}
-\vspace{20 mm}
+$\overline{x}$ of $x$ modulo 3 is $\PP^1$-isolated. Hence it follows that $x$ is $\PP^1$-isolated.  %\abbey{I believe we mean that it \emph{is} $\PP^1$-isolated.} \filip{Yes, fixed.}
+% \sachi{Do we need to prove this is isolated or was it already done in van Hoeij and Derickx?
+It seems asymmetric that this is the only isolated point we talk about, of the four.} \abbey{I don't think they proved (or, at least, published a proof) that it was $\PP^1$-isolated -- it's not sporadic, and it looks like they stopped looking for points on $X_1(37)$ after degree 17.
+See here: https://www.math.fsu.edu/~hoeij/files/X1N/LowDegreePlaces.
+The other three $j$-invariants were known to be isolated before and are described in the introduction.
+However, $j(x)=-162677523113838677$ was known to give a degree 18 point prior to our computation, since it gives a rational point on $X_0(37)$ and $\deg(X_1(37) \rightarrow X_0(37))=18$.
+So it's not so much that this is ``discovering" a new $\PP^1$-isolated point, as just making the official observation that this known point is actually $\PP^1$-isolated.}
+
+\subsubsection{Degree $4$ point on $X_1(17)$ corresponding to $j=-882216989/131072$ and degree $4$ point on $X_1(24)$ corresponding to $j=16778985534208729/81000$ }
+To show that these points are not isolated we compute the coordinates of a degree $4$ point $x$ corresponding to our curve on a model of $X_1(17)$ and $X_1(24)$.
+Such a point $x$ is defined over a cyclic quartic field.
+Let $\sigma_i$, for $i=1,\ldots, 4$ be the automorphisms of $K$ and $D=\sum_{i=1}^4\sigma_i(x)$.
+In each case, we compute $\ell(D)=2$, which implies that $x$ is not $\PP^1$-isolated.
+
+The fact that the degree $4$ point on $X_1(17)$ is not $\PP^1$-isolated also follows from the results of \cite[Proposition 6.7]{DerickxMazurKamienny}, where it is shown that there are no $\PP^1$-isolated quartic points on $X_1(17)$.
+
 \bibliographystyle{alpha}

### 2023-09-22 isolatedpoints.m
remove GL2genus check

@@ -183,11 +183,6 @@ intrinsic NotIsolated(j::FldRatElt, path::Assoc : ainvs :=[]) -> List
     end if;
 
     G0 := ChangeRing(G,Integers(m0));
-
-    if GL2Genus(G0) eq 0 then
-        return [* j, {* *} *];
-    end if;
-
     primitivepts := PrimitiveDegreesOfPoints(G0); 
     potisolated := FilterByRiemannRoch(primitivepts);
 

### 2023-09-22 TeX/zevs_draft.tex

--- 2023-07-27 TeX/draft.tex
@@
 \newtheorem{exercise}[theorem]{Exercise}
-% \newtheorem{algorithm}[theorem]{Algorithm}
+%\newtheorem{Algorithm}[theorem]{Algorithm}
 \DeclareMathOperator{\gon}{gon}
@@
 \newcommand{\travis}[1]{\textcolor{orange}{Travis: #1}}
-\newcommand{\dldedit}[1]{{\color{Plum} #1}}
+\newcommand{\dldedit}[1]{{\color{VioletRed} #1}}
 \newcommand{\abedit}[1]{{\color{blue} #1}}
@@
 \newcommand{\sedit}[1]{{\color{purple} #1}}
+\newcommand{\hs}[1]{{\color{brown}{Himanshu: [#1]}}}
 
@@
 
-The modular curve $X_1(N)$ is an algebraic curve over $\Q$ whose non-cuspidal points parametrize elliptic curves with a distinguished point of order $N$.
-We are interested in studying isolated points on $X_1(N)$.
-Roughly speaking, these are points of degree $d$ not belonging to an infinite family of degree $d$ points parametrized by a geometric object.
-For example, if $f: X_1(N) \rightarrow \PP^1$ is a rational map of degree $d$, then $f^{-1}(\PP^1(\Q))$ contains infinitely many closed points of degree $d$ by Hilbert's irreducibility theorem \cite[Chapter~9]{serre97}.
+%\timo{Suggestion: Write canonical isomorphisms as $\iso$ and general isomorphisms as $\isom$.}
+
+%\timo{At the end: uniformize paramet(e)riz; replace $f: A$ by $f\colon A$}
+
+\label{sec:intro}
+
+The modular curve $X_1(N)$ is an algebraic curve over $\Q$ whose non-cuspidal points parameterize elliptic curves with a distinguished point of order $N$.
+We are interested in studying isolated points on $X_1(N)$, which are roughly those not belonging to an infinite family of points parameterized by a geometric object.
+
+For example, if $f: X_1(N) \rightarrow \PP^1$ is a rational map of degree $d$, then $f^{-1}(\PP^1(\Q))$ contains~infinitely many closed points of degree $d$ by Hilbert irreducibility.
+%'s irreducibility theorem.
+% \cite[Chapter~9]{serre97}.
 We say a degree $d$ point \emph{not} arising from such a map is \textbf{$\PP^1$-isolated}.
-Other infinite families of degree $d$ points correspond to positive rank abelian subvarieties of the curve's Jacobian; see Section \ref{sec:background} for details.
-A point which is not thus parametrized is \textbf{AV-isolated}.
-If a closed point $x\in X_1(N)$ is both $\PP^1$- and AV-isolated, then we say $x$ is \textbf{isolated}.
-
-Isolated points can be thought of as those points whose existence is not explained by a geometric construction.
-The lack of control of isolated points in infinite families of modular curves lies at the heart of several important open problems.
-See, for example, \cite[Question~1]{MazurNote} and \cite[Theorem~1.3]{BourdonNajman2021}.
-
-One special class of isolated points is \textbf{sporadic} points, which are
-points $x \in X_1(N)$ such that there are only finitely many points on $X_1(N)$
-of degree at most $\deg(x)$. Hence a non-cuspidal sporadic point corresponds to
-an elliptic curve with a point of order $N$ \dldedit{with ``unusually low degree.''}
-Elliptic curves with complex multiplication (CM) provide many natural examples
-of sporadic points, since the extra endomorphisms of a CM elliptic curve
-constrain the size of the image of the associated Galois representation.
-Indeed, as shown in \cite[Theorem~8.2]{CGPS2022}, there exist sporadic CM
-points on $X_1(N)$ for all $N\geq 721$.
-
-Non-CM isolated points on $X_1(N)$ remain much more mysterious.
+Other infinite families of degree $d$ points correspond to positive rank abelian subvarieties of the curve's Jacobian.
+%;see Section \ref{sec:background} for details.
+A point which is not thus parameterized is called \textbf{AV-isolated}. If a closed point $x\in X_1(N)$ is both $\PP^1$- and AV-isolated, then we say $x$ is \textbf{isolated}.
+
+One special class of isolated points is \textbf{sporadic} points, which are points $x \in X_1(N)$ such that there are only finitely many points on $X_1(N)$ of degree at most $\deg(x)$.
+While every sporadic point is isolated \cite[Theorem 4.2]{BELOV}, the converse need not hold.
+
+Elliptic curves with complex multiplication (CM) provide many natural examples of isolated points, since the extra endomorphisms of a CM elliptic curve constrain the size of the image of the associated Galois representation.
+Indeed, as shown in \cite[Theorem~8.2]{CGPS2022}, there exist sporadic CM points on $X_1(N)$ for all $N\geq 721$.
+Non-CM isolated points on $X_1(N)$ remain much more mysterious, and are tied to open uniformity problems of Balakrishnan and Mazur \cite[Conjecture 17]{BalakrishnanMazur23} and Serre \cite[$\S4.3$]{serre72}; see Section \ref{sec:UniformityConnections} for details.
+
 One recent line of investigation has focused on the class of isolated points associated to non-CM elliptic curves with $j$-invariant in $\Q$.
-To date, there are only three known examples of such curves, up to isomorphism over $\overline{\Q}$:
-\begin{itemize}
-    \item The elliptic curve with $j$-invariant $-140625/8$ corresponds to two points of degree 3 on $X_1(21)$.
-Since there are only finitely many points of degree at most 3 on this modular curve, these are sporadic (and hence isolated) points.
-This example was first discovered by Najman \cite{najman16}.
-In fact, this is the unique elliptic curve giving a sporadic point of degree at most 3 on \emph{any} modular curve of the form $X_1(N)$, as shown in recent work of Derickx, Etropolski, van Hoeij, Morrow, and Zureick-Brown \cite{DEvHMZB2021}.
-
-    \item The elliptic curve with $j$-invariant $-9317$ gives three degree 6 points on $X_1(37)$, as in work of van Hoeij \cite{vanHoeij}.
-Since 6 is less than half the $\Q$-gonality of $X_1(37)$, as computed in \cite{DerickxVanHoeij2014}, the point is necessarily sporadic by work of Frey \cite{frey}.
-
-    \item The elliptic curve with $j$-invariant $351/4$ gives an isolated point of degree 9 on $X_1(28)$; see \cite[Theorem 2]{OddDeg}.
-There are infinitely many points on $X_1(28)$ of degree 6, as shown in \cite{DerickxVanHoeij2014}, so this point is isolated but not sporadic.
-\end{itemize}
-
-If $x \in X_1(N)$ is a sporadic (resp.
-isolated) point, we say $j(x) \in X_1(1) \cong \mathbf{P}^1$ is a \textbf{sporadic} (resp.
-\textbf{isolated}) \textbf{$j$-invariant}.
-Thus the three $j$-invariants listed above are isolated $j$-invariants, while $-140625/8$  and $-9317$ are also sporadic $j$-invariants.
-We have good reason to believe that the set of all isolated $j$-invariants in $\Q$ is finite.
-\begin{theorem}[Bourdon, Ejder, Liu, Odumodu, Viray \cite{BELOV}]
-\label{BELOVfiniteness}
-Suppose there exists a constant $C$ such that the mod $\ell$ Galois representation of any non-CM elliptic curve over $\Q$ is surjective for primes $\ell>C$.
-Then there are only finitely many isolated $j$-invariants in $\Q$.
-\end{theorem}
-
-\noindent The assumption about Galois representations stated in Theorem \ref{BELOVfiniteness} was originally asked as a question by Serre \cite{serre72}, and it has now been formally conjectured by both Sutherland \cite{sutherland} and Zywina \cite{ZywinaImages}.
-It is even suspected that $C=37$.
-Theorem \ref{BELOVfiniteness} is known unconditionally for points of odd degree \cite{OddDeg}: indeed, $j=-140625/8$ and $j=351/4$ are the only non-CM $j$-invariants in $\Q$ giving an isolated point of odd degree on $X_1(N)$, even as $N$ ranges over all positive integers.
-
-In \cite{BELOV}, they ask whether one can explicitly determine the set of isolated $j$-invariants in $\Q$.
-This is the motivation for the present work.
-We develop an algorithm which can be used to determine whether a given non-CM $j$-invariant $j\in \Q$ is isolated.
-Starting with the adelic image of the adelic Galois representation associated $E/\Q$ with $j(E)=j(x)$, as computed by Zywina \cite{ZywinaAlgorithm}, we apply various filters to determine whether there exists an isolated point on $x \in X_1(N)$ with $j(x)=j$.
-
-\begin{algorithm}[h!]
+We present a new algorithm which helps determine whether a given non-CM $j$-invariant comes from an isolated point on some $X_1(N)$:
+
+%\begin{algorithm}[h!]
+\begin{algorithm}[H]
+\label{alg:mainalgorithm}
 \caption{Main Algorithm}
     \KwIn{A non-CM $j$-invariant $j \in \Q$.}
-    \KwOut{A \abedit{finite} list $[j,\{\langle a_1,d_1\rangle, \dots, \langle a_k,d_k\rangle \}]$ such that any isolated point $x \in X_1(N)$ with $j(x)=j$ maps down under the natural projection map to an isolated point of degree $d_i$ on $X_1(a_i)$ for some $1 \leq i \leq k$.}
+    \KwOut{A finite list $\{ (a_1,d_1), \dots, (a_k,d_k) \}$ such that any isolated point $x \in X_1(N)$ with $N \in \Z^+$ and $j(x)=j$ maps down under the natural projection map to an isolated point of degree $d_i$ on $X_1(a_i)$ for some $1 \leq i \leq k$.}
 \end{algorithm}
 
-\noindent In particular, if the output of Algorithm \ref{alg:mainalgorithm} is the empty set, then $j$ is not an isolated $j$-invariant.
-
-One of the key filters we use is based on \cite[Theorem 4.3]{BELOV}.
-
-\begin{theorem}[\cite{BELOV}]
-Let $f: C \rightarrow D$ be a finite map of curves, let $x \in C$ be a closed point, and let $y=f(x)\in D$. Assume that $\deg(x)=\deg(y)\cdot \deg(f)$.
-\begin{enumerate}
-\item If $x$ is $\PP^1$-isolated, then $y$ is $\PP^1$-isolated.
-\item If $x$ is AV-isolated, then $y$ is AV-isolated.
-\item $x$ is sporadic, then $y$ is sporadic.
-\end{enumerate}
-\end{theorem}
-
-\noindent Since the image of the adelic Galois representation of a non-CM elliptic curve $E/\Q$ has finite level, this theorem reduces the problem of determining whether $j(E)$ is isolated to the problem of determining whether $E$ gives rise to an isolated point on a finite number of modular curves.
-While a sufficient finite list can be deduced directly from the adelic level as found by Zywina's Algorithm~\cite{ZywinaAlgorithm}, our \dldedit{approach attempts to reduce the size of this list as much as possible}.
-This inspires the notion of \textbf{primitive points} on modular curves, as studied in Section \ref{sec:PrimitivePoints}.
-In particular, $j(E)$ is isolated if and only if there exists an isolated primitive point corresponding to $E$.
-Moreover, any point $x\in X_1(N)$ with $j(x)=j(E)$ corresponds to a \emph{unique} primitive point (Proposition \ref{Prop:single_sink}).
-
-The second part of Algorithm \ref{alg:mainalgorithm} works to show the primitive points corresponding to $E$ are \emph{not} isolated.
-For example, if the Riemann-Roch space associated to $x \in X_1(N)$ with $j(x)=j(E)$ has dimension at least 2, then $x$ is not $\PP^1$-isolated (and hence not isolated).
-In other cases, we can show $x \in X_1(N)$ is not isolated by applying the following result.
-
-\begin{proposition} \label{Prop:Genus0Intro}
-Let $E/\Q$ be an elliptic curve, and let $H \leq \GL_2(\Z/N\Z)$ be the image of the mod $N$ Galois representation of $E$, after some choice of basis.
-If the modular curve $X_H$ has genus 0, then there are no isolated points on $X_1(N)$ associated to $E$.
-\end{proposition}
-
-\noindent In particular, this result implies any elliptic curve with adelic image of genus 0 does not give rise to any isolated points on $X_1(N)$, even as $N$ ranges over all positive integers.
-However, even when the adelic image of $E$ has positive genus, it can still be that $\im \rho_{E,N}$ has genus 0 for all $N$ corresponding to primitive points.
-This makes Proposition \ref{Prop:Genus0Intro} more broadly applicable.
-
-Running Algorithm \ref{alg:mainalgorithm} on all elliptic curves currently in the $L$-functions and Modular Forms Database (LMFDB) \cite{LMFDB} gives a list of 95 $j$-invariants which require further consideration; see the Appendix.
-\abbey{I think we should build Prop.
-\ref{Prop:Genus0Intro} into the algorithm.
-Would need to update to mention only Table 1 instead.} After applying certain additional filters to address special cases, as discussed in Section~\ref{sec:remainingfilters}, we arrive at the following result.
+Algorithm \ref{alg:mainalgorithm} proceeds by computing the image of the adelic Galois representation associated to $E/\Q$ with $j(E)=j$ using an algorithm of Zywina \cite{ZywinaAlgorithm}, which allows us to enumerate a finite set of levels $N$ for which there can possibly exist an isolated point on $x \in X_1(N)$ with $j(x)=j$.
+We then apply various filters to each $N$ in this set in an attempt to rule out the possibility that $j$ comes from on isolated point on $X_1(N)$.
+
+The set of levels produced at the first step tends to be redundant, in the sense that in many cases, an isolated point can only exist on $X_1(N)$ if it maps down an isolated point on $X_1(N^\prime)$ for some $N^\prime \mid N$ which is also in the set.
+To this end, we develop a notion of \emph{primitive degrees}, which allows us to reduce our initial set of levels to a set of minimal levels, greatly reducing to number of levels we need to attempt to rule out.
+See Section \ref{sec:primitivedeg} for more details.
+
+In some cases, such as when the output of Algorithm \ref{alg:mainalgorithm} is the empty set, we can immediately say that $j$ does not come from an isolated point.
+When the set returned by Algorithm \ref{alg:mainalgorithm} is non-empty, we can attempt to perform additional calculations on a case-by-case basis to determine whether each point of degree $d_i$ on $X_1(a_i)$ associated to $E$ is isolated, which in some cases allows us to definitively determine whether or not $j$ comes from an isolated point.%is an isolated $j$-invariant.%See Section \ref{sec:remainingfilters} for more details.
+
+We ran Algorithm \ref{alg:mainalgorithm} on all elliptic curves currently in the $L$-functions and Modular Forms Database (LMFDB) \cite{LMFDB} and were able to determine the following:
 
@@
 \end{itemize}
-Then $j(E) \in \{-140625/8,-9317,351/4, -162677523113838677\}$.
-Moreover, each one of these $j$-invariants corresponds to a $\PP^1$-isolated point on $X_1(21)$, $X_1(37)$, $X_1(28)$, and $X_1(37)$, respectively.
+Then $j(E) \in \{-140625/8,-9317,351/4, -162677523113838677\}$.% Moreover, each one of these $j$-invariants corresponds to a $\PP^1$-isolated point on $X_1(21)$, $X_1(37)$, $X_1(28)$, and $X_1(37)$, respectively.
 \end{theorem}
 
-Based on these results, we conjecture that the four non-CM isolated $j$-invariants identified above are in fact the \emph{only} $j$-invariants in $\Q$ associated to non-CM elliptic curves which give rise to $\PP^1$-isolated points.
-Since any CM elliptic curve is known to produce sporadic points on infinitely many modular curves of the form $X_1(N)$ by \cite[Theorem 7.1]{BELOV}, it follows conversely that every $j$-invariant in this set is isolated.
+If $x \in X_1(N)$ is a sporadic (resp.
+isolated/$\PP^1$-isolated) point, we say $j(x) \in X_1(1) \cong \mathbf{P}^1$ is a \textbf{sporadic} (resp.
+\textbf{isolated}/\textbf{$\PP^1$-isolated}) \textbf{$j$-invariant}.
+Running Algorithm \ref{alg:mainalgorithm} on all elliptic curves in the LMFDB immediately showed that all but 6 of the non-CM $j$-invariants in $\Q$ are \emph{not} isolated.
+Since three of these remaining $j$-invariants were already known to be isolated (see below), it was only necessary to do a case-by-case analysis on 3 rational $j$-invariants, 2 of which were found to be non-isolated and the last of which is the final $j$-invariant in the theorem; see Section~\ref{sec:remainingfilters}.
+
+The origins of the 4 $j$-invariants in Theorem \ref{LMFDBoutputThm} are as follows:
+
+\begin{itemize}
+    \item The elliptic curve with $j$-invariant $-140625/8$ corresponds to two sporadic points of degree 3 on $X_1(21)$.
+This example was first discovered by Najman \cite{najman16}.
+In fact, this is the unique elliptic curve giving a sporadic point of degree at most 3 on \emph{any} modular curve $X_1(N)$, as shown in work of Derickx, Etropolski, van Hoeij, Morrow, and Zureick-Brown \cite{DEvHMZB2021}.
+
+    \item The elliptic curve with $j$-invariant $-9317$ gives three points of degree 6 on $X_1(37)$, as in work of van Hoeij \cite{vanHoeij}.
+Since 6 is less than half the $\Q$-gonality of $X_1(37)$, as computed in \cite{DerickxVanHoeij2014}, the points are necessarily sporadic by work of Frey \cite{frey}.
+
+    \item The elliptic curve with $j$-invariant $351/4$ gives an isolated point of degree 9 on $X_1(28)$; see \cite[Theorem 2]{OddDeg}.
+There are infinitely many points on $X_1(28)$ of degree 6, as shown in \cite{DerickxVanHoeij2014}, so this point is isolated but not sporadic.
+
+    \item The elliptic curve with $j$-invariant $-162677523113838677$ comes from a degree 18 point on $X_1(37)$ that was well-known prior to this work.
+It corresponds to one of the two non-CM elliptic curves over $\Q$ with a rational cyclic 37-isogeny, and any elliptic curve with a $\Q$-rational cyclic $N$-isogeny will give a point on $X_1(N)$ in degree at most $\varphi(N)/2$.
+However, it does not appear to have been previously observed that the point on $X_1(37)$ is $\PP^1$-isolated.
+\end{itemize}
+
+Thus the first three $j$-invariants above are isolated $j$-invariants, all four are $\PP^1$-isolated $j$-invariants, and $-140625/8$  and $-9317$ are also sporadic $j$-invariants.
+
+%We conjecture that the four non-CM isolated $j$-invariants identified above are in fact the \emph{only} $j$-invariants in $\Q$ associated to non-CM elliptic curves which give rise to $\PP^1$-isolated points on $X_1(N)$.
+We conjecture that the four non-CM isolated $j$-invariants identified above are in fact the \emph{only} $j$-invariants in $\Q$ associated to non-CM elliptic curves which are $\PP^1$-isolated.
 
 \begin{conjecture}\label{conj}
-If $x\in X_1(N)$ is a $\PP^1$-isolated point with $j(x) \in \Q$, then $j(x)=-140625/8$, $-9317$, $351/4$, $-162677523113838677$, or one of the 13 CM $j$-invariants in $\Q$.
+If $x\in X_1(N)$ is a $\PP^1$-isolated point with $j(x) \in \Q$, then $j(x)=-140625/8$, $-9317$, $351/4$, $-162677523113838677$, or one of the $13$ CM $j$-invariants in $\Q$.
 \end{conjecture}
+
+Conjecture \ref{conj} has already been established for points of odd degree: by \cite{OddDeg} we know that $j=-140625/8$ and $j=351/4$ are the only non-CM $j$-invariants in $\Q$ giving an isolated point of odd degree on $X_1(N)$, even as $N$ ranges over all positive integers.
+
 \begin{remark}
-\filip{New remark.}
-Let $x\in X_1(N)$ be a $\PP^1$-isolated point with $j(x) \in \Q$.
-One expects that the square-free part of the conductor of any $E$ with $j(E)=j(x)$ will be very small.
-The reason for this is that any such isolated point will necessarily have small mod $p$ image for some $p$ dividing $N$.
-This in turn forces potentially good reduction on $E$ in all primes, except possibly for $p=2$, see \cite[Corollary 4.4]{Mazur1978} for one (out of many) example of this phenomenon.
-Indeed this is the case for all the curves appearing in \Cref{conj}; their conductors are either a square, or twice a square.
-
-Hence one might except to find most or all of the $\PP^1$-isolated points among elliptic curves with relatively small conductor (and hence in the LMFDB).
-This observation perhaps makes the computational evidence supporting \Cref{conj} more convincing.
+        In his famous Open Image paper, Serre asked whether there exists some constant $C$ such that the mod $\ell$ Galois representation of any non-CM elliptic curve over $\Q$ is surjective for all primes $\ell>C$.
+Serre's question is widely believed to have an affirmative answer, and it has formally been conjectured by both Sutherland \cite{sutherland} and Zywina \cite{ZywinaImages} that $C = 37$.
+Assuming such a constant exists, Corollary 1.7 in \cite{BELOV} then shows that there are only finitely many $j$-invariants in $\Q$ coming from isolated points on $X_1(N)$ as $N$ ranges over all positive integers.
+The novel content of Conjecture \ref{conj} is that the given list is complete with respect to $\PP^1$-isolated points.
+We expand on why we expect this to be the case in Section \ref{conj_motivation}.
 \end{remark}
 
+%\abbey{Connect to Zywina's exceptional set of $j$-invariants?
+Specifically, can show that any isolated $j$-invariant must correspond to an exceptional rational point on $X_H$, where $H$ is an ``agreeable" subgroup?
+See Theorem 1.9 in \cite{ZywinaAlgorithm}.
+It seems to me that his Conjecture 1.5 is coming from the belief that he's found all the exceptional non-CM rational points corresponding to agreeable subgroups.
+I emailed him to ask for clarification on this point...
+while he replied to my first email, it turned out my question wasn't precise enough.
+I have not received a reply to my followup.}
+
 We say a point $x \in X_0(N)(\Q)$ is \textbf{exceptional} if $X_0(N)(\Q)$ is finite and $x$ corresponds to a non-CM elliptic curve over $\Q$.
-It is worth noting that the sporadic points on $X_1(21)$ associated to $j=-140625/8$ and the sporadic points on $X_1(37)$ associated to $j=-9317$ lie above exceptional points on $X_0(21)$ and $X_0(37)$, respectively.
-Thus it is natural to ask whether there exist other sporadic \abedit{$j$-invariants corresponding to} exceptional rational points on $X_0(N)$.
-Running Algorithm~\ref{alg:mainalgorithm} on the 14 $j$-invariants corresponding to exceptional rational points on $X_0(N)$ (see, for example, \cite[Table 4]{LRAnn}) shows that there are no additional sporadic $j$-invariants in this set.
+It is worth noting that the sporadic points on $X_1(21)$ associated to $j=-140625/8$ and the sporadic points on $X_1(37)$ associated to $j=-9317$ lie above exceptional rational points on $X_0(21)$ and $X_0(37)$, respectively.
+It is natural to ask whether other sporadic $j$-invariants can be obtained by a similar construction.
+Running Algorithm~\ref{alg:mainalgorithm} on the 14 $j$-invariants corresponding to exceptional rational points on $X_0(N)$ (see, for example, \cite[Table 4]{LRAnn}) shows that there are no additional sporadic $j$-invariants.
 \begin{theorem}
-Let $E$ be an elliptic curve corresponding to an exceptional rational point on $X_0(N)$ for some positive integer $N$. \abedit{If $j(E)$ is sporadic, then $j(E)=-140625/8$ or $-9317$.}
+Let $E$ be an elliptic curve corresponding to an exceptional rational point on $X_0(N)$ for some positive integer $N$. If $j(E)$ is sporadic, then $j(E)=-140625/8$ or $-9317$.
 \end{theorem}
@@
 
+\subsection{Key Components of Algorithm.} The first step of our algorithm applies results of \cite{BELOV} and \cite{ZywinaAlgorithm} to compute the finite set of \textbf{primitive points} associated to a non-CM elliptic curve $E/\Q$.
+The primitive points are characterized by the following theorem.
+
+\begin{theorem}\label{Thm:PrimPtsIntro}
+Let $E/\Q$ be a non-CM elliptic curve.  There exists a finite set $\mathcal{P}=\mathcal{P}(E)$ of primitive points in $\cup_{n \in \Z^+} X_1(n)$ characterized by the following properties:
+\begin{enumerate}
+\item For each $N\in \Z^+$, a point $x \in X_1(N)$ with $j(x)=j(E)$ corresponds to a unique element $x' \in \mathcal{P}$ under the natural projection map.
+Moreover, if $x' \in X_1(a)$, then $a \mid N$ and $\deg(x)=\deg(f)\cdot \deg(x')$, where $f: X_1(N) \rightarrow X_1(a)$ is the natural map.
+\item The rational number $j(E)$ is isolated if and only if there exists an isolated point in $\mathcal{P}$.
+\end{enumerate}
+Moreover, the set $\mathcal{P}$ is minimal with respect to conditions (i) and (ii).
+\end{theorem} 
+\noindent By Theorem~\ref{Thm:PrimPtsIntro}\,(i), one can think of $\mathcal{P}(E)$ as the minimal set needed to reproduce the degrees of all points $x \in \cup_{n \in \Z^+} X_1(n)$ with $j(x) = j(E)$.
+See Section \ref{sec:PrimitivePoints} for details.
+
+The second part of Algorithm \ref{alg:mainalgorithm} works to show the primitive points corresponding to $E$ are \emph{not} isolated.
+For example, if the Riemann--Roch space associated to $x \in X_1(N)$ has dimension at least 2, then $x$ is not $\PP^1$-isolated (and therefore not isolated).
+In other cases, we can show $x \in X_1(N)$ is not isolated by applying the following result.
+
+\begin{theorem} \label{Prop:Genus0Intro}
+Let $E/\Q$ be an elliptic curve, and let $H \leq \GL_2(\Z/N\Z)$ be the image of the mod $N$ Galois representation of $E$, after some choice of basis.
+If the modular curve $X_H$ has genus 0, then there are no isolated points on $X_1(N)$ associated to $E$.
+\end{theorem}
+
+\noindent In particular, any elliptic curve with adelic image of genus 0 does not give rise to any isolated points on $X_1(N)$, even as $N$ ranges over all positive integers.
+However, Theorem \ref{Prop:Genus0Intro} is more broadly applicable.
+Even when the adelic image of $E$ has positive genus, it can still be that for all primitive points $x \in X_1(a)$ associated to $E$, the mod $a$ Galois representation of $E$ gives a genus 0 modular curve.
+This occurs more often than one might expect: our preliminary computations identified at least 89 examples, just within non-CM elliptic curves currently in the LMFDB.
+
+\subsection{Connection to Open Uniformity Problems}\label{sec:UniformityConnections} Several well-known uniformity problems can be tied to isolated points on $X_1(N)$.
+One of the most longstanding examples is Serre's Uniformity Problem \cite[\S\,4.3]{serre72}, which in modern formulations \cite{sutherland,ZywinaImages} asks whether the mod $\ell$ Galois representation for any non-CM elliptic curve over $\Q$ is surjective for all $\ell>37$.
+In the proof of \cite[Theorem~1.3]{BourdonNajman2021}, the authors show that a non-CM elliptic curve $E/\Q$ with non-surjective mod $\ell$ Galois representation can be used to construct sporadic points on $X_1(\ell^2)$ for all $\ell$ sufficiently large.
+This approach allows one to phrase Serre's Uniformity Problem as one about controlling isolated points on $X_1(\ell^2)$ within certain families of non-CM $\Q$-curves.
+
+A more recent example is \cite[Conjecture 17]{BalakrishnanMazur23}, where Balakrishnan and Mazur conjecture that for sufficiently large $N$, any elliptic curve giving a quadratic point on $X_0(N)$ must have complex multiplication.
+Since a quadratic point on $X_0(N)$ will give a sporadic point on $X_1(N)$ for $N$ sufficiently large, we can connect this conjecture to one about non-CM isolated points $x \in X_1(N)$ with $j(x)$ generating at most a quadratic extension.
+
 \subsection{Outline}
-After providing relevant background material in Section \ref{sec:background}, we establish  preliminary mathematical results on genus 0 adelic images ($\S$\ref{sec:genus0}) and primitive points on modular curves ($\S$\ref{sec:PrimitivePoints}).
-We give an overview of the main algorithm in Section \ref{sec:mainalg}, with key sub-algorithms described in detail in Sections \ref{sec:madicrep} and \ref{sec:primitivedeg}.
+After providing relevant background material in Section \ref{sec:background}, we give an overview of the main algorithm in Section \ref{sec:mainalg}.
+The sub-algorithms used to compute primitive points and related mathematical results are discussed in Sections \ref{sec:madicrep}--\ref{sec:primitivedeg}, with the proof of Theorem \ref{Thm:PrimPtsIntro} appearing in Section \ref{sec:PrimitivePoints}.
+Results on genus 0 adelic images, including the proof of Theorem \ref{Prop:Genus0Intro}, are in Section \ref{sec:genus0}.
 We address the validity of Algorithm \ref{alg:mainalgorithm} in Section \ref{sec:validity}.
-The output of the algorithm and its final analysis is discussed in Section \ref{sec:remainingfilters}.
+The output the main algorithm obtained after running it on all elliptic curves in the LMFDB and its final analysis is discussed in Section \ref{sec:remainingfilters}.
 
@@
 We thank Pete Clark, Maarten Derickx, Jeremy Rouse, and David Zureick-Brown for helpful conversations.
-\dld{Perhaps we also give an explicit shoutout to Zywina for making his code public too?}
+\dld{Perhaps we also give an explicit shoutout to Zywina for making his code public too?}\abbey{sure, can you add what you had in mind?}
 
@@
 To any closed point $x \in C$ of degree $d$ we associate the $k$-rational effective divisor
-\[
- x=P_1+ \cdots +P_{d},
+\travis{should this be $D$?
+or below, should $D$ be $x$?} \dld{Yes, this should be $D$ I think.} \abbey{no, here $x$ is irreducible b/c it's a closed point of degree $d$, whereas $D$ below is an abritrary effective divisor of degree $d$} \filip{Well, if we're associating $D$ to $x$ in the way described below, then $D$ will have to be irreducible since $x$ is of degree $d$, or I am misunderstanding someothing here.} \abbey{Yes, the divisor associated to $x$ will be irreducible...
+originally it was just notated as $x$ in the offset equation below.
+My objection to using $D$ here \textbf{and} in the definition of $\Phi_d$ is that I don't want people to think the map $\Phi_d$ is only defined on irreducible divisors.
+I'm trying to define $\Phi_d$ in general below.}
+\[
+ \dldedit{D}=P_1+ \cdots +P_{d} \abbey{\text{ Originally denoted $x$, not $D$.}}, 
 \] 
@@
 \end{align}
-which sends the effective divisor $D$ of degree $d$ to the class $[D - dP_0]$, where $P_0 \in C(k)$.
+which sends \abedit{an} effective divisor $D$  \abbey{In the start of the paragraph, $x$ is a closed point of degree $d$ and hence an \textbf{irreducible} effective divisor of degree $d$.
+But $C^{(d)}$ contains \emph{all} effective divisors of degree $d$, not just the irreducible ones.
+So here $D$ is meant to denote an arbitrary effective divisor and thus is more general than $x$.} of degree $d$ to the class $[D - dP_0]$, where $P_0 \in C(k)$.
 If $\Phi_d(x)=\Phi_d(y)$ for some other point $y \in C^{(d)}(k)$, then there exists a non-constant function $f \in k(C)^{\times}$ with $\text{div}(f)=x-y$.
 Since $x$ is a degree $d$ point and $x\not=y$, $x$ and $y$ have distinct support so $f: C \rightarrow \mathbf{P}^1_{k}$ is a dominant morphism of degree $d$.\footnote{In particular, this shows $\Phi_d$ is injective if $d$ is less than the $k$-gonality of $C$, which is the least degree of a non-constant rational map to $\mathbf{P}^1$.} By Hilbert's irreducibility theorem \cite[Chapter 9]{serre97}, $f^{-1}(\mathbf{P}^{1}(k))$ will contain infinitely many closed points of degree $d$.
-On the other hand, if $\Phi_d$ is injective on closed points of degree $d$, then by Faltings' Theorem \cite{faltings} there can exist infinitely many such points only if all but finitely many are parametrized by translates of positive rank abelian subvarieties of $\Jac(C)$.
+On the other hand, if $\Phi_d$ is injective on closed points of degree $d$, \abedit{then Faltings' Theorem \cite{faltings} implies all but finitely many such points are parametrized by translates of positive rank abelian subvarieties of $\Jac(C)$.} This inspires the following:
+
+%there can exist infinitely many such points only if all but finitely many are parametrized by translates of positive rank abelian subvarieties of $\Jac(C)$.
 \sachi{or maybe: Suppose $\Phi_d$ is injective on closed points of degree $d$.
 Then Faltings' theorem \cite{faltings} implies all but finitely many such points are parametrized by translates of positive rank abelian subvarieties of $\Jac(C)$.}
-This inspires the following:
 
@@
 \begin{enumerate}
-\item []
-\item A closed point $x \in C$ of degree $d$ is $\PP^1$\textbf{-parametrized} if there exists a point $x' \in C^{(d)}(k)$ such that $\Phi_d(x)=\Phi_d(x')$.
+\item A closed point $x \in C$ of degree $d$ is $\PP^1$\textbf{-parametrized} if there exists a point $x' \in C^{(d)}(k)$ with $x' \neq x$ such that $\Phi_d(x)=\Phi_d(x')$.
 Otherwise, we say $x$ is $\PP^1$\textbf{-isolated}.
@@
 The curve $X_H$ is a scheme over $\text{Spec }\Z[1/N]$ and parametrizes generalized elliptic curves with $H$-level structure.
-\abedit{In particular, its $k$-rational points roughly classify elliptic curves over $k$ whose mod $N$ image is contained in $H$}; see, for example, \cite[$\S2.3$]{RSZB2022} for details.
+In particular, its $k$-rational points roughly classify elliptic curves over $k$ whose mod $N$ image is contained in $H$; see, for example, \cite[$\S2.3$]{RSZB2022} for details.
 If we take
@@
 
-\abedit{We may also define a modular curve associated to an open subgroup $G$ of $\GL_2(\widehat{\Z})$.
+We may also define a modular curve associated to an open subgroup $G$ of $\GL_2(\widehat{\Z})$.
 For any $N \in \Z^+$, let $\pi:\GL_2(\widehat{\Z}) \rightarrow \GL_2(\Z/N\Z)$ be the natural projection map, and define $G(N) \coloneqq \pi(G)$.
-We say $G$ has \textbf{level} $N$ if $G=\pi^{-1}(G(N))$ and $N$ is minimal with respect to this property.} If $\det(G)=\widehat{\Z}^{\times}$, we define the modular curve $X_G \coloneqq X_{G(N)}$.
+We say $G$ has \textbf{level} $N$ if $G=\pi^{-1}(G(N))$ and $N$ is minimal with respect to this property.
+If $\det(G)=\widehat{\Z}^{\times}$, we define the modular curve $X_G \coloneqq X_{G(N)}$.
 If $G=\GL_2(\widehat{\Z})$, then we identify $X_G \cong \PP^1$ with the $j$-line.
 
-\subsection{Closed Points on Modular Curves}\abbey{I updated the first 2 paragraphs of this section.} To discuss isolated points on modular curves, we must consider closed points on $X_1(N)$, viewed always as a scheme over $\Q$.
+\subsection{Closed Points on Modular Curves} To discuss isolated points on modular curves, we must consider closed points on $X_1(N)$, viewed always as a scheme over $\Q$.
 Let $k$ be a field with an embedding of $k$ into $\overline \Q$.
@@
 We denote this $k$-valued point by $(E,P)_k$, and by definition it corresponds to a morphism of $\Q$-schemes $f:\text{Spec } k \rightarrow X_1(N)$.
-The map $f$ sends the unique point of $\text{Spec } k$ to a point $x \in X$, and we call $x$ the \textbf{closed point} associated to $(E,P)$.\footnote{Note $x$ is indeed closed since $\Q(x)/\Q$ is finite; see, for example, \cite[Exercise 5.9, p.76] {Liu2002}.} We define the \textbf{degree} of $x$ to be the degree of the residue field $\Q(x)$ over $\Q$.
+The map $f$ sends the unique point of $\text{Spec } k$ to a point $x \in X$, and we call $x$ the \textbf{closed point} associated to $(E,P)$.\footnote{Note $x$ is indeed closed since $\Q(x)/\Q$ is finite; see, for example, \cite[Exercise~5.9, p.~76] {Liu2002}.} We define the \textbf{degree} of $x$ to be the degree of the residue field $\Q(x)$ over $\Q$.
 Since there are many scheme-valued points which induce the same closed point, it is sometimes preferable to consider Galois orbits of points in $X_1(N)(\overline{\Q})$, which are in bijection with the set of closed points.
@@
 However, there always exists $E'/\Q(x)$ with $j(E')=j(E)$ and $P' \in E'(\Q(x))$, where the point $P' \in E'$ maps to $P \in E$ under a $\overline \Q$-isomorphism sending $E$ to $E'$.
-See \cite[p.
-274, Proposition VI.3.2]{DR}.
+See \cite[p.~274, Proposition~VI.3.2]{DR}.
 The pair $(E',P')$ gives a $\Q(x)$-valued point, and it is the unique $\Q(x)$-valued point such that $(E,P)_{k}=(E',P')_{k}.$
@@
 
-\abbey{Add Shimura definition of $\mathfrak{h}$.}
-
-\begin{remark}\label{ResidueFieldRmk} In particular, if $E/\Q(j(E))$ does not have complex multiplication and $P=(x_0,y_0)$, then one can take $\Q(x)\cong\Q(j(E),x_0)$. See \cite[p. 107]{shimura}.
+ \begin{remark}\label{ResidueFieldRmk}\abedit{At times, it can be useful to work with an explicit model-independent formulation of a Weber function.
+For example, if $E:y^2=4x^3-c_2x-c_3$ and $j(E)\neq 0,1728$, we can define
+\[
+\mathfrak{h}((x,y))=\frac{c_2c_3}{\Delta}x,
+\]
+where $\Delta=c_2^3-27c_3^2$. One can verify:
+\begin{enumerate}
+    \item We have $\mathfrak{h}(P)=\mathfrak{h}(P')$ if and only if $P=\xi P'$ for some $\xi \in \Aut(E)$.
+    \item If $\eta: E \rightarrow E'$ is an isomorphism, then $\mathfrak{h}_E=\mathfrak{h}_{E'}\circ \eta$.
+\end{enumerate}
+See \cite[p. 107]{shimura}.} In particular, if $E/\Q(j(E))$ does not have complex multiplication and $P=(x_0,y_0)$, then one can take $\Q(x)\cong\Q(j(E),x_0)$. 
 \end{remark}
@@
 On the other hand, let $E_2:y^2=x^3-43x-166$ and $P_2=(5,i\sqrt{256})$ a point of order 7.
-Then $(E_2,P_2)$ gives a $\Q(i)$-valued point on $X_1(7)/\Q$ and also a closed point $x\in X_1(7)$ of degree 1 by \abedit{Remark \ref{ResidueFieldRmk}}.
+Then $(E_2,P_2)$ gives a $\Q(i)$-valued point on $X_1(7)/\Q$ and also a closed point $x\in X_1(7)$ of degree 1 by Remark \ref{ResidueFieldRmk}.
 In fact, both $(E_1,P_1)$ and $(E_2,P_2)$ induce the same geometric point on $X_1(7)$ since $(E_1,P_1)_{\overline{\Q}}=(E_2,P_2)_{\overline{\Q}}$.
@@
                 \]
-                where $c_{f}=1/2$ if $a \leq 2$ and $ab>2$ and $c_{f}=1$ otherwise.
+                where $c_{f}=\frac{1}{2}$ if $a \leq 2$ and $ab>2$ and $c_{f}=1$ otherwise.
     \end{corollary}
@@
 From this we can obtain two other Galois representations.
-On the one hand, fixing a positive integer $m$, we can choose to record the action of $\Gal_k$ on points \abedit{whose order is divisible only by those primes dividing $m$}.
+On the one hand, fixing a positive integer $m$, we can choose to record the action of $\Gal_k$ on points whose order is divisible only by those primes dividing $m$.
 This is the \textbf{$m$-adic Galois representation} associated to $E$:
@@
 In particular, if $m=\ell$ is a prime number, we recover the standard $\ell$-adic representation associated to $E$.
-Alternatively, we may wish to record Galois action only on points of order dividing $m$; we use $E[m]$ to denote the finite subgroup of such points.
+Alternatively, we may wish to record the Galois action only on points of order dividing $m$; we use $E[m]$ to denote the finite subgroup of such points.
 This gives the \textbf{mod $m$ Galois representation} associated to $E$,
@@
 Though $\rho_E$ is never surjective when $k=\Q$, this can occur for elliptic curves defined over number fields of higher degree \cite[Theorem 1.2]{Greicius2010}.
+
+\section{Overview of the Main Algorithm}
+\label{sec:mainalg}
+The following algorithm is the main procedure for determining whether a given non-CM $j$-invariant in $\Q$ is the image of a $\PP^1$-isolated point on $X_1(N)$ for some $N$ based on results in \cite{BELOV,ZywinaAlgorithm}.
+We note that for any CM $j$-invariant $j$, there exists infinitely many $N\in\Z^+$ for which there is a sporadic point $x\in X_1(N)$ with $j(x)=j$ by \cite[Theorem 7.1]{BELOV}, so it is not necessary to consider them in this algorithm.
+The outline below gives an overview of the structure, while the algorithms to perform particular steps are described in detail in Sections \ref{sec:madicrep} and \ref{sec:primitivedeg}.
+We will prove a theorem on the validity of Algorithm \ref{alg:mainalgorithm} in Section \ref{sec:validity}.
+
+\setcounter{algocf}{0}
+\begin{algorithm}[h!]
+\caption{Main Algorithm}\label{alg:mainalgorithm}
+\KwIn{A non-CM $j$-invariant $j \in \Q$.}
+\KwOut{A finite list $\{( a_1,d_1), \dots, (a_k,d_k)\}$ such that any isolated point $x \in X_1(N)$ with $j(x)=j$ maps down under the natural projection map to an isolated point of degree $d_i$ on $X_1(a_i)$ for some $1 \leq i \leq k$.}
+Construct an elliptic curve $E/\Q$ with $j(E)=j$.\\
+Compute the adelic image $G$ of $E/\Q$ as a subgroup of $\GL_2(\hat{\Z})$ using Zywina's algorithm \cite{ZywinaAlgorithm}.
+Represent the output as the level $N$ and the subgroup $G(N)$ of $\GL_2(\Z/N\Z)$.\\
+Apply Algorithm \ref{alg:reduce_level} to $G(N)$ to obtain the level $m_0$ of the $m$-adic Galois representation associated to $E$, where $m$ is the product of 2, 3, and all non-surjective primes.\\
+Using Algorithm \ref{alg:compute_prim_degree}, return a multiset $D$ with entries $\langle n, (a, d) \rangle$
+    for all positive divisors $n$ of $m_0$ such that the closed point on $X_1(n)$ associated to $E$ lies above the primitive point on $X_1(a) $
+    of degree $d$.\\
+Construct the multiset $D' \subseteq D$ containing only those elements $\langle n, (a, d)\rangle$ for which $d \leq \text{genus}(X_1(a))+1$.\\
+Create the multiset $M$ consisting of all pairs $(a_i,d_i)$ appearing in $D'$, where $(a_i,d_i) $ has multiplicity $\mu$ if and only if $X_1(a_i)$ has $\mu$ distinct closed points of degree $d_i$.\\
+\abbey{Add genus 0 check for each mod $a_i$ image.}\\
+\Return{$[j,M]$}
+
+\end{algorithm}
+
+In particular, note that if Algorithm \ref{alg:mainalgorithm} outputs $\{\}$, then $j$ is not the image of any $\mathbf{P}^1$-isolated point on $X_1(N)$, even as $N$ ranges over all positive integers.
+See Corollary \ref{cor:P1_isolated}.
+
+\begin{example}
+If $j=-9317$, then Algorithm \ref{alg:mainalgorithm} returns $ \{(37,6) ^3\}$.
+This means that any isolated point $x\in X_1(N)$ with $j(x)=j$ and $N \in \Z^+$ maps down under the natural projection map to one of the 3 closed points of degree 6 on $X_1(37)$.
+In fact, these points are all sporadic by \cite[Proposition 2]{frey}, since $6 < \frac{1}{2} \gon_{\Q}(X_1(37)) = 18$.
+Here, the gonality computation is a result of \cite{DerickxVanHoeij2014}.
+Thus $j$ is a sporadic --- and hence isolated --- $j$-invariant.
+\end{example}
+
+\begin{example}
+If $j=-121$, then Algorithm \ref{alg:mainalgorithm} returns $\{\}$. This means that there are no isolated points on $X_1(N)$ associated to this $j$-invariant.
+\end{example}
+
+\begin{example}
+If $j=-882216989/131072$, then Algorithm \ref{alg:mainalgorithm} returns  $\{( 17,4) ^2\}$.
+This means that $j$ is associated to an isolated point on a modular curve of the form $X_1(N)$ if and only if there exists a degree 4 isolated point $x \in X_1(17)$ with $j(x)=j$.
+In Section \ref{sec:remainingfilters}, we will show that no such isolated point exists, from which we can conclude that $j$ is not an isolated $j$-invariant.
+\end{example}
 
@@
 
-\section{Genus 0 adelic images do not produce isolated points}
-\label{sec:genus0images}
-
-\abbey{I moved this from the end.}
-\label{sec:genus0}
-Let $E/\Q$ be an elliptic curve and $G\in \GL_2(\hat \Z)$ its adelic image.
-Let $G(N)$ denote the image of its mod $N$ representation.
-Denote by $B_1(N)$ the subgroup of $\GL_2(\Z/N\Z)$ consisting of the upper triangular matrices with a $1$ in the upper left entry.
-Note that $X_{B_1(N)}=X_1(N)$.
-We say that a congruence group $\Gamma$ is of genus $g$ if $X_\Gamma$ is of genus $g$.
-We say that a point $P$ corresponds to an elliptic curve $E$ if $j(P)=j(E)$.
-\sedit{In this section, we show that elliptic curves with genus $0$ mod $N$ image  do not correspond to $\PP^1$-isolated points on $X_1(N)$.}
-
-\abbey{Do we want to add a check for this as part of our main algorithm?
-That is, if $\langle a, d\rangle$ appears in our list indicating that $E$ gives a possibly isolated point on $X_1(a)$ of degree $d$, should we check whether $X_{\im \rho_{E,a}}$ has genus 0?
-If so, $\langle a, d\rangle$ can be removed from the list.
-Then the long list currently in the appendix could be removed, since Table 1 would suffice.}
-
-\begin{lemma} \label{lem:map to Symd}
-Let $f\colon X \to Y$ be a finite morphism of curves of degree $d$. Then $f$ induces a non-constant morphism $f^*\colon Y \to X^{(d)}$.
-\end{lemma}
-\begin{proof}
-    See~\cite[Theorem~3.13]{MilneJV}. The morphism is non-constant since fibers above different points are mapped to different points.
-\end{proof}
-
-Note that a rational map from $\PP^1$ to a smooth variety of degree $1$ extends uniquely to a morphism (by the valuative criterion of properness) and is an isomorphism onto its image since a genus $0$ curve cannot have singularities.
-The symmetric powers of a smooth projective curve are smooth~\cite[Proposition~3.2]{MilneJV}.
-
-\begin{lemma} \label{lem:iso1}
-Let $X$ be a curve with a copy of $\bP^1$ inside $X^{(d)}$ and let $x\in X^{(d)}(\Q)$ be irreducible and lying on the image of $\PP^1$ inside of $X^{(d)}$. Then $x$ is not $\PP^1$-isolated.
-\end{lemma}
-\begin{proof}
-The restriction of the map $\Phi_d:X^{(d)}\rightarrow \Jac (X)$ to the image of $\PP^1$ inside $X^{(d)}$ factors through $\Jac(\PP^1)=\{0 \}$ by the Albanese property of the Jacobian, so it contracts the $\PP^1$ to a point on $\Jac(X)$.\footnote{Or because abelian varieties contain no positive dimensional rational varieties~\cite[Corollary~3.9]{MilneAV}.} Hence $\Phi_d(y) = \Phi_d(x)$ for any $y$ lying on this image of $\PP^1$.
-\end{proof}
-
-\begin{lemma} \label{lem:iso2}
-Let $f: X\rightarrow Y$ be a finite morphism of curves and $x$ a point on $X$, and assume  $\deg x = \deg f(x)$. If $x$ is not $\PP^1$-isolated, then neither is $f(x)$.
-\end{lemma}
-\begin{proof}
-If $x$ is not $\bP^1$-isolated (i.e., $x$ is $\bP^1$-parametrized), then
-by Lemmas \ref{lem:iso1} and \ref{lem:iso2} $x$ lies on a $\PP^1$ inside of $X^{(d)}$ and $f(x)$ lies on the image of this $\PP^1$ (which is again a $\PP^1$ by \Cref{lem:map to Symd} or because the induced morphism on the $d$-th symmetric power is again finite) inside of $Y^{(d)}$.
-Now the conclusion follows by \Cref{lem:iso1}.
-\end{proof}
-
-\begin{proposition} \label{Genus0Prop}
-Let $E/\Q$ be an elliptic curve with mod $N$ image $G(N)$ of genus $0$ and $N$ a positive integer. Then there does not exist a point corresponding to $E$ on $X_1(N)$ that is $\PP^1$-isolated.
+\section{\texorpdfstring{Computing the level of the $m$-adic representation}{Computing the level of the m-adic representation}}
+\label{sec:madicrep}
+
+\abbey{Revised first paragraph to account for Filip's suggestion.} Given a non-CM elliptic curve $E/\Q$, we define the set
+\[
+S_E\coloneqq \{2,3\} \cup \{ \ell: \rho_{E,\ell^{\infty}}(\Gal_{\Q}) \neq \GL_2(\Z_{\ell}) \}.
+\] 
+For $m \coloneqq \prod_{\ell \in S_E} \ell$, we want an algorithm to obtain the level of the $m$-adic Galois representation associated to $E$ from the image of the adelic representation of $E$, where the later can be computed by Zywina's algorithm \cite{ZywinaAlgorithm}.
+If $\im \rho_E$ has level $N$, define $n=\prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$ and let $m_0$ denote the level of $\rho_{E,m^{\infty}}$.
+We note that $m_0| n$ and $n | N$.
+Each of these divisibilities can be proper, as the following examples illustrates.
+
+  \begin{example}
+ If $E=75072.bc2$, we see that $\rho_E$ has level $N=4682=2^2 \cdot 3 \cdot 17 \cdot 23$.
+Since 2 is the only non-surjective prime, $n=2^2$.
+However, the level of the $m$-adic Galois representation associated to $E$ is 2.
+On the other hand, it can also happen that $N=m_0$.
+For example, if $E=54.b2$, we see that $\rho_E$ has level 72, and this is also the level of the $m$-adic Galois representation associated to $E$.
+\end{example}
+
+\begin{algorithm}[H]
+  \KwIn{$G(N)\leq \GL_2(\Z/N\Z)$ where $\im\rho_E=G$ and $N$ is the level.}
+  \KwOut{$m_0 \in \Z^+$ the level of $\rho_{E,m^{\infty}}$ for $m= \prod_{\ell \in S_E} \ell$.}
+  \caption{Reduced level}%
+  \label{alg:reduce_level}
+  Let $n = \prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$.\\
+Compute smallest $m_0$ dividing $n$ such that \[\#G(n)=\#G(m_0) \cdot \#\ker(\GL_2(\Z/n\Z) \rightarrow \GL_2(\Z/m_0\Z)).\]\\
+  \Return{$m_0$}
+\end{algorithm}
+
+\abedit{The validity of this algorithm is a consequence of the following proposition.}
+  \begin{proposition}
+  Let $E/\Q$ be a non-CM elliptic curve, and let $\im \rho_E=G \leq \GL_2(\widehat{\Z})$ be a subgroup of level $N$.
+Define $n \coloneqq \prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$.
+If $m_0$ is the smallest positive integer dividing $n$ such that \[\#G(n)=\#G(m_0) \cdot \#\ker(\GL_2(\Z/n\Z) \rightarrow \GL_2(\Z/m_0\Z)),\] then $m_0$ is the level of the $m$-adic Galois representation associated to $E$ for $m= \prod_{\ell \in S_E} \ell$.
   \end{proposition}
   \begin{proof}
-Let $x$ be a $\Q$-rational point on $X_{G(N)}$ corresponding to $E$.
-
-%Let $B$ be the group generated by $G(n)$ and a conjugate of $B_1(n)$ in $\GL_2(\Z/n\Z)$; this is again a group of genus $0$ on which the image $P'$ of $P$ under the map $X_{G(n)}\rightarro X_B$ is $\Q$-rational.
-The inclusion of subgroups $B\subset B_1(n)$ induces a map $X_1(n)\rightarrow  X_B$.
-
-Let $(E,P)=\abedit{y} \in X_1(N)$ correspond to $E$.
-Let $B \colonequals B_1(N) \cap c(G(N))$ in $c(G(N))$, where $c$ denotes the appropriate choice of conjugation in $\GL_2(\Z/N\Z)$ such that $P$ is an element of the basis inducing the mod $N$ representation.
-Let $d \colonequals [\pm c(G(N)) : \pm B]$.
-%\abbey{Seems like we'd want to take the conjugate of $G(N)$ such that $P$ is the first basis element, but keep $B_1(N)$ as is.
-Also, we want the index of $\pm B$ in $\pm G(N)$.} \filip{Yes, fixed.}
-
-Let $f\colon X_{B}\rightarrow X_{G(N)} \simeq \PP^1$ be the corresponding degree $d$ map of modular curves.
-%\timo{One has $\deg(x) = \deg(f(x))$ [yes, but this is not what we need]: $B$ is the exact stabilizer of $x$ in $G(N)$, so the fiber above $f(x)$ is completely split, working with quotients $f\colon X/H \to X/G$ by finite groups $H \leq G$ such that $H = G_x$ because $f(x) = Gx = G/Hx$ has $\#G/H = \deg(f)$ preimages.}
-\Cref{lem:map to Symd} yields a non-constant morphism $f^*\colon X_{G(N)} \to X_{B}^{(d)}$ such that $f^*(x)$ lies on a $\PP^1 \simeq X_{G(N)}$.
-Hence $x \in X_B$ is not $\PP^1$-isolated by \Cref{lem:iso1} [irreducible].
-Consider the morphism $g\colon X_B \to X_1(N)$ corresponding to $B \leq B_1(N)$.
-It is totally ramified above $g(x)$ because $B_1(N)$ stabilizes $g(x) = y$ and so does $B$, so the decomposition group of $x$ equals its inertia subgroup.
-Hence it satisfies $\deg(g(x)) = \deg(x)$, so $g(x)$ is not $\PP^1$-isolated by \Cref{lem:iso2}.
-%\abbey{How do we know $f^{-1}(x)$ is irreducible, in order to apply \Cref{lem:iso1}?} \filip{Well because the mod $N$ image is equal to $G(N)$ (and not a subgroup).
-So to get the image to reduce to $B$, we need to go to an extension of the index of $B$ in $G(N)$.
-This is a more general result: if $G\geq H$ are congruence groups of level $N$ and $f:X_H\rightarrow X_G$ and $x$ corresponds to an elliptic curve whose mod $N$ image is $G$ over $\Q$, then the degree of $f^{-1}(x)$ is $\deg f$.} \abbey{Oh, right -- that makes sense.
-Thanks.}
+  First we will show that $\im \rho_{E,m^{\infty}}=\pi_1^{-1}(G(n))$, where $\pi_1:\prod_{\ell \in S_E} \GL_2(\Z_{\ell}) \rightarrow \GL_2(\Z/n\Z)$ is the natural reduction map.
+It suffices to show that $\ker \pi_1 \subseteq \im \rho_{E,m^{\infty}}$.
+We have $N=n\cdot n'$ with $(n,n')=1$, and so we may identify $G(N)$ as a subgroup of $\GL_2(\Z/n\Z) \times \GL_2(\Z/n'\Z)$.
+Under this identification, let $H$  be the intersection of $G(N)$ with the subgroup $\{I\} \times \GL_2(\Z/n'\Z)$.
+Then since $G$ has level $N$,
+  \[
+  \pi^{-1}(H) \subseteq \im \rho_E,
+  \]
+  where $\pi: \GL_2(\widehat{\Z}) \rightarrow \GL_2(\Z/N\Z)$ is the natural reduction map.
+The image of this subset relation under the natural projection map  $\GL_2(\widehat{\Z}) \cong \prod_{\ell} \GL_2(\Z_{\ell}) \rightarrow  \prod_{\ell \in S_E} \GL_2(\Z_{\ell}) $ gives
+  \[
+  \ker(\pi_1) \subseteq \im \rho_{E,m^{\infty}},
+  \]
+  as desired.
+
+Let $\pi_2: \GL_2(\Z/n\Z) \rightarrow \GL_2(\Z/m_0\Z)$ be the natural reduction map.
+The assumption on $m_0$ implies that $\ker(\pi_2) \subseteq G(n)$, so it follows that $G(n) = \pi_2^{-1}(G(m_0))$.
+Thus if $\pi_3: \prod_{\ell \in S_E} \GL_2(\Z_{\ell}) \rightarrow \GL_2(\Z/m_0\Z)$ denotes the reduction map, we have
+  \begin{align*}
+  \pi_3^{-1}(G(m_0))&=\pi_1^{-1}(\pi_2^{-1}(G(m_0))\\
+  &=\pi_1^{-1}(G(n))\\
+  &=\im \rho_{E,m^{\infty}}.
+  \end{align*}
+By construction $m_0$ is the smallest positive integer with this property.
   \end{proof}
@@
   \begin{corollary}
-Let $E/\Q$ be an elliptic curve with adelic image $G$ of genus $0$ and $n$ a positive integer. Then there does not exist an $n$ such that a point corresponding to $E$ on $X_1(n)$ is $\PP^1$-isolated.
+  Algorithm \ref{alg:reduce_level} is correct.
   \end{corollary}
-\begin{proof}
-Since $G$ is by assumption of genus $0$, it follows that so is $G(n)$. The result then follows from Proposition \ref{Genus0Prop}.
-\end{proof}
-
-\begin{comment}
-are of degree $d$.
-Let $x'\in f^{-1}(x) \subseteq X_{B}$ be a point corresponding to $E$, and let $g\colon X_{B}\rightarrow X_1(n)$ be the map induced by the inclusion $B_1(N) \supseteq B$.
-The point $x'$ lies on a $\PP^1$ inside $X_B^{(d)}$ and hence $g(x')$ lies on a $\PP^1$ inside $X_1(n)^{(d)}$.
-Since no Abelian variety has $\PP^1$ as a subvariety, $\Phi_d$ contracts this $\PP^1$ inside $X_1(n)^{(d)}$ to a single point; it follows that $g(x')$ is not $\PP^1$-isolated.
-
-We have the following commutative diagram:
-
-$$
-\xymatrix{
-& X_B \ar[r]^{g} \ar[d]^{f} & X_1(N) \ar[d]^{q} \\
-&X_{G(N)} \ar[r]^{h} & X_{G'},
-}
-$$
-where $G'$ is defined to be the subgroup of $\GL_2(\Z/N\Z)$ generated by the union of $B_1(N)$ and $G(N)$, and the maps $q:X_1(N) \rightarrow X_{G'}$ and $h:X_G(N) \rightarrow X_{G'}$ are induced by the inclusion of the corresponding subgroups.
-The curve $X_{G'}$ is obviously of genus $0$ as it is covered by $X_{G(N)}$ of genus 0.
-
-As $g(x')$ is of degree $d$ and $q(g(x'))=h(x)\in X_{G'}(\Q)$, it follows $\deg q\geq d$. Alternatively, the same conclusion follows from $\deg q=[\pm G':\pm B_1(N)]\geq [\pm G':\pm B]=d. $
-
-\filip{Work in progress.
-If we prove $\deg q=d$, we are done.
-There's a more general question here, which I think is interesting: given a morphism $f:X\rightarrow \PP^1$ over $\Q$, with genus of $X$ at least 2, is it possible that there's infinitely many points of degree $<d$ in $f^{-1}(\PP^1(\Q))$.
-For $d=2$, the answer is no, and I think this might be the case in general.
-If anyone knows of a reference (or proof) of this, let me know; this would complete the proof of this lemma.
-} \abbey{Seems like you'd want some sort of strong form of Hilbert's irreducibility for this?
-I hadn't thought of this before...
-I believe there are infinitely many $c\in\Q$ such that $f-c$ is irreducible, which gives infinitely many degree $d$ points.
-So you want to know whether there are only finitely many $c$ such that $f-c$ is reducible?
-It looks like in some cases something like this is true (e.g., ``Finiteness results for Hilbert's irreducibility theorem" by M\"{u}ller), but not in general.}
-\filip{Yes, this would be some strong form of Hilbert's irreducibility.
-Is there a single example, of an $X$ of genus $\geq 2$ and $f$, where $f$ does not factor as $f=f_1\circ f_2$  with $\deg f_i>1$ (otherwise there can be many counterexamples), where this is not true?}
-\end{comment}
-
-%\filip{I remember what the issue was: we construct maps $X_B\rightarrow X_{G(n)}$ and $f:X_B\rightarrow X_1(n)$, and show that the point associated to $E$ on $X_B$ is not $\PP^1$-isolated.
-But I don't know how to show that this would imply that the image of this point under $f$ is not $\PP^1$-isolated.
-}\\
-%\filip{This is I think a more general group theoretic problem: we have a subgroup $A$ of $G(n)$ of index $d$, i.e.
-$[G(n):A]=d$, where $A\leq B_1(N)$ (or some conjugate of $B_1(n)$).
-Then we ask what is the index of $B_1(N)$ in the group generated by $G(n)$ and $B_1(n)$.
-If the answer is again necessarily $d$ (or we can always choose a conjugate of $B_1(n)$) such that the index is $d$, then we are good.}
 
@@
 
-\abbey{New section which answers Zev's question about the PrimitiveDegreesOfPoints algorithm in the affirmative.}
-At a high level, our algorithm to decide whether a given $E/\Q$ gives rise to an isolated point on $X_1(N)$ for some $N\geq 1$ proceeds in two steps.
+\abbey{Section revised to account for new statement of primitive points theorem in introduction.} Let $E$ be a non-CM elliptic curve.
+In this section, we will reduce the question of determining whether $j(E)$ is isolated to the analysis of an associated finite set of primitive points on modular curves.
+The primitive points are characterized by the following theorem.
+
+\begin{theorem}\label{Thm:PrimPts}
+Let $E/\Q$ be a non-CM elliptic curve.  There exists a finite set $\mathcal{P}=\mathcal{P}(E)$ of primitive points in $\cup_{n \in \Z^+} X_1(n)$ characterized by the following properties:
+\begin{enumerate}
+\item For each $N\in \Z^+$, a point $x \in X_1(N)$ with $j(x)=j(E)$ corresponds to a unique element $x' \in \mathcal{P}$ under the natural projection map.
+Moreover, if $x' \in X_1(a)$, then $a \mid N$ and $\deg(x)=\deg(f)\cdot \deg(x')$, where $f: X_1(N) \rightarrow X_1(a)$ is the natural map.
+\item The rational number $j(E)$ is isolated if and only if there exists an isolated point in $\mathcal{P}$.
+\end{enumerate}
+Moreover, the set $\mathcal{P}$ is minimal with respect to conditions (i) and (ii).
+\end{theorem}
+
+\noindent Though in many ways this can be viewed as a refinement of results in \cite{BELOV}, the uniqueness of Theorem \ref{Thm:PrimPts}(i) is new.
+In Section~\ref{sec:primitivedeg}, we give an algorithm for enumerating $\mathcal{P}(E)$ given a non-CM $E/\Q$.
+
+\abbey{Should examples go here or in next section?}
+\begin{example}
+We will show that the level of the primitive points of $E$ will always divide the level of the adelic Galois representation (see Remark \ref{Rmk:Level}).
+For example, let $E/\Q$ be the non-CM elliptic curve 147.b1.
+Zywina's algorithm \cite{ZywinaAlgorithm} shows that the image of the adelic Galois representation of $E$ has level $546=2 \cdot 3 \cdot 7 \cdot 13$.
+Here, $\mathcal{P}(E)$ consists of 4 points: one point on $X_1(13)$ of degree 6, two points on $X_1(13)$ of degree 39, and one point on $X_1(1)$ of degree 1.
+The points on $X_1(13)$ are expected, since the mod 13 Galois representation of $E$ is not surjective.
+
+However, it is not necessarily the case that non-surjective primes must divide the level of some primitive point.
+For example, let $E/\Q$ be the non-CM elliptic curve 232544.f1.
+Then the adelic Galois representation of $E$ has level $1892=2^2\cdot11 \cdot 43$ and the mod 11 Galois representation associated to $E$ is non-surjective.
+However, in this case $\mathcal{P}(E)$ consists of a single point, namely, the degree one point on $X_1(1)$ associated to $E$.
+\end{example}
+
+%\abbey{New section which answers Zev's question about the PrimitiveDegreesOfPoints algorithm in the affirmative.}
+%At a high level, our algorithm to decide whether a given $E/\Q$ gives rise to an isolated point on $X_1(N)$ for some $N\geq 1$ proceeds in two steps.
 First, we reduce this to a finite computation by computing a level $n$ associated to the adelic image of $E$, so that we need only consider levels $m|n$.
@@
 In this section, we introduce a notion of a primitive point on a modular curve.
-For a computable integer $m$ \abbey{We don't need any restrictions here -- $m$ doesn't have to correspond to the level.
+%For a computable integer $m$ \abbey{We don't need any restrictions here -- $m$ doesn't have to correspond to the level.
 The point is that any isolated point on $X_1(n)$ for $n \mid m$ will map down under the natural projection map to a primitive point which is isolated by \cite[Theorem 4.3]{BELOV}.
@@
 
-Let $m\geq 1$ be an integer.
-%We now define the $m$-primitive points above a given elliptic curve $E/\Q$.
+\subsection{\texorpdfstring{Construction of $\mathcal{P}(E)$ and minimality.}{Construction of P(E) and minimality}} Let $m\geq 1$ be an integer.
 We begin by defining a directed graph $G(E,m)$ on the points of $X_1(n)$ corresponding to $E$ for all $n|m$. The vertices of $G(E,m)$ are tuples $(x,n,d)$ where:
@@
 \end{enumerate}
-We connect $(x,n,d)$ with an arrow \sachi{a directed edge} to $(x',n',d')$ if:
+We connect $(x,n,d)$ with a directed edge to $(x',n',d')$ if:
 \begin{enumerate}
@@
     Let $E$ be an elliptic curve over $\Q$ and let $m\geq 1$ be an integer.
-The \textbf{$m$-primitive points} above $E$ are the sinks \abedit{of} $G(E,m)$.
+The \textbf{$m$-primitive points} above $E$ are the sinks of $G(E,m)$.
 The \textbf{$m$-primitive degrees} are the tuples $(n,d)$, where $(x,n,d)$ is $m$-primitive for $E$.
-\travis{multiplicity?}
+The union of all $m$-primitive points as $m$ ranges over all positive integers is the set of \textbf{primitive points} associated to $E$, denoted $\mathcal{P}(E)$.
 \end{definition}
 
-\abedit{
-\begin{theorem}
-    Let $E/\Q$ be a non-CM elliptic curve.
-Then there are only finitely many primitive points associated to $E$.
-Moreover, $j(E)$ is isolated if and only if one of the primitive points associated to $E$ is isolated.
-\end{theorem}
-
-}
-In Section~\ref{sec:primitivedeg}, we give an algorithm for enumerating the sinks of $G(E,m)$.
+\abedit{By construction, for any $(x,n,d) \in \mathcal{P}(E)$, there does \emph{not} exist a proper divisor $n' \mid n$ with $d=\deg(f) \cdot \deg(f(x))$, where $f: X_1(n) \rightarrow X_1(n')$ is the natural map.
+Thus $\mathcal{P}(E)$ is the minimal set which can satisfy Theorem \ref{Thm:PrimPts}(i).}
+
 \begin{remark}\label{Remark:Transitivity}
 Suppose $n'' | n' | n | m$ and that $(x,n,d), (x',n',d'), (x'',n'',d'')$ are vertices.
-This graph is \textbf{transitive}, meaning that if there is an arrow \sedit{edge} from $(x,n,d)$ \sedit{to} $(x',n',d')$ and from $(x',n',d')$ to $(x'',n'',d''),$ then
-there is also an arrow \sedit{edge} from $(x,n,d)$ to $(x'',n'',d'')$.
-\travis{Moreover, if there is an arrow from $(x,n,d)$ to $(x'',n'',d''),$ then we  claim there \abedit{is} an arrow from $(x,n,d)$ to $(x',n',d')$, \abedit{where $x'$ is the image of $x$ on $X_1(n')$ and $n'$ is any multiple of $n''$ which properly divides $n$}.
+This graph is \textbf{transitive}, meaning that if there is an edge from $(x,n,d)$ to $(x',n',d')$ and from $(x',n',d')$ to $(x'',n'',d''),$ then
+there is also an edge from $(x,n,d)$ to $(x'',n'',d'')$.
+Moreover, if there is an edge from $(x,n,d)$ to $(x'',n'',d''),$ then we  claim there is an edge from $(x,n,d)$ to $(x',n',d')$, \abedit{where $x'$ is the image of $x$ on $X_1(n')$ and $n'$ is any multiple of $n''$ which properly divides $n$}.
 Intuitively, if the degree grows as much as possible from level $n''$ to level $n$ then it also grows as much as possible from level $n'$ to level $n$.
@@
 Suppose for the sake of contradiction that  $\abedit{d}<\abedit{d'}\cdot\deg g_1$.
-But since $\abedit{d'} \leq \abedit{d''} \cdot \deg g_2$, this would imply $\abedit{d}<\abedit{d''} \cdot\deg g_1\cdot \deg g_2 $.
-This contradicts our assumption that there is an arrow from $(x,n,d)$ to $(x'',n'',d'')$.}
+Since $\abedit{d'} \leq \abedit{d''} \cdot \deg g_2$, this would imply $\abedit{d}<\abedit{d''} \cdot\deg g_1\cdot \deg g_2 $.
+This contradicts our assumption that there is an edge from $(x,n,d)$ to $(x'',n'',d'')$.
 \end{remark}
 
-Now fix a vertex $(x,n,d)$ and consider \travis{the graph induced by $(x,n,d)$ and} its \textbf{descendants}, i.e.
-all vertices $(x',n',d')$ reachable by a path from $(x,n,d)$.
+\begin{definition}
+Let $E/\Q$ be an ellitpic curve and $m \in \Z^+$.
+For a fixed vertex $(x,n,d)$ in $G(E,m)$, consider the directed graph induced by $(x,n,d)$ and its \textbf{descendants}, i.e., all vertices $(x',n',d')$ reachable by a path from $(x,n,d)$.
 This is a directed acyclic graph with a single source, $(x,n,d)$.
-\abedit{In this section, we will show that this graph has a single sink as well.}    \abbey{Is there standard notation for this?
-I use $D(v)$ below.} \sachi{I think this is typically the out-neighborhood of a vertex, denoted $N^+(v)$.
-i.e.
-this is the set of vertices $w$ such that there is an edge from $v$ to $w$.
-By the way, what we have defined as $D(v)$ (and also $N^+(v)$) is technically not directed acyclic graph, it's just a set -- but we can consider the induced subgraph on $N^+(v)$, i.e.
-the set of these vertices and along with all of the edges going between them that were in the original graph.} \travis{added that we consider the induced graph, making it a graph instead of a set}\travis{I think out-neighborhood happens to work for our DAG, since $(x,n,d)$ is adjacent to any vertex it has a path to.
-It wouldn't in general be the same thing.}
-
-\begin{proposition}\label{Prop:single_sink}
-    Let $m\geq 1$ be an integer and let $E/\Q$ be an elliptic curve.
-Fix $v=(x,n,d)$ in $G(E,m)$, and consider the \sedit{induced} subgraph \sedit{on the set} $D(v)$ of all its descendants.
-Then \sedit{this subgraph} has a single sink.
-\abbey{Is there a reason why we can't let $D(v)$ -- or some other, better notation -- denote the induced subgraph, not just the set of descendants?
-It seems better to emphasize the subgraph for the purposes of this statement.
-We could also just say, ``For any fixed vertex $v$ in $G(E,m)$, the induced subgraph on its descendants has a single sink." Is this better?} \sachi{There is no reason why -- we should just define it this way in the beginning :) Right now we are saying it's a set, so I found it a bit confusing, since it's not entirely clear which edges we are taking on the set of vertices.
-I think either phrasing is OK -- as you suggest, we can also define $D(v)$ to be the induced subgraph on the set of descendents (instead of the set of descendents itself), or remark that we abuse notation and denote the induced subgraph and the set of vertices by the same notation.}
-\end{proposition}
-
-\subsection{Preliminary Results}
+\end{definition}
+
+\abedit{In Corollary \ref{Cor:SingleSink} below, we will show the induced graph on the descendants of $(x,n,d)$ has a single sink as well; this is $x' \in \mathcal{P(E)}$ associated to $x$, as in Theorem \ref{Thm:PrimPts}(i).}
+
+\subsection{Preliminary Results} In this section, we establish two results concerning the residue fields of points on modular curves.
 
@@
 
-There exists $E'/F_1$ such that $\varphi:E \rightarrow E'$ is an isomorphism and $\varphi(n_2'P) \in E'(F_1)$; see, for example, \cite[p.
-274, Proposition VI.3.2]{DR}.
-Moreover, we have $F_2= \Q(j(E),\mathfrak{h}(n_1'P))=\Q(j(E),\mathfrak{h}(\varphi(n_1'P)))$ by \cite[p.
-107]{shimura}.
-In particular, the explicit formulas for $\mathfrak{h}$ as in \cite[p.
-107]{shimura} show that the $x$-coordinate of $\varphi(n_1'P)$ is rational over $F_1F_2$.
+There exists $E'/F_1$ such that $\varphi:E \rightarrow E'$ is an isomorphism and $\varphi(n_2'P) \in E'(F_1)$; see, for example, \cite[p.~274, Proposition~VI.3.2]{DR}.
+Moreover, we have $F_2= \Q(j(E),\mathfrak{h}(n_1'P))=\Q(j(E),\mathfrak{h}(\varphi(n_1'P)))$ by \cite[p.~107]{shimura}.
+In particular, the explicit formulas for $\mathfrak{h}$ as in \cite[p.~107]{shimura} show that the $x$-coordinate of $\varphi(n_1'P)$ is rational over $F_1F_2$.
 The $y$-coordinate of $\varphi(n_1'P)$ is defined over at worst a quadratic extension $L/F_1F_2$, and $L=F_1F_2$ if $n_2=2$.
@@
 
-\subsection{Proof of Proposition \ref{Prop:single_sink}}
-The proof of Proposition \ref{Prop:single_sink} will appear as a corollary to the following result.
+\subsection{Proof of Theorem \ref{Thm:PrimPts}\,(i)}
+The proof of Theorem \ref{Thm:PrimPts}(i) will appear as a corollary to the following result.
 
@@
 
-\begin{corollary}
-Let $m\geq 1$ be an integer and let $E/\Q$ be an elliptic curve.
-Fix $v=(x,n,d)\in G(E,m)$, and consider the \sedit{induced} subgraph \sedit{on} $D(v)$ \sedit{the set} of all its descendants.
-Then $D(v)$ has a single sink.
+\begin{corollary}\label{Cor:SingleSink}
+   Let $m\geq 1$ be an integer and let $E/\Q$ be an elliptic curve. \abedit{For any fixed vertex $v=(x,n,d)$ in $G(E,m)$, the induced subgraph on its descendants has a single sink.}
 \end{corollary}
@@
 \begin{proof}
-Suppose for the sake of contradiction that \sedit{the subgraph induced by} $D(v)$ has two distinct sinks, $v_1=(x_1,n_1,d_1)$ and $v_2=(x_2,n_2,d_2)$.
-\abedit{If $n_1 \mid n_2$, then the arrows from $v$ to $v_1$ and $v$ to $v_2$ force there to be an arrow from $v_2$ to $v_1$.
+Suppose for the sake of contradiction that \abedit{the induced subgraph} has two distinct sinks, $v_1=(x_1,n_1,d_1)$ and $v_2=(x_2,n_2,d_2)$.
+\abedit{If $n_1 \mid n_2$, then the edges from $v$ to $v_1$ and $v$ to $v_2$ force there to be a edge from $v_2$ to $v_1$.
 This contradicts the fact that $v_2$ is a sink, so it must be that $n_1 \nmid n_2$.
@@
 
-\section{Overview of the Main Algorithm}
-\label{sec:mainalg}
-The following algorithm is the main procedure for determining whether a given non-CM $j$-invariant in $\Q$ is the image of a $\PP^1$-isolated point on $X_1(N)$ for some $N$ based on results in \cite{BELOV,ZywinaAlgorithm}.
-We note that for any CM $j$-invariant $j$, there exists infinitely many $N\in\Z^+$ for which there is a sporadic point $x\in X_1(N)$ with $j(x)=j$ by \cite[Theorem 7.1]{BELOV}, so it is not necessary to consider them in this algorithm.
-The outline below gives an overview of the structure, while the algorithms to perform particular steps are described in detail in Sections \ref{sec:madicrep} and \ref{sec:primitivedeg}.
-We will prove a theorem on the validity of Algorithm \ref{alg:mainalgorithm} in Section \ref{sec:validity}.
-
-\setcounter{algocf}{0}
-\begin{algorithm}[h!]
-\caption{Main Algorithm}\label{alg:mainalgorithm}
-\KwIn{A non-CM $j$-invariant $j \in \Q$.}
-\KwOut{A list $[j,\{\langle a_1,d_1\rangle, \dots, \langle a_k,d_k\rangle \}]$ such that any isolated point $x \in X_1(N)$ with $j(x)=j$ maps down under the natural projection map to an isolated point of degree $d_i$ on $X_1(a_i)$ for some $1 \leq i \leq k$.}
-Construct an elliptic curve $E/\Q$ with $j(E)=j$.\\
-Compute the adelic image $G$ of $E/\Q$ as a subgroup of $\GL_2(\hat{\Z})$ using Zywina's algorithm \cite{ZywinaAlgorithm}.
-Represent the output as the level $N$ and the subgroup $G(N)$ of $\GL_2(\Z/N\Z)$.\\
-Apply Algorithm \ref{alg:reduce_level} to $G(N)$ to obtain the level $m_0$ of the $m$-adic Galois representation associated to $E$, where $m$ is the product of 2, 3, and all non-surjective primes.\\
-Using Algorithm \ref{alg:compute_prim_degree}, return a multiset $D$ \abbey{updated to match new definitions} with entries $\langle n, \{\langle a_1, d_1\rangle ,  \dots,  \langle a_r, d_r\rangle \} \rangle$
-    for all positive divisors $n$ of $m_0$ such that the degree of the corresponding
-    closed point on $X_1(n)$ is as large as possible given that its image on $X_1(a_i) $
-    has degree $d_i$.\\
-Construct the multiset $D' \subseteq D$ containing only those elements $\langle n, \{\langle a_1, d_1\rangle ,  \dots,  \langle a_r, d_r\rangle \} \rangle$ for which $d_i \leq \text{genus}(X_1(a_i))+1$ for all $1 \leq i \leq r$.\\
-Create the multiset $M$ consisting of all pairs $\langle a_i,d_i\rangle $ appearing in $D'$, where $\langle a_i,d_i\rangle $ has multiplicity $\mu$ if and only if $X_1(a_i)$ has $\mu$ distinct closed points of degree $d_i$.\\
-\Return{$[j,M]$}
-
-\end{algorithm}
-
-In particular, note that if Algorithm \ref{alg:mainalgorithm} outputs $[j,\{\}]$, then $j$ is not the image of any $\mathbf{P}^1$-isolated point on $X_1(N)$, even as $N$ ranges over all positive integers.
-See Corollary \ref{cor:P1_isolated}.
-
-\begin{example}
-If $j=-9317$, then Algorithm \ref{alg:mainalgorithm} returns $[j, \{\langle 37,6\rangle ^3\}]$.
-This means that any isolated point $x\in X_1(N)$ with $j(x)=j$ and $N \in \Z^+$ maps down under the natural projection map to one of the 3 closed points of degree 6 on $X_1(37)$.
-In fact, these points are all sporadic by \cite[Proposition 2]{frey}, since $6 < \frac{1}{2} \gon_{\Q}(X_1(37)) = 18$.
-Here, the gonality computation is a result of \cite{DerickxVanHoeij2014}.
-Thus $j$ is a sporadic --- and hence isolated --- $j$-invariant.
-\end{example}
-
-\begin{example}
-If $j=-121$, then Algorithm \ref{alg:mainalgorithm} returns $[j, \{\}]$. This means that there are no isolated points on $X_1(N)$ associated to this $j$-invariant.
-\end{example}
-
-\begin{example}
-If $j=-882216989/131072$, then Algorithm \ref{alg:mainalgorithm} returns  $[j,\{\langle 17,4\rangle ^2\}]$.
-This means that $j$ is associated to an isolated point on a modular curve of the form $X_1(N)$ if and only if there exists a degree 4 isolated point $x \in X_1(17)$ with $j(x)=j$.
-In Section \ref{sec:remainingfilters}, we will show that no such isolated point exists, from which we can conclude that $j$ is not an isolated $j$-invariant.
-\end{example}
-
-\section{\texorpdfstring{Computing the level of the $m$-adic representation}{Computing the level of the m-adic representation}}
-\label{sec:madicrep}
-
-Let $E/\Q$ be a non-CM elliptic curve, and define the set
-\[
-S_E\coloneqq \{2,3\} \cup \{ \ell: \rho_{E,\ell^{\infty}}(\Gal_{\Q}) \neq \GL_2(\Z_{\ell}) \}.
-\] For $m \coloneqq \prod_{\ell \in S_E} \ell$, we give an algorithm to obtain the level of the $m$-adic Galois representation associated to $E$ from the image of the adelic representation of $E$.
-In practice, we can obtain $\im \rho_E$ from Zywina's algorithm \cite{ZywinaAlgorithm}.\\
-
-\begin{algorithm}[H]
-  \KwIn{$G(N)\leq \GL_2(\Z/N\Z)$ where $\im\rho_E=G$ and $N$ is the level.}
-  \KwOut{$m_0 \in \Z^+$ the level of $\rho_{E,m^{\infty}}$ for $m= \prod_{\ell \in S_E} \ell$.}
-  \caption{Reduced level}%
-  \label{alg:reduce_level}
-  Let $n = \prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$.\\
-Compute smallest $m_0$ dividing $n$ such that \[\#G(n)=\#G(m_0) \cdot \#\ker(\GL_2(\Z/n\Z) \rightarrow \GL_2(\Z/m_0\Z)).\]\\
-  \Return{$m_0$}
-\end{algorithm}
-
-  \begin{example}
-Suppose $E/\Q$ is a non-CM elliptic curve such that $\rho_{E}$ has level $N$.
-As above, define $n=\prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$ and let $m_0$ be the level of $\rho_{E,m^{\infty}}$ for $m= \prod_{\ell \in S_E} \ell$.
-It follows that $m_0| n$ and $n | N$.
-Each of these divisibilities can be proper \abbey{emphasize at start -- or start of secction}.
-For example, if $E=75072.bc2$, we see that $\rho_E$ has level $N=4682=2^2 \cdot 3 \cdot 17 \cdot 23$.
-Since 2 is the only non-surjective prime, $n=2^2$.
-However, the level of the $m$-adic Galois representation associated to $E$ is 2.
-On the other hand, it can also happen that $N=m_0$.
-For example, if $E=54.b2$, we see that $\rho_E$ has level 72, and this is also the level of the $m$-adic Galois representation associated to $E$.
-\end{example}
-  \begin{proposition}
-  Let $E/\Q$ be a non-CM elliptic curve, and let $\im \rho_E=G \leq \GL_2(\widehat{\Z})$ be a subgroup of level $N$.
-Define $n \coloneqq \prod_{\ell \in S_E} \ell^{v_{\ell}(N)}$.
-If $m_0$ is the smallest positive integer dividing $n$ such that \[\#G(n)=\#G(m_0) \cdot \#\ker(\GL_2(\Z/n\Z) \rightarrow \GL_2(\Z/m_0\Z)),\] then $m_0$ is the level of the $m$-adic Galois representation associated to $E$ for $m= \prod_{\ell \in S_E} \ell$.
-  \end{proposition}
-  \begin{proof}
-  First we will show that $\im \rho_{E,m^{\infty}}=\pi_1^{-1}(G(n))$, where $\pi_1:\prod_{\ell \in S_E} \GL_2(\Z_{\ell}) \rightarrow \GL_2(\Z/n\Z)$ is the natural reduction map.
-It suffices to show that $\ker \pi_1 \subseteq \im \rho_{E,m^{\infty}}$.
-We have $N=n\cdot n'$ with $(n,n')=1$, and so we may identify $G(N)$ as a subgroup of $\GL_2(\Z/n\Z) \times \GL_2(\Z/n'\Z)$.
-Under this identification, let $H$  be the intersection of $G(N)$ with the subgroup $\{I\} \times \GL_2(\Z/n'\Z)$.
-Then since $G$ has level $N$,
-  \[
-  \pi^{-1}(H) \subseteq \im \rho_E,
-  \]
-  where $\pi: \GL_2(\widehat{\Z}) \rightarrow \GL_2(\Z/N\Z)$ is the natural reduction map.
-The image of this subset relation under the natural projection map  $\GL_2(\widehat{\Z}) \cong \prod_{\ell} \GL_2(\Z_{\ell}) \rightarrow  \prod_{\ell \in S_E} \GL_2(\Z_{\ell}) $ gives
-  \[
-  \ker(\pi_1) \subseteq \im \rho_{E,m^{\infty}},
-  \]
-  as desired.
-
-Let $\pi_2: \GL_2(\Z/n\Z) \rightarrow \GL_2(\Z/m_0\Z)$ be the natural reduction map.
-The assumption on $m_0$ implies that $\ker(\pi_2) \subseteq G(n)$, so it follows that $G(n) = \pi_2^{-1}(G(m_0))$.
-Thus if $\pi_3: \prod_{\ell \in S_E} \GL_2(\Z_{\ell}) \rightarrow \GL_2(\Z/m_0\Z)$ denotes the reduction map, we have
-  \begin{align*}
-  \pi_3^{-1}(G(m_0))&=\pi_1^{-1}(\pi_2^{-1}(G(m_0))\\
-  &=\pi_1^{-1}(G(n))\\
-  &=\im \rho_{E,m^{\infty}}.
-  \end{align*}
-By construction $m_0$ is the smallest positive integer with this property.
-  \end{proof}
-
-  \begin{corollary}
-  Algorithm \ref{alg:reduce_level} is correct.
-  \end{corollary}
+\subsection{\texorpdfstring{Finiteness of $\mathcal{P}(E)$}{Finiteness of P(E)}} Let $E/\Q$ be a non-CM elliptic curve, and let $m$ be the product of 2, 3, and any primes $\ell$ such that the mod $\ell$ Galois representation of $E$ is non-surjective.
+It is a consequence of Serre's Open Image Theorem \cite{serre72} that $m \in \Z^+$, and there exists $m_0 \in \Z^+$ which is the level of the $m$-adic Galois representation of $E$.
+By \cite[Theorem 5.1]{BELOV}, for any $x \in X_1(n)$ with $j(x)=j(E)$ we have
+\[
+\deg(x)=\deg(f) \cdot \deg(f(x)),
+\]
+where $f: X_1(n) \rightarrow X_1(\gcd(n,m_0))$ is the natural map.
+It follows that the sinks of the graph $G(E,n)$ are contained in the sinks of $G(E,m_0)$.
+Since $m_0$ is a fixed positive integer depending only on $E$, it follows that $\mathcal{P}(E)$ is the set of sinks of $G(E,m_0)$ and thus is finite.
+
+\begin{remark}\label{Rmk:Level}
+    We note in particular that the level of any primitive point will divide $m_0$, which in turn divides the level of the adelic Galois representation associated to $E$.
+\end{remark}
+
+\subsection{Proof of Theorem \ref{Thm:PrimPts}\,(ii)} Let $E/\Q$ be a non-CM elliptic curve.
+If there exists an isolated point in $\mathcal{P}(E)$, then $j(E)$ is isolated by definition.
+To establish the other direction, suppose $j(E)$ is isolated.
+Then there exists an isolated point $x \in X_1(n)$ with $j(x)=j(E)$.
+By Theorem \ref{Thm:PrimPts}(i), we see that $x$ corresponds to a unique element $(x',n',d') \in \mathcal{P}(E)$ under the natural projection map.
+By the definition of $\mathcal{P}(E)$,
+\[
+\deg(x)=\deg(f)\cdot d',
+\]
+where $f: X_1(n) \rightarrow X_1(n')$ is the natural projection map. By \cite[Theorem 4.3]{BELOV}, the point $x'$ is isolated.
 
@@
 
-\abbey{In practice, it appeared that for an element $\langle n, \{\langle a_1, d_1\rangle,  \ldots \}\rangle$ in the output of this algorithm, the set $\#\{\langle a_1, d_1\rangle,  \ldots \}$ contains only 1 element.
-(Zev's observation) See section 4 for a proof of this.}
-
 We briefly discuss how we execute the loop in Step~\ref{alg:compute_primitive_degrees:minimal_levels} in Algorithm~\ref{alg:compute_prim_degree}.
@@
 
+\section{Genus 0 adelic images do not produce isolated points}
+\label{sec:genus0images}
+
+\label{sec:genus0}
+Let $E/\Q$ be an elliptic curve and $G\abedit{\leq} \GL_2(\hat \Z)$ its adelic image.
+Let $G(N)$ denote the image of its mod $N$ representation.
+Denote by $B_1(N)$ the subgroup of $\GL_2(\Z/N\Z)$ consisting of the upper triangular matrices with a $1$ in the upper left entry.
+Note that $X_{B_1(N)}=X_1(N)$.
+We say that a congruence group $\Gamma$ is of genus $g$ if $X_\Gamma$ is of genus $g$.
+We say that a point \abedit{$x$} corresponds to an elliptic curve $E$ if \abedit{$j(x) = j(E)$}.
+In this section, we show that elliptic curves with genus $0$ mod $N$ image  do not correspond to $\PP^1$-isolated points on $X_1(N)$.
+
+\begin{lemma} \label{lem:map to Symd}
+Let $f\colon X \to Y$ be a finite morphism of curves of degree $d$. Then $f$ induces a non-constant morphism $f^*\colon Y \to X^{(d)}$.
+\end{lemma}
+\begin{proof}
+    The point is to show that the natural map $y \mapsto f^{-1}(y)$ is a morphism of schemes.
+Note that the composition of $\Gamma_f\colon X \to X \times Y$ sending $X$ to the graph of $f$ with $X \times Y \to Y$ is just $f$, which is flat as a finite morphism of irreducible curves~\cite[Proposition~4.3.9]{Liu2002}.
+So the graph of $f$ defines a relative effective Cartier divisor in the sense of~\cite[Definition~3.4]{MilneJV} on $X \times Y/Y$ of degree $d$.
+    Since all our schemes are regular, we can identify Cartier with Weil divisors. 
+    In the hypothesis of the statement of~\cite[Theorem~3.13]{MilneJV}, we can thus take the effective divisor to be the graph of $f$.
+This allows us to conclude that, as a map of sets, $f^*$ maps $y \in Y$ to the degree-$d$ divisor $f^{-1}(y) \colonequals [\{y\} \times_Y X]$ with the multiplicities of the reduced subscheme of the points in the fiber product equal to the ramification indices (see~\cite[\S\,1.5, \S\,1.7]{FultonIntersectionTheory}).
+
+    The morphism $f^*$ is non-constant since fibers above different points are mapped to different points by $f^*$.
+\end{proof}
+
+%Note that a rational map from $\PP^1$ to a smooth variety of degree $1$ extends uniquely to a morphism (by the valuative criterion of properness) and is an isomorphism onto its image since a genus $0$ curve cannot have singularities.
+The symmetric powers of a smooth projective curve are smooth~\cite[Proposition~3.2]{MilneJV}.
+\sachi{right now this reads like a random pair of facts, what are we trying to say with this pair of facts?} \filip{I agree, I'm not sure we need this.}
+
+The following lemma rephrases the definition of a point being $\PP^1$-parametrized of degree $d$. 
+\begin{lemma}[Characterization of $\bP^1$-parametrized points] \label{lem:iso1}
+Let $X/k$ be a curve. Let $x \in X^{(d)}(k)$ be an irreducible degree $d$ divisor. The following are equivalent:
+\begin{enumerate}
+    \item The point $x$ is $\bP^1$-parametrized.
+
+    \item There is a non-constant rational map $\bP^1 \dashrightarrow X^{(d)}$ containing $x$ in its image.
+\end{enumerate}
+\end{lemma}
+\begin{proof}
+(i)$\implies$(ii): If $x$ is $\PP^1$-parametrized, then there is an $x' \in X^{(d)}(k)$ different from $x$ such that 
+$x-x'=\mathrm{div}(f)$ for a non-constant function $f\in k(X)$.
+Here we treat $x$ and $x'$ effective divisors of degree $d$ on $X$.
+This gives a degree $d$ map $f\colon X \to \PP^1$, which gives the copy of $\PP^1$ inside $X^{(d)}$ as the image under pullback of $f$ as in Lemma~\ref{lem:map to Symd}.
+
+(ii)$\implies$(i): 
+The restriction of the map $\Phi_d\colon X^{(d)}\rightarrow \Jac(X)$ to the image of $\PP^1$ inside $X^{(d)}$ factors through a translate of $\Jac(\PP^1)=\{0\}$ by the Albanese property of the Jacobian,\footnote{For pointed varieties, this is~\cite[Proposition~6.1]{MilneJV}.
+For general morphisms, note that any scheme morphism between abelian varieties is the composition of a homomorphism with a translation~\cite[Corollary~3.6]{MilneAV}.} so it contracts the $\PP^1$ to a point on $\Jac(X)$.\footnote{Or because abelian varieties contain no positive dimensional rational varieties~\cite[Corollary~3.9]{MilneAV}.} Hence $\Phi_d(y) = \Phi_d(x)$ for any $y$ lying on this image of $\PP^1$.
+\end{proof}
+
+\begin{lemma} \label{lem:iso2}
+Let $f\colon X\rightarrow Y$ be a finite morphism of curves and $x$ a closed point on $X$, and assume  $\deg x = \deg f(x)$. If $x$ is $\PP^1$-parametrized, then so is $f(x)$.
+\end{lemma}
+\begin{proof}
+Let $d=\deg(x)$. The proof is diagram chasing using $\PP^1 \to X^{(d)}\stackrel{f^{(d)}}{\to} Y^{(d)}$, where $f^{(d)}$ is the natural map from $X^{(d)}$ to $Y^{(d)}$ induced by $f$.
+If $x\in X$ is not $\bP^1$-isolated (i.e., $x$ is $\bP^1$-parametrized), then
+by Lemma~\ref{lem:iso1}, $x$ can be viewed as a point on $X^{(d)}$ lying on the image of a non-constant map from $\PP^1$ to $X^{(d)}$.  
+Furthermore, $f(x)$ lies on the image of this $\PP^1$ (which is again a $\PP^1$ by \Cref{lem:map to Symd} or because the induced morphism on the $d$-th symmetric power is again finite) inside of $Y^{(d)}$.
+Now the conclusion follows by \Cref{lem:iso1}.
+\end{proof}
+
+\begin{theorem} \label{Genus0Prop}
+Let $E/\Q$ be an elliptic curve with mod $N$ image $G(N)$ of genus $0$ and $N$ a positive integer.
+%Then there does not exist a point corresponding to $E$ on $X_1(N)$ that is $\PP^1$-isolated.
+\abbey{Perhaps here and in corollary: Every $x\in X_1(N)$ with $j(x)=j(E)$ is $\PP^1$-parametrized.}
+Then every $x \in X_1(N)$ with $j(x) = j(E)$ is $\PP^1$-parametrized.
+\end{theorem}
+\begin{proof}
+Let $x$ be a $\Q$-rational point on $X_{G(N)}$ corresponding to $E$.
+
+Let $[E,P] = y \in X_1(N)$ correspond to $E$.
+Let $B \colonequals B_1(N) \cap c(G(N))$ in $c(G(N))$, where $c$ denotes the appropriate choice of conjugation in $\GL_2(\Z/N\Z)$ such that $P$ is an element of the basis inducing the mod $N$ representation.
+Let $d \colonequals [\pm c(G(N)) : \pm B]$.
+The proof is diagram chasing in the following two diagrams while keeping track of the degree of the point.
+The situation is as follows:
+\[
+\begin{tikzcd}
+     &X_B \arrow[rd, "f"] \dlar["g"] &  \\
+     X_1(N) & &X_{G(N)} \isom \PP^1
+\end{tikzcd}
+     \Longrightarrow
+\begin{tikzcd}
+      &X_B^{(d)} \dlar["g^{(d)}"] & \\
+     X_1(N)^{(d)} & &X_{G(N)} \isom \PP^1\arrow[ul, "f^*"]
+\end{tikzcd}
+\]
+Let $f\colon X_{B}\rightarrow X_{G(N)} \isom \PP^1$ be the corresponding degree $d$ map of modular curves.
+\Cref{lem:map to Symd} yields a non-constant morphism $f^*\colon X_{G(N)} \to X_{B}^{(d)}$ such that $f^*(x)$ lies on a $\PP^1 \isom X_{G(N)}$. 
+Hence any point in the support of the divisor represented by $f^*(x)$ in $X_B$ is $\PP^1$-parametrized by~\Cref{lem:iso1}.
+Consider the morphism $g\colon X_B \to X_1(N)$ corresponding to $B \leq B_1(N)$.
+Let $x'\in X_B$ be such that $g(x')=y$ and $f(x')=x$.
+We want to show that $g(x')$ has the same degree as $x'$.
+Note that $\deg(x')$ is $d$ and of $\deg(y)=[\pm c(G(N)): \pm B]$ as $\pm B$ is the stabilizer of $y$.
+Hence it satisfies $\deg(g(x')) = \deg(x')$, so $y$ is $\PP^1$-parametrized by~\Cref{lem:iso2}.
+%\abbey{How do we know $f^{-1}(x)$ is irreducible, in order to apply \Cref{lem:iso1}?} \filip{Well because the mod $N$ image is equal to $G(N)$ (and not a subgroup).
+So to get the image to reduce to $B$, we need to go to an extension of the index of $B$ in $G(N)$.
+This is a more general result: if $G\geq H$ are congruence groups of level $N$ and $f:X_H\rightarrow X_G$ and $x$ corresponds to an elliptic curve whose mod $N$ image is $G$ over $\Q$, then the degree of $f^{-1}(x)$ is $\deg f$.} \abbey{Oh, right -- that makes sense.
+Thanks.}
+\end{proof}
+
+\begin{corollary}
+Let $E/\Q$ be an elliptic curve with adelic image $G$ of genus $0$ and $n$ a positive integer. %Then there does not exist an $n$ such that a point corresponding to $E$ on $X_1(n)$ is $\PP^1$-isolated.
+Then for all $n$ every $x \in X_1(n)$ with $j(x) = j(E)$ is $\PP^1$-parametrized.
+\end{corollary}
+\begin{proof}
+Since $G$ is by assumption of genus $0$, it follows that so is $G(n)$. The result then follows from Proposition~\ref{Genus0Prop}.
+\end{proof}
+
+\begin{comment}
+are of degree $d$.
+Let $x'\in f^{-1}(x) \subseteq X_{B}$ be a point corresponding to $E$, and let $g\colon X_{B}\rightarrow X_1(n)$ be the map induced by the inclusion $B_1(N) \supseteq B$.
+The point $x'$ lies on a $\PP^1$ inside $X_B^{(d)}$ and hence $g(x')$ lies on a $\PP^1$ inside $X_1(n)^{(d)}$.
+Since no Abelian variety has $\PP^1$ as a subvariety, $\Phi_d$ contracts this $\PP^1$ inside $X_1(n)^{(d)}$ to a single point; it follows that $g(x')$ is not $\PP^1$-isolated.
+
+We have the following commutative diagram:
+
+$$
+\xymatrix{
+& X_B \ar[r]^{g} \ar[d]^{f} & X_1(N) \ar[d]^{q} \\
+&X_{G(N)} \ar[r]^{h} & X_{G'},
+}
+$$
+where $G'$ is defined to be the subgroup of $\GL_2(\Z/N\Z)$ generated by the union of $B_1(N)$ and $G(N)$, and the maps $q:X_1(N) \rightarrow X_{G'}$ and $h:X_G(N) \rightarrow X_{G'}$ are induced by the inclusion of the corresponding subgroups.
+The curve $X_{G'}$ is obviously of genus $0$ as it is covered by $X_{G(N)}$ of genus 0.
+
+As $g(x')$ is of degree $d$ and $q(g(x'))=h(x)\in X_{G'}(\Q)$, it follows $\deg q\geq d$. Alternatively, the same conclusion follows from $\deg q=[\pm G':\pm B_1(N)]\geq [\pm G':\pm B]=d. $
+
+\filip{Work in progress.
+If we prove $\deg q=d$, we are done.
+There's a more general question here, which I think is interesting: given a morphism $f:X\rightarrow \PP^1$ over $\Q$, with genus of $X$ at least 2, is it possible that there's infinitely many points of degree $<d$ in $f^{-1}(\PP^1(\Q))$.
+For $d=2$, the answer is no, and I think this might be the case in general.
+If anyone knows of a reference (or proof) of this, let me know; this would complete the proof of this lemma.
+} \abbey{Seems like you'd want some sort of strong form of Hilbert's irreducibility for this?
+I hadn't thought of this before...
+I believe there are infinitely many $c\in\Q$ such that $f-c$ is irreducible, which gives infinitely many degree $d$ points.
+So you want to know whether there are only finitely many $c$ such that $f-c$ is reducible?
+It looks like in some cases something like this is true (e.g., ``Finiteness results for Hilbert's irreducibility theorem" by M\"{u}ller), but not in general.}
+\filip{Yes, this would be some strong form of Hilbert's irreducibility.
+Is there a single example, of an $X$ of genus $\geq 2$ and $f$, where $f$ does not factor as $f=f_1\circ f_2$  with $\deg f_i>1$ (otherwise there can be many counterexamples), where this is not true?}
+\end{comment}
+
+%\filip{I remember what the issue was: we construct maps $X_B\rightarrow X_{G(n)}$ and $f:X_B\rightarrow X_1(n)$, and show that the point associated to $E$ on $X_B$ is not $\PP^1$-isolated.
+But I don't know how to show that this would imply that the image of this point under $f$ is not $\PP^1$-isolated.
+}\\
+%\filip{This is I think a more general group theoretic problem: we have a subgroup $A$ of $G(n)$ of index $d$, i.e.
+$[G(n):A]=d$, where $A\leq B_1(N)$ (or some conjugate of $B_1(n)$).
+Then we ask what is the index of $B_1(N)$ in the group generated by $G(n)$ and $B_1(n)$.
+If the answer is again necessarily $d$ (or we can always choose a conjugate of $B_1(n)$) such that the index is $d$, then we are good.}
+
 \section{Validity of Main Algorithm}
@@
 
-In this section, we will prove results on the validity of our Main Algorithm as stated in Section \ref{sec:mainalg}.
-After recording preliminary results in Section \ref{sec:prelimresult}, we will give the proof in Section \ref{sec:proofvalidity}.
+In this section, we will prove results on the validity of our Main Algorithm as stated in Section~\ref{sec:mainalg}.
+After recording preliminary results in Section~\ref{sec:prelimresult}, we will give the proof in Section~\ref{sec:proofvalidity}.
 The section concludes with an additional example.
@@
 In the case where $C$ is a modular curve, this condition can be translated into one involving arithmetic properties of the corresponding elliptic curves.
-Though result stated below is formulated for more general elliptic curves in \cite{BELOV}, we record here the version for elliptic curves over $\Q$.
+Though result stated below is formulated for more general elliptic curves in~\cite{BELOV}, we record here the version for elliptic curves over $\Q$.
 
@@
 
-\abedit{Suppose $E/\Q$ is non-CM elliptic curve such that one of the following holds:
+Suppose $E/\Q$ is non-CM elliptic curve such that one of the following holds:
 \begin{itemize}
@@
     \item $N_E=p \leq 200{,}000{,}000$ for some prime number $p$.
-\end{itemize} Then running Algorithm 1 on $E$ results in the empty set, aside from the output for those $95$ $j$-invariants given in the Appendix.}
-Additionally, the only $j$-invariants corresponding to points of degree $d$ on $X_1(N)$ whose mod $N$ image is genus $>0$ are listed in Table~\ref{table:imagegt0}, along with the output of the algorithm and the genus of the mod $N$ image.
+\end{itemize} Then running Algorithm 1 on $E$ results in the empty set, aside from the $j$-invariants listed in Table~\ref{table:imagegt0}.
+The final step in the main algorithm filters out curves with mod $N$ genus $0$; we also list in the table the mod $N$ genus.
 \abbey{I'm so interested in this genus 5 curve with an exceptional non-CM rational point which gives rise to the degree 9 point on $X_1(28)$.
 Is there any explanation for the rational point on this genus 5 curve?
-We kind of understand why the other isolated $j$-invariants arise, but not this one.}
+We kind of understand why the other isolated $j$-invariants arise, but not this one.} \sachi{do you want to make some remark about this here / question?}
 	\begin{table}[h]
 	\begin{center}
-		\begin{tabularx}{242pt}{l l c} \toprule
-		$j$ & $<N, d>$ & genus  \\\midrule
-$-140625/8$ &  $\{ <21, 3>^2 \} $ & $1$\\
- $-162677523113838677$& $\{ <37, 18> \}$ & $4$\\
- $-882216989/131072$ & $\{ <17, 4>^2\}$ & $1$ \\
- $-9317$ & $\{ <37, 6>^3 \} $ & $4$\\
- $16778985534208729/81000$ & $\{ <24, 4>^2 \}$ & $1$\\
- $351/4$ & $\{ <28, 9>^2 \}$ & $5$\\ \bottomrule
+		\begin{tabularx}{277pt}{l l c} \toprule
+		$j$ & $\langle N, d \rangle$ & genus mod $N$  \\\midrule
+$-140625/8$ &  $\{ \langle 21, 3 \rangle^2 \} $ & $1$\\
+ $-162677523113838677$& $\{ \langle 37, 18 \rangle \}$ & $4$\\
+ $-882216989/131072$ & $\{ \langle 17, 4 \rangle^2\}$ & $1$ \\
+ $-9317$ & $\{ \langle 37, 6 \rangle^3 \} $ & $4$\\
+ $16778985534208729/81000$ & $\{ \langle 24, 4 \rangle^2 \}$ & $1$\\
+ $351/4$ & $\{ \langle 28, 9 \rangle^2 \}$ & $5$\\ \bottomrule
 		\end{tabularx}
-		\caption{Output of main algorithm with mod $N$ genus $>0$}\label{table:imagegt0}
+
+		\caption{Output of main algorithm}\label{table:imagegt0}
 	\end{center}
@@
 
-In this section we describe additional computations that prove that the only $\PP^1$-isolated points on $X_1(N)$ for a fixed $N$ correspond to the four $j$-invariants $j=-140625/8,-9317,351/4, -16267752311383867$, proving Theorem \ref{LMFDBoutputThm}.
+In this section we describe additional computations that prove that the only $\PP^1$-isolated points on $X_1(N)$ for a fixed $N$ correspond to the four $j$-invariants $j=-140625/8,-9317,351/4,$ and $ -16267752311383867$, proving Theorem \ref{LMFDBoutputThm}.
 \if{false}
@@
 $\overline{x}$ of $x$ modulo 3 is $\PP^1$-isolated, and hence it follows that $x$ is $\PP^1$-isolated.  %\abbey{I believe we mean that it \emph{is} $\PP^1$-isolated.} \filip{Yes, fixed.}
-\sachi{Do we need to prove this is isolated or was it already done in van Hoeij and Derickx?
+% \sachi{Do we need to prove this is isolated or was it already done in van Hoeij and Derickx?
 It seems asymmetric that this is the only isolated point we talk about, of the four.} \abbey{I don't think they proved (or, at least, published a proof) that it was $\PP^1$-isolated -- it's not sporadic, and it looks like they stopped looking for points on $X_1(37)$ after degree 17.
@@
 
-\subsubsection{Degree $4$ point on $X_1(17)$ corresponding to $j=-882216989/131072$}
-To show that this point is not isolated we compute the coordinates of \fedit{a} degree $4$ point $x$ corresponding to our curve on a model of $X_1(17)$.
-\abbey{Does this construction depend on which closed point of degree 4 we choose?
-There are 2.} \filip{I didn't check, but it probably shouldn't.
-I changed "the" to "a" in the previous sentence.} The point $x$ is defined over a cyclic quartic field.
+\subsubsection{Degree $4$ point on $X_1(17)$ corresponding to $j=-882216989/131072$ and degree $4$ point on $X_1(24)$ corresponding to $j=16778985534208729/81000$ }
+To show that these points are not isolated we compute the coordinates of a degree $4$ point $x$ corresponding to our curve on a model of $X_1(17)$ and $X_1(24)$.
+Such a point $x$ is defined over a cyclic quartic field.
 Let $\sigma_i$, for $i=1,\ldots, 4$ be the automorphisms of $K$ and $D=\sum_{i=1}^4\sigma_i(x)$.
-We compute $\ell(D)=2$, which implies that $x$ is not $\PP^1$-isolated.
-
-The fact that this point is not $\PP^1$-isolated also follows from the results of \cite[Proposition 6.7]{DerickxMazurKamienny}, where it is shown that there are no $\PP^1$-isolated quartic points on $X_1(17)$.
-
-\filip{I did not go into much details here, as I think more details would entail just writing a bunch of equations, and the code where all the computations are dove, will be supplied.}
-
-\subsubsection{Degree $4$ point on $X_1(24)$ corresponding to $j=16778985534208729/81000$}
-\sachi{can/should we combine this with the previous subsection?}
-To show that this point is not isolated we compute the coordinates of a degree $4$ point $x$ corresponding to our curve on a model of $X_1(24)$.
-The point $x$ is defined over a quartic field.
-Let $\sigma_i$, for $i=1,\ldots, 4$ be the automorphisms of $K$ and $D=\sum_{i=1}^4\sigma_i(x)$.
-\sachi{is this how you did this Filip?}
-We compute $\ell(D)=2$, which implies that $x$ is not $\PP^1$-isolated.
+In each case, we compute $\ell(D)=2$, which implies that $x$ is not $\PP^1$-isolated.
+
+The fact that the degree $4$ point on $X_1(17)$ is not $\PP^1$-isolated also follows from the results of \cite[Proposition 6.7]{DerickxMazurKamienny}, where it is shown that there are no $\PP^1$-isolated quartic points on $X_1(17)$.
+
+\section{Motivation for Conjecture \ref{conj}}\label{conj_motivation}
+Let $x\in X_1(N)$ be a $\PP^1$-isolated point with $j(x) \in \Q$.
+One expects that the square-free part of the conductor of any $E$ with $j(E) = j(x)$ will be very small.
+The reason for this is that any such isolated point will necessarily have small mod $p$ image for some $p$ dividing $N$.
+This in turn forces potentially good reduction on $E$ in all primes, except possibly for $p=2$; see~\cite[Corollary 4.4]{Mazur1978} for one example of this phenomenon.
+Indeed this happens for all the curves appearing in~\Cref{conj}; their conductors are either a square, or twice a square.
+\timo{For the last part: If $E$ has potentially good reduction at $p$, then $v_p(N) \neq 1$, hence $v_p(N) \in \{0,2\}$ if $p > 3$.
+So the problem must be in the part before, right?
+Could we explicitly state what would need to be proved and what is know in this direction?
+It's not necessary, but I find it very interesting.}
+
+Hence one might except to find most or all of the $\PP^1$-isolated points among elliptic curves with relatively small conductor (and hence in the LMFDB).
+This observation perhaps makes the computational evidence supporting \Cref{conj} more convincing.
+\timo{How far is this from a proof?} \dld{Very far.}
 
 \newpage
-\section*{Appendix}
-\label{appendix}
-
-Suppose $E/\Q$ is non-CM elliptic curve such that one of the following holds:
-\begin{itemize}
-    \item$N_E \leq 500{,}000$,
-    \item $N_E$ is only divisible by primes $p \leq 7$, or
-    \item $N_E=p \leq 200{,}000{,}000$ for some prime number $p$.
-\end{itemize}
-If the output of Algorithm 1 is non-empty, then $j(E)$ and the output appear in the list below.
-\scriptsize{
-\begin{align*}
-&-1/15:\{<32, 8>^2\}\\
-&-1139466686381936641/17587891077120:\{<32, 8>^2 \}\\
-&-13123858413236228917847770385659606286401/20767600023946451721766482684226058876:\{ <25, 10> \}\\
-&-1376562883316985524655287925404037121/1193272631368179777536:\{ <25, 5>^2 \}\\
-&-12757618324042173549858425461682176/1823806051450564693130128615083:\{ <25, 10> \}\\
-&-1415127831921321522248426938217281/3666855487972497940063476562500:\{ <32, 16>^2 \}\\
-&-140625/8:\{ <21, 3>^2 \}\\
-&-162677523113838677:\{ <37, 18> \}\\
-&-19328649688935739391016961/18446462598732840960:\{ <32, 16>^2 \}\\
-&-19465109/22:\{ <25, 10> \}\\
-&-18975420587737213095292649/255881160051786:\{<25, 10> \}\\
-&-225741686871429146260559062081/146211902909299839467520000:\{ <16, 2>^4 \}\\
-&-24680042791780949/369098752:\{ <25, 5>^2 \}\\
-&-2926956820564562516641/35459588343029760000:\{ <16, 2>^4 \}\\
-&-279328676638409/15200157696:\{ <25, 10> \}\\
-&-324503698618794407582644992737281/19342794667089993085747200:\{ <32, 8>^2 \}\\
-&-326573981641149886485204481/194520794324722008975:\{ <32, 8>^2 \}\\
-&-1638541430081273024/26265946892733:\{ <25, 10> \}\\
-&-353498371667659682101/113715890591105024:\{ <25, 10> \}\\
-&-3545733621855029067330337757367361/9094574488699436187744140625:\{ <32, 8>^2 \}\\
-&-3552277140342294754589991537894721/568432733416557312011718750:\{ <32, 16>^2 \}\\
-&-36703062611518813711084873444252734518401/397925291030084608863799302120300:\{ <32, 16>^2 \}\\
-&-4033422215926741/404:\{ <25, 10> \}\\
-&-4096/11:\{ <25, 5>^2 \}\\
-&-488162845931504468669161001/502:\{<25, 10> \}\\
-&-49019660417634625566551535616/52295500263431403:\{ <25, 5>^2 \}\\
-&-5107501047547200669121/186932676651373720080:\{ <32, 16>^2 \}\\
-&-52893159101157376/11:\{ <25, 10> \}\\
-&-56667352321/16711680:\{ <32, 16>^2 \}\\
-&-60627540058019895893705412918183361/10979320318525440000000000000000:\{ <16, 2>^4 \}\\
-&-60698457/40960:\{ <13, 2>^3 \}\\
-&-617298465273089376571121350031405627538001/165066:\{ <25, 10> \}\\
-&-70809965983288820433601/12128017136035299345:\{ <32, 8>^2 \}\\
-&-79184385609230668294081/759738277429254810:\{ <32, 16>^2 \}
-\end{align*}
-\begin{align*}
-&-882216989/131072: \{ <17, 4>^2\}\\
-&-460815199424/93:\{ <25, 10> \}\\
-&-9317:\{ <37, 6>^3 \}\\
-&1023887723039/928972800:\{ <16, 2>^4 \}\\
-&1139466686381936641/4080:\{ <32, 16>^2 \}\\
-&1144081181272479239133643526834383042983361/757051842880264964991840000:\{ <16, 2>^4 \}\\
-&115099000398621243971890559/78239096930039062500000000:\{ <16, 2>^4 \}\\
-&1259954716599707317761635279/782145653991396014555136:\{ <25, 5>^2 \}\\
-&128394017933147245660796166417119/493274390082338961058364010000:\{ <16, 2>^4 \}\\
-&13087181362848921857775657601/10116926999101440000:\{ <16, 2>^4 \}\\
-&13527956825588849127121/25701087819771000:\{ <24, 4>^2 \}\\
-&13619385906841/6048000:\{ <24, 4>^2 \}\\
-&13831657260716704136482954281709863361/17374959614531090376562500:\{ <32, 16>^2 \}\\
-&14551803469961881301880007324200000001/9536718750:\{ <32, 16>^2 \}\\
-&150336917982741967163778998756395764357350401/2077057800300:\{ <32, 16>^2 \}\\
-&1542085860252894509103949/6408896512:\{ <25, 10> \}\\
-&164711681450297281/8097103872000:\{ <24, 4>^2 \}\\
-&1663986362115498724215359/108912513076663261593600:\{ <32, 16>^2 \}\\
-&1663986362115498724215359/1169329859973065744640:\{ <32, 8>^2 \}\\
-&16778985534208729/81000:\{ <24, 4>^2 \}\\
-&178296503348692983836197044001/1342:\{ <25, 10> \}\\
-&1815401516599/8422162432:\{ <25, 10> \}\\
-&190705121216/71:\{ <25, 10> \}\\
-&19328649688935739391016961/1048320:\{ <32, 8>^2 \}\\
-&20250020461466473637047669654178374039681/501531896655344498219343780249600:\{ <32, 8>^2 \}\\
-&2119184381004022710620128465357091164489/26664780077208000:\{ <24, 4>^2 \}\\
-&2366200373628880151/2612420149248000:\{ <24, 4>^2 \}\\
-&236979190359324065638429091444161/447618521651352874905600:\{ <32, 16>^2 \}\\
-&291546910741641055583105024/382127162858793:\{ <25, 5>^2 \}\\
-&297106512928238351998640242081/3977028808593750000:\{ <16, 2>^4 \}\\
-&300872095888141441/22515023872:\{ <25, 5>^2 \}\\
-&324503698618794407582644992737281/268431360:\{ <32, 16>^2 \}\\
-&326573981641149886485204481/2690010:\{ <32, 16>^2 \}\\
-&3358085834636749/382:\{ <25, 10> \}\\
-&351/4:\{ <28, 9>^2 \}\\
-&3552277140342294754589991537894721/152581640625:\{ <32, 8>^2 \}\\
-&3634704740957616196378170215513091769/168224880645019054412841796875000:\{ <24, 4>^2 \}\\
-&364421318680576777174674911/450962301637624725000000:\{ <24, 4>^2 \}\\
-&36546944013036856482908761/14157275332658039712000:\{ <24, 4>^2 \}\\
-&378499465220294881/120530818800:\{ <16, 2>^4 \}\\
-&3922540634246430781376/71:\{ <25, 10> \}\\
-&44992447464066442427196092139811199/65124493101588450372219085693359375:\{ <32, 8>^2 \}\\
-&45960438227854760543785319/46920791622800342016000000:\{ <24, 4>^2 \}\\
-&5107501047547200669121/69461926257623040:\{ <32, 8>^2 \}\\
-&52300395461270777993673352489/30181158775846600704000000:\{ <24, 4>^2 \}\\
-&5345287166085790635663218704920974401/226978257155929261920000:\{ <16, 2>^4 \}
-\end{align*}
-\begin{align*}
-&5444502293860223539938743709179943321601/68719411200:\{ <32, 8>^2 \}\\
-&546397111960658404325211701139833360188801/209323126216982833463548776182030859375:\{<32, 8>^2 \}\\
-&5481351580593489628916345933548801/688740975:\{ <32, 8>^2 \}\\
-&56667352321/15:\{ <32, 8>^2 \}\\
-&56868272654707881404486749117441/10748658652923870314496000:\{ <24, 4>^2 \}\\
-&573007087724441463649920782881/67058993610000000000000000:\{ <16, 2>^4 \}\\
-&591720065532918583239955136329/116891407012939453125000000:\{ <24, 4>^2 \}\\
-&628284678908027418152998936285681/19884708881378173828125000:\{ <24, 4>^2 \}\\
-&6271688643866537984/1353:\{ <25, 10> \}\\
-&68699533290471196810719174361/268409217024000:\{ <24, 4>^2 \}\\
-&70809965983288820433601/2711034593280:\{ <32, 16>^2 \}\\
-&79184385609230668294081/42941745:\{ <32, 8>^2 \}\\
-&818546927584539194367471866449/14273634375000:\{ <24, 4>^2 \}\\
-&8827236347661221188886967161105287201/46539238473000000:\{ <24, 4>^2 \}\\
-&96653256179049031824319796125471784879999/341359290480134366830343600487545241600:\{ <32, 8>^2 \}
-\end{align*}}
-\vspace{20 mm}
+% \section*{Appendix}
+% \label{appendix}
+
+% Suppose $E/\Q$ is non-CM elliptic curve such that one of the following holds:
+% \begin{itemize}
+%     \item$N_E \leq 500{,}000$,
+%     \item $N_E$ is only divisible by primes $p \leq 7$, or
+%     \item $N_E=p \leq 200{,}000{,}000$ for some prime number $p$.
+% \end{itemize}
+% If the output of Algorithm 1 is non-empty, then $j(E)$ and the output appear in the list below.
+% \scriptsize{
+% \begin{align*}
+% &-1/15:\{<32, 8>^2\}\\
+% &-1139466686381936641/17587891077120:\{<32, 8>^2 \}\\
+% &-13123858413236228917847770385659606286401/20767600023946451721766482684226058876:\{ <25, 10> \}\\
+% &-1376562883316985524655287925404037121/1193272631368179777536:\{ <25, 5>^2 \}\\
+% &-12757618324042173549858425461682176/1823806051450564693130128615083:\{ <25, 10> \}\\
+% &-1415127831921321522248426938217281/3666855487972497940063476562500:\{ <32, 16>^2 \}\\
+% &-140625/8:\{ <21, 3>^2 \}\\
+% &-162677523113838677:\{ <37, 18> \}\\
+% &-19328649688935739391016961/18446462598732840960:\{ <32, 16>^2 \}\\
+% &-19465109/22:\{ <25, 10> \}\\
+% &-18975420587737213095292649/255881160051786:\{<25, 10> \}\\
+% &-225741686871429146260559062081/146211902909299839467520000:\{ <16, 2>^4 \}\\
+% &-24680042791780949/369098752:\{ <25, 5>^2 \}\\
+% &-2926956820564562516641/35459588343029760000:\{ <16, 2>^4 \}\\
+% &-279328676638409/15200157696:\{ <25, 10> \}\\
+% &-324503698618794407582644992737281/19342794667089993085747200:\{ <32, 8>^2 \}\\
+% &-326573981641149886485204481/194520794324722008975:\{ <32, 8>^2 \}\\
+% &-1638541430081273024/26265946892733:\{ <25, 10> \}\\
+% &-353498371667659682101/113715890591105024:\{ <25, 10> \}\\
+% &-3545733621855029067330337757367361/9094574488699436187744140625:\{ <32, 8>^2 \}\\
+% &-3552277140342294754589991537894721/568432733416557312011718750:\{ <32, 16>^2 \}\\
+% &-36703062611518813711084873444252734518401/397925291030084608863799302120300:\{ <32, 16>^2 \}\\
+% &-4033422215926741/404:\{ <25, 10> \}\\
+% &-4096/11:\{ <25, 5>^2 \}\\
+% &-488162845931504468669161001/502:\{<25, 10> \}\\
+% &-49019660417634625566551535616/52295500263431403:\{ <25, 5>^2 \}\\
+% &-5107501047547200669121/186932676651373720080:\{ <32, 16>^2 \}\\
+% &-52893159101157376/11:\{ <25, 10> \}\\
+% &-56667352321/16711680:\{ <32, 16>^2 \}\\
+% &-60627540058019895893705412918183361/10979320318525440000000000000000:\{ <16, 2>^4 \}\\
+% &-60698457/40960:\{ <13, 2>^3 \}\\
+% &-617298465273089376571121350031405627538001/165066:\{ <25, 10> \}\\
+% &-70809965983288820433601/12128017136035299345:\{ <32, 8>^2 \}\\
+% &-79184385609230668294081/759738277429254810:\{ <32, 16>^2 \}
+% \end{align*}
+% \begin{align*}
+% &-882216989/131072: \{ <17, 4>^2\}\\
+% &-460815199424/93:\{ <25, 10> \}\\
+% &-9317:\{ <37, 6>^3 \}\\
+% &1023887723039/928972800:\{ <16, 2>^4 \}\\
+% &1139466686381936641/4080:\{ <32, 16>^2 \}\\
+% &1144081181272479239133643526834383042983361/757051842880264964991840000:\{ <16, 2>^4 \}\\
+% &115099000398621243971890559/78239096930039062500000000:\{ <16, 2>^4 \}\\
+% &1259954716599707317761635279/782145653991396014555136:\{ <25, 5>^2 \}\\
+% &128394017933147245660796166417119/493274390082338961058364010000:\{ <16, 2>^4 \}\\
+% &13087181362848921857775657601/10116926999101440000:\{ <16, 2>^4 \}\\
+% &13527956825588849127121/25701087819771000:\{ <24, 4>^2 \}\\
+% &13619385906841/6048000:\{ <24, 4>^2 \}\\
+% &13831657260716704136482954281709863361/17374959614531090376562500:\{ <32, 16>^2 \}\\
+% &14551803469961881301880007324200000001/9536718750:\{ <32, 16>^2 \}\\
+% &150336917982741967163778998756395764357350401/2077057800300:\{ <32, 16>^2 \}\\
+% &1542085860252894509103949/6408896512:\{ <25, 10> \}\\
+% &164711681450297281/8097103872000:\{ <24, 4>^2 \}\\
+% &1663986362115498724215359/108912513076663261593600:\{ <32, 16>^2 \}\\
+% &1663986362115498724215359/1169329859973065744640:\{ <32, 8>^2 \}\\
+% &16778985534208729/81000:\{ <24, 4>^2 \}\\
+% &178296503348692983836197044001/1342:\{ <25, 10> \}\\
+% &1815401516599/8422162432:\{ <25, 10> \}\\
+% &190705121216/71:\{ <25, 10> \}\\
+% &19328649688935739391016961/1048320:\{ <32, 8>^2 \}\\
+% &20250020461466473637047669654178374039681/501531896655344498219343780249600:\{ <32, 8>^2 \}\\
+% &2119184381004022710620128465357091164489/26664780077208000:\{ <24, 4>^2 \}\\
+% &2366200373628880151/2612420149248000:\{ <24, 4>^2 \}\\
+% &236979190359324065638429091444161/447618521651352874905600:\{ <32, 16>^2 \}\\
+% &291546910741641055583105024/382127162858793:\{ <25, 5>^2 \}\\
+% &297106512928238351998640242081/3977028808593750000:\{ <16, 2>^4 \}\\
+% &300872095888141441/22515023872:\{ <25, 5>^2 \}\\
+% &324503698618794407582644992737281/268431360:\{ <32, 16>^2 \}\\
+% &326573981641149886485204481/2690010:\{ <32, 16>^2 \}\\
+% &3358085834636749/382:\{ <25, 10> \}\\
+% &351/4:\{ <28, 9>^2 \}\\
+% &3552277140342294754589991537894721/152581640625:\{ <32, 8>^2 \}\\
+% &3634704740957616196378170215513091769/168224880645019054412841796875000:\{ <24, 4>^2 \}\\
+% &364421318680576777174674911/450962301637624725000000:\{ <24, 4>^2 \}\\
+% &36546944013036856482908761/14157275332658039712000:\{ <24, 4>^2 \}\\
+% &378499465220294881/120530818800:\{ <16, 2>^4 \}\\
+% &3922540634246430781376/71:\{ <25, 10> \}\\
+% &44992447464066442427196092139811199/65124493101588450372219085693359375:\{ <32, 8>^2 \}\\
+% &45960438227854760543785319/46920791622800342016000000:\{ <24, 4>^2 \}\\
+% &5107501047547200669121/69461926257623040:\{ <32, 8>^2 \}\\
+% &52300395461270777993673352489/30181158775846600704000000:\{ <24, 4>^2 \}\\
+% &5345287166085790635663218704920974401/226978257155929261920000:\{ <16, 2>^4 \}
+% \end{align*}
+% \begin{align*}
+% &5444502293860223539938743709179943321601/68719411200:\{ <32, 8>^2 \}\\
+% &546397111960658404325211701139833360188801/209323126216982833463548776182030859375:\{<32, 8>^2 \}\\
+% &5481351580593489628916345933548801/688740975:\{ <32, 8>^2 \}\\
+% &56667352321/15:\{ <32, 8>^2 \}\\
+% &56868272654707881404486749117441/10748658652923870314496000:\{ <24, 4>^2 \}\\
+% &573007087724441463649920782881/67058993610000000000000000:\{ <16, 2>^4 \}\\
+% &591720065532918583239955136329/116891407012939453125000000:\{ <24, 4>^2 \}\\
+% &628284678908027418152998936285681/19884708881378173828125000:\{ <24, 4>^2 \}\\
+% &6271688643866537984/1353:\{ <25, 10> \}\\
+% &68699533290471196810719174361/268409217024000:\{ <24, 4>^2 \}\\
+% &70809965983288820433601/2711034593280:\{ <32, 16>^2 \}\\
+% &79184385609230668294081/42941745:\{ <32, 8>^2 \}\\
+% &818546927584539194367471866449/14273634375000:\{ <24, 4>^2 \}\\
+% &8827236347661221188886967161105287201/46539238473000000:\{ <24, 4>^2 \}\\
+% &96653256179049031824319796125471784879999/341359290480134366830343600487545241600:\{ <32, 8>^2 \}
+% \end{align*}}
+% \vspace{20 mm}
 \bibliographystyle{alpha}

### 2023-09-22 dolinesteinwatkins.m
Delete dolinesteinwatkins.m

@@ -1,26 +1,0 @@
-AttachSpec("../OpenImage/OpenImage.spec");                                                      
-path := OpenImageContext("../OpenImage/data-files");  
-Attach("../ell-adic-galois-images/groups/gl2.m");                                                             
-AttachSpec("isolated.spec");
-
-
-if assigned seq then
-    SetColumns(0);
-    SetAutoColumns(false);
-    n := #seq;
-    if n lt 4 then 
-    	for i in [1 .. 4-n] do
-    		seq := "0" cat seq;
-    	end for;
-    end if;
-    seq := "x" cat seq;
-    inputs := Split(Read(seq), "\n");
-    for i in [1..#inputs] do
-        jinv := inputs[i];
-        jinv := eval jinv;
-        jinv := Rationals()!jinv;
-        output := NotIsolated(jinv, path);
-        print Join([Sprint(elt) : elt in output], ":");
-	end for;
-    exit;
-end if;

### 2023-10-27 TeX/draft.tex
Updates from Overleaf

@@
 \usepackage{soul}%added for \st
-
+\usepackage{numprint} %for numbers
 % Enable UTF-8 encodings for input, to enter é instead of \'{e}.
@@
 
+% Longstanding AMS bug: https://tex.stackexchange.com/a/540046/32739
+\makeatletter
+\let\@wraptoccontribs\wraptoccontribs
+\makeatother
+
 \title{Towards a Classification of Isolated $j$-invariants}
 \input{author_info.tex}
+\contrib[with an appendix by]{Maarten Derickx and Mark van Hoeij}
+
 %\date{\today}
@@
 \begin{document}
+\maketitle
 
@@
 This builds on prior work of Zywina which gives a method for computing the image of the adelic Galois representation associated to $E$.
-Running this algorithm on all elliptic curves presently in the $L$-functions and Modular Forms Database yields strong evidence for the conjecture that $E$ gives rise to a $\PP^1$-isolated point on $X_1(N)$ if and only if $j(E)=-140625/8, -9317,$ $351/4$, or $-162677523113838677$.
+Running this algorithm on all elliptic curves presently in the $L$-functions and Modular Forms Database and the Stein--Watkins Database gives strong evidence for the conjecture that $E$ gives rise to an isolated point on $X_1(N)$ if and only if $j(E)=-140625/8, -9317,$ $351/4$, or $-162677523113838677$.
 \end{abstract}
-
-\maketitle
 
@@
 Starting with the image of the adelic Galois representation associated to $E/\Q$ with $j(E)=j$, as computed by Zywina \cite{ZywinaAlgorithm}, we apply various filters to determine whether there exists an isolated point $x \in X_1(N)$ with $j(x)=j$ for some $N$.
-% DLD TODO - words on what algorithm is
 
 \begin{algorithm}[h!]
+\renewcommand{\thealgocf}{} % We force this algorithm to be unnumbered so that
+                            % hyperrefs to Algorithm1 go the the correct algorithm.
 \caption{Main Algorithm} 
@@
 
-Running Algorithm \ref{alg:mainalgorithm} on all elliptic curves currently in the $L$-functions and Modular Forms Database (LMFDB) \cite{LMFDB} shows that all but 6 of the non-CM $j$-invariants in $\Q$ from the LMFDB
-are \emph{not} isolated.
-As noted above, three of these $6$ $j$-invariants are known to be isolated; in Section~\ref{sec:remainingfilters} we perform a case-by-case analysis to study the remaining $3$ candidates.
-This gives the following result.
+We ran Algorithm \ref{alg:mainalgorithm} on all elliptic curves currently in the $L$-functions and Modular Forms Database (LMFDB) \cite{LMFDB} and in the Stein--Watkins Database \cite{SteinWatkins}, which together contain over 36~million distinct non-CM $j$-invariants associated to elliptic curves over $\Q$ of conductor at most $10^8$.
+The output shows that all but 6 of the non-CM $j$-invariants included in these databases are \emph{not} isolated.
+As noted above, half of these remaining $j$-invariants are known to be isolated; in Section~\ref{sec:remainingfilters} we perform a case-by-case analysis on the remaining $3$ candidates.
+In particular, these findings imply the following result.
 
@@
 \begin{itemize}
-    \item $N_E \leq 500{,}000$,
+    \item $N_E \leq \numprint{500000}$,
     \item $N_E$ is only divisible by primes $p \leq 7$, or
-    \item $N_E=p \leq 300{,}000{,}000$ for some prime number $p$.
+    \item $N_E=p \leq \numprint{300000000}$ for some prime number $p$.
 \end{itemize}
@@
 Indeed, this $j$-invariant corresponds to one of two non-CM elliptic curves over $\Q$ with a rational cyclic 37-isogeny (see, e.g., \cite[Table 4]{LRAnn}), and any elliptic curve with a $\Q$-rational cyclic $N$-isogeny will give a point on $X_1(N)$ in degree at most $\varphi(N)/2$.
+\abedit{The appendix by} Maarten Derickx and Mark van Hoeij \abedit{shows} that this point is AV-isolated as well, allowing us to conclude that the 4 $j$-invariants identified in Theorem \ref{LMFDBoutputThm} are in fact \emph{isolated}.
 \end{remark}
-We conjecture that the four non-CM isolated $j$-invariants identified above are in fact the \emph{only} $j$-invariants in $\Q$ associated to non-CM elliptic curves which give rise to $\PP^1$-isolated points on $X_1(N)$.
+
+We conjecture that the four non-CM $j$-invariants identified above are the \emph{only} $j$-invariants in $\Q$ associated to non-CM elliptic curves which give rise to isolated points on $X_1(N)$.
 Such a result has already been established for points of odd degree: by \cite{OddDeg} we know that $j=-140625/8$ and $j=351/4$ are the only non-CM $j$-invariants in $\Q$ giving an isolated point of odd degree on $X_1(N)$, even as $N$ ranges over all positive integers.
@@
 \begin{conjecture}\label{conj}
-If $x\in X_1(N)$ is a $\PP^1$-isolated point with $j(x) \in \Q$, then $j(x)=-140625/8$, $-9317$, $351/4$, $-162677523113838677$, or one of the 13 CM $j$-invariants in $\Q$.
+If $x\in X_1(N)$ is an isolated point with $j(x) \in \Q$, then $j(x)=-140625/8$, $-9317$, $351/4$, $-162677523113838677$, or one of the 13 CM $j$-invariants in $\Q$.
 \end{conjecture}
 
-\noindent Since any CM elliptic curve is known to produce sporadic points on infinitely many modular curves of the form $X_1(N)$ by \cite[Theorem 7.1]{BELOV}, it follows conversely that every $j$-invariant in this set is $\PP^1$-isolated.
+\noindent Since any CM elliptic curve is known to produce sporadic points on infinitely many modular curves of the form $X_1(N)$ by \cite[Theorem 7.1]{BELOV}, it follows conversely that every $j$-invariant in this set is $\PP^1$-isolated (and in fact isolated --- \abedit{see the appendix}).
 
 \begin{remark}
-Let $x\in X_1(N)$ be a $\PP^1$-isolated point with $j(x) \in \Q$.
+Let $x\in X_1(N)$ be an isolated point with $j(x) \in \Q$.
 One expects that the square-free part of the conductor of any $E$ with $j(E) = j(x)$ will be very small.
@@
 
-Heuristically one might except to find most or all of the $\PP^1$-isolated points among elliptic curves with relatively small conductor (and hence in the LMFDB).
+Heuristically one might except to find most or all of the isolated points among elliptic curves with relatively small conductor (and hence in the LMFDB).
 One can also numerically observe that elliptic curves with small Galois representations are over-represented among curves with small conductor.
@@
 We address the validity of Algorithm \ref{alg:mainalgorithm} in Section \ref{sec:validity}.
-The output the main algorithm obtained after running it on all elliptic curves in the LMFDB and its final analysis is discussed in Section \ref{sec:remainingfilters}.
+The output the main algorithm obtained after running it on elliptic curves in the LMFDB and the Stein--Watkins database is discussed in Section \ref{sec:remainingfilters}, along with its final analysis.
 
@@
 \section*{Acknowledgments}
-We thank Pete Clark, Maarten Derickx, Jeremy Rouse, and David Zureick-Brown for helpful conversations.
+We thank Pete Clark, Maarten Derickx, Jeremy Rouse, Andrew Sutherland, and David Zureick-Brown for helpful conversations.
 We also thank David Zywina for making his code to compute Galois images available, and David Roe for further making Zywina's code and implementation more readily available for other mathematicians to use; this project would not have been possible without their work.
 This project began at the \emph{COmputations and their Uses in Number Theory} conference at CIRM in March 2023; we thank the organizers as well as CIRM for providing the opportunity for collaboration.
+
+AB was supported by NSF Grants DMS-2145270 and DMS-1928930.
+Part of the work was completed while this author was in residence at the Simons Laufer Mathematical Science Institute in Berkeley, CA, during the semester of Diophantine Geometry.
+TK was partially supported by the 2021 MSCA Postdoctoral Fellowship 01064790 -- ExplicitRatPoints.
+DLD was supported by the Simons Collaboration in Arithmetic Geometry, Number Theory, and Computation via the Simons Foundation grant 546235.
+TM was partially supported by the Commonwealth Cyber Initiative.
+FN is supported by the QuantiXLie Centre of Excellence, a
+  project co-financed by the Croatian Government and European Union
+  through the European Regional Development Fund - the Competitiveness
+  and Cohesion Operational Programme (Grant KK.01.1.1.01.0004). HS is supported by the DFG-grant STO 299/17-1.
 
@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:adelicgaloisgenus0}
 Let $E/\Q$ be an elliptic curve with adelic image $G$ of genus $0$ and $n$ a positive integer. %Then there does not exist an $n$ such that a point corresponding to $E$ on $X_1(n)$ is $\PP^1$-isolated.
@@
 \begin{proof}
-Since $G$ is by assumption of genus $0$, it follows that so is $G(n)$. The result then follows from Proposition~\ref{Genus0Prop}.
+Since $G$ is by assumption of genus $0$, it follows that so is $G(n)$. The result then follows from Theorem~\ref{Genus0Prop}.
 \end{proof}
@@
 
-\section{Remaining Filters}
+\section{Remaining Filters and Computational Results}
 \label{sec:remainingfilters}
@@
 \begin{itemize}
-    \item$N_E \leq 500{,}000$,
+    \item$N_E \leq \numprint{500000} $,
     \item $N_E$ is only divisible by primes $p \leq 7$, or
-    \item $N_E=p \leq 300{,}000{,}000$ for some prime number $p$.
-\end{itemize} Then running Algorithm 1 on $E$ results in the empty set, aside from the $j$-invariants listed in Table~\ref{table:imagegt0}.
+    \item $N_E=p \leq \numprint{300000000}$ for some prime number $p$.
+\end{itemize} Then running Algorithm \ref{alg:mainalgorithm} on $E$ results in the empty set, aside from the $j$-invariants listed in Table~\ref{table:imagegt0}; the output from elliptic curves in the Stein--Watkins database yields no additional $j$-invariants.
 The final step in the main algorithm filters out curves with mod $N$ genus $0$; we also list in the table the mod $N$ genus.
@@
 
+\subsection{Computations}
+We give some details on the implementation and runtime of the algorithm in this section.
+We ran Algorithm \ref{alg:mainalgorithm}
+on two databases of $j$-invariants of elliptic curves over $\Q$:
+\begin{itemize}
+\item The LMFDB \cite{LMFDB} contains all elliptic curves over $\Q$ of conductor up to \numprint{500000} and includes roughly $2$~million $j$-invariants.
+\item The Stein--Watkins database \cite{SteinWatkins} contains roughly $36$~million unique $j$-invariants of elliptic curves over $\Q$ of absolute discriminant at most $10^{12}$ that have conductor at most $10^8$ or prime conductor at most $10^{10}$.
+However, it has been filtered to include just one representative from each isogeny class and each class of quadratic twists.
+\end{itemize}
+All computations were run on a server with an AMD EPYC 7713 2GHz CPU and Magma V2.28-3 \cite{Magma}.
+For every elliptic curve $E/\Q$ in the LMFDB, the database contains the genus of $X_G$ where $G$ is the image of the adelic Galois represenation of $E$.
+Applying Corollary \ref{cor:adelicgaloisgenus0}, we filtered the roughly $2$~million $j$-invariants of non-CM elliptic curves $E/\Q$ in the LMFDB to a set of \numprint{30141}, such that the image of the adelic Galois representation of $E$ is greater than $0$.
+On this set, the computation took $2$~CPU hours and $1714$ MB of memory.
+The Stein--Watkins database contains \numprint{35788699} unique $j$-invariants of non-CM elliptic curves over $\Q$, with no information about the image of the adelic Galois representation.
+Running Algorithm \ref{alg:mainalgorithm} on this database took $442$ CPU hours.
+
+\section{Appendix: \abbey{Title Here}\\ by Maarten Derickx and Mark van Hoeij}
+
+        % READ Definition / Proposition 2.1 / Proposition 3.7 in https://arxiv.org/pdf/1707.00364v1.pdf
+        % The X in that definition will be X1(37)^{(18}) and the Y in that definition will be J1(37)/A
+        % where A is an abelian subvariety of J1(37). Now phi goes from X to Y.
+
+Let $X = X_1(37)$ and $D$ be the divisor for the degree 18 closed point in Section 9.0.1.
+Through the maps $X \rightarrow X_0(37) \rightarrow X_0(37)^+$, we can view the Jacobian of the latter, $A :=J_0(37)^+$,
+as a abelian subvariety of $J_1(37)$.
+The question of whether $D$ is % (positive rank)
+AV isolated is equivalent to $\Phi_d(D) + A$ not being contained in $W_{18}(X)$,
+where $W_d(X) := \Phi_d(X^{(d)})$ with $\Phi_d$ as in Section 2.1.
+
+\begin{lemma}
+Let $A$ be an abelian subvariety of ${\rm Jac}(X)$ and let
+$\pi: X^{(d)} \rightarrow J(X)/A$ be the composition of $\Phi_d$ with the quotient map.
+Let $D \in  X^{(d)}$ and suppose that $\Phi_d(D) + A \subseteq W_d(X)$,
+then $\pi$, restricted to the tangent space at $D$, is not injective.
+\end{lemma}
+
+\begin{proof} Assume that $\Phi_d$ is injective on the tangent space at $D$,
+otherwise there is nothing to prove as $\pi$ factors through $\Phi_d$.
+Then $\Phi_d$ induces an isomorphism between the tangent spaces of $X^{(d)}$ at $D$, and $W_d$ at $\Phi_d(D)$.
+The positive dimensional variety $\Phi_d(D) + A$ is contracted to a point under the quotient map
+$J(X) \rightarrow J(X)/A$, in particular the entire tangent space of  $\Phi_d(D) + A$ at $\Phi_d(D)$
+is sent to zero under the quotient map, and the result follows.
+\end{proof}
+
+\begin{corollary} If the corresponding map $\pi^* : {\rm Cot}_0 \,J(X)/A \rightarrow {\rm Cot}_D \,X^{(d)}$
+on cotangent spaces is surjective then there is no translate of $A$ contained in $W_d(X)$ passing through $\Phi_d(D)$.
+\end{corollary}
+
+\begin{proof} This is because a map on tangent spaces is injective if and only if the corresponding map
+on cotangent spaces is surjective.
+\end{proof}
+
+In other words,  if $\pi$ is a {\em formal immersion} \cite{Version1}
+        %
+        % Version1 = arxiv.org/pdf/1707.00364v1.pdf
+        % The definition is also in \cite[Definition 4.1]{DKKS2023}
+        % arxiv.org/pdf/1707.00364.pdf  or   https://msp.org/ant/2023/17-2/ant-v17-n2-p01-s.pdf
+        %
+        % However, Version 1  ( arxiv.org/pdf/1707.00364v1.pdf ) has more details!
+        %
+at $D$ then $D$ is AV-isolated.
+To prove that $\pi$ is a formal immersion at $D$, can use Proposition 3.7 in \cite{Version1}
+if we have a basis of the cotangent space of $A$ viewed as a subspace of $J(X)$.
+
+Write $D = y_1 + \cdots + y_{18}$ where the $y_i$ form the Galois orbit corresponding
+to the degree 18 closed point.
+These $y_i$ also form one orbit under the diamond operators (they map to the same point in $X_0(37)$).
+We order them in such a way that $y_i = \langle 2^i\rangle y_1$.
+Let $q_1$ be a uniformizer at $y_1$, and let $q_i := q_1 \circ \langle 2^{-i} \rangle$
+be the corresponding uniformizer at $y_i$. Note that since $A$ is inside $J_0(37)$
+we have $(\langle 2\rangle - 1)(A) = 0$, so $\langle2\rangle  - 1$ factors via $J(X)/A$.
+In particular all one-forms of the form $\langle 2^i\rangle (\langle 2\rangle  - 1) w$ inside ${\rm Cot}_0 \,J(X)$ come from ${\rm Cot}_0 \,J(X)/A$.
+
+Next we show that there is a one-form $w$ such that $a(w,q_1,1) = 1$ and $a(w,q_i,1)=0$ for all $i > 1$, with $a(\ldots)$ as
+in Proposition 3.7 in \cite{Version1}.
+By Riemann Roch, \[{\rm dim\,} H^0(O_X(y_1+ \ldots +y_{18})) - {\rm dim\,} H^0(\Omega^1(-y_1-\ldots-y_{18})) = 18 + 1 - 40\]
+and
+\[{\rm dim\,} H^0(O_X(y_2+ \ldots +y_{18})) - {\rm dim\,} H^0(\Omega^1(-y_2-\ldots-y_{18})) = 17 + 1 - 40.\] 
+Now ${\rm dim\,} H^0(O_X(y_1 + \ldots +y_{18}))  = 1$ (equivalent to the degree 18 point being $\PP^1$-isolated)
+and thus equal to ${\rm dim\,} H^0(O_X(y_2+\ldots+y_{18}))$. 
+Then by Riemann Roch, \[
+{\rm dim\,} H^0(\Omega^1(-y_2-\ldots-y_{18})) > {\rm dim\,} H^0(\Omega^1(-y_1-\ldots-y_{18})).\]
+So the wanted one-form $w$ can be found by picking an element of $H^0(\Omega^1(-y_2-\ldots-y_{18}))$
+that is not in $H^0(\Omega^1(-y_1-\ldots-y_{18}))$ and scaling it to make  $a(w,q_1,1) = 1$.
+
+Now let $w_i =  \langle 2^i\rangle(\langle2\rangle - 1)w$. These one-forms all come from ${\rm Cot}_0 \,J(X)/A$ as mentioned before.
+The matrix in Proposition 3.7 in \cite{Version1} now has the following form:
+
+\[
+\begin{pmatrix}
+1& -1& 0& 0& \ldots& 0 \\
+0& 1& -1& 0& \ldots& 0 \\
+0& 0& 1& -1& \ldots & 0 \\
+\vdots&  \vdots  & \vdots   &   \ddots &  \ddots & \vdots\\
+0& 0& 0& \ldots & 1 & -1
+\end{pmatrix}
+\]
+
+This matrix has rank 17, but for Proposition 3.7, we need rank 18.
+An additional one-form $w’$ with $a(w’,q_1,1) = \ldots = a(w’,q_{18},1) = 1$ would increase
+the rank to 18.
+We can take $w’$ to be the pullback of a one-form on $J_0(37)^-$ to $J(X)$. Indeed, $J_0(37)^-$ is a quotient of
+$J_0(37)/A$ and thus of $J(X)/A$. Such $w'$ is invariant under the diamond operators so $a(w’,q_1,1) = \ldots = a(w’,q_{18},1)$
+automatically holds. It remains to show that it does not vanish at $y_1$.  
+% Let $y$ be the image of $y_1$ in $J_0(37)^-$.
+Since $J_0(37)^-$ is an elliptic curve, $w’$ does not vanish anywhere,
+and in particular not at the image of $y_1$ in $J_0(37)^-$.
+The only possibility for $w’$ to vanish at $y_1$ is then for $X_1(37) \rightarrow J_0(37)^-$
+to be ramified at $y_1$, however, this is not the case since the map is only ramified at CM points, and $y_1$ does not have CM. 
+Indeed, $X_1(37) \rightarrow X_0(37)$ only ramifies at $j=0$ and $j=1728$,
+while $X_0(37) \rightarrow J_0(37)^-$ only ramifies at fixed points of the Atkin-Lehner involution, which have CM as well (by an order in $\mathbb Q(\sqrt{-37})$).
+
 \bibliographystyle{alpha}

### 2023-10-27 TeX/author_info.tex

@@
 \email{\url{bourdoam@wfu.edu}}
-\thanks{AB was supported by NSF Grants DMS-2145270 and DMS-1928930.
-Part of the work was completed while the author was in residence at the Simons Laufer Mathematical Science Institute in Berkeley, CA, during the semester of Diophantine Geometry.}
 
@@
 \urladdr{\url{https://www.timo-keller.de}}
-\thanks{%
-  TK was partially supported by the 2021 MSCA Postdoctoral Fellowship 01064790 -- ExplicitRatPoints.
-}
 
 \author[Klagsbrun]{Zev Klagsbrun}
-\address{Zev Klagsbrun, Center for Communications Research, San Diego, CA}
+\address{
+    Zev Klagsbrun,
+    Center for Communications Research - La Jolla, 
+    4320 Westerra Court,
+    San Diego, CA, 92121}
 \email{zdklags@ccr-lajolla.org}
@@
 \urladdr{\url{https://davidlowryduda.com}}
-\thanks{%
-  DLD was supported by the Simons Collaboration in Arithmetic Geometry, Number
-  Theory, and Computation via the Simons Foundation grant 546235.
-}
+
 \author[Morrison]{Travis Morrison}
@@
 \urladdr{\url{https://travismo.github.io/}}
-\thanks{TM was partially supported by the Commonwealth Cyber Initiative.}
 
@@
 \urladdr{\url{https://web.math.pmf.unizg.hr/~fnajman/}}
-\thanks{FN is supported by the QuantiXLie Centre of Excellence, a
-  project co-financed by the Croatian Government and European Union
-  through the European Regional Development Fund - the Competitiveness
-  and Cohesion Operational Programme (Grant KK.01.1.1.01.0004).}
 
@@
 \urladdr{\url{https://www.mathe2.uni-bayreuth.de/hishukla/}}
-\thanks{HS is supported by the DFG-grant STO 299/17-1}
